### 2018-07-03 PoA.tex
first commit

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[toc,page]{appendix}

\usepackage{epstopdf}
\usepackage{comment}
\usepackage[retainorgcmds]{IEEEtrantools}

\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

\def\balpha{\boldsymbol{\alpha}}
\def\bbeta{\boldsymbol{\beta}}
\def\bgamma{\boldsymbol{\gamma}}
\def\bmu{\boldsymbol{\mu}}
\def\bnu{\boldsymbol{\nu}}
\def\bmubar{\boldsymbol{\bar{\mu}}}
\def\bnubar{\boldsymbol{\bar{\nu}}}
\def\btheta{\boldsymbol{\theta}}

\newcommand\cA{\mathcal A}
\newcommand\cB{\mathcal B}
\newcommand\cC{\mathcal C}
\newcommand\cD{\mathcal D}
\newcommand\cE{\mathcal E}
\newcommand\cF{\mathcal F}
\newcommand\cG{\mathcal G}
\newcommand\cI{\mathcal I}
\newcommand\cL{\mathcal L}
\newcommand\cM{\mathcal M}
\newcommand\cP{\mathcal P}
\newcommand\cS{\mathcal S}
\newcommand\cU{\mathcal U}
\newcommand\cX{\mathcal X}
\newcommand\cY{\mathcal Y}

\newcommand\bF{\mathbf F}
\newcommand\bN{\mathbf N}
\newcommand\bX{\mathbf X}
\newcommand\bY{\mathbf Y}

\newcommand\bp{\mathbf p}

\newcommand\EE{\mathbb E}
\newcommand\FF{\mathbb F}
\newcommand\PP{\mathbb P}
\newcommand\NN{\mathbb N}
\newcommand\RR{\mathbb R}
\newcommand\TT{\mathbb T}
\newcommand\ZZ{\mathbb Z}

\title{Price of Anarchy for Mean Field Games}
\author{
Ren\'{e} Carmona\thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1716673 and ARO \#W911NF-17-1-0578} 
\and 
Christy V. Graves\thanks{Program in Applied and Computational Mathematics, Princeton University, Partially supported by NSF \#DMS-1515753 and NSF GRFP}
\and
Zongjun Tan \thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1515753} 
}

\begin{document}

\maketitle

\begin{abstract}
    The price of anarchy, originally introduced to quantify the inefficiency of selfish behavior in routing games, is extended to mean field games. The price of anarchy is defined as the ratio of a worst case social cost computed for a mean field game equilibrium to the optimal social cost as computed by a central planner. We illustrate properties of such a price of anarchy on linear quadratic extended mean field games, for which explicit computations are possible. Various asymptotic behaviors of the price of anarchy are proved for limiting behaviors of the coefficients in the model and numerics are presented.
\end{abstract}

\section{\textbf{Introduction}} \label{se:introduction}
The concept of the `price of anarchy' was introduced to quantify the inefficiency of selfish behavior in finite player games \cite{christodoulou2005price2}\cite{christodoulou2005price}\cite{koutsoupias1999worst}\cite{Roughgarden}\cite{roughgarden2002bad}\cite{zhu2010price}. In this report, we extend the notion of price of anarchy to mean field games (MFG). Mean field games were introduced by Lasry and Lions \cite{Lasry_Lions} and Caines and his collaborators \cite{Huang} to describe the limiting regime of large symmetric games when the number of players, $N$, tends to infinity. A mean field game equilibrium characterizes the analogue of a Nash equilibrium in the $N=\infty$ regime. Thus, as in the finite player case, it is possible that the mean field game equilibrium is inefficient. In fact, in the paper of Balandat and Tomlin \cite{balandat2013efficiency}, they present a numerical example that shows that mean field game equilibria are not efficient, in general. The suboptimality of a mean field game equilibrium is also illustrated numerically for a congestion model in a paper of Achdou and Lauri\`{e}re \cite{achdou2015system}. More recently Cardaliaguet and Rainer gave in \cite{pierre_poa} a partial differential equation based thorough analysis of the \emph{(in)efficiency} of the mean field game equilibria.

In this report, the goal is to define the price of anarchy in the context of mean field games, and to compute it for a class of linear quadratic mean field game models, which can be solved explicitly. In fact, we consider an even more general class of games by allowing for interaction between the players through their controls, in addition to interaction through their states. This is often referred in the literature as extended mean field game, or mean field game of control. We compare the social cost of a mean field game equilibrium to the cost incurred when the players execute a strategy computed centrally.

We consider a system of $N$ players whose private states are denoted at time $t$ by $X^1_t$, $X^2_t$, $\cdots$, $X^N_t$. To keep the presentations simple, we assume the state space is $\mathbb{R}$. We denote by $\mu^N_t$ the empirical distribution of the states, namely
\begin{equation*}
\mu^N_t=\frac1N\sum_{i=1}^N\delta_{X^i_t}.
\end{equation*}
We assume that these states evolve in continuous time under the influences of controls  $\alpha^1_t$, $\alpha^2_t$, $\cdots$ , $\alpha^N_t$ $\in \mathbb{A}$, where the set of admissible controls, $\mathbb{A}$, will be defined later. Let $\nu^N_{t}$ denote the empirical measure of the controls:
\begin{equation*}
\nu^N_t=\frac1N\sum_{i=1}^N\delta_{\alpha^i_t}.
\end{equation*}
We also assume that if and when interactions between these states and controls are present, they are of a mean field type, i.e. through $\mu^N_t$ and $\nu^N_t$. The time evolution of the state for player $i$ is given by the It\^{o} dynamics:
\begin{equation*}
    dX^i_t=b(t,X^i_t,\mu^N_t,\alpha^i_t,\nu^N_t)dt+\sigma dW_t.
\end{equation*}
We work over the interval $[0,T]$ limited by a finite time horizon $T \in \mathbb{R}^+$. We assume the drift function $b(t,x,\mu,\alpha,\nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A})  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs. For the sake of simplicity, we assume that the volatility, $\sigma$, is a positive constant.

\subsubsection*{\textbf{Cost Functionals}}
We assume that we are given two functions $f(t,x,\mu,\alpha, \nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \rightarrow \mathbb{R}$ and $g(x,\mu):\mathbb{R}\times \cP(\mathbb{R}) \rightarrow \mathbb{R}$ which we call running and terminal cost functions, respectively. We assume $f$ and $g$ are Lipschitz in each of it's arguments. The goal of player $i$ is to minimize its expected cost as given by:
\begin{equation*}
J^i(\balpha^1,\cdots,\balpha^N)=\EE\bigg[\int_0^Tf(t,X^i_t,\mu^N_{t},\alpha^i_t,\nu^N_{t})\,dt +g(X^i_T,\mu^{N}_{T})\bigg].
\end{equation*}

\subsubsection*{\textbf{Social Cost}}
We restrict ourselves to Markovian control strategies $\balpha=(\alpha_t)_{0\le t\le T}$ given by feedback functions in the form $\alpha_t=\phi(t,X_{t})$ and we let $\mathbb{A}$ denote the set of such controls. If the $N$ players use distributed Markovian control strategies of the form $\alpha^i_t=\phi(t,X^i_t)$, we define the cost (per player) to the system as the quantity $J^{(N)}_\phi$:
\begin{equation*}
J^{(N)}_\phi=\frac1N\sum_{i=1}^NJ^i(\balpha^1,\cdots,\balpha^N).
\end{equation*}
We shall compute this social cost in the limit $N\to\infty$ when all the players use the distributed control strategies given by the same feedback function $\phi$ identified by solving an optimization problem in the limit $N\to\infty$. We take the social cost to be the limit as $N\to\infty$ of $J^{(N)}_\phi$, namely
\begin{equation*}
\begin{split}
\lim_{N\to\infty}J^{(N)}_\phi
&=\lim_{N\to\infty}\frac1N\sum_{i=1}^NJ^i(\balpha^1,\cdots,\balpha^N)\\
&=\lim_{N\to\infty}\frac1N\sum_{i=1}^N\EE\bigg[\int_0^Tf(t,X^i_t,\mu^{N}_{t},\phi(t,X^i_t),\nu^{N}_{t})\,dt +g(X^i_T,\mu^{N}_{T})
\bigg],\\
&=\lim_{N\to\infty}\EE\bigg[\int_0^T<f(t,\,\cdot\,,\mu^{N}_{X_t},\phi(t,\,\cdot\,),\nu^{N}_{t}),\mu^N_{t}>\,dt +<g(\,\cdot\,,\mu^{N}_{X_T}),\mu^{N}_{T}>
\bigg],
\end{split}
\end{equation*}
if we use the notation $<\varphi,\rho>$ for the integral $\int \varphi(z)\rho(dz)$ of the function $\varphi$ with respect to the measure $\rho$. Now if we assume that in the limit $N\to\infty$ the empirical distributions $\mu^N_{t}$ converge toward a measure $\mu_t$, and thus $\nu^N_{t}=\frac1N\sum_{i=1}^N\delta_{\phi(t,X^i_t)}$ also converges toward a measure $\nu_t$, then the social cost of the feedback function $\phi$ becomes:
\begin{equation*}
SC(\phi)=\int_0^T<f(t,\,\cdot\,,\mu_t,\phi(t,\,\cdot\,),\nu_t),\mu_t>\,dt \;+\; <g(\,\cdot\,,\mu_T),\mu_T>
\end{equation*}
with the expectation, $\EE$, disappearing when the limiting flows $\bmu=(\mu_t)_{0\le t\le T}$ and $\bnu=(\nu_t)_{0\le t\le T}$ are deterministic.

We would like to evaluate $SC(\phi)$ in the $N=\infty$ regime directly, without having to construct the deterministic measure flows $\bmu$ and $\bnu$ as limits of the finite player empirical measures. To do this, we assume that propagation of chaos holds and that the states of the $N$ players become asymptotically independent in the limit as $N \rightarrow \infty$. We consider a representative agent whose state is given by $\boldsymbol{X^{\phi}}=(X^{\phi}_t)_{0 \leq t \leq T}$, the continuous time solution of the stochastic differential equation of McKean-Vlasov type:
\begin{equation}
    dX^{\phi}_t=b(t,X^{\phi}_t,\cL(X^{\phi}_t),\phi(t,X^{\phi}_t),\cL(\phi(t,X^{\phi}_t))dt+\sigma dW_t
\label{eq:X}
\end{equation}
controlled by $\phi$. Then we can identify $\bmu$ as the law of a representative agent using the feedback function $\phi$, i.e. $\mu_t=\cL(X^{\phi}_t)$, and similarly, we can identify $\bnu$ as the law of the control, such that $\nu_t=\cL(\phi(t,X^{\phi}_t))$. Thus, in the $N=\infty$ regime, we rewrite the social cost as
\begin{equation*}
SC(\phi)=\int_0^T<f(t,\,\cdot\,,\cL(X^{\phi}_t),\phi(t,\,\cdot\,),\cL(\phi(t,X^{\phi}_t))),\cL(X^{\phi}_t)>\,dt+<g(\,\cdot\,,\cL(X^{\phi}_T)),\cL(X^{\phi}_T)>
\end{equation*}
where $\boldsymbol{X^{\phi}}$ satisfies equation (\ref{eq:X}). For the remainder of the paper, we work in the $N=\infty$ regime. As mentioned earlier, $\phi$ should be identified by solving an optimal control problem. We consider two distinct problems:
\begin{itemize}\itemsep=-2pt
\item $\phi$ is a feedback function providing a mean field game equilibrium. We detail more precisely what is meant by $\phi$ providing a mean field game equilibrium in Section \ref{sub:MFG_formulation}.
\item $\phi$ is the feedback function minimizing the social cost $SC(\phi)$, without having to be a mean field game equilibrium, in which case we use the notation $SC^{MKV}$ for $SC(\phi)$. This is a control problem of McKean-Vlasov type, which is detailed more precisely in Section \ref{sub:MKV_formulation}.
\end{itemize}
The two problems are detailed more precisely in Sections \ref{sub:MFG_formulation} and \ref{sub:MKV_formulation}. In Section \ref{Price_Of_Anarchy}, we define the price of anarchy based on these two problem formulations. The class of linear quadratic models is explored in Section \ref{sec:PoA_LQ}, where we provide some theoretical results on the price of anarchy for this class of games, show numerical results, and detail a particular example of flocking. We conclude in Section \ref{sec:conclusion}.

\subsection{\textbf{Nash Equilibrium: Mean Field Game Formulation}}
\label{sub:MFG_formulation}
The goal of this subsection is to articulate what is meant by a feedback function providing a mean field game equilibrium. To begin, we define what we call the \textit{mean field environment}. By symmetry of the players, we suppose all of the players in the mean field use the same feedback function, $\phi$. Then the \textit{mean field environment} specified by $\phi$ is characterized by $\cL(X^{\phi}_t)_{0\le t\le T}$ and $\cL(\phi(t,X^{\phi}_t))_{0\le t\le T}$ where the dynamics of $(X^{\phi}_t)_{0\le t\le T}$ are given by equation (\ref{eq:X}). Since we search for a Nash equilibrium, we consider a representative agent who wishes to find their best response, $\phi'$, to the mean field environment specified by $\phi$, in which case their state is given by $\boldsymbol{X^{\phi',\phi}}=(X^{\phi',\phi}_t)_{0\le t\le T}$ solving the standard stochastic differential equation:
\begin{equation*}
    dX^{\phi',\phi}_t=b(t,X^{\phi',\phi}_t,\cL(X^{\phi}_t),\phi'(t,X^{\phi',\phi}_t),\cL(\phi(t,X^{\phi}_t))dt+\sigma dW_t.
\end{equation*}
Consider the function:
\begin{equation*}
    \cS(\phi',\phi)=\biggl[\int_0^T<f(t,\cdot,\cL(X^{\phi}_t),\phi'(t,\cdot),\cL(\phi(t,X^{\phi}_t)),\cL(X^{\phi',\phi}_t)> dt +<g(\cdot,\cL(X^{\phi}_T)),\cL(X^{\phi',\phi}_t)>\biggr].
\end{equation*}
The best response for the representative agent in the mean field environment specified by $\phi$ is the feedback function minimizing this cost, namely $\phi^*=\arg\inf_{\phi'}\cS(\phi',\phi)$. Assuming the minimizer is unique (which will be the case for the models we consider), this defines a mapping $\Phi:\phi \rightarrow \phi^*$. If there is a $\hat{\phi}$ such that $\Phi(\hat{\phi})=\hat{\phi}$, then the players are in a mean field game equilibrium.

Thus, the search for a feedback function providing a mean field game equilibrium can be summarized as the following set of two successive steps:
\begin{enumerate}
\item For each feedback function $\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}$, solve the optimal control problem
\begin{equation*}
    \phi^*=\arg \inf_{\phi'}\cS(\phi',\phi).
\end{equation*}
Define the mapping $\Phi:\phi \rightarrow \phi^*$.
\item Find a fixed point $\hat{\phi}$ of $\Phi$ such that $\Phi(\hat{\phi})=\hat{\phi}$.
\end{enumerate}

When these two steps can be taken successfully, we say that $\hat{\phi}$ provides a mean field game equilibrium. Note that $\boldsymbol{X^{\hat{\phi},\hat{\phi}}}=\boldsymbol{X^{\hat{\phi}}}$ and therefore $\cS(\hat{\phi},\hat{\phi})=SC(\hat{\phi})$ gives the social cost for the mean field game equilibrium provided by $\hat{\phi}$. Notice that there could possibly be many feedback functions providing a mean field game equilibrium. Let $\mathcal{N}$ denote the set of all such feedback functions providing mean field game equilibria, as detailed above, i.e.
\begin{equation*}
    \mathcal{N}=\{\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}: \Phi(\phi)=\phi \}.
\end{equation*}

\subsection{\textbf{Centralized Control: Optimal Control of McKean-Vlasov Type}}\label{sub:MKV_formulation}
The goal of this subsection is to articulate how to compute the cost associated with the control problem of McKean-Vlasov type, $SC^{MKV}$. The central planner considers the following control problem:
\begin{equation*}
\begin{split}
   \hat{\phi}&=\arg \inf_{\phi}SC(\phi) \\
   &=\arg \inf_{\phi}\left[\int_0^T<f(t,\,\cdot\,,\cL(X^{\phi}_t),\phi(t,\,\cdot\,),\cL(\phi(t,X^{\phi}_t))),\cL(X^{\phi}_t)>\,dt \;+\; <g(\,\cdot\,,\cL(X^{\phi}_T)),\cL(X^{\phi}_T)>\right].
\end{split}
\end{equation*}
Thus, the cost of the solution to the optimal control problem of McKean-Vlasov is given by
\begin{equation*}
    SC^{MKV}=SC(\hat{\phi}).
\end{equation*}
\begin{remark}
We are not concerned with uniqueness for the control of McKean-Vlasov type problem, because $SC^{MKV}=SC(\phi_1)=SC(\phi_2)$ is still well defined even if there are two different optimal feedback functions $\phi_1$ and $\phi_2$ minimizing $SC(\phi)$.
\end{remark}

\subsection{\textbf{Price of Anarchy}}\label{Price_Of_Anarchy}
We have described two approaches to compute the optimal feedback function $\phi$. In the mean field game formulation, we require $\phi \in \mathcal{N}$, where $\mathcal{N}$ denotes the set of feedback functions providing mean field game equilibria. In the optimal control of McKean-Vlasov type formulation, the optimal control to be adopted by all players is computed by a central planner, who optimizes the social cost function $SC(\phi)$ directly. Thus, we necessarily have:
\begin{equation*}
    SC^{MKV} \leq SC(\phi),\ \forall \phi \in \mathcal{N}.
\end{equation*}
In other words, there is a `price of anarchy' associated with allowing players to choose their controls selfishly. We thus define the price of anarchy (denoted $PoA$) as the ratio between the worst case cost for a mean field game equilibrium and the optimal cost computed by a central planner:
\begin{equation*}
    PoA=\frac{\sup_{\phi \in \mathcal{N}}SC(\phi)}{SC^{MKV}}.
\end{equation*}

\section{\textbf{Price of Anarchy for Linear Quadratic Extended Mean Field Games}}\label{sec:PoA_LQ}
The class of linear quadratic extended mean field games is a class of problems for which explicit solutions can be computed analytically, and thus, we can compute the price of anarchy explicitly. To the best of our knowledge, the case of linear quadratic extended mean field games has not been explored in the literature, as well as computing the price of anarchy for this class of games.

To begin, we need to describe in more detail the two problems that will be used to compute the price of anarchy: the linear quadratic extended mean field game, and the linear quadratic control problem of McKean-Vlasov type with dependence on the law of the control. To specify the problems, we only need to specify the drift and cost functions, $b$, $f$, and $g$ introduced in Section \ref{se:introduction}. For the linear quadratic models, we take the drift to be linear:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=b_1(t)x+\bar{b}_1(t) \bar{\mu}+b_2(t) \alpha+\bar{b}_2(t) \bar{\nu},
\end{equation*}
where $\bar{\mu}$ denotes the mean of the measure $\mu$, namely, $\bar{\mu}=\int_{\mathbb{R}}xd\mu(x)$, and similarly for $\bar{\nu}$. We take the running and terminal costs to be quadratic:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right), \\
    g(x,\mu)&=\frac{1}{2}\left(q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right).
\end{split}
\end{equation*}
\begin{remark}
If $\bar{b}_2(t)\equiv0$ and $\bar{r}(t)\equiv0$, then we have the standard mean field game or control problem of McKean-Vlasov type. (See Theorem \ref{th:exist_uniq} for assumptions that provide existence and uniqueness.)
\end{remark}

\subsection{\textbf{Linear Quadratic Extended Mean Field Games}}\label{sec:EMFG}
To solve the linear quadratic extended mean field game (LQEMFG), we begin by considering the reduced Hamiltonian for this problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y \\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right),
\end{split}
\end{equation*}
and whenever the flows $\bmubar=(\bar{\mu}_t)_{0\leq t\leq T}$ and $\bnubar=(\bar{\nu}_t)_{0\leq t\leq T}$ are fixed, we consider for each control process $\balpha=(\alpha_t)_{0\leq t\leq T}$ the adjoint equation:

\begin{equation*}
\begin{split}
    dY_t&=- \partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T)).
\end{split}
\end{equation*}
A sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. According to the Pontryagin stochastic maximum principle, we introduce the function:
\begin{equation*}
    \hat{\alpha}(t,x,\bar{\mu},\bar{\nu},y)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)y}{r(t)+\bar{r}(t)},
\end{equation*}
and use the control $\hat{\alpha}_t=\hat{\alpha}(t,x,\bar{\mu},\bar{\nu},Y_t)$. When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$. By taking the expectation, we find:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    c^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))}.
\end{equation*}
Thus, necessarily we must have:
\begin{equation*}
    \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t)
\end{equation*}
with:
\begin{equation*}
    a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)},
\end{equation*}
and:
\begin{equation*}
    b^{MFG}(t)=-\frac{\bar{r}(t)\bar{s}(t)b_2(t)}{(r(t)+\bar{r}(t))(r(t)+\bar{r}(t)(1-\bar{s}(t)))}.
\end{equation*}
So the solution of the mean field game equilibrium problem is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t&=\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMFG}
\end{equation}
with initial condition $X_0=\xi$, a random variable with finite mean and variance, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T-\bar{q}_Ts_T\mathbb{E}X_T$.

This is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$  denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem. Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
\end{equation*}
Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
\begin{equation*}
\begin{split}
    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
    &+(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
\end{equation*}

\subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
To solve the linear quadratic optimal control problem of McKean Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
\begin{equation*}
\begin{split}
    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right).
\end{split}
\end{equation*}
Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality. A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}. This sufficient condition is the following:
$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
\begin{equation*}
    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t)(X_t,\hat{\alpha}_t) \right]=0,
\end{equation*}
where the adjoint equation is given by:
\begin{equation*}
\begin{split}
    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\mu}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t)(X_t,\alpha_t) \right] \right]dt+Z_tdW_t \\
    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
\end{split}
\end{equation*}
where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.

In the present LQ case, the sufficient condition can be used to solve for:
\begin{equation*}
    \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
and:
\begin{equation*}
    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
\end{split}
\end{equation*}
So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
\begin{equation}
\begin{split}
        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
\end{split}
\label{eq:FBSDE_EMKV}
\end{equation}
with initial condition $X_0=\xi$, and terminal condition $Y_T=(q_T+\bar{q}_T)X_T+s_T\bar{q}_T(s_T-2)\mathbb{E}X_T$.

As in the previous section, this is a linear FBSDE of McKean-Vlasov type, which can be solved explicitly under mild assumptions (or at least in the case of time-independent coefficients which we will consider later. See Appendix \ref{appendix_solving_fbsdes}). Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$  denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem. Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
\begin{equation*}
    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
\end{equation*}
Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
\begin{equation*}
\begin{split}
    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
    &+\int_0^T(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
\end{split}
\end{equation*}
where we have used the fact that:
\begin{equation*}
    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
\end{equation*}
and:
\begin{equation*}
    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
\end{equation*}

\subsection{\textbf{Theoretical Results}}
For the remainder of the paper, we assume the coefficients are independent of time and nonnegative:
\begin{equation*}
    (b_1(t), \bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10}
\end{equation*}
and therefore,
\begin{equation*}
\begin{split}
    (a^{MFG}(t),b^{MFG}(t),c^{MFG}(t))&=(a^{MFG},b^{MFG},c^{MFG}) \\
    (a^{MKV}(t) b^{MKV}(t),c^{MKV}(t))&=(a^{MKV},b^{MKV},c^{MKV}).
\end{split}
\end{equation*}

\begin{theorem} \label{th:exist_uniq}
Assume the following:
\begin{equation}
\begin{array}{rclcrclcrcl}
    b_2 &>& 0 & & b_2 + \bar{b}_2 &>& 0 & & \\
    r+\bar{r} &>&0 &&  r+\bar{r}(1-\bar{s}) &>&0 & & r+\bar{r}(1-\bar{s})^2 &>& 0 \\
    q+\bar{q} &>& 0 && q + \bar{q}(1-s) &>& 0 & & q+ \bar{q}(1-s)^2 &>& 0 \\
    q_T + \bar{q}_T &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T) &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T)^2 &\geq& 0
\end{array}
\label{eq:assumptions}
\end{equation}
then there exists a unique solution to the LQEMFG problem, and there exists a unique solution to the LQEMKV problem. And therefore, $PoA=\frac{SC^{MFG}}{SC^{MKV}}$ where $SC^{MFG}:=SC(\phi)$ for $\phi$ given by the explicit solution constructed in Appendix \ref{appendix_solving_fbsdes}.
\end{theorem}

\begin{remark}
    Note that existence in Theorem \ref{th:exist_uniq} follows from the explicit construction in Appendix \ref{appendix_solving_fbsdes}, because the above conditions provide existence to the solutions of the Riccati equations. Uniqueness comes from the connection between LQEMFG or LQEMKV and deterministic LQ optimal control. (See Section 3.5.1 in \cite{Carmona_book}).
\end{remark}

To compute the price of anarchy, it is useful to make the following observations:
\begin{equation*}
\begin{split}
    a^{MFG}&=a^{MKV}=:a \\
    \eta_t^{MFG}&=\eta_t^{MKV}=:\eta_t \\
    v_t^{MFG}&=v_t^{MKV}=:v_t
\end{split}
\end{equation*}

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left(s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right)\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}\left[(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2\right]&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), the result is clear.
\end{proof}

\begin{corollary}
Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, and $s_T\bar{q}_T(s_T-1)=0$ and at least one of the following holds: $b_2=\bar{b}_2=0$ or $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$
then $PoA=1$.
\label{corollary_1}
\end{corollary}

\begin{remark}
The only result similar to Proposition \ref{eq:lq_prop} that we are aware of is Remark 6.1 in \cite{nourian2013nash}.
\end{remark}

Using the above observations, we can rewrite:
\begin{equation}
\begin{split}
    SC^{MFG}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MFG})^2+\frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt\\
    &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MFG}\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt,
\end{split}
\label{eq:SC_MFG_1}
\end{equation}
and:
\begin{equation}
\begin{split}
    SC^{MKV}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MKV})^2+ \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt \\
    &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MKV}\bar{\eta}_t^{MKV})^2\right)](\bar{x}_t^{MKV})^2dt.
\end{split}
\label{eq:SC_MKV_1}
\end{equation}

In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems. First, we consider the last integral, where we drop the superscripts ${MFG}$ and ${MKV}$ to address both problems simultaneously. By using the Riccati equation associated with $\bar{\eta}_t$ and the equation $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}), we notice that
\begin{equation*}
\begin{split}
	&\int_0^T \bar{\eta}_t^2 \bar{x}_t^2 dt\\
	=& - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}_t \bar{x}_t^2 dt -  \int_0^T ( (b_1 + \bar{b}_1 - b^y - b^{\bar{y}}) \bar{\eta}_t - (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right]\\
	= & - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \bar{\eta}_T\bar{x}_T^2-\bar{\eta}_0\bar{x}_0^2-2\int_0^T\bar{\eta}_t\bar{x}_t\dot{\bar{x}}_t dt -  \int_0^T ( (b_1 + \bar{b}_1 - b^y - b^{\bar{y}}) \bar{\eta}_t - (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right] \\
	= & 2 \int_0^T \bar{\eta}_t^2 \bar{x}_t^2  - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \bar{\eta}_T \bar{x}_T^2 - \bar{\eta}_0 \bar{x}_0^2 - \int_0^T  ((b_1 + \bar{b}_1 + b^y + b^{\bar{y}} ) \bar{\eta}_t + (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right],
\end{split}
\end{equation*}
where we applied integration by parts for the second equality. Thus, if we denote
\begin{equation*}
	\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}
\end{equation*}
the equations (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) can be rewritten as
\begin{equation}
\begin{split}
	SC^{MFG} = & h_{var}(t) +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
	& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - \bar{\eta}^{MFG}_T (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
	SC^{MKV} = & h_{var}(t) + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2,
\end{split}
\label{eq:SC_MFG_MKV_2}
\end{equation}
where $ h_{var}(t): = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T  $.

Let's denote the (weighted) difference between the solutions of the Riccati equations associated with $\bar{\eta}_t^{MFG}$ and $\bar{\eta}_t^{MKV}$ by:
\begin{equation}
	\Delta \bar{\eta}_t = \lambda \bar{\eta}_t^{MFG} - \bar{\eta}_t^{MKV} .
\label{eq:delta_eta}
\end{equation}

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the associated Riccati equations are well defined under assumption (\ref{eq:assumptions}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients 
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from the two equations in (\ref{eq:SC_MFG_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 \bar{x}_0^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t)\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt
		\end{split}
	\end{equation*}
	where we use the relationship $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}) for the fourth equality.

\end{proof}

\begin{remark}
	We can see directly from Proposition \ref{prop:diff_SC} that the social cost in the LQEMFG problem is larger than (or possibly equal to) the social cost in the LQEMKV problem. This result is consistent with the definition of the price of anarchy in Section \ref{Price_Of_Anarchy}.
\end{remark}

Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by 
\begin{equation}
PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} \bar{x}_0^2}.
\label{eq:PoA_LQ}
\end{equation}\\

\begin{corollary}
    Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then $PoA=1$.
\end{corollary}
\begin{proof}
    By the explicit equation for $\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}), $\bar{x}_0=0$ implies $\bar{x}_t=0,\ \forall t \in [0,T]$. Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$. From the explicit formula for the variance, $h_{var}(t)>0$ and therefore by equation (\ref{eq:SC_MFG_MKV_2}), $SC^{MKV}>0$. Therefore, $PoA=1$.
\end{proof}

We study in the following the variation of $PoA$ by letting one of the coefficients tends to $0$ or to $\infty$. It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
    \begin{equation}
		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
		\label{eq:riccati_ut}
	\end{equation}	
	\begin{equation}
	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
	\label{eq:riccati_wt}
	\end{equation}
	\begin{equation}
	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
	\label{eq:riccati_etat}
	\end{equation}
	where
	\begin{IEEEeqnarray*}{rClcrClcrCl}
		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
		A^\eta &=& - b_1 \nonumber \\
		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
		C^\eta &=& q + \bar{q} \nonumber \\
		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
		D^\eta &=& q_T + \bar{q}_T 
	\end{IEEEeqnarray*}
If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
\begin{equation}
		u_t= \frac{-(C^u+D^u \delta^+_u) + (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(\delta^-_u - D^u B^u) - (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
	\label{eq:riccati_ut_sol}
\end{equation}
where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.

\begin{corollary}
    Assuming (\ref{eq:assumptions}), if $\bar{b}_1=0$ and $\lambda=1$, then $PoA=1$.
\end{corollary}
\begin{proof}
    Under these assumptions, $(A^u,C^u,D^u)=(A^w,C^w,D^w)$, and thus $(u_t)_{0\leq t\leq T}=(w_t)_{0\leq t\leq T}$. Thus, $\Delta \bar{\eta}_t=0,\ \forall t \in [0,T]$. By Proposition \ref{prop:diff_SC}, $\Delta SC=0$. It can be shown that $w_0\geq0$. Since $v_t>0$ for $t>0$, clearly $SC^{MKV}>0$. Therefore, $PoA=1$.
\end{proof}

\begin{proposition}
	Assuming (\ref{eq:assumptions}),
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad and \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions for the scalar Riccati equations associated with $u_t$, $w_t$ and $\eta_t$.

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}). The limiting solution $u_t^{\infty,r}$ is given by:
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u}\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t)
	\end{split}
	\end{equation*}
	which is bounded for $t \in [0,T]$.
	Similarly, we have the bounded limiting solutions over $[0,T]$:
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
	Moreover, since $\bar{x}_t^{MFG} = \bar{x}_0 \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \bar{x}_0 e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
	$$
	which are also bounded over $t\in[0,T]$.
	Hence, by the bounded convergence theorem we have
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $\lim_{r \to \infty}v_t >0$ for $t>0$ and therefore,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
	\end{equation*}
	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.

	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we can have $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

\end{proof}

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 \neq 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

\begin{proof}
    First, we consider $b_2 \to 0$. We assume here $\bar{b}_2 \neq 0$. Otherwise, if $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. 
    For $\bar{b}_2 \neq 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$

	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u = -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u = 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
	This implies that $\bar{x}_t^{MFG} \to \bar{x}_0 \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.

	Since $B^{0,b_2} \neq0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$. Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t)
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the limiting variance function $ v_t \to  v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for $t>0$ and $v^{0,b_2}_t$ is bounded.
	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	    \lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
	    \lim_{b_2 \to 0} \Delta SC &>0, \\
	    \lim_{b_2 \to 0} \Delta SC &< \infty ,
	\end{split}
	\end{equation*}
	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MFG_MKV_2}), $ \lim_{b_2\to 0} SC^{MKV} >0 $.
	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$

	Now, we consider the case when $b_2 \to \infty$. We have $\displaystyle \lambda \to \lambda^{\infty,b_2}:= \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and
	$$ B \to \infty,\ B^{\eta} \to \infty,\ C^u \to C^{\infty,b_2}_u := \lambda^{\infty,b_2}(q+ \bar{q}(1-s)),\ D^u \to D^{\infty,b_2}_u := \lambda^{\infty,b_2}(q_T + \bar{q}_T(1-s_T)).$$
	Since 
	$ \frac{\delta^\pm_u}{b_2 + \bar{b}_2} \xrightarrow[b_2 \to \infty]{} \pm \sqrt{\frac{ C_u^{\infty,b_2}}{r + \bar{r}(1-\bar{s})^2}}$
	and  $e^{- (\delta^+_u - \delta^-_u)(T-t)} \to 0$, for $t \in [0,T)$, with equation (\ref{eq:riccati_ut_sol}) we have for $t \in [0,T)$:
	$$ (b_2 + \bar{b}_2) u_t = \frac{- \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u . \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u . \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
	{ \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C_u^{\infty,b_2}}.
	$$
	Similarly, we have $(b_2+\bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$ and $b_2 \eta_t \to \sqrt{(r + \bar{r}) C^\eta}$ for $t \in [0,T)$.

	The next step is to look at the order of magnitude in terms of $b_2$ for the mean $\bar{x}_t^{MFG}$ and the variance $v_t$.
	For large $b_2$ and $t \in [0,T)$, we have:
	$$ B\cdot u_t = \frac{b_2 + \bar{b}_2}{r+\bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)u_t \sim \sqrt{\frac{q+ \bar{q}(1-s)}{r+ \bar{r}(1-\bar{s})} } (b_2 +\bar{b}_2) = \kappa_u (b_2+ \bar{b}_2). $$ Thus, we have the approximation:
	$$ \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds}\sim \bar{x}_0 e^{ (b_1 + \bar{b}_1 - \kappa_u (b_2+ \bar{b}_2) ) t},\qquad b_2 \to \infty.$$
	Similarly, we have for large $b_2$ and $t \in [0,T)$:
	$$B^{\eta} \cdot \eta_t = \frac{b_2}{r+ \bar{r}} b_2 \eta_t \sim \sqrt{\frac{q + \bar{q}}{r + \bar{r}} } b_2 = \kappa_v b_2,$$
	and:
	\begin{equation*}
		\begin{split}
		v_t &= Var(\xi) e^{2\int_0^t (b_1 - B^{\eta} \eta_u) du} + \sigma^2 \int_0^t e^{2 \int_s^t (b_1 - B^{\eta} \eta_u) du} ds\\
		& \sim Var(\xi) e^{(2b_1 - 2\kappa_v b_2)t} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{(2b_1 - 2\kappa_v b_2)t} - 1\right).
		\end{split}
	\end{equation*}
	Hence, using Proposition \ref{prop:diff_SC}, for large $b_2$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		\Delta SC &\sim & \frac{1}{2} (\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \int_0^T (\bar{x}_t^{MFG} )^2 dt \\
			&=& \frac{(\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \cdot \bar{x}_0^2 }{2 (2b_1 +2\bar{b}_1 - 2 \kappa_u (b_2 + \bar{b}_2) )} \left(  e^{(2b_1 + 2\bar{b}_1 - 2\kappa_u (b_2+ \bar{b}_2) ) T} - 1\right)\\
			&\sim & \frac{\zeta_1 }{b_2 } e^{- 2 \kappa_u T \cdot b_2 }  + \frac{\zeta_2}{ b_2},
	\end{IEEEeqnarray*}
	and using equation (\ref{eq:SC_MFG_MKV_2}), we deduce:
	\begin{IEEEeqnarray*}{rCl}
		SC^{MKV} &\sim & (q + \bar{q} )  \int_0^T v_t dt + \frac{1}{2}(q_T + \bar{q}_T)v_T + \frac{1}{2}w_0 \bar{x}_0^2\\
		&\sim& (q + \bar{q}) \left[ \left(\frac{Var(\xi)}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2\kappa_v b_2)^2} \right) e^{2b_1 T - 2 \kappa_v T b_2} - \left( \frac{Var(\xi) + \sigma^2 T}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2 \kappa_v b_2)^2} \right) \right]\\
		& & + \frac{(q_T + \bar{q}_T)}{2} \left[  Var(\xi) e^{2b_1T - 2\kappa_v T\cdot b_2} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{2b_1 T - 2\kappa_v T\cdot b_2} - 1\right) \right] + \frac{\bar{x}_0^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2) C^w} }{2(b_2 + \bar{b}_2)}\\
		&\sim & \left( \frac{\zeta_3}{b_2^2} + \frac{\zeta_4}{b_2} + \zeta_5 \right) e^{-2\kappa_v T\cdot b_2}  + \left( \frac{\zeta_6}{b_2^2} + \frac{\zeta_7}{b_2}  \right)
	\end{IEEEeqnarray*}
	where $(\zeta_i)_{i=1..7}$ are constant w.r.t. $b_2$. In particular
	$$ \zeta_2 =  \frac{ \left(\sqrt{ \frac{ (r + \bar{r}(1-\bar{s})^2 )( q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } - \sqrt{ q + \bar{q}(1-s)^2 }\right)^2 \cdot \bar{x}_0^2 }{4 \kappa_u },$$
	and $$\zeta_7 =  \frac{(q+\bar{q}) (Var(\xi) + \sigma^2 T)+ \frac{\sigma^2}{2} (q_T + \bar{q}_T) ) }{2 \kappa_v} + \frac{1}{2}\bar{x}_0^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2)(q + \bar{q}(1-s)^2)}. $$ 
	Hence, for large $b_2$ we have:
	\begin{equation*}
		\frac{\Delta SC}{SC^{MKV}} \sim \zeta_2 \zeta_7  .
	\end{equation*}
	Therefore, if $\zeta_2 \neq 0$, namely:
	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then we deduce:
	$$ \lim_{b_2 \to \infty} PoA =: PoA^{\infty,b_2} > 1;$$
	otherwise $$ \lim_{b_2 \to \infty} PoA = 1.$$ 
\end{proof}

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1\neq 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad and \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and 
	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \neq 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold. Let's denote the limiting solutions by 
	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
	\begin{equation*}
    \begin{split}
	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var}(t) + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
    \end{split}
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda \to 0$
	and $B \to \infty,\ C^u \to 0,\ D^u \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
	$$ \lambda = \mathcal{O}(\bar{b}^{-1}_2),\ C^u = \mathcal{O}(\bar{b}_2^{-1}),\ D^u = \mathcal{O}(\bar{b}_2^{-1}),\ B = \mathcal{O}(\bar{b}_2^2),$$
	and 
	$$ \frac{\delta^\pm_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\infty,\bar{b}_2}.$$
	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u_t &= \frac{ - \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^+_u}{\sqrt{b_2 + \bar{b}_2}}  \right) + \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^-_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^+_u - \delta^-_u)(T-t)}}{ \left( \frac{\delta^-_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) - \left( \frac{\delta^+_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) 
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
	Thus, we have $B \cdot u_t = \mathcal{O}\left({\bar{b}_2}^{1/2}\right)$ for $t \in [0,T)$ and 
	$$ \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
	As in the proof of Proposition \ref{prop:b2}, for $t \in [0,T)$:
	$$ (b_2 + \bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$$
	so that $w_t \to 0, \forall t \in [0,T)$ as $\bar{b}_2 \to \infty$. Hence, by the bounded convergence theorem, we deduce:
	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty} \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w_t \right)^2 \cdot \left(\bar{x}_t^{MFG} \right)^2 dt \to 0.
	$$	
	Moreover, as shown in the case $\bar{b}_2 \to 0$, $\eta_t$ as well as the variance $v_t$ are invariant w.r.t. $\bar{b}_2$ and $v_t>0$ for $t>0$. Thus,
	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}(t)> 0.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
\end{proof}

\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $\lambda \neq 1$, then
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &and \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &and \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
    Clearly we have $\lim_{b_1 \to 0}u_t=:u^{0,b_1}_t$, $\lim_{b_1 \to 0}w_t=:w^{0,b_1}_t$, and $\lim_{b_1 \to 0}\eta_t=:\eta^{0,b_1}_t$, where all three limiting processes are bounded. By the assumption on $\lambda$, $u_t \neq w_t$ on a set of positive Lebesgue measure. By the assumption on $\xi$, we have $\lim_{b_1 \to 0} \bar{x}^{MFG}_t=:\bar{x}^{0,b_1,MFG}_t>0,\ \forall t \in [0,T]$ which is also bounded. Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
    \begin{equation*}
        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ and\ \Delta SC^{0,b_1}>0.
    \end{equation*}
    Since $\eta^{0,b_1}_t$ is bounded, $\lim_{b_1 \to 0}v_t=:v_t^{0,b_1}>0,\ \forall t>0$ which is also bounded. Using equation (\ref{eq:SC_MFG_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$. Therefore, $\lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1$.

    Now we consider $b_1 \to \infty$. We see that:
    \begin{equation*}
        \delta^+_u \to 0,\ \frac{\delta^-_u}{b_1+\frac{\bar{b}_1}{2}} \to -2,\ \delta^+_w \to 0,\ \frac{\delta^-_w}{b_1+\bar{b}_1} \to -2,\ \delta^+_{\eta} \to 0,\ \frac{\delta^-_{\eta}}{b_1} \to -2.
    \end{equation*}
    and therefore we find for $t \in [0,T)$:
    \begin{equation*}
    \begin{split}
        \left(b_1+\frac{\bar{b}_1}{2}\right)u_t&\to 2 C^u \\
        \left(b_1+\bar{b}_1\right)w_t&\to 2 C^w \\
        b_1 \eta_t&\to 2 C^{\eta}.
    \end{split}
    \end{equation*}
    Thus, $\Delta \bar{\eta}_t=\mathcal{O}(b_1^{-1})$ for $t \in [0,T)$. We find $\bar{x}^{MFG}_t=\mathcal{O}(e^{b_1})$ for $t \in (0,T]$. Thus, using Proposition \ref{prop:diff_SC}, we have $\Delta SC=\mathcal{O}\left(\frac{e^{b_1}}{b_1}\right)$. We also find $v_t=\mathcal{O}(e^{2b_1})$. Therefore with equation (\ref{eq:SC_MFG_MKV_2}) we have:
    \begin{equation*}
        \frac{\Delta SC}{SC^{MKV}}=\mathcal{O}\left(\frac{e^{-b_1}}{b_1}\right)\to 0.
    \end{equation*}
    We conclude that $PoA \to 1$ as $b_1 \to \infty$.

    Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$. We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
\end{proof}

\subsection{\textbf{Numerical Results}}

Using the explicit formulas derived in Appendix \ref{appendix_solving_fbsdes}, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}). In particular, when we allow for full interaction (i.e. through the states and the controls), we choose the following default values:

\begin{equation*}
\begin{split}
    &\xi\equiv 1,\ T=1 \\
    &b_1=1,\  \bar{b}_1=1,\ b_2=1,\ \bar{b}_2=1,\ \sigma=1 \\
    &q=1,\ \bar{q}=1,\ s=0.5,\ r=1,\ \bar{r}=1,\ \bar{s}=0.5 \\
    &q_T=1,\  \bar{q}_T=1,\ s_T=0.5.
\end{split}
\end{equation*}

Unless otherwise stated, the parameters stay at these default values. For results involving only interaction through the states, we set $\bar{b}_2=0$ and $\bar{r}=0$. For results involving only interaction through the controls, we set $\bar{b}_1=0$, $\bar{q}=0$, and $\bar{q}_T=0$. Figures \ref{fig:b1_b1bar}-\ref{fig:r_rbar} show the price of anarchy as we vary one parameter at a time for each of three cases: full interaction (i.e. through the states and the controls), interaction only through the states, and interaction only through the controls.

\begin{figure}[!htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps}
    \end{subfigure}
    \caption{PoA as we vary $b_1$ (left) and $\bar{b}_1$ (right).}
    \label{fig:b1_b1bar}
\end{figure}
\begin{figure}[!htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_b2.eps}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_even_more_steps_b2bar_2.eps}
    \end{subfigure}
    \caption{PoA as we vary $b_2$ (left) and $\bar{b}_2$ (right).}
    \label{fig:b2_b2bar}
\end{figure}
\begin{figure}[!htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_q.eps}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar.eps}
    \end{subfigure}
    \caption{PoA as we vary $q$ (left) and $q_T$ (right).}
    \label{fig:q_q_T}
\end{figure}
\begin{figure}[!htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_q_T.eps}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar_T.eps}
    \end{subfigure}
    \caption{PoA as we vary $\bar{q}$ (left) and $\bar{q}_T$ (right).}
    \label{fig:qbar_qbar_T}
\end{figure}
\begin{figure}[!htb]
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_r.eps}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[scale=0.5]{PoA_half_more_steps_rbar.eps}
    \end{subfigure}
    \caption{PoA as we vary $r$ (left) and $\bar{r}$ (right).}
    \label{fig:r_rbar}
\end{figure}

The results show various limiting behaviors, such as some of the cases proved in the previous section. In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed. For all three cases, as $b_1 \to 0$, we see that $PoA \to PoA^{0,b_1}>1$ and as $\bar{b}_1 \to 0$, we see that $PoA \to PoA^{0,\bar{b}_1}>1$. We also see that $PoA\to 1$ as $b_1 \to \infty$ and $PoA \to \infty$ as $\bar{b}_1 \to \infty$. Proposition \ref{prop:b2} is confirmed in Figure \ref{fig:b2_b2bar}. When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $PoA \to 1$ as $b_2 \to 0$. When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $PoA \to PoA^{0,b_2}>1$ as $b_2 \to 0$. For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $PoA \to 1$ as $b_2 \to \infty$. For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $PoA \to PoA^{0,\bar{b}_2}>1$ as $\bar{b}_2 \to 0$ and $PoA \to 1$ as $\bar{b}_2 \to \infty$. Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $PoA \to 1$ as $r \to \infty$ or $\bar{r} \to \infty$.

\subsection{\textbf{A Particular Example: Flocking}}
Mean field game models of flocking have been proposed in the literature by Nourian et al \cite{nourian2010synthesis}\cite{nourian2011mean}. Here we consider a slightly different formulation as described in Section 3.6.1 of the book \cite{Carmona_book}. A representative bird in the flock controls their velocity, $X_t$, through the drift:
\begin{equation*}
    b(t,x,\mu,\alpha,\nu)=\alpha.
\end{equation*}
They choose the control with two goals in mind: to minimize their kinetic energy put into their control, and to align their velocity with the average velocity of the group. Thus, they consider the cost functions given by:
\begin{equation*}
\begin{split}
    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(\bar{q}|x-s\bar{\mu}|^2 +\alpha^2 \right), \\
    g(x,\mu)&=0.
\end{split}
\end{equation*}

In our general linear quadratic formulation, this is equivalent to taking $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $s=1$, $r=1$, $\bar{r}=0$, and $\bar{s}=0$. Note that for these values of the parameters, the assumptions of Theorem \ref{th:exist_uniq} and Corollary \ref{corollary_1} are satisfied. Therefore, $PoA=1$. In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.

\section{\textbf{Conclusion}} \label{sec:conclusion}
We defined the price of anarchy ($PoA$) in the context of extended mean field games as the ratio of the worst case social cost when the players are in a mean field game equilibrium to the social cost as computed by a central planner. Since the central planner does not require that the players be in a mean field game equilibrium, the central planner will realize a social cost that is no worse than that of a mean field game equilibrium. Thus, $PoA \geq 1$.

We computed the price of anarchy for linear quadratic extended mean field games, for which explicit computations are possible. We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollary \ref{corollary_1}), as well as some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity. The numerics support our theoretical results.

\section{\textbf{Acknowledgments}}
The authors would like to thank the organizers of CEMRACS 2017 for putting together such a successful summer school.

\begin{thebibliography}{10}

\bibitem{achdou2015system}
Y.~Achdou and M.~Lauri\`{e}re.
\newblock On the system of partial differential equations arising in mean field
  type control.
\newblock {\em arXiv preprint arXiv:1503.05044}, 2015.

\bibitem{balandat2013efficiency}
M.~Balandat and C.~J. Tomlin.
\newblock On efficiency in mean field differential games.
\newblock In {\em American Control Conference (ACC), 2013}, pages 2527--2532.
  IEEE, 2013.

\bibitem{bensoussan2013mean}
A.~Bensoussan, J.~Frehse, and P.~Yam.
\newblock {\em Mean field games and mean field type control theory}, volume
  101.
\newblock Springer, 2013.

\bibitem{pierre_poa}
P.~Cardaliaguet and C.~Rainer.
\newblock On the (in)efficiency of {MFG} equilibria.
\newblock Technical report, 2018.

\bibitem{cite_todo}
R.~Carmona, B.~Acciaio, and J.~Backhoff~Veraguas.
\newblock Generalized {M}c{K}ean-{V}lasov ({M}ean {F}ield) {C}ontrol: a
  stochastic maximum principle and a transport perspective.
\newblock Technical report, 2018.

\bibitem{carmona2013probabilistic}
R.~Carmona and F.~Delarue.
\newblock Probabilistic analysis of mean-field games.
\newblock {\em SIAM Journal on Control and Optimization}, 51(4):2705--2734,
  2013.

\bibitem{Carmona_book}
R.~Carmona and F.~Delarue.
\newblock {\em Probabilistic Theory of Mean Field Games with Applications I}.
\newblock Springer, 2018.

\bibitem{christodoulou2005price2}
G.~Christodoulou and E.~Koutsoupias.
\newblock On the price of anarchy and stability of correlated equilibria of
  linear congestion games.
\newblock In {\em European Symposium on Algorithms}, pages 59--70. Springer,
  2005.

\bibitem{christodoulou2005price}
G.~Christodoulou and E.~Koutsoupias.
\newblock The price of anarchy of finite congestion games.
\newblock In {\em Proceedings of the thirty-seventh annual ACM symposium on
  Theory of computing}, pages 67--73. ACM, 2005.

\bibitem{huang2012social}
M.~Huang, P.~E. Caines, and R.~P. Malham{\'e}.
\newblock Social optima in mean field {LQG} control: centralized and
  decentralized strategies.
\newblock {\em IEEE Transactions on Automatic Control}, 57(7):1736--1751, 2012.

\bibitem{Huang}
M.~Huang, R.~P. Malham{\'e}, and P.~E. Caines.
\newblock Large population stochastic dynamic games: closed-loop
  {M}c{K}ean-{V}lasov systems and the {N}ash certainty equivalence principle.
\newblock {\em Communications in Information \& Systems}, 6(3):221--252, 2006.

\bibitem{koutsoupias1999worst}
E.~Koutsoupias and C.~Papadimitriou.
\newblock Worst-case equilibria.
\newblock In {\em Annual Symposium on Theoretical Aspects of Computer Science},
  pages 404--413. Springer, 1999.

\bibitem{Lasry_Lions}
J.~M. Lasry and P.~L. Lions.
\newblock Mean field games.
\newblock {\em Japanese Journal of Mathematics}, 2(1):229--260, 2007.

\bibitem{nourian2010synthesis}
M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
\newblock Synthesis of {C}ucker-{S}male type flocking via mean field stochastic
  control theory: {N}ash equilibria.
\newblock In {\em Communication, Control, and Computing (Allerton), 2010 48th
  Annual Allerton Conference on}, pages 814--819. IEEE, 2010.

\bibitem{nourian2011mean}
M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
\newblock Mean field analysis of controlled {C}ucker-{S}male type flocking:
  Linear analysis and perturbation equations.
\newblock {\em IFAC Proceedings Volumes}, 44(1):4471--4476, 2011.

\bibitem{nourian2013nash}
M.~Nourian, P.~E. Caines, R.~P. Malhame, and M.~Huang.
\newblock {N}ash, social and centralized solutions to consensus problems via
  mean field control theory.
\newblock {\em IEEE Transactions on Automatic Control}, 58(3):639--653, 2013.

\bibitem{Roughgarden}
T.~Roughgarden.
\newblock Intrinsic robustness of the price of anarchy.
\newblock In {\em Proceedings of the forty-first annual ACM symposium on Theory
  of computing}, pages 513--522. ACM, 2009.

\bibitem{roughgarden2002bad}
T.~Roughgarden and {\'E}.~Tardos.
\newblock How bad is selfish routing?
\newblock {\em Journal of the ACM (JACM)}, 49(2):236--259, 2002.

\bibitem{zhu2010price}
Q.~Zhu and T.~Ba{\c{s}}ar.
\newblock Price of anarchy and price of information in {N}-person
  linear-quadratic differential games.
\newblock In {\em American Control Conference (ACC), 2010}, pages 762--767.
  IEEE, 2010.

\end{thebibliography}

\begin{appendices}

\section{\textbf{Solving Linear FBSDEs of McKean-Vlasov Type}} \label{appendix_solving_fbsdes}

Consider a linear FBSDE system of McKean-Vlasov type:
\begin{equation}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^{\bar{x}}_t \mathbb{E}X_t+a^y_tY_t+a^{\bar{y}}_t \mathbb{E}Y_t\right)dt+\sigma dW_t \\
        X_0&=\xi \\
        dY_t&=\left(b^x_tX_t+b^{\bar{x}}_t \mathbb{E}X_t+b^y_tY_t+b^{\bar{y}}_t \mathbb{E}Y_t\right)dt +Z_t dW_t \\
        Y_T&=c^xX_T+c^{\bar{x}}\mathbb{E}X_T.
\end{split}
\label{eq:FBSDE_general}
\end{equation}
For the LQEMFG model considered in Section \ref{sec:EMFG}, the FBSDE system in equation (\ref{eq:FBSDE_EMFG}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MFG}(t)b_2(t),\ a^{\bar{y}}_t=b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=\bar{q}(t)s(t),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=0 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=-\bar{q}_Ts_T.
\end{split}
\end{equation*}
For the LQEMKV model considered in Section \ref{sec:EMKV}, the FBSDE system in equation (\ref{eq:FBSDE_EMKV}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
\begin{equation*}
\begin{split}
    &a^x_t=b_1(t),\ a^{\bar{x}}_t=\bar{b}_1(t),\ a^y_t=a^{MKV}(t)b_2(t),\ a^{\bar{y}}_t=b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t) \\
    &b^x_t=-(q(t)+\bar{q}(t)),\ b^{\bar{x}}_t=-s(t)\bar{q}(t)(s(t)-2),\ b^y_t=-b_1(t),\ b^{\bar{y}}_t=-\bar{b}_1 \\
    &c^x_t=q_T+\bar{q}_T,\ c^{\bar{x}}_t=s_T\bar{q}_T(s_T-2).
\end{split}
\end{equation*}

Now we return to the general FBSDE system (\ref{eq:FBSDE_general}). By taking expectations in equation (\ref{eq:FBSDE_general}), and letting $\bar{x}_t$ and $\bar{y}_t$ denote $\mathbb{E}X_t$ and $\mathbb{E}Y_t$, respectively, we get:
\begin{equation}
\begin{split}
        \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t)\bar{x}_t+(a^y_t+a^{\bar{y}}_t)\bar{y}_t\\
        \bar{x}_0&=\mathbb{E}(\xi) \\
        \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t\\
        \bar{y}_T&=(c^x+c^{\bar{x}})\bar{x}_T
\end{split}
\label{eq:FBSDE_general_means}
\end{equation}
where the dot is the standard ODE notation for a derivative. We then make the ansatz $\bar{y}_t=\bar{\eta}_t\bar{x}_t+\bar{\chi}_t$ for deterministic functions $[0,T] \ni t \mapsto \bar{\eta}_t \in \mathbb{R}$ and $[0,T] \ni t \mapsto \bar{\chi}_t \in \mathbb{R}$. By plugging in the ansatz, the system in equation (\ref{eq:FBSDE_general_means}) is equivalent to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\bar{\eta}}_t+(a^y_t+a^{\bar{y}}_t) \bar{\eta}_t^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}_t -b^x_t-b^{\bar{x}}_t&=0\\
    \bar{\eta}_T-c^x-c^{\bar{x}}&=0 \\
    \dot{\bar{\chi}}_t+(\bar{\eta}_t(a^y_t+a^{\bar{y}}_t)-b^y_t-b^{\bar{y}}_t)\bar{\chi}_t &=0\\
    \bar{\chi}_T&=0.
\end{split}
\end{equation*}
The first equation is a Riccati equation. Note that $\bar{\chi}_t$ solves a first order homogeneous linear equation. Thus $\bar{\chi}_t=0$, $\forall t\in[0,T]$. Once the equation for $\bar{\eta}_t$ is solved, we can compute $\bar{x}_t$ by solving the linear ODE:
\begin{equation*}
\begin{split}
    \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t \\
    \bar{x}_0&=\mathbb{E}(\xi)
\end{split}
\end{equation*}
and thus,
\begin{equation*}
    \bar{x}_t=\bar{x}_0 e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}_u)du}.
\end{equation*}

Once we have computed $(\bar{x}_t)_{0\leq t\leq T}$, we can rewrite the original FBSDE system:
\begin{equation*}
\begin{split}
        dX_t&=\left(a^x_tX_t+a^y_tY_t+a^0_t\right)dt+\sigma dW_t \\
        X_0&=\xi \\
        dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t \\
        Y_T&=c^xX_T+c^0
\end{split}
\end{equation*}
with:
\begin{equation*}
\begin{split}
    a^0_t&=(a^{\bar{x}}_t+a^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t \\
    b^0_t&=(b^{\bar{x}}_t+b^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t\\
    c^0&=c^{\bar{x}}\bar{x}_T.
\end{split}
\end{equation*}

Now we make the ansatz: $Y_t=\eta_t X_t+\chi_t$, which reduces the problem to the ODE system:
\begin{equation*}
\begin{split}
    \dot{\eta}_t+a^y_t\eta_t^2+(a^x_t-b^y_t)\eta_t-b^x_t&=0 \\
    \eta_T&=c^x, \\
    \dot{\chi}_t+(-b^y_t+a^y_t\eta_t)\chi_t+a^0_t\eta_t-b^0_t&=0, \\
    \chi_T&=c^0, \\
    Z_t&=\sigma \eta_t.
\end{split}
\end{equation*}
Again, the first equation is a Riccati equation. Note that it is not necessary to solve for $\chi_t$ because of the relationship:
\begin{equation*}
    \bar{\eta}_t\bar{x}_t=\bar{y}_t=\mathbb{E}(Y_t)=\mathbb{E}(\eta_t X_t+\chi_t)=\eta_t \bar{x}_t+\chi_t.
\end{equation*}
Thus,
\begin{equation*}
    \chi_t=(\bar{\eta}_t-\eta_t)\bar{x}_t.
\end{equation*}

In summary, the solution to the linear FBSDE of McKean-Vlasov type is reduced to solving linear ODEs and Riccati equations. It will also be useful to compute $Var(X_t)$, which we denote by $v_t$. After we have solved the above equations, we have
\begin{equation*}
\begin{split}
        dX_t&=\left((a^x_t+a^y_t \eta_t)X_t+a^y_t \chi_t+a^0_t\right)dt+\sigma dW_t \\
        X_0&=\xi.
\end{split}
\end{equation*}
Thus,
\begin{equation*}
    v_t=Var(X_t)=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta_u) du}ds.
\end{equation*}
In the case where the coefficients are time-independent, the Riccati equations for $\bar{\eta}_t$ and $\eta_t$ can be solved explicitly.

\subsection*{\textbf{Scalar Riccati Equation}} If the scalar Riccati equation 
	\begin{equation*}
		\dot{\rho}_t - B \rho_t^2 - 2A \rho_t  + C = 0 
	\end{equation*}
	with terminal condition $\rho_T = D$ satisfies:
	\begin{equation}
		B \neq 0, BD \geq 0, BC>0,
	\label{eq:Riccati_assumptions}
	\end{equation}
	then it has a unique solution:
\begin{equation}
		\rho_t= \frac{-(C+D \delta^+) + (C+D \delta^-) e^{-(\delta^+ - \delta^-)(T-t)}}{(\delta^- - D B) - (\delta^+ - D B) e^{-(\delta^+ - \delta^-)(T-t)}}
	\label{eq:riccati_ut_sol_app}
\end{equation}
	where $\delta^\pm = -A \pm \sqrt{(A)^2 + B C}$.

	Furthermore, if $B \to 0$ and $A\neq 0$, we can deduce that the limiting solution of the scalar Riccati equation coincides with the first-order differential equation:
	\begin{equation*}
		\dot{\rho}_t - 2A \rho_t +C = 0 
	\end{equation*}
	with terminal condition $\rho_T = D$, namely:
	\begin{equation*}
		\rho_t = \left(D - \frac{C}{2A} \right) e^{-2A (T-t)} + \frac{C}{2A}.
	\end{equation*}

	If $B \to 0$ and $A = 0$, the limiting solution of the scalar Riccati equation coincides with the first-order differential equation:
	\begin{equation*}
	    \dot{\rho}_t +C = 0
	\end{equation*}
	with terminal condition $\rho_T = D$, namely:
	\begin{equation*}
	    \rho_t = D + C(T-t).
	\end{equation*}\\
Hence, returning to the linear FBSDE (\ref{eq:FBSDE_general}), for $\bar{\eta}_t$, we use:
\begin{equation*}
	\left\{
	\begin{array}{rl}
		A=&-\frac{1}{2}(a^x+a^{\bar{x}}-b^y-b^{\bar{y}}) \\
		B=&-(a^y+a^{\bar{y}}) \\
		C=&-(b^x+b^{\bar{x}}) \\
		D=&\ c^x+c^{\bar{x}}
	\end{array}
	\right.
\end{equation*}
The conditions (\ref{eq:Riccati_assumptions}) are satisfied if:
\begin{equation*}
	\left\{
	\begin{array}{rl}
		-(a^y+a^{\bar{y}})&>0 \\
		-(b^x+b^{\bar{x}})&>0 \\
		c^x+c^{\bar{x}}& \geq 0
	\end{array}
	\right.
\end{equation*}
For $\eta_t$, we use:
\begin{equation*}
	\left\{
	\begin{array}{rl}
		A=&-\frac{1}{2}(a^x-b^y) \\
		B=&-a^y \\
		C=&-b^x \\
		D=&\ c^x.
	\end{array}
	\right.
\end{equation*}
The conditions (\ref{eq:Riccati_assumptions}) are satisfied if:
\begin{equation*}
	\left\{
	\begin{array}{rl}
		-a^y&>0 \\
		-b^x&>0 \\
		c^x& \geq0.
	\end{array}
	\right.
\end{equation*}
Returning to the LGEMFG and LGEMKV problems, if we assume the coefficients are nonnegative, we see that these conditions are exactly assumption (\ref{eq:assumptions}).

\end{appendices}

\end{document}

### 2018-07-03 PoA.tex
addressed minor points 1-3, 5, 7-9, 11-13

@@
 We work over the interval $[0,T]$ limited by a finite time horizon $T \in \mathbb{R}^+$.
-We assume the drift function $b(t,x,\mu,\alpha,\nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A})  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs.
+We assume the drift function $b:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha,\nu)  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs.
 For the sake of simplicity, we assume that the volatility, $\sigma$, is a positive constant.
@@
 \subsubsection*{\textbf{Cost Functionals}}
-We assume that we are given two functions $f(t,x,\mu,\alpha, \nu): [0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \rightarrow \mathbb{R}$ and $g(x,\mu):\mathbb{R}\times \cP(\mathbb{R}) \rightarrow \mathbb{R}$ which we call running and terminal cost functions, respectively.
-We assume $f$ and $g$ are Lipschitz in each of it's arguments.
+We assume that we are given two functions $f:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha, \nu) \rightarrow \mathbb{R}$ and $g:\mathbb{R}\times \cP(\mathbb{R}) \ni (x,\mu) \rightarrow \mathbb{R}$ which we call running and terminal cost functions, respectively.
+We assume $f$ and $g$ are Lipschitz in each of their arguments.
 The goal of player $i$ is to minimize its expected cost as given by:
@@
 To begin, we define what we call the \textit{mean field environment}.
-By symmetry of the players, we suppose all of the players in the mean field use the same feedback function, $\phi$.
+By symmetry of the players, we suppose all of the players in the mean field game use the same feedback function, $\phi$.
 Then the \textit{mean field environment} specified by $\phi$ is characterized by $\cL(X^{\phi}_t)_{0\le t\le T}$ and $\cL(\phi(t,X^{\phi}_t))_{0\le t\le T}$ where the dynamics of $(X^{\phi}_t)_{0\le t\le T}$ are given by equation (\ref{eq:X}).
@@
 \begin{equation*}
-    dX^{\phi',\phi}_t=b(t,X^{\phi',\phi}_t,\cL(X^{\phi}_t),\phi'(t,X^{\phi',\phi}_t),\cL(\phi(t,X^{\phi}_t))dt+\sigma dW_t.
+    dX^{\phi',\phi}_t=b(t,X^{\phi',\phi}_t,\cL(X^{\phi}_t),\phi'(t,X^{\phi',\phi}_t),\cL(\phi(t,X^{\phi}_t)))dt+\sigma dW_t.
 \end{equation*}
@@
 \begin{equation*}
-    \cS(\phi',\phi)=\biggl[\int_0^T<f(t,\cdot,\cL(X^{\phi}_t),\phi'(t,\cdot),\cL(\phi(t,X^{\phi}_t)),\cL(X^{\phi',\phi}_t)> dt +<g(\cdot,\cL(X^{\phi}_T)),\cL(X^{\phi',\phi}_t)>\biggr].
+    \cS(\phi',\phi)=\biggl[\int_0^T<f(t,\cdot,\cL(X^{\phi}_t),\phi'(t,\cdot),\cL(\phi(t,X^{\phi}_t)),\cL(X^{\phi',\phi}_t))> dt +<g(\cdot,\cL(X^{\phi}_T)),\cL(X^{\phi',\phi}_t)>\biggr].
 \end{equation*}
@@
 \begin{enumerate}
-\item For each feedback function $\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}$, solve the optimal control problem
+\item For each feedback function $\phi:[0,T] \times \mathbb{R} \ni (t,x) \rightarrow \mathbb{R}$, solve the optimal control problem
 \begin{equation*}
@@
 \end{equation*}
-Define the mapping $\Phi:\phi \rightarrow \phi^*$.
+Define the mapping $\Phi(\phi):=\phi^*$.
 \item Find a fixed point $\hat{\phi}$ of $\Phi$ such that $\Phi(\hat{\phi})=\hat{\phi}$.
@@
 \begin{equation*}
-    \mathcal{N}=\{\phi:[0,T] \times \mathbb{R} \rightarrow \mathbb{R}: \Phi(\phi)=\phi \}.
+    \mathcal{N}=\{\phi:[0,T] \times \mathbb{R} \ni (t,x) \rightarrow \mathbb{R}\ |\ \Phi(\phi)=\phi \}.
 \end{equation*}
@@
 \end{equation*}
-A sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. According to the Pontryagin stochastic maximum principle, we introduce the function:
+According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. We introduce the function:
 \begin{equation*}
@@
 \end{equation*}
-and use the control $\hat{\alpha}_t=\hat{\alpha}(t,x,\bar{\mu},\bar{\nu},Y_t)$.
+and use the control $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$.
 When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$.
@@
 \end{equation*}
-So the solution of the mean field game equilibrium problem is given by the solution to the FBSDE system:
+Note that $c^{MFG}(t)=a^{MFG}(t)+b^{MFG}(t)$. The solution of the mean field game equilibrium problem is given by the solution to the FBSDE system:
 \begin{equation}
@@
 			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
-			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t)\right] dt\\
+			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t\right] dt\\
 			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt
@@
 
-We study in the following the variation of $PoA$ by letting one of the coefficients tends to $0$ or to $\infty$.
+We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$.
 It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
@@
 	\end{equation*}
-	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $\lim_{r \to \infty}v_t >0$ for $t>0$ and therefore,
+	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_0 >0$ for $t>0$ and therefore,
 	\begin{equation*}
@@
 
-	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u = -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u = 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
+	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
 	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$

### 2018-07-03 PoA.tex
major point 7

@@
 \subsection{\textbf{Numerical Results}}
-
-Using the explicit formulas derived in Appendix \ref{appendix_solving_fbsdes}, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}).
+The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
+Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}).
 In particular, when we allow for full interaction (i.e.

### 2018-07-03 PoA.tex
Major point 4, removed Corollary 3

@@
 Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem.
+Then from the appendix, we have:
+
+ToDo
+\begin{equation*}
+\begin{split}
+\dot{\bar{\eta}}^{MFG}_t+(a^y_t+a^{\bar{y}}_t) (\bar{\eta}^{MFG}_t)^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}^{MFG}_t -b^x_t-b^{\bar{x}}_t&=0,\\
+\bar{\eta}^{MFG}_T-c^x-c^{\bar{x}}&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\dot{\eta}^{MFG}_t+a^y_t(\eta^{MFG}_t)^2+(a^x_t-b^y_t)\eta^{MFG}_t-b^x_t&=0, \\
+\eta^{MFG}_T&=c^x,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}^{MFG}_u)du},
+\end{equation*}
+\begin{equation*}
+v_t=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta^{MFG}_u) du}ds.
+\end{equation*}
 Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
@@
 \subsection{\textbf{Linear Quadratic Control of McKean-Vlasov Type Involving the Law of the Control}}\label{sec:EMKV}
-To solve the linear quadratic optimal control problem of McKean Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
+To solve the linear quadratic optimal control problem of McKean-Vlasov type involving the law of the control (LQEMKV), we begin with the reduced Hamiltonian, which is the same as in the LQEMFG problem:
 \begin{equation*}
@@
 See Appendix \ref{appendix_solving_fbsdes}).
-Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$  denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem.
+Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem.
+Then from the appendix, we have:
+
+ToDo
+\begin{equation*}
+\begin{split}
+\dot{\bar{\eta}}^{MKV}_t+(a^y_t+a^{\bar{y}}_t) (\bar{\eta}^{MKV}_t)^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}^{MKV}_t -b^x_t-b^{\bar{x}}_t&=0,\\
+\bar{\eta}^{MKV}_T-c^x-c^{\bar{x}}&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\dot{\eta}^{MKV}_t+a^y_t(\eta^{MKV}_t)^2+(a^x_t-b^y_t)\eta^{MKV}_t-b^x_t&=0, \\
+\eta^{MKV}_T&=c^x,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}^{MKV}_u)du},
+\end{equation*}
+\begin{equation*}
+v_t=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta^{MKV}_u) du}ds.
+\end{equation*}
 Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
@@
 where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.
-
-\begin{corollary}
-    Assuming (\ref{eq:assumptions}), if $\bar{b}_1=0$ and $\lambda=1$, then $PoA=1$.
-\end{corollary}
-\begin{proof}
-    Under these assumptions, $(A^u,C^u,D^u)=(A^w,C^w,D^w)$, and thus $(u_t)_{0\leq t\leq T}=(w_t)_{0\leq t\leq T}$.
-Thus, $\Delta \bar{\eta}_t=0,\ \forall t \in [0,T]$.
-By Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-It can be shown that $w_0\geq0$.
-Since $v_t>0$ for $t>0$, clearly $SC^{MKV}>0$.
-Therefore, $PoA=1$.
-\end{proof}
 
@@
 \begin{equation*}
-    \bar{x}_t=\bar{x}_0 e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}_u)du}.
+    \bar{x}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}_u)du}.
 \end{equation*}

### 2018-07-03 PoA.tex
major point 1

@@
 Then from the appendix, we have:
-
-ToDo
-\begin{equation*}
-\begin{split}
-\dot{\bar{\eta}}^{MFG}_t+(a^y_t+a^{\bar{y}}_t) (\bar{\eta}^{MFG}_t)^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}^{MFG}_t -b^x_t-b^{\bar{x}}_t&=0,\\
-\bar{\eta}^{MFG}_T-c^x-c^{\bar{x}}&=0,
-\end{split}
-\end{equation*}
-\begin{equation*}
-\begin{split}
-\dot{\eta}^{MFG}_t+a^y_t(\eta^{MFG}_t)^2+(a^x_t-b^y_t)\eta^{MFG}_t-b^x_t&=0, \\
-\eta^{MFG}_T&=c^x,
-\end{split}
-\end{equation*}
-\begin{equation*}
-\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}^{MFG}_u)du},
-\end{equation*}
-\begin{equation*}
-v_t=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta^{MFG}_u) du}ds.
+\begin{equation*}
+\begin{split}
+\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
+\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-\bar{q}s_T))&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
+\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
+\end{equation*}
+\begin{equation*}
+v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
 \end{equation*}
@@
 Then from the appendix, we have:
-
-ToDo
-\begin{equation*}
-\begin{split}
-\dot{\bar{\eta}}^{MKV}_t+(a^y_t+a^{\bar{y}}_t) (\bar{\eta}^{MKV}_t)^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}^{MKV}_t -b^x_t-b^{\bar{x}}_t&=0,\\
-\bar{\eta}^{MKV}_T-c^x-c^{\bar{x}}&=0,
-\end{split}
-\end{equation*}
-\begin{equation*}
-\begin{split}
-\dot{\eta}^{MKV}_t+a^y_t(\eta^{MKV}_t)^2+(a^x_t-b^y_t)\eta^{MKV}_t-b^x_t&=0, \\
-\eta^{MKV}_T&=c^x,
-\end{split}
-\end{equation*}
-\begin{equation*}
-\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(a^x_u+a^{\bar{x}}_u+(a^y_u+a^{\bar{y}}_u)\bar{\eta}^{MKV}_u)du},
-\end{equation*}
-\begin{equation*}
-v_t=Var(\xi)e^{\int_0^t 2(a^x_s+a^y_s\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (a^x_u+a^y_u\eta^{MKV}_u) du}ds.
+\begin{equation*}
+\begin{split}
+\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
+\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
+\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
+\end{split}
+\end{equation*}
+\begin{equation*}
+\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
+\end{equation*}
+\begin{equation*}
+v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
 \end{equation*}
@@
 	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
-	Moreover, since $\bar{x}_t^{MFG} = \bar{x}_0 \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have
+	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have
 	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \bar{x}_0 e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad

### 2018-07-04 PoA.tex
Major point 2 fixed

@@
 \begin{split}
-    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right), \\
+    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right), \\
     g(x,\mu)&=\frac{1}{2}\left(q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right).
@@
     H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y \\
-    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right),
+    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right),
 \end{split}
@@
     SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
-    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
-    &+(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
+    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
+    &+(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
 \end{split}
@@
     H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
-    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}\bar{\nu})^2\right).
+    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right).
 \end{split}
@@
 A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}.
-This sufficient condition is the following:
+Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
 $\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
 \begin{equation*}
-    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t)(X_t,\hat{\alpha}_t) \right]=0,
+    \partial_{\alpha}H(t,X_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\nu}}H(t,\tilde{X}_t,\mathbb{E}(X_t),\hat{\alpha}_t,\mathbb{E}(\hat{\alpha}_t),\tilde{Y}_t) \right]=0,
 \end{equation*}
@@
 \begin{split}
-    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\mu}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t)(X_t,\alpha_t) \right] \right]dt+Z_tdW_t \\
+    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
     Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
@@
 \end{equation*}
-where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
-
+and $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
 In the present LQ case, the sufficient condition can be used to solve for:
@@
     SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
-    &+\int_0^T (q_t+\bar{q}_t+(r_t+\bar{r}_t)(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
-    &+\int_0^T(q_t+\bar{q}_t(1-s_t)^2+(r_t+\bar{r}_t(1-\bar{s}_t)^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
+    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
+    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
 \end{split}

### 2018-07-04 PoA.tex
h_{var}(t) fixed

@@
 \begin{split}
-	SC^{MFG} = & h_{var}(t) +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
+	SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
 	& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - \bar{\eta}^{MFG}_T (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
-	SC^{MKV} = & h_{var}(t) + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2,
+	SC^{MKV} = & h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2,
 \end{split}
@@
 \end{equation}
-where $ h_{var}(t): = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T  $.
+where $ h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T  $.
 
@@
 Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-From the explicit formula for the variance, $h_{var}(t)>0$ and therefore by equation (\ref{eq:SC_MFG_MKV_2}), $SC^{MKV}>0$.
+From the explicit formula for the variance, $h_{var}>0$ and therefore by equation (\ref{eq:SC_MFG_MKV_2}), $SC^{MKV}>0$.
 Therefore, $PoA=1$.
@@
     \begin{split}
-	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var}(t) + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
+	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
 	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
@@
 	Moreover, as shown in the case $\bar{b}_2 \to 0$, $\eta_t$ as well as the variance $v_t$ are invariant w.r.t. $\bar{b}_2$ and $v_t>0$ for $t>0$. Thus,
-	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}(t)> 0.$$
+	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}> 0.$$
 	Therefore, we conclude that:

### 2018-07-04 PoA.tex
Major point 3 fixed

@@
 Then from the appendix, we have:
-\begin{equation*}
+\begin{equation}
 \begin{split}
 \dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
-\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-\bar{q}s_T))&=0,
-\end{split}
-\end{equation*}
-\begin{equation*}
+\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-s_T))&=0,
+\end{split}
+\label{eq:eta_bar_MFG}
+\end{equation}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
+\end{equation}
+\begin{equation}
+\begin{split}
+\dot{\bar{x}}^{MFG}_t&=(b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t)\bar{x}^{MFG}_t, \\
+\bar{x}^{MFG}_0&=\mathbb{E}(\xi).
+\end{split}
+\label{eq:x_bar_MFG}
+\end{equation}
+And thus,
 \begin{equation*}
@@
 Then from the appendix, we have:
-\begin{equation*}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
-\begin{equation*}
+\label{eq:eta_bar_MKV}
+\end{equation}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
+\end{equation}
+\begin{equation}
+\begin{split}
+\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
+\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
+\end{split}
+\label{eq:x_bar_MKV}
+\end{equation}
+And thus,
 \begin{equation*}
@@
 In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems.
-First, we consider the last integral, where we drop the superscripts ${MFG}$ and ${MKV}$ to address both problems simultaneously.
-By using the Riccati equation associated with $\bar{\eta}_t$ and the equation $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}), we notice that
-\begin{equation*}
-\begin{split}
-	&\int_0^T \bar{\eta}_t^2 \bar{x}_t^2 dt\\
-	=& - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}_t \bar{x}_t^2 dt -  \int_0^T ( (b_1 + \bar{b}_1 - b^y - b^{\bar{y}}) \bar{\eta}_t - (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right]\\
-	= & - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \bar{\eta}_T\bar{x}_T^2-\bar{\eta}_0\bar{x}_0^2-2\int_0^T\bar{\eta}_t\bar{x}_t\dot{\bar{x}}_t dt -  \int_0^T ( (b_1 + \bar{b}_1 - b^y - b^{\bar{y}}) \bar{\eta}_t - (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right] \\
-	= & 2 \int_0^T \bar{\eta}_t^2 \bar{x}_t^2  - \frac{1}{c(b_2 + \bar{b}_2)} \left[ \bar{\eta}_T \bar{x}_T^2 - \bar{\eta}_0 \bar{x}_0^2 - \int_0^T  ((b_1 + \bar{b}_1 + b^y + b^{\bar{y}} ) \bar{\eta}_t + (b^x + b^{\bar{x}}) ) \bar{x}_t^2 dt \right],
-\end{split}
-\end{equation*}
-where we applied integration by parts for the second equality. Thus, if we denote
-\begin{equation*}
-	\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}
-\end{equation*}
-the equations (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) can be rewritten as
+First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$.
+Using equation (\ref{eq:eta_bar_MFG}), we have:
+\begin{equation*}
+\begin{split}
+&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
+=& - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
+\end{split}
+\end{equation*}
+Then by integration by parts:
+\begin{equation*}
+\begin{split}
+= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
+& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
+\end{split}
+\end{equation*}
+Then using equation (\ref{eq:x_bar_MFG}):
+\begin{equation*}
+\begin{split}
+= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
+&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
+\end{split}
+\end{equation*}
+Finally, we solve:
+\begin{equation*}
+\begin{split}
+\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
+&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
+\end{split}
+\end{equation*}
+If we denote:
+\begin{equation*}
+\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
+\end{equation*}
+\begin{equation*}
+h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
+\end{equation*}
+and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
 \begin{equation}
@@
 SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
-	& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - \bar{\eta}^{MFG}_T (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
-	SC^{MKV} = & h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2,
-\end{split}
-\label{eq:SC_MFG_MKV_2}
-\end{equation}
-where $ h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T  $.
+& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
+\end{split}
+\label{eq:SC_MFG_2}
+\end{equation}
+Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
+\begin{equation*}
+\begin{split}
+\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\bar{x}^{MKV}_0)^2 \\
+&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
+\end{split}
+\end{equation*}
+Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
+\begin{equation}
+SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2.
+\label{eq:SC_MKV_2}
+\end{equation}
 
@@
 	\end{equation*} 
-	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from the two equations in (\ref{eq:SC_MFG_MKV_2}) that:
+	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
 	\begin{equation*}
@@
 Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-From the explicit formula for the variance, $h_{var}>0$ and therefore by equation (\ref{eq:SC_MFG_MKV_2}), $SC^{MKV}>0$.
+From the explicit formula for the variance, $h_{var}>0$ and therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
 Therefore, $PoA=1$.
@@
 	\end{equation*}
-	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MFG_MKV_2}), $ \lim_{b_2\to 0} SC^{MKV} >0 $.
+	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), $ \lim_{b_2\to 0} SC^{MKV} >0 $.
 	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
@@
 	\end{IEEEeqnarray*}
-	and using equation (\ref{eq:SC_MFG_MKV_2}), we deduce:
+	and using equation (\ref{eq:SC_MKV_2}), we deduce:
 	\begin{IEEEeqnarray*}{rCl}
@@
     Since $\eta^{0,b_1}_t$ is bounded, $\lim_{b_1 \to 0}v_t=:v_t^{0,b_1}>0,\ \forall t>0$ which is also bounded.
-Using equation (\ref{eq:SC_MFG_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$.
+Using equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$.
 Therefore, $\lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1$.
@@
 We also find $v_t=\mathcal{O}(e^{2b_1})$.
-Therefore with equation (\ref{eq:SC_MFG_MKV_2}) we have:
+Therefore with equation (\ref{eq:SC_MKV_2}) we have:
     \begin{equation*}

### 2018-07-04 PoA.tex
Minor point 10 fixed

@@
 And thus,
-\begin{equation*}
+\begin{equation}
 \bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
-\end{equation*}
-\begin{equation*}
+\label{eq:x_bar_MFG_explicit}
+\end{equation}
+\begin{equation}
 v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
-\end{equation*}
+\label{eq:v_t}
+\end{equation}
 Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
@@
     \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}\left[(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2\right]&=0,\ \forall t \in [0,T] \\
-    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0
+    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
 \end{split}
@@
 \begin{proof}
-	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the associated Riccati equations are well defined under assumption (\ref{eq:assumptions}).
+	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}).
 We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
 	\begin{equation*}
-		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t
+		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
 		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
 	\end{equation*}
-	with coefficients 
+	with coefficients:
 	\begin{equation*}
@@
 	\end{equation*} 
-	Since $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
+	Since $q_T + \bar{q}_T(1-s_T) = \bar{\eta}_T^{MFG}$, $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
 	\begin{equation*}
@@
 			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
-			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}) - \gamma_t\right] dt\\
-			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt
-		\end{split}
-	\end{equation*}
-	where we use the relationship $\dot{\bar{x}}_t = (a^x+a^{\bar{x}}+(a^y+a^{\bar{y}})\bar{\eta}_t)\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}) for the fourth equality.
+			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
+			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
+		\end{split}
+	\end{equation*}
+	where we use equation (\ref{eq:x_bar_MFG}) for the fourth equality.
 
@@
 \begin{proof}
-    By the explicit equation for $\bar{x}_t$ (see Appendix \ref{appendix_solving_fbsdes}), $\bar{x}_0=0$ implies $\bar{x}_t=0,\ \forall t \in [0,T]$.
+    By equation (\ref{eq:x_bar_MFG_explicit}), $\mathbb{E}(\xi)=0$ implies $\bar{x}^{MFG}_t=0,\ \forall t \in [0,T]$.
 Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-From the explicit formula for the variance, $h_{var}>0$ and therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
-Therefore, $PoA=1$.
+From equation (\ref{eq:v_t}), $v_t>0$ which implies $h_{var}>0$.
+Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
+We conclude that $PoA=1$.
 \end{proof}

### 2018-07-04 PoA.tex
small typos

@@
 \begin{equation}
-v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
+v^{MFG}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
 \label{eq:v_t}
@@
 \begin{equation*}
-v_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
+v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
 \end{equation*}
@@
 	\begin{equation*}
-			\lim_{r \to \infty} PoA = 1 \qquad and \qquad
+			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
 			\lim_{\bar{r} \to \infty} PoA = 1.
@@
 	\begin{split}
-	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u}\\
-	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t)
+	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
+	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
 	\end{split}
@@
 	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have
-	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \bar{x}_0 e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
+	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
 	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
@@
 	\end{equation*}
-	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_0 >0$ for $t>0$ and therefore,
+	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
 	\begin{equation*}
@@
 	\begin{equation*}
-	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad and \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
+	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
 	\end{equation*}
@@
 	\begin{split}
-	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &and \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
-	    \lim_{b_1 \to \infty} PoA = 1 \qquad &and \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
+	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
+	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
 	\end{split}
@@
     \begin{equation*}
-        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ and\ \Delta SC^{0,b_1}>0.
+        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ \text{and}\ \Delta SC^{0,b_1}>0.
     \end{equation*}

### 2018-07-06 PoA.tex
small changes

@@
 \begin{split}
-= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
+= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
 &- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
@@
 \begin{split}
-\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
+\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
 &+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
@@
 SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
-& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
+& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
 \end{split}
@@
 \begin{split}
-\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\bar{x}^{MKV}_0)^2 \\
+\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
 &+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
@@
 \begin{equation}
-SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2.
+SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2.
 \label{eq:SC_MKV_2}
@@
 			& SC^{MFG} - SC^{MKV}\\
-			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 \bar{x}_0^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
+			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
 			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
@@
 \begin{equation}
-PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} \bar{x}_0^2}.
+PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} (\mathbb{E}(\xi))^2}.
 \label{eq:PoA_LQ}
@@
 	\begin{equation*}
-		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
+		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
 	\end{equation*}
@@
 \begin{proof}
-    First, we consider $b_2 \to 0$.
-We assume here $\bar{b}_2 \neq 0$.
-Otherwise, if $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$.
-    For $\bar{b}_2 \neq 0$, we have $\lambda \to 0 $ and
+    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
+    As $b_2 \to 0$, we have $\lambda \to 0 $ and
 	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
-
-	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
+	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
 	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
-	This implies that $\bar{x}_t^{MFG} \to \bar{x}_0 \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.
-
-	Since $B^{0,b_2} \neq0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
-Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get
-	\begin{equation*}
-	\begin{split}
-	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }\\
-	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t)
+
+	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.
+
+	Since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
+Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
+	\begin{equation*}
+	\begin{split}
+	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
+	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
 	\end{split}
@@
 	    \lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
-	    \lim_{b_2 \to 0} \Delta SC &>0, \\
-	    \lim_{b_2 \to 0} \Delta SC &< \infty ,
-	\end{split}
-	\end{equation*}
-	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), $ \lim_{b_2\to 0} SC^{MKV} >0 $.
+	    0<&\lim_{b_2 \to 0} \Delta SC < \infty,
+	\end{split}
+	\end{equation*}
+	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ (ToDo: need to justify why it is also finite!).
 	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
@@
 	$ \frac{\delta^\pm_u}{b_2 + \bar{b}_2} \xrightarrow[b_2 \to \infty]{} \pm \sqrt{\frac{ C_u^{\infty,b_2}}{r + \bar{r}(1-\bar{s})^2}}$
-	and  $e^{- (\delta^+_u - \delta^-_u)(T-t)} \to 0$, for $t \in [0,T)$, with equation (\ref{eq:riccati_ut_sol}) we have for $t \in [0,T)$:
+	and therefore,  $e^{- (\delta^+_u - \delta^-_u)(T-t)} \to 0$, for $t \in [0,T)$, with equation (\ref{eq:riccati_ut_sol}) we have for $t \in [0,T)$:
 	$$ (b_2 + \bar{b}_2) u_t = \frac{- \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
@@
 	For large $b_2$ and $t \in [0,T)$, we have:
-	$$ B\cdot u_t = \frac{b_2 + \bar{b}_2}{r+\bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)u_t \sim \sqrt{\frac{q+ \bar{q}(1-s)}{r+ \bar{r}(1-\bar{s})} } (b_2 +\bar{b}_2) = \kappa_u (b_2+ \bar{b}_2).
-$$ Thus, we have the approximation:
-	$$ \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds}\sim \bar{x}_0 e^{ (b_1 + \bar{b}_1 - \kappa_u (b_2+ \bar{b}_2) ) t},\qquad b_2 \to \infty.$$
+	$$ B\cdot u_t = \frac{b_2 + \bar{b}_2}{r+\bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)u_t \sim \sqrt{\frac{q+ \bar{q}(1-s)}{r+ \bar{r}(1-\bar{s})} } (b_2 +\bar{b}_2) =: \kappa_u \cdot (b_2+ \bar{b}_2).
+$$ Thus, from equation (\ref{eq:x_bar_MFG_explicit}) we have the approximation:
+	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds}\sim \mathbb{E}(\xi) e^{ (b_1 + \bar{b}_1 - \kappa_u (b_2+ \bar{b}_2) ) t}$$
 	Similarly, we have for large $b_2$ and $t \in [0,T)$:
-	$$B^{\eta} \cdot \eta_t = \frac{b_2}{r+ \bar{r}} b_2 \eta_t \sim \sqrt{\frac{q + \bar{q}}{r + \bar{r}} } b_2 = \kappa_v b_2,$$
+	$$B^{\eta} \cdot \eta_t = \frac{b_2}{r+ \bar{r}} b_2 \eta_t \sim \sqrt{\frac{q + \bar{q}}{r + \bar{r}} } b_2 =: \kappa_v b_2,$$
 	and:
@@
 		\Delta SC &\sim & \frac{1}{2} (\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \int_0^T (\bar{x}_t^{MFG} )^2 dt \\
-			&=& \frac{(\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \cdot \bar{x}_0^2 }{2 (2b_1 +2\bar{b}_1 - 2 \kappa_u (b_2 + \bar{b}_2) )} \left(  e^{(2b_1 + 2\bar{b}_1 - 2\kappa_u (b_2+ \bar{b}_2) ) T} - 1\right)\\
-			&\sim & \frac{\zeta_1 }{b_2 } e^{- 2 \kappa_u T \cdot b_2 }  + \frac{\zeta_2}{ b_2},
+			&=& \frac{(\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \cdot (\mathbb{E}(\xi))^2 }{2 (2b_1 +2\bar{b}_1 - 2 \kappa_u (b_2 + \bar{b}_2) )} \left(  e^{(2b_1 + 2\bar{b}_1 - 2\kappa_u (b_2+ \bar{b}_2) ) T} - 1\right)\\
+			&\sim & \frac{\zeta_1 }{b_2 } e^{- 2 \kappa_u T b_2 }  + \frac{\zeta_2}{ b_2},
 	\end{IEEEeqnarray*}
@@
 	\begin{IEEEeqnarray*}{rCl}
-		SC^{MKV} &\sim & (q + \bar{q} )  \int_0^T v_t dt + \frac{1}{2}(q_T + \bar{q}_T)v_T + \frac{1}{2}w_0 \bar{x}_0^2\\
-		&\sim& (q + \bar{q}) \left[ \left(\frac{Var(\xi)}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2\kappa_v b_2)^2} \right) e^{2b_1 T - 2 \kappa_v T b_2} - \left( \frac{Var(\xi) + \sigma^2 T}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2 \kappa_v b_2)^2} \right) \right]\\
-		& & + \frac{(q_T + \bar{q}_T)}{2} \left[  Var(\xi) e^{2b_1T - 2\kappa_v T\cdot b_2} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{2b_1 T - 2\kappa_v T\cdot b_2} - 1\right) \right] + \frac{\bar{x}_0^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2) C^w} }{2(b_2 + \bar{b}_2)}\\
-		&\sim & \left( \frac{\zeta_3}{b_2^2} + \frac{\zeta_4}{b_2} + \zeta_5 \right) e^{-2\kappa_v T\cdot b_2}  + \left( \frac{\zeta_6}{b_2^2} + \frac{\zeta_7}{b_2}  \right)
+		SC^{MKV} &\sim & \frac{1}{2}(q + \bar{q} )  \int_0^T v_t dt + \frac{1}{2}(q_T + \bar{q}_T)v_T + \frac{1}{2}w_0 (\mathbb{E}(\xi))^2\\
+		&\sim& \frac{(q + \bar{q})}{2} \left[ \left(\frac{Var(\xi)}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2\kappa_v b_2)^2} \right) e^{2b_1 T - 2 \kappa_v T b_2} - \left( \frac{Var(\xi) + \sigma^2 T}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2 \kappa_v b_2)^2} \right) \right]\\
+		& & + \frac{(q_T + \bar{q}_T)}{2} \left[  Var(\xi) e^{2b_1T - 2\kappa_v Tb_2} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{2b_1 T - 2\kappa_v Tb_2} - 1\right) \right]\\
+		& &+ \frac{(\mathbb{E}(\xi))^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2) C^w} }{2(b_2 + \bar{b}_2)}\\
+		&\sim & \left( \frac{\zeta_3}{b_2^2} + \frac{\zeta_4}{b_2} + \zeta_5 \right) e^{-2\kappa_v Tb_2}  + \left( \frac{\zeta_6}{b_2^2} + \frac{\zeta_7}{b_2}  \right),
 	\end{IEEEeqnarray*}
-	where $(\zeta_i)_{i=1..7}$ are constant w.r.t. $b_2$. In particular
-	$$ \zeta_2 =  \frac{ \left(\sqrt{ \frac{ (r + \bar{r}(1-\bar{s})^2 )( q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } - \sqrt{ q + \bar{q}(1-s)^2 }\right)^2 \cdot \bar{x}_0^2 }{4 \kappa_u },$$
-	and $$\zeta_7 =  \frac{(q+\bar{q}) (Var(\xi) + \sigma^2 T)+ \frac{\sigma^2}{2} (q_T + \bar{q}_T) ) }{2 \kappa_v} + \frac{1}{2}\bar{x}_0^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2)(q + \bar{q}(1-s)^2)}. $$ 
+	where $(\zeta_i)_{i=1,\dots, 7}$ are constant w.r.t. $b_2$. In particular
+	$$ \zeta_2 =  \frac{ \left(\sqrt{ \frac{ (r + \bar{r}(1-\bar{s})^2 )( q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } - \sqrt{ q + \bar{q}(1-s)^2 }\right)^2 \cdot (\mathbb{E}(\xi))^2 }{4 \kappa_u }\geq0,$$
+	and $$\zeta_7 =  \frac{(q+\bar{q}) (Var(\xi) + \sigma^2 T)+ \sigma^2 (q_T + \bar{q}_T) ) }{4 \kappa_v} + \frac{1}{2}(\mathbb{E}(\xi))^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2)(q + \bar{q}(1-s)^2)}>0. $$ 
 	Hence, for large $b_2$ we have:
@@
 	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
    	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
@@
     \begin{split}
-	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 \bar{x}_0^2, \\
+	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 (\mathbb{E}(\xi))^2, \\
 	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
@@
 	Thus, we have $B \cdot u_t = \mathcal{O}\left({\bar{b}_2}^{1/2}\right)$ for $t \in [0,T)$ and 
-	$$ \bar{x}_t^{MFG} = \bar{x}_0 e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
+	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
 	As in the proof of Proposition \ref{prop:b2}, for $t \in [0,T)$:

### 2018-07-06 PoA.tex
major point 5

@@
 
+%Nicolas: major point 5
 \begin{proposition}
@@
 	\begin{equation*}
-			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
+			\lim_{r \to \infty} PoA = 1 \qquad and \qquad
 			\lim_{\bar{r} \to \infty} PoA = 1.
@@
 	\end{equation*}
-	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}).
-The limiting solution $u_t^{\infty,r}$ is given by:
-	\begin{equation*}
-	\begin{split}
-	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
-	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
-	\end{split}
-	\end{equation*}
-	which is bounded for $t \in [0,T]$.
-	Similarly, we have the bounded limiting solutions over $[0,T]$:
-	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
-	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have
-	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
+	% modification Main point 5 (nicolas)
+	Let's $u^{\infty,r}:[0,T] \to \mathbb{R}$ be the solution to a first-order differential equation
+	\begin{equation}
+		\dot{u}^{\infty,r}_t - 2A^u u_t^{\infty,r} + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u
+	\end{equation}
+	when $A^u \neq 0$,
+	or the solution to the equation
+	\begin{equation}
+		\dot{u}^{\infty,r}_t + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u
+	\end{equation}
+	when $A^u = 0$.
+
+	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, with the explicit formula of the solution to the scalar Riccati equation, it is easy to show that the solution $u$ to equation (\ref{eq:riccati_ut}) converges point-wisely to the solution $u^{\infty,r}$ for any fixed time $t\in[0,T]$ when $r$ tends towards infinity (see Appendix \ref{appendix_solving_fbsdes}).
+This limiting solution $u^{\infty,r}$ can be given by the following expressions: for every $t\in [0,T]$
+	\begin{equation*}
+	\begin{split}
+	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u}\\
+	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t)
+	\end{split}.
+	\end{equation*}
+	We can deduce that $u^{\infty,r}$ over $[0,T]$.	Similarly, for any fixed time $t\in [0,T]$, the real solution $w_t$ and $\eta_t$ of the equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) at time $t$ converge towards the solution $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations.
+Namely, for every $t\in [0,T]$,
+	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}$$
+	and the function $w^{\infty,r}$ and $\eta^{\infty,r}$ are bounded over $[0,T]$.
+
+	Moreover, since $\bar{x}_t^{MFG} = \bar{x}_0 \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have
+	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \bar{x}_0 e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
 	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
@@
 	which are also bounded over $t\in[0,T]$.
-	Hence, by the bounded convergence theorem we have
+	Hence, by the bounded convergence theorem again we obtain
 	\begin{equation*}
@@
 	\end{equation*}
-	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
-	\begin{equation*}
-		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
-	\end{equation*}
-	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.
-
-	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we can have $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
+	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_0 >0$ for $t>0$ and therefore,
+	\begin{equation*}
+		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
+	\end{equation*}
+	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce
+	$$ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2} \longrightarrow 0$$ 
+	and thus $\displaystyle \lim_{r \to \infty} PoA = 1$.
+
+	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} := \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we can have $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
 

### 2018-07-06 PoA.tex
major point 5
major point 5

@@
 	\end{equation*}
-	We can deduce that $u^{\infty,r}$ over $[0,T]$.	Similarly, for any fixed time $t\in [0,T]$, the real solution $w_t$ and $\eta_t$ of the equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) at time $t$ converge towards the solution $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations.
+	It is also clear that $u^{\infty,r}$ is bonded over $[0,T]$.
+
+	Similarly, for any fixed time $t\in [0,T]$, the solution $w_t$ and $\eta_t$ to the equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) at time $t$ converge towards the solution $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations.
 Namely, for every $t\in [0,T]$,
@@
 	$$
-	which are also bounded over $t\in[0,T]$.
-	Hence, by the bounded convergence theorem again we obtain
+	The limits $\bar{x}_t^{\infty,r,MFG}$ as well as $v_t^{\infty,r}$ are bounded over $[0,T]$, then by the bounded convergence theorem again we obtain
 	\begin{equation*}
@@
 	\end{equation*}
-	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_0 >0$ for $t>0$ and therefore,
+	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for any $t>0$. Hence,
 	\begin{equation*}
@@
 	\end{equation*}
-	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce
-	$$ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2} \longrightarrow 0$$ 
-	and thus $\displaystyle \lim_{r \to \infty} PoA = 1$.
-
-	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} := \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we can have $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), when $r$ tends towards infinity we have $ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2} \rightarrow 0$	and then $\displaystyle \lim_{r \to \infty} PoA = 1$.
+
+	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} := \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
 

### 2018-07-08 PoA.tex
merged Nicolas edits for major point 5

--- 2018-07-06 PoA.tex
@@
 	\end{equation*}
-	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}).
-The limiting solution $u_t^{\infty,r}$ is given by:
+	% modification Main point 5 (nicolas)
+	If $A^u \neq 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
+	\begin{equation}
+		\dot{u}^{\infty,r}_t - 2A^u u_t^{\infty,r} + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u,
+	\end{equation}
+	or if $A^u = 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ solve:
+	\begin{equation}
+		\dot{u}^{\infty,r}_t + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u.
+	\end{equation}	
+	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u$ to equation (\ref{eq:riccati_ut}) converges pointwise for any $t\in[0,T]$ to the solution $u^{\infty,r}$, as $r \to \infty$.
+This limiting solution $u^{\infty,r}$ can be given by the following expressions: for every $t\in [0,T]$
 	\begin{equation*}
@@
 	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
-	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
-	\end{split}
-	\end{equation*}
-	which is bounded for $t \in [0,T]$.
-	Similarly, we have the bounded limiting solutions over $[0,T]$:
-	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
-	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have
+	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t).
+	\end{split}
+	\end{equation*}
+
+	It is clear that $u^{\infty,r}$ is bounded over $[0,T]$.	Similarly, for any fixed time $t\in [0,T]$, the solutions $w_t$ and $\eta_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations.
+Namely, for every $t\in [0,T]$,
+	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}$$
+	and the functions $w^{\infty,r}$ and $\eta^{\infty,r}$ are bounded over $[0,T]$.
+
+	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have:
 	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
-	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
+	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t,
 	$$
-	which are also bounded over $t\in[0,T]$.
-	Hence, by the bounded convergence theorem we have
+	The limits $\bar{x}_t^{\infty,r,MFG}$ and $v_t^{\infty,r}$ are bounded over $[0,T]$. By the bounded convergence theorem, we obtain:
 	\begin{equation*}
@@
 	\end{equation*}
-	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
+	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$. Hence,
 	\begin{equation*}
@@
 	\end{equation*}
-	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.
-
-	Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}} = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we can have $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), when $r\to \infty$, we have $ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt \rightarrow 0$	and thus, $\displaystyle \lim_{r \to \infty} PoA = 1$.
+Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
 

### 2018-07-09 PoA.tex
change major point 6

@@
 	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
-	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
-	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
+	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $.
+Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
+	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$
 
@@
 
-	Since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
+	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
+	\begin{equation*}
+	\begin{split}
+	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
+	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
+	\end{split}
+	\end{equation*}
+
+	Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
 Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
@@
 	\end{equation*}
-	which are bounded over $[0,T]$. Thus, the limiting variance function $ v_t \to  v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for $t>0$ and $v^{0,b_2}_t$ is bounded.
-	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
-	\begin{equation*}
-	\begin{split}
-	    \lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
-	    0<&\lim_{b_2 \to 0} \Delta SC < \infty,
-	\end{split}
-	\end{equation*}
-	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ (ToDo: need to justify why it is also finite!).
+	which are bounded over $[0,T]$.
+Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
+	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with the equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
+
 	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
 
-	Now, we consider the case when $b_2 \to \infty$. We have $\displaystyle \lambda \to \lambda^{\infty,b_2}:= \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}$
+	Now we consider the case when $b_2 \to \infty$.
+It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
+In order to study the limit of the PoA,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
+
+	For the shake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
+	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
+	\begin{equation*}
+	\begin{array}{rclcrcl}
+	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
+	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
+	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
+	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
+	\end{array}
+	\end{equation*}
 	and 
-	$$ B \to \infty,\ B^{\eta} \to \infty,\ C^u \to C^{\infty,b_2}_u := \lambda^{\infty,b_2}(q+ \bar{q}(1-s)),\ D^u \to D^{\infty,b_2}_u := \lambda^{\infty,b_2}(q_T + \bar{q}_T(1-s_T)).$$
-	Since 
-	$ \frac{\delta^\pm_u}{b_2 + \bar{b}_2} \xrightarrow[b_2 \to \infty]{} \pm \sqrt{\frac{ C_u^{\infty,b_2}}{r + \bar{r}(1-\bar{s})^2}}$
-	and therefore,  $e^{- (\delta^+_u - \delta^-_u)(T-t)} \to 0$, for $t \in [0,T)$, with equation (\ref{eq:riccati_ut_sol}) we have for $t \in [0,T)$:
-	$$ (b_2 + \bar{b}_2) u_t = \frac{- \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
+	\begin{IEEEeqnarray*}{rCl}
+		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
+		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
+		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
+	\end{IEEEeqnarray*}
+
+	Thus, for $b_2$ tends to infinity, we have $$e^{-(\delta_u^+ - \delta_u^-) (T-t)} = e^{-( (2 b_2+\bar{b}_2)\kappa_u (T-t) + \mathcal{O}(b_2^{-1}) }$$
+	which is uniformly bounded over $[0,T]$. Clearly, $e^{-(\delta_u^+ - \delta_u^-) (T-t)} = \mathcal{O}(b_2^{-2}) \to 0$ for $t \in [0, T)$.
+
+	The next step is to give an estimation of $\Delta SC$. To do so, we need to expand the product $B u_t$ up till $b_2^{-2}$. We first notice that for $t \in [0,T)$, 
+	\begin{IEEEeqnarray*}{rCl}
+		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
 \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
 \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
-	{ \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C_u^{\infty,b_2}}.
-	$$
-	Similarly, we have $(b_2+\bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$ and $b_2 \eta_t \to \sqrt{(r + \bar{r}) C^\eta}$ for $t \in [0,T)$.
-
-	The next step is to look at the order of magnitude in terms of $b_2$ for the mean $\bar{x}_t^{MFG}$ and the variance $v_t$.
-	For large $b_2$ and $t \in [0,T)$, we have:
-	$$ B\cdot u_t = \frac{b_2 + \bar{b}_2}{r+\bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)u_t \sim \sqrt{\frac{q+ \bar{q}(1-s)}{r+ \bar{r}(1-\bar{s})} } (b_2 +\bar{b}_2) =: \kappa_u \cdot (b_2+ \bar{b}_2).
-$$ Thus, from equation (\ref{eq:x_bar_MFG_explicit}) we have the approximation:
-	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds}\sim \mathbb{E}(\xi) e^{ (b_1 + \bar{b}_1 - \kappa_u (b_2+ \bar{b}_2) ) t}$$
-	Similarly, we have for large $b_2$ and $t \in [0,T)$:
-	$$B^{\eta} \cdot \eta_t = \frac{b_2}{r+ \bar{r}} b_2 \eta_t \sim \sqrt{\frac{q + \bar{q}}{r + \bar{r}} } b_2 =: \kappa_v b_2,$$
-	and:
-	\begin{equation*}
-		\begin{split}
-		v_t &= Var(\xi) e^{2\int_0^t (b_1 - B^{\eta} \eta_u) du} + \sigma^2 \int_0^t e^{2 \int_s^t (b_1 - B^{\eta} \eta_u) du} ds\\
-		& \sim Var(\xi) e^{(2b_1 - 2\kappa_v b_2)t} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{(2b_1 - 2\kappa_v b_2)t} - 1\right).
-		\end{split}
-	\end{equation*}
-	Hence, using Proposition \ref{prop:diff_SC}, for large $b_2$, we deduce:
+		{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \nonumber \\
+		&=& \frac{ - (\mathcal{O}(b_2^{-1}) + \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \kappa_u + \mathcal{O}(b_2^{-1}) ) + \mathcal{O}(b_2^{-2})}{(\mathcal{O}(b_2^{-1})- \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} ) - \mathcal{O}(b_2^{-2}) } \nonumber \\
+		&=& \zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})
+	\end{IEEEeqnarray*}
+	Then, we can continue do the expansion and obtain
 	\begin{IEEEeqnarray*}{rCl}
-		\Delta SC &\sim & \frac{1}{2} (\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \int_0^T (\bar{x}_t^{MFG} )^2 dt \\
-			&=& \frac{(\sqrt{C^{\infty,b_2} }- \sqrt{C^w})^2 \cdot (\mathbb{E}(\xi))^2 }{2 (2b_1 +2\bar{b}_1 - 2 \kappa_u (b_2 + \bar{b}_2) )} \left(  e^{(2b_1 + 2\bar{b}_1 - 2\kappa_u (b_2+ \bar{b}_2) ) T} - 1\right)\\
-			&\sim & \frac{\zeta_1 }{b_2 } e^{- 2 \kappa_u T b_2 }  + \frac{\zeta_2}{ b_2},
+		&&(b_2 + \bar{b}_2) ( (b_2 + \bar{b}_2) u_t - \zeta_1 \kappa_u ) \nonumber\\
+		&=& \frac{-(C^u + D^u \delta^+_u) + \mathcal{O}(b_2^{-2}) }{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) + \mathcal{O}(b_2^{-2}) } - (b_2 + \bar{b}_2) \zeta_1 \kappa_u \nonumber \\
+		&=& \frac{-\left( C^u + D^u \delta_u^+ + (b_2 + \bar{b}_2) \zeta_1 \kappa_u \left( \frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right) \right) + \mathcal{O}(b_2^{-2})}{  \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right)-  \mathcal{O}(b_2^{-2})} \nonumber \\
+		&=& \frac{  -\left( C^u +\zeta_1 \kappa_u \frac{\delta_u^-}{b_2 + \bar{b}_2} +  D^u (b_2 + \bar{b}_2)(\frac{\delta^+_u}{b_2 + \bar{b}_2} - \kappa_u) \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1}) } \nonumber \\
+		&=& \frac{- \left( \zeta_1 \kappa_u^2 (1 -\frac{\bar{b}_2}{b_2} )  + \zeta_1 \kappa_u (- \kappa_u + (A^u + \frac{\bar{b}_2}{2} \kappa_u) \frac{1}{b_2}) ) + D^u (b_2 + \bar{b}_2) \left[ (A^u - \frac{\bar{b}_2}{2} \kappa_u )\frac{1}{b_2} + \mathcal{O}(b_2^{-2}) \right] \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1})} \nonumber \\
+		&=& \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u ) + \mathcal{O}(b_2^{-1})
 	\end{IEEEeqnarray*}
-	and using equation (\ref{eq:SC_MKV_2}), we deduce:
+	Thus, we have for any given $t \in [0,T)$,
+	\begin{equation*}
+		(b_2+\bar{b}_2)^2 u_t = \zeta_1 \kappa_u (b_2 + \bar{b}_2) + \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u) + h_t(b_2)
+	\end{equation*}
+	where $h_t(b_2) = \mathcal{O}(b_2^{-1})$.
+	Since for any $t \in [0,T)$, $\int_0^t h_s(b_2) ds = \mathcal{O}(b_2^{-1})$ and $B = (b_2+ \bar{b}_2)^2 / \zeta_1$, we deduce that 
+	\begin{equation*}
+	\bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t + \mathcal{O}(b_2^{-1}) }
+	\end{equation*}
+	which tends uniformly to $0$ over $[0,T)$ as $b_2 \to \infty$.
+	Moreover, since 
+	\begin{equation*}
+	\begin{split}
+		(b_2 + \bar{b}_2) (u_t - w_t) 
+	= (\zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})) - (\sqrt{\zeta_1 (q+\bar{q}(1-s)^2)} + \mathcal{O}(b_2^{-1}) )\\
+	= \sqrt{\zeta_1} (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})
+	\end{split}
+	\end{equation*}
+	Thus
 	\begin{IEEEeqnarray*}{rCl}
-		SC^{MKV} &\sim & \frac{1}{2}(q + \bar{q} )  \int_0^T v_t dt + \frac{1}{2}(q_T + \bar{q}_T)v_T + \frac{1}{2}w_0 (\mathbb{E}(\xi))^2\\
-		&\sim& \frac{(q + \bar{q})}{2} \left[ \left(\frac{Var(\xi)}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2\kappa_v b_2)^2} \right) e^{2b_1 T - 2 \kappa_v T b_2} - \left( \frac{Var(\xi) + \sigma^2 T}{2b_1 - 2\kappa_v b_2} + \frac{\sigma^2}{(2b_1 - 2 \kappa_v b_2)^2} \right) \right]\\
-		& & + \frac{(q_T + \bar{q}_T)}{2} \left[  Var(\xi) e^{2b_1T - 2\kappa_v Tb_2} + \frac{\sigma^2}{2b_1 - 2\kappa_v b_2} \left(e^{2b_1 T - 2\kappa_v Tb_2} - 1\right) \right]\\
-		& &+ \frac{(\mathbb{E}(\xi))^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2) C^w} }{2(b_2 + \bar{b}_2)}\\
-		&\sim & \left( \frac{\zeta_3}{b_2^2} + \frac{\zeta_4}{b_2} + \zeta_5 \right) e^{-2\kappa_v Tb_2}  + \left( \frac{\zeta_6}{b_2^2} + \frac{\zeta_7}{b_2}  \right),
+		\Delta SC &=& \frac{1}{2} \frac{(b_2+\bar{b}_2)^2}{\zeta_1} \int_0^T (u_t - w_t)^2 (\bar{x}_t^{MFG})^2 dt \\
+		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 .
+e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
+		&=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
+		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right].
+e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
 	\end{IEEEeqnarray*}
-	where $(\zeta_i)_{i=1,\dots, 7}$ are constant w.r.t. $b_2$. In particular
-	$$ \zeta_2 =  \frac{ \left(\sqrt{ \frac{ (r + \bar{r}(1-\bar{s})^2 )( q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } - \sqrt{ q + \bar{q}(1-s)^2 }\right)^2 \cdot (\mathbb{E}(\xi))^2 }{4 \kappa_u }\geq0,$$
-	and $$\zeta_7 =  \frac{(q+\bar{q}) (Var(\xi) + \sigma^2 T)+ \sigma^2 (q_T + \bar{q}_T) ) }{4 \kappa_v} + \frac{1}{2}(\mathbb{E}(\xi))^2 \sqrt{(r+ \bar{r}(1-\bar{s})^2)(q + \bar{q}(1-s)^2)}>0. $$ 
-	Hence, for large $b_2$ we have:
-	\begin{equation*}
-		\frac{\Delta SC}{SC^{MKV}} \sim \zeta_2 \zeta_7  .
-	\end{equation*}
-	Therefore, if $\zeta_2 \neq 0$, namely:
-	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	then we deduce:
+
+	For the first term, a direct computation yields that
+	\begin{equation*}
+	\begin{array}{rl}
+	&\frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
+	=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
+	=& \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
+	\end{array}
+	\end{equation*}
+	For the second term, we know that 
+	$$ \vert e^{-2\int_0^t h_s(b_2) ds} - 1 \vert \leq \vert e^{ \mathcal{O}(b_2^{-1}) } -1 \vert = \mathcal{O}(b_2^{-1}).$$
+	Together with the estimation of the first term above, we have 
+	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right].
+e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
+	Hence, we deduce that
+	\begin{equation}
+		\Delta SC = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2}).
+	\end{equation}
+
+	Similarly, we can have $SC^{MKV} =  \frac{\zeta_2}{b_2} + \mathcal{O}(b_2^{-2})$
+	for some constant $\zeta_2 \neq 0$. Thus,
+	\begin{equation}
+		\frac{\Delta SC}{SC^{MKV}} = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{\zeta_2} + \mathcal{O}(b_2^{-1})
+	\end{equation}
+	Therefore, if $ \zeta_1 \kappa_u^2 \neq q + \bar{q}(1-s)^2$, i.e.
+	$$\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
+	we have
 	$$ \lim_{b_2 \to \infty} PoA =: PoA^{\infty,b_2} > 1;$$
 	otherwise $$ \lim_{b_2 \to \infty} PoA = 1.$$
+
 \end{proof}

### 2018-07-09 PoA.tex
small changes

--- 2018-07-08 PoA.tex
@@
 
-	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have:
+	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$:
 	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
@@
 	\begin{equation*}
-		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
+		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty,
+	\end{equation*}
+	and thus,
+	\begin{equation*}
+	\lim_{r \to \infty} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = 0.
 	\end{equation*}
@@
 	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), when $r\to \infty$, we have $ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt \rightarrow 0$	and thus, $\displaystyle \lim_{r \to \infty} PoA = 1$.
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$.
 Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
@@
 	\end{equation*}
-	whereas if $\bar{b}_2 \neq 0$, then:
+	whereas if $\bar{b}_2 > 0$, then:
 	\begin{equation*}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1\neq 0$, then 
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, then 
 	\begin{equation*}
@@
 	and 
-	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \neq 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
+	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} > 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
 	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold.
 Let's denote the limiting solutions by
-	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
+	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit: (ToDo reference equation)
    	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 

### 2018-07-09 PoA.tex
test hello

--- 2018-07-09 PoA.tex
@@
 	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.
+Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
 
@@
 
-	Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
 	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
@@
 
-	For the shake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
+	For the sake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
 	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
@@
 
+hello
+
 \end{document}

### 2018-07-11 PoA.tex
hello from Christy
proposition 3

@@
 
+% proposition r infinity
 \begin{proposition}
@@
 \begin{proof}
-	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions for the scalar Riccati equations associated with $u_t$, $w_t$ and $\eta_t$.
-
-	When $r \to \infty$ we have
-	\begin{equation*}
-		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
+	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions to the scalar Riccati equations associated with $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ for every given $r >0$.
+The superscript $r$ here indicates the dependence on this coefficient because we intend to study the behavior of these solutions in the asymptotic regime.
+
+	When $r \to \infty$, we have
+	\begin{equation*}
+		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2}
 	\end{equation*}
@@
 	\begin{equation*}
-		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
-	\end{equation*}
+	\begin{array}{l}
+		B^r \longrightarrow 0,\quad \ B^{\eta,r} \longrightarrow 0,\\
+		C^{u,r} \longrightarrow C_u^{r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D_u^{r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
+	\end{array}
+	\end{equation*}
+
+	In order to show that the $PoA$ tends to $1$, we can indeed show that $\Delta SC^{r}$ tends towards $0$ while $SC^{r, MKV} >0$ in the asymptotic regime.
+From the equation (\ref{eq:PoA_LQ}), a sufficient condition is to demonstrate that $\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt$ is finite and the variance function $v^r_t$ is strictly positive in the asymptotic regime.\\
+
 	% modification Main point 5 (nicolas)
-	If $A^u \neq 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
-	\begin{equation}
-		\dot{u}^{\infty,r}_t - 2A^u u_t^{\infty,r} + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u,
-	\end{equation}
-	or if $A^u = 0$, let $u^{\infty,r}:[0,T] \to \mathbb{R}$ solve:
-	\begin{equation}
-		\dot{u}^{\infty,r}_t + C^{\infty,r}_u = 0, \qquad u_T^{\infty,r} = D^{\infty,r}_u.
-	\end{equation}	
-	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u$ to equation (\ref{eq:riccati_ut}) converges pointwise for any $t\in[0,T]$ to the solution $u^{\infty,r}$, as $r \to \infty$.
-This limiting solution $u^{\infty,r}$ can be given by the following expressions: for every $t\in [0,T]$
-	\begin{equation*}
-	\begin{split}
-	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
-	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t).
-	\end{split}
-	\end{equation*}
-
-	It is clear that $u^{\infty,r}$ is bounded over $[0,T]$.	Similarly, for any fixed time $t\in [0,T]$, the solutions $w_t$ and $\eta_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{\infty,r}_t$ and $\eta_t^{\infty,r}$ of some first-order differential equations.
+	If $A^u \neq 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
+	\begin{equation}
+		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u,
+	\end{equation}
+	or if $A^u = 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ solve:
+	\begin{equation}
+		\dot{\left(u^{r\to \infty}_t\right)} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
+	\end{equation}	
+	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u^r$ to equation (\ref{eq:riccati_ut}) converges pointwise for every time $t\in [0,T]$ to the solution $u^{r \to \infty}$ as long as $r \to \infty$.
+This limiting solution $u^{r \to \infty}$ can be given by the following expressions: for every $t\in [0,T]$
+	\begin{equation*}
+	\begin{split}
+	    \text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
+	    \text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
+	\end{split}
+	\end{equation*}
+
+	From the formula (\ref{eq:riccati_ut}), we can bound the solution $u^r$ uniformly over $[0,T]$ for large enough $r$.
+More precisely, under assumption (\ref{eq:assumptions}), we have $B^r>0, C^{u,r}>0, D^{u,r}>0$, and $\delta^{+,r}_u > 0 > \delta^{-,r}_u$.
+In the asymptotic regime, we have $\lambda^{r\to \infty} >0$, $C^{r \to \infty}_u >0$ and $D^{r \to \infty}_u \geq 0$.
+Thus, for $r$ large enough, there exists a constant $\zeta > 0 $ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \zeta$.
+We also observe the following two inequalities when $A^u \neq 0$:
+	\begin{IEEEeqnarray*}{rl}
+		&\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
+		=& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
+		< & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
+		= & C^{u,r} + D^{u,r} 2 \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
+		\leq&  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  
+	\end{IEEEeqnarray*}
+	and 
+	\begin{IEEEeqnarray*}{rl}
+		& \left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
+		= & D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
+		\geq & \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
+		= & \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
+		\geq & \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
+		> & 0
+	\end{IEEEeqnarray*}
+
+	Thus, for $A^u \neq 0$, we can deduce that for $r$ large enough, for every $t \in [0,T]$
+	\begin{IEEEeqnarray}{rCl}
+		\vert u_t^{r} \vert  &=& \frac{\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
+		& < & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{ \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\} }  \nonumber \\
+		& \leq & \min \{ \kappa, \kappa e^{\kappa (T-t)} \}  \nonumber \\
+		&\leq & \kappa e^{\kappa T}
+	\end{IEEEeqnarray}
+	where the constant $\kappa >0$ is given by
+	\begin{equation}
+		\kappa = \left\{
+			\begin{array}{ll}
+				\frac{\zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}}{A^u + \vert A^u \vert}, & if \quad A^u > 0 \\
+				\max\left\{ \frac{\zeta + 2 \zeta \sqrt{(A^u)^2+ \zeta^2} }{ -A^u + \vert A_u \vert }, 2 \sqrt{ (A^u)^2 + \zeta^2 } \right\} & if \quad A^u < 0
+			\end{array}
+		\right.
+	\end{equation}
+	Thus, 
+	Since $\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B^r \cdot u^r_s)ds)$,  by bounded convergence theorem we have for every $t \in [0,T]$,
+	\begin{equation*}
+		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG},
+	\end{equation*}
+	and moreover for $r$ large enough, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $[0,T]$, i.e. 
+	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}[\xi] \vert e^{ (\vert{b_1} + \vert{\bar{b}_1} + \zeta \kappa e^{\kappa T} ) T }, \quad t \in [0,T]. $$
+
+	Similarly, for any fixed time $t\in [0,T]$, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some first-order differential equations.
 Namely, for every $t\in [0,T]$,
-	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}$$
-	and the functions $w^{\infty,r}$ and $\eta^{\infty,r}$ are bounded over $[0,T]$.
-
-	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$:
-	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
-	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t,
+	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty}$$
+	and the functions $w^{r}$ and $\eta^{r}$ are uniformly bounded over $[0,T]$ for $r$ large enough.
+
+	Again, by the bounded convergence theorem we have for every $t \in [0,T]$
+	\begin{equation*}
+	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{r\to \infty,MFG})^2 dt \  < \infty,
+	\end{equation*}
+	and thus
+	\begin{equation*}
+	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
+	\end{equation*}
+
+	%---------------------------
+	Also, since $v^r_t = Var(\xi)\exp(2\int_0^t (b_1 - B^{\eta,r} \eta^r_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^{\eta,r} \eta^r_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$:
+	$$	v^r_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t,
 	$$
-	The limits $\bar{x}_t^{\infty,r,MFG}$ and $v_t^{\infty,r}$ are bounded over $[0,T]$. By the bounded convergence theorem, we obtain:
-	\begin{equation*}
-		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty,
-	\end{equation*}
-	and thus,
-	\begin{equation*}
-	\lim_{r \to \infty} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = 0.
-	\end{equation*}
-	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$. Hence,
-	\begin{equation*}
-		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
+	The variance function $v_t^{r}$ is also uniformly bounded over $[0,T]$ for $r$ large enough.	It can be shown that $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	\begin{equation*}
+		\lim_{r \to \infty} SC^{MKV} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
 	\end{equation*}
 	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$.
-Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
+Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
 
@@
 
+% proposition b_2
 \begin{proposition}
@@
 
-hello
-
 \end{document}

### 2018-07-13 PoA_response_to_referee.tex
added template for response to referee

\documentclass[]{article}

%opening
\title{Response to Referee}
\author{}

\begin{document}

\maketitle

We would like to thank the reviewer for their remarks. We have addressed each of their points as follows:

Main Points:
\begin{enumerate}
	\item 
\end{enumerate}

Minor Points:
\begin{enumerate}
	\item 
\end{enumerate}

In addition to the suggested revisions, we have also made the following minor modifications:
\begin{enumerate}
	\item 
\end{enumerate}

\end{document}

### 2018-07-14 PoA.tex
editing proposition 3

@@
 And thus,
-\begin{equation*}
+\begin{equation}
 \bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
-\end{equation*}
-\begin{equation*}
+\label{eq:x_bar_MKV}
+\end{equation}
+\begin{equation}
 v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
-\end{equation*}
+\label{eq:v_t_MKV}
+\end{equation}
 Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
@@
 Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-From equation (\ref{eq:v_t}), $v_t>0$ which implies $h_{var}>0$.
+From equation (\ref{eq:v_t}), which we recall is equivalent to equation (\ref{eq:v_t_MKV}), $v_t>0$ which implies $h_{var}>0$.
 Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
@@
 
+To make the following computations easier to follow, we repeat equations (\ref{eq:PoA_LQ}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations:
+\begin{equation}
+PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2}.
+\label{eq:PoA_LQ_new_notation}
+\end{equation}
+\begin{equation}
+\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds},
+\label{eq:x_bar_MFG_explicit_new_notation}
+\end{equation}
+\begin{equation}
+v_t=Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds.
+\label{eq:v_t_new_notation}
+\end{equation}
+
 % proposition r infinity
@@
 \begin{proof}
-	When assumption $(\ref{eq:assumptions})$ is satisfied, we have the existence and uniqueness of solutions to the scalar Riccati equations associated with $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ for every given $r >0$.
-The superscript $r$ here indicates the dependence on this coefficient because we intend to study the behavior of these solutions in the asymptotic regime.
-
-	When $r \to \infty$, we have
-	\begin{equation*}
-		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2}
+	First, we consider $r \to \infty$.
+When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
+Note that we have added the superscript $r$ to emphasize the dependence on this coefficient.
+
+	When $r \to \infty$, we have:
+	\begin{equation*}
+		\lambda^r \longrightarrow \lambda^{r\to\infty} := \frac{b_2}{b_2 + \bar{b}_2},
 	\end{equation*}
@@
 
-	In order to show that the $PoA$ tends to $1$, we can indeed show that $\Delta SC^{r}$ tends towards $0$ while $SC^{r, MKV} >0$ in the asymptotic regime.
-From the equation (\ref{eq:PoA_LQ}), a sufficient condition is to demonstrate that $\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt$ is finite and the variance function $v^r_t$ is strictly positive in the asymptotic regime.\\
+	In order to show that $\lim_{r \to \infty} PoA^r = 1$, it suffices to show that $\lim_{r \to \infty}\Delta SC^{r} = 0$ while $\lim_{r \to \infty} SC^{r, MKV} >0$.
+From equation (\ref{eq:PoA_LQ_new_notation}), a sufficient condition is to demonstrate that $\lim_{r \to \infty}\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt<\infty$, $\lim_{r \to \infty}v^r_T>0$, and $\lim_{r \to \infty}w^r_0>0$.\\
 
 	% modification Main point 5 (nicolas)
-	If $A^u \neq 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
-	\begin{equation}
-		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u,
-	\end{equation}
-	or if $A^u = 0$, let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ solve:
-	\begin{equation}
-		\dot{\left(u^{r\to \infty}_t\right)} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
-	\end{equation}	
-	Since assumption (\ref{eq:assumptions}) holds for arbitrarily large $r$, from the explicit formula of the solution to the scalar Riccati equation (see Appendix \ref{appendix_solving_fbsdes} equation (\ref{eq:riccati_ut_sol_app})), it is easy to show that the solution $u^r$ to equation (\ref{eq:riccati_ut}) converges pointwise for every time $t\in [0,T]$ to the solution $u^{r \to \infty}$ as long as $r \to \infty$.
-This limiting solution $u^{r \to \infty}$ can be given by the following expressions: for every $t\in [0,T]$
+	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
+	\begin{equation}
+		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
+	\end{equation}
+	Then we have:
 	\begin{equation*}
@@
 	\end{equation*}
+	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$.
 
@@
 Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
-	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with the equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
+	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
 
@@
 It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
-In order to study the limit of the PoA,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
+In order to study the limit of $PoA$,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
 

### 2018-07-14 PoA.tex
continuing to edit proposition 3

@@
 &\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
-=& - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
+&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
 \end{split}
@@
 			& SC^{MFG} - SC^{MKV}\\
-			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
-			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
-			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
-			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
-			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
+			&= \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
+			&= \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
+			&= \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
+			&= \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
+			&= \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
 		\end{split}
@@
 \begin{equation}
-		u_t= \frac{-(C^u+D^u \delta^+_u) + (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(\delta^-_u - D^u B^u) - (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
+		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
 	\label{eq:riccati_ut_sol}
@@
 When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
-Note that we have added the superscript $r$ to emphasize the dependence on this coefficient.
+Note that we have added the superscript $r$ to emphasize the dependence on this parameter.
 
@@
 	\end{equation*}
-	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$.
-
-	From the formula (\ref{eq:riccati_ut}), we can bound the solution $u^r$ uniformly over $[0,T]$ for large enough $r$.
-More precisely, under assumption (\ref{eq:assumptions}), we have $B^r>0, C^{u,r}>0, D^{u,r}>0$, and $\delta^{+,r}_u > 0 > \delta^{-,r}_u$.
-In the asymptotic regime, we have $\lambda^{r\to \infty} >0$, $C^{r \to \infty}_u >0$ and $D^{r \to \infty}_u \geq 0$.
-Thus, for $r$ large enough, there exists a constant $\zeta > 0 $ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \zeta$.
-We also observe the following two inequalities when $A^u \neq 0$:
+	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
+
+	Note that $B^r, C^{u,r}, \lambda^{r\to \infty}, C^{r \to \infty}_u>0$, $D^{u,r} , D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+Let $\epsilon>0$.
+Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
+When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$:
 	\begin{IEEEeqnarray*}{rl}
-		&\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
-		=& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
-		< & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
-		= & C^{u,r} + D^{u,r} 2 \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
-		\leq&  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  
+		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
+		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
+		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
+		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
+		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
+		&< \infty,
 	\end{IEEEeqnarray*}
@@
 	\begin{IEEEeqnarray*}{rl}
-		& \left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
-		= & D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
-		\geq & \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
-		= & \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
-		\geq & \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
-		> & 0
+		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
+		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
+		&\geq \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
+		&\geq  \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
+		&=  \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
+		&\geq  \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
+		&>  0
 	\end{IEEEeqnarray*}
@@
 	&\frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
-	=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
-	=& \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
+	&= \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
+	&= \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
 	\end{array}
@@
 \begin{equation}
-		\rho_t= \frac{-(C+D \delta^+) + (C+D \delta^-) e^{-(\delta^+ - \delta^-)(T-t)}}{(\delta^- - D B) - (\delta^+ - D B) e^{-(\delta^+ - \delta^-)(T-t)}}
+		\rho_t= \frac{(C+D \delta^+) - (C+D \delta^-) e^{-(\delta^+ - \delta^-)(T-t)}}{(-\delta^- + D B) + (\delta^+ - D B) e^{-(\delta^+ - \delta^-)(T-t)}}
 	\label{eq:riccati_ut_sol_app}

### 2018-07-14 PoA.tex
continuing to edit proposition 3 still

@@
 	\begin{equation*}
-		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
+		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2}\cdot \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
 	\end{equation*}
@@
 			&= \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
-			&= \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
+			&= \frac{1}{2}\cdot \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
 		\end{split}
@@
 \begin{equation}
-PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2}.
+PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
 \label{eq:PoA_LQ_new_notation}
@@
 	\end{equation*}
-	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$. Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
-
-	Note that $B^r, C^{u,r}, \lambda^{r\to \infty}, C^{r \to \infty}_u>0$, $D^{u,r} , D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
+Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
+
+	Note that  $A^u \leq 0$, $B^r, C^{u,r}, \lambda^{r\to \infty}, C^{r \to \infty}_u>0$, $D^{u,r} , D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
 Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
-When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$:
+When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
 	\begin{IEEEeqnarray*}{rl}
@@
 		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
-		&\geq \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
-		&\geq  \max \left\{ - \delta^{-,r}_u , \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
-		&=  \max \left\{ A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } , (-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \right\} \\
-		&\geq  \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\}\\
-		&>  0
+		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
+		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
+		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + \zeta^2}}\\
+		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
+		&>  0.
 	\end{IEEEeqnarray*}
-
-	Thus, for $A^u \neq 0$, we can deduce that for $r$ large enough, for every $t \in [0,T]$
+	Thus, for $A^u \neq 0$, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
 	\begin{IEEEeqnarray}{rCl}
-		\vert u_t^{r} \vert  &=& \frac{\left\vert -(C^{u,r} + D^{u,r} \delta^{+,r}_u) + (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( \delta^{-,r}_u - D^{u,r} B^{r} ) - (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
-		& < & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{ \max \left\{ A^u + \vert A^u \vert, (-A^u + \vert A_u \vert) e^{-2 \sqrt{(A^u)^2 + \zeta^2} (T-t) } \right\} }  \nonumber \\
-		& \leq & \min \{ \kappa, \kappa e^{\kappa (T-t)} \}  \nonumber \\
-		&\leq & \kappa e^{\kappa T}
+		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
+		& \leq & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } \nonumber \\
+		&=:&\kappa.  \nonumber
 	\end{IEEEeqnarray}
-	where the constant $\kappa >0$ is given by
-	\begin{equation}
-		\kappa = \left\{
-			\begin{array}{ll}
-				\frac{\zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}}{A^u + \vert A^u \vert}, & if \quad A^u > 0 \\
-				\max\left\{ \frac{\zeta + 2 \zeta \sqrt{(A^u)^2+ \zeta^2} }{ -A^u + \vert A_u \vert }, 2 \sqrt{ (A^u)^2 + \zeta^2 } \right\} & if \quad A^u < 0
-			\end{array}
-		\right.
-	\end{equation}
-	Thus, 
-	Since $\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B^r \cdot u^r_s)ds)$,  by bounded convergence theorem we have for every $t \in [0,T]$,
-	\begin{equation*}
-		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG},
-	\end{equation*}
-	and moreover for $r$ large enough, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $[0,T]$, i.e. 
-	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}[\xi] \vert e^{ (\vert{b_1} + \vert{\bar{b}_1} + \zeta \kappa e^{\kappa T} ) T }, \quad t \in [0,T]. $$
-
-	Similarly, for any fixed time $t\in [0,T]$, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some first-order differential equations.
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+	\begin{equation*}
+		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
+	\end{equation*}
+	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
+	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad t \in [0,T]. $$
+
+	Similarly, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some first-order differential equations.
 Namely, for every $t\in [0,T]$,
 	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty}$$
-	and the functions $w^{r}$ and $\eta^{r}$ are uniformly bounded over $[0,T]$ for $r$ large enough.
-
-	Again, by the bounded convergence theorem we have for every $t \in [0,T]$
+	and the functions $w^{r}$ and $\eta^{r}$ are uniformly bounded over $t \in[0,T]$ and large $r$.
+
+	Again, by the bounded convergence theorem we have for every $t \in [0,T]$:
 	\begin{equation*}
@@
 	\end{equation*}
-	and thus
-	\begin{equation*}
-	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
+	and thus,
+	\begin{equation*}
+	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
 	\end{equation*}

### 2018-07-15 PoA.tex
almost finished editing proposition 3

@@
 	In order to show that $\lim_{r \to \infty} PoA^r = 1$, it suffices to show that $\lim_{r \to \infty}\Delta SC^{r} = 0$ while $\lim_{r \to \infty} SC^{r, MKV} >0$.
-From equation (\ref{eq:PoA_LQ_new_notation}), a sufficient condition is to demonstrate that $\lim_{r \to \infty}\int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG} )^2 dt<\infty$, $\lim_{r \to \infty}v^r_T>0$, and $\lim_{r \to \infty}w^r_0>0$.\\
 
@@
 
-	Note that  $A^u \leq 0$, $B^r, C^{u,r}, \lambda^{r\to \infty}, C^{r \to \infty}_u>0$, $D^{u,r} , D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that  $A^u \leq 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
@@
 Namely, for every $t\in [0,T]$,
-	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty}$$
-	and the functions $w^{r}$ and $\eta^{r}$ are uniformly bounded over $t \in[0,T]$ and large $r$.
+	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty},$$
+	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$.
 
@@
 	%---------------------------
-	Also, since $v^r_t = Var(\xi)\exp(2\int_0^t (b_1 - B^{\eta,r} \eta^r_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^{\eta,r} \eta^r_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$:
-	$$	v^r_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t,
+	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
+	$$	v^r_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $[0,T]$ for $r$ large enough.	It can be shown that $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	It can be shown that $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
 	\begin{equation*}

### 2018-07-15 PoA.tex
Proposition 3 is completely finished

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}),
+	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
 	\begin{equation*}
@@
 	\begin{equation*}
-	\begin{split}
-	\text{when } A^u \neq 0,\qquad & u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u},\\
-	\text{when } A^u = 0, \qquad & u_t^{r \to \infty} = D^{r \to \infty}_u + C^{r \to \infty}_u (T-t).
-	\end{split}
+	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
 	\end{equation*}
@@
 
-	Note that  $A^u \leq 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
 Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
-When $A^u \neq 0$, we have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
+We have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
 	\begin{IEEEeqnarray*}{rl}
@@
 	\end{IEEEeqnarray*}
-	Thus, for $A^u \neq 0$, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
+	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
 	\begin{IEEEeqnarray}{rCl}

### 2018-07-15 PoA.tex
finished with first half of proposition 5

@@
 	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}).
-We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
+We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following linear first-order differential equation:
 	\begin{equation*}
@@
 \begin{equation}
-PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
+PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle B\int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
 \label{eq:PoA_LQ_new_notation}
@@
 
-	In order to show that $\lim_{r \to \infty} PoA^r = 1$, it suffices to show that $\lim_{r \to \infty}\Delta SC^{r} = 0$ while $\lim_{r \to \infty} SC^{r, MKV} >0$.
-
 	% modification Main point 5 (nicolas)
-	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the first-order differential equation:
+	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
 	\begin{equation}
@@
 Let $\epsilon>0$.
-Then there exists $r^*>0$ such that for $r \geq r^*$, we have $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
-We have the following two inequalities for $r \geq r^*$ and $\forall t \in [0,T]$:
+Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
+We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
 	\begin{IEEEeqnarray*}{rl}
@@
 	\begin{equation*}
-		\bar{x}_t^{r,MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
+		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
 	\end{equation*}
 	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
-	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad t \in [0,T]. $$
-
-	Similarly, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some first-order differential equations.
+	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
+
+	Similarly, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some linear first-order differential equations.
 Namely, for every $t\in [0,T]$,
-	$$w^r_t \xrightarrow[r \to \infty]{} w_t^{r\to \infty},\qquad \eta^r_t \xrightarrow[r \to \infty]{} \eta_t^{r\to \infty},$$
+	$$\lim_{r\to \infty}w^r_t = w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t = \eta_t^{r\to \infty},$$
 	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$.
@@
 	\begin{equation*}
-	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
+	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
 	\end{equation*}
@@
 	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
-	$$	v^r_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
+	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	It can be shown that $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
 	\begin{equation*}
@@
 	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$.
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$.
 Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
@@
 
-	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
+	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
 
@@
 	\begin{equation*}
-	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
+	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
 	\end{equation*}
@@
 \begin{proof}
-	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
+	First, we consider $\bar{b}_2 \to 0$.
+When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
+Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.
+
+	When $\bar{b}_2 \to 0$, we have:
+	$$\displaystyle \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})},$$
 	and 
-	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} > 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
-	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold.
-Let's denote the limiting solutions by
-	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit: (ToDo reference equation)
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
-   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
-   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
-	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
+	$$B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\ C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,$$
+	$$D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0.$$
+
+	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
+	\begin{equation}
+	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
+	\end{equation}
+	which we recall has an explicit solution.
+It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
+Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$.
+
+	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$.
+Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:\zeta$.
+We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
+		\begin{IEEEeqnarray*}{rl}
+			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
+			&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
+			&< \infty,
+		\end{IEEEeqnarray*}
+		and 
+		\begin{IEEEeqnarray*}{rl}
+			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
+			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
+			&>  0.
+		\end{IEEEeqnarray*}
+		Thus, we can deduce that:
+		\begin{IEEEeqnarray}{rCl}
+			\vert u_t^{\bar{b}_2} \vert  &\leq& \kappa,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
+		\end{IEEEeqnarray}
+	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.
+
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t.$$
+	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
+	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+
+   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
+Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce:
+	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0.
+$$
 	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
-By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
-	\begin{equation*}
-    \begin{split}
-	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 (\mathbb{E}(\xi))^2, \\
-	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
-	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
-    \end{split}
+It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
+	\begin{equation*}
+	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
 	\end{equation*}
 	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$
+	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2 \to 0} > 1. $$
 
@@
 
-	Furthermore, if $B \to 0$ and $A\neq 0$, we can deduce that the limiting solution of the scalar Riccati equation coincides with the first-order differential equation:
+	Furthermore, if $B \to 0$ and $A\neq 0$, we can deduce that the limiting solution of the scalar Riccati equation coincides with the linear first-order differential equation:
 	\begin{equation*}
@@
 
-	If $B \to 0$ and $A = 0$, the limiting solution of the scalar Riccati equation coincides with the first-order differential equation:
+	If $B \to 0$ and $A = 0$, the limiting solution of the scalar Riccati equation coincides with the linear first-order differential equation:
 	\begin{equation*}

### 2018-07-15 PoA.tex
just starting second half of proposition 5

@@
 	First, we consider $r \to \infty$.
-When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
+For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
 Note that we have added the superscript $r$ to emphasize the dependence on this parameter.
@@
 	First, we consider $\bar{b}_2 \to 0$.
-When assumption $(\ref{eq:assumptions})$ is satisfied, for every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
+For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
 Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.
@@
 
-	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda \to 0$
-	and $B \to \infty,\ C^u \to 0,\ D^u \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
-	$$ \lambda = \mathcal{O}(\bar{b}^{-1}_2),\ C^u = \mathcal{O}(\bar{b}_2^{-1}),\ D^u = \mathcal{O}(\bar{b}_2^{-1}),\ B = \mathcal{O}(\bar{b}_2^2),$$
+	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
+	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
+	$$ \lambda^{\bar{b}_2} = \mathcal{O}(\bar{b}^{-1}_2),\ B^{\bar{b}_2} = \mathcal{O}(\bar{b}_2^2),\ C^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),\ D^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),$$
 	and 
-	$$ \frac{\delta^\pm_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\infty,\bar{b}_2}.$$
+	$$ \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty}.$$
 	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:

### 2018-07-16 PoA.tex
editing second half of proposition 5

@@
 Since we require $\bar{\nu}_t$ to be equal to $\mathbb{E}(\alpha_t)$ throughout the optimization, it is not sufficient to minimize the Hamiltonian with respect to the $\alpha$ input alone in order to guarantee optimality.
-A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{cite_todo}.
+A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{carmona_acciaio}.
 Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
@@
 Let $\epsilon>0$.
-Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$.
+Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$.
 We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
@@
 		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
-		&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
+		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
 		&< \infty,
@@
 		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + \zeta^2}}\\
-		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
+		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
+		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
 		&>  0.
@@
 		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
-		& \leq & \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } \nonumber \\
-		&=:&\kappa.  \nonumber
+		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
+		&=:&c_2.  \nonumber
 	\end{IEEEeqnarray}
@@
 	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
-	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
+	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
 
@@
 	\begin{equation*}
-		\lim_{r \to \infty} SC^{MKV} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
-	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$.
-Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.
+		\lim_{r \to \infty} SC^{MKV,r} = \frac{1}{2} \left( \int_0^T (q+\bar{q}) v^{r \to \infty}_t dt + (q_T + \bar{q}_T) v^{r\to \infty}_T + w^{r \to \infty}_0 (\mathbb{E}(\xi))^2 \right)  >0.
+	\end{equation*}
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$.
+Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.
 
@@
 	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$.
-Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:\zeta$.
+Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
 We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
@@
 			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
-			&\leq  \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2} \\
+			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
 			&< \infty,
@@
 			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
-			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} }\\
+			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
 			&>  0.
@@
 		\begin{IEEEeqnarray}{rCl}
-			\vert u_t^{\bar{b}_2} \vert  &\leq& \kappa,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
+			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
 		\end{IEEEeqnarray}
@@
 	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
-	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + \zeta \kappa) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
 
@@
 Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0.
+	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0.
 $$
@@
 	\begin{equation*}
-	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
+	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
 	\end{equation*}
 	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2 \to 0} > 1. $$
+	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
 
 	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
-	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. Moreover, if we consider the magnitude w.r.t. $\bar{b}_2$, we have:
-	$$ \lambda^{\bar{b}_2} = \mathcal{O}(\bar{b}^{-1}_2),\ B^{\bar{b}_2} = \mathcal{O}(\bar{b}_2^2),\ C^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),\ D^{u,\bar{b}_2} = \mathcal{O}(\bar{b}_2^{-1}),$$
+	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
+	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
 	and
-	$$ \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} \xrightarrow[\bar{b}_2 \to \infty]{} \pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty}.$$
+	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
+	and therefore,
+	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
+	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
 	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
@@
 	\begin{split}
-	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u_t &= \frac{ - \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^+_u}{\sqrt{b_2 + \bar{b}_2}}  \right) + \left( C^u\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^-_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^+_u - \delta^-_u)(T-t)}}{ \left( \frac{\delta^-_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) - \left( \frac{\delta^+_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }\\
-	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) 
+	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t &= \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
+	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
 	 \end{split} 
@@
 	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$. 
-	Thus, we have $B \cdot u_t = \mathcal{O}\left({\bar{b}_2}^{1/2}\right)$ for $t \in [0,T)$ and 
-	$$ \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s) ds} \xrightarrow[\bar{b}_2 \to \infty]{} 0,\ \forall t \in (0,T]. $$	
-	As in the proof of Proposition \ref{prop:b2}, for $t \in [0,T)$:
-	$$ (b_2 + \bar{b}_2) w_t \to \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}$$
-	so that $w_t \to 0, \forall t \in [0,T)$ as $\bar{b}_2 \to \infty$. Hence, by the bounded convergence theorem, we deduce:
-	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty} \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w_t \right)^2 \cdot \left(\bar{x}_t^{MFG} \right)^2 dt \to 0.
-	$$	
-	Moreover, as shown in the case $\bar{b}_2 \to 0$, $\eta_t$ as well as the variance $v_t$ are invariant w.r.t. $\bar{b}_2$ and $v_t>0$ for $t>0$. Thus,
-	$$ \lim_{\bar{b}_2 \to \infty} SC^{MKV} = h_{var}> 0.$$
+	Thus, for $t \in [0,T)$, we have:
+	\begin{equation*}
+	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
+	\end{equation*}
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
+	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
+	Similarly, we can show that for $t \in [0,T)$:
+	$$\lim_{\bar{b}_2 \to \infty} (b_2 + \bar{b}_2) w^{\bar{b}_2}_t = \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},$$
+	Hence, by the bounded convergence theorem (ToDo: show all 3 terms are uniformly bounded), we deduce:
+	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$
+	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
+	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
 	Therefore, we conclude that:
-	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
+	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
 \end{proof}
@@
 
-\bibitem{cite_todo}
+\bibitem{carmona_acciaio}
 R.~Carmona, B.~Acciaio, and J.~Backhoff~Veraguas.

### 2018-07-16 PoA.tex
finished with proposition 5

@@
 	\begin{split}
-	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t &= \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
+	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
 	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
@@
 	Similarly, we can show that for $t \in [0,T)$:
-	$$\lim_{\bar{b}_2 \to \infty} (b_2 + \bar{b}_2) w^{\bar{b}_2}_t = \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},$$
-	Hence, by the bounded convergence theorem (ToDo: show all 3 terms are uniformly bounded), we deduce:
+	\begin{equation*}
+	\begin{split}
+	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
+	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}.
+	\end{split}
+	\end{equation*}
+	Similar to the proof of Proposition \ref{prop:r_bar_r}, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
+	\begin{equation*}
+	\begin{split}
+	|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
+	|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
+	|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
+	\end{split}
+	\end{equation*}
+
+	Hence, by the bounded convergence theorem, we deduce:
 	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$

### 2018-07-16 PoA.tex
still working on proposition 5

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, then 
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $b_2> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
 	\begin{equation*}
@@
 	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
-	Thus, from equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
+	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
 	\begin{equation*}
@@
 	\end{equation*}
-	Similar to the proof of Proposition \ref{prop:r_bar_r}, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
-	\begin{equation*}
-	\begin{split}
-	|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
-	|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
-	|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
-	\end{split}
-	\end{equation*}
+	%Similar to the proof of Proposition \ref{prop:r_bar_r}, and using the assumptions $b_2>0$ and $q_T+\bar{q}_T(1-s_T)>0$, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
+	%\begin{equation*}
+	%\begin{split}
+	%|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
+	%|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
+	%|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
+	%\end{split}
+	%\end{equation*}
+
+	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$.
+Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$.
+We can check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
+Then we have for $t\in[0,T)$:
+		\begin{equation*}
+		\begin{split}
+		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
+			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
+		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
+		&=:c_1.
+		\end{split} 
+		\end{equation*}
+	ToDo: other 2 function bounds
 

### 2018-07-17 PoA.tex
problem with proposition 5!

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $b_2> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
 	\begin{equation*}
@@
 It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
-Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$.
-
-	Following the methodology of the proof of Proposition \ref{prop:r_bar_r}, let $\epsilon>0$.
+Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
+Let $\epsilon>0$.
 Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
@@
 	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
-	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w}.
-	\end{split}
-	\end{equation*}
-	%Similar to the proof of Proposition \ref{prop:r_bar_r}, and using the assumptions $b_2>0$ and $q_T+\bar{q}_T(1-s_T)>0$, it can be shown that there exists a $c>0$ and $\bar{b}_2^*$ such that for $\bar{b}_2>\bar{b}^*_2$ and $\forall t \in [0,T]$:
-	%\begin{equation*}
-	%\begin{split}
-	%|(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t| <& c, \\
-	%|(b_2 + \bar{b}_2) w^{\bar{b}_2}_t| <& c, \\
-	%|\bar{x}_t^{\bar{b}_2,MFG}|<&c.
-	%\end{split}
-	%\end{equation*}
+	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},
+	\end{split}
+	\end{equation*}
+	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$ and therefore $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2}=0$.
 
@@
 Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$.
-We can check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
-Then we have for $t\in[0,T)$:
+It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
+Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
 		\begin{equation*}
@@
 		\end{equation*}
-	ToDo: other 2 function bounds
+	ToDo setup
+	\begin{equation*}
+	\begin{split}
+		\left| (b_2 + \bar{b}_2) w^{\bar{b}_2}_t \right| &\leq \frac{ \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot\left( \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}-\frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2} \right)}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} } \\
+		& \leq \frac{}{0!!!}
+	\end{split}
+	\end{equation*}
+
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and the non-negativity of $u^{\bar{b}_2}_t$, we have:
+	\begin{equation*}
+		\left| \bar{x}^{\bar{b}_2,MFG,}_t \right| \leq \left|\mathbb{E}(\xi)\right|e^{(b_1+\bar{b}_1)T}.
+	\end{equation*}
 

### 2018-07-17 PoA.tex
editing first case of proposition 6

@@
 Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$.
-It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, and $\delta^{\bar{b}_2 \to \infty}-\epsilon<\left| \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right|< \delta^{\bar{b}_2 \to \infty} +\epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
+It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, $\left| \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-\delta^{\bar{b}_2 \to \infty}\right|< \epsilon$, and $\left| \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-(-\delta^{\bar{b}_2 \to \infty})\right|< \epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
 Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
@@
 \begin{proof}
-    Clearly we have $\lim_{b_1 \to 0}u_t=:u^{0,b_1}_t$, $\lim_{b_1 \to 0}w_t=:w^{0,b_1}_t$, and $\lim_{b_1 \to 0}\eta_t=:\eta^{0,b_1}_t$, where all three limiting processes are bounded.
-By the assumption on $\lambda$, $u_t \neq w_t$ on a set of positive Lebesgue measure.
-By the assumption on $\xi$, we have $\lim_{b_1 \to 0} \bar{x}^{MFG}_t=:\bar{x}^{0,b_1,MFG}_t>0,\ \forall t \in [0,T]$ which is also bounded.
+	First, we consider $b_1 \to 0$.
+We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
+Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
+Next, we show that the three sequences are uniformly bounded.
+Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
+There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$.
+Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
+	\begin{equation*}
+	\begin{split}
+		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
+		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
+		&=:c,
+	\end{split}
+	\end{equation*}
+	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By the assumption on $\lambda$, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+	\begin{equation*}
+	\lim_{b_1\to 0}\bar{x}_t^{b_1,MFG} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{b_1\to 0,MFG}>0.
+	\end{equation*}
+	Moreover, $\bar{x}_t^{b_1\to 0,MFG}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
+	$$ \left| \bar{x}^{b_1,MFG}_t \right| \leq \vert \mathbb{E}(\xi) \vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$
+
 	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
@@
 We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
+    ToDo: check that we showed all 4 cases.
 \end{proof}

### 2018-07-17 PoA.tex
first half of proposition 6 finished

@@
 
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t.$$
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
 	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
@@
    	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
-Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce:
+Thus, from Proposition \ref{prop:diff_SC}, and by the bounded convergence theorem, we deduce:
 	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0.
@@
 
-	Hence, by the bounded convergence theorem, we deduce:
+	Hence, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
 	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$
@@
     \begin{equation*}
-        \lim_{b_1 \to 0} \Delta SC=:\Delta SC^{0,b_1},\  \Delta SC^{0,b_1}<\infty,\ \text{and}\ \Delta SC^{0,b_1}>0.
-    \end{equation*}
-    Since $\eta^{0,b_1}_t$ is bounded, $\lim_{b_1 \to 0}v_t=:v_t^{0,b_1}>0,\ \forall t>0$ which is also bounded.
-Using equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}), the fact that $0 \leq \eta^{0,b_1}_0 < \infty$, and the bounded convergence theorem, $\lim_{b_1 \to 0} SC^{MKV}>0$ and $\lim_{b_1 \to 0} SC^{MKV}<\infty$.
-Therefore, $\lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1$.
-The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1$.
+        0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty.
+    \end{equation*}
+    By the bounded convergence theorem, $\lim_{b_1 \to 0}v_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus:
+    $$0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$$
+    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_1 \to 0} > 1$.
 

### 2018-07-18 PoA.tex
proposition 6
working on the last half of proposition 6

@@
 
-    Now we consider $b_1 \to \infty$. We see that:
-    \begin{equation*}
-        \delta^+_u \to 0,\ \frac{\delta^-_u}{b_1+\frac{\bar{b}_1}{2}} \to -2,\ \delta^+_w \to 0,\ \frac{\delta^-_w}{b_1+\bar{b}_1} \to -2,\ \delta^+_{\eta} \to 0,\ \frac{\delta^-_{\eta}}{b_1} \to -2.
-    \end{equation*}
-    and therefore we find for $t \in [0,T)$:
-    \begin{equation*}
-    \begin{split}
-        \left(b_1+\frac{\bar{b}_1}{2}\right)u_t&\to 2 C^u \\
-        \left(b_1+\bar{b}_1\right)w_t&\to 2 C^w \\
-        b_1 \eta_t&\to 2 C^{\eta}.
-    \end{split}
-    \end{equation*}
-    Thus, $\Delta \bar{\eta}_t=\mathcal{O}(b_1^{-1})$ for $t \in [0,T)$.
+    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
+    \begin{equation*}
+    \begin{split}
+	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:f_u(b_1) \\
+		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:f_w(b_1) \\
+		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:f_{\eta}(b_1) \\
+		\left| \bar{x}^{b_1,MFG}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:f_{\bar{x}}(b_1).
+    \end{split}
+    \end{equation*}
+    Thus, from Proposition \ref{prop:diff_SC}, we have:
+    \begin{equation*}
+	    \Delta SC^{b_1} \leq \frac{1}{2}BT(f_u(b_1)+f_w(b_1))^2 (f_{\bar{x}}(b_1))^2.
+    \end{equation*}
+
+    %We see that:
+    %\begin{equation*}
+    %    \delta^+_u \to 0,\ \frac{\delta^-_u}{b_1+\frac{\bar{b}_1}{2}} \to -2,\ \delta^+_w \to 0,\ \frac{\delta^-_w}{b_1+\bar{b}_1} \to -2,\ \delta^+_{\eta} \to 0,\ \frac{\delta^-_{\eta}}{b_1} \to -2.
+    %\end{equation*}
+    %and therefore we find for $t \in [0,T)$:
+    %\begin{equation*}
+    %\begin{split}
+    %    \left(b_1+\frac{\bar{b}_1}{2}\right)u_t&\to 2 C^u \\
+    %    \left(b_1+\bar{b}_1\right)w_t&\to 2 C^w \\
+    %    b_1 \eta_t&\to 2 C^{\eta}.
+    %\end{split}
+    %\end{equation*}
+    %Thus, $\Delta \bar{\eta}_t=\mathcal{O}(b_1^{-1})$ for $t \in [0,T)$.
 We find $\bar{x}^{MFG}_t=\mathcal{O}(e^{b_1})$ for $t \in (0,T]$.
@@
 Therefore with equation (\ref{eq:SC_MKV_2}) we have:
-    \begin{equation*}
-        \frac{\Delta SC}{SC^{MKV}}=\mathcal{O}\left(\frac{e^{-b_1}}{b_1}\right)\to 0.
-    \end{equation*}
-    We conclude that $PoA \to 1$ as $b_1 \to \infty$.
-
-    Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$.
+    %\begin{equation*}
+    %    \frac{\Delta SC}{SC^{MKV}}=\mathcal{O}\left(\frac{e^{-b_1}}{b_1}\right)\to 0.
+    %\end{equation*}
+    %We conclude that $PoA \to 1$ as $b_1 \to \infty$.
+    %Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$.
 We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
-    ToDo: check that we showed all 4 cases.
+
 \end{proof}

### 2018-07-19 PoA.tex
3rd case of Proposition 6 finished

--- 2018-07-17 PoA.tex
@@
 	\end{equation*}
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce: (ToDo: Nicolas, do you think this needs to be justified further? It seems obvious to me, but I'm not sure.)
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
 	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $\lambda \neq 1$, then
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then
 	\begin{equation*}
@@
     \end{equation*}
-    By the bounded convergence theorem, $\lim_{b_1 \to 0}v_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus:
+    By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus:
     $$0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$$
-    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_1 \to 0} > 1$.
-
-    Now we consider $b_1 \to \infty$. We see that:
-    \begin{equation*}
-        \delta^+_u \to 0,\ \frac{\delta^-_u}{b_1+\frac{\bar{b}_1}{2}} \to -2,\ \delta^+_w \to 0,\ \frac{\delta^-_w}{b_1+\bar{b}_1} \to -2,\ \delta^+_{\eta} \to 0,\ \frac{\delta^-_{\eta}}{b_1} \to -2.
-    \end{equation*}
-    and therefore we find for $t \in [0,T)$:
-    \begin{equation*}
-    \begin{split}
-        \left(b_1+\frac{\bar{b}_1}{2}\right)u_t&\to 2 C^u \\
-        \left(b_1+\bar{b}_1\right)w_t&\to 2 C^w \\
-        b_1 \eta_t&\to 2 C^{\eta}.
-    \end{split}
-    \end{equation*}
-    Thus, $\Delta \bar{\eta}_t=\mathcal{O}(b_1^{-1})$ for $t \in [0,T)$.
-We find $\bar{x}^{MFG}_t=\mathcal{O}(e^{b_1})$ for $t \in (0,T]$.
-Thus, using Proposition \ref{prop:diff_SC}, we have $\Delta SC=\mathcal{O}\left(\frac{e^{b_1}}{b_1}\right)$.
-We also find $v_t=\mathcal{O}(e^{2b_1})$.
-Therefore with equation (\ref{eq:SC_MKV_2}) we have:
-    \begin{equation*}
-        \frac{\Delta SC}{SC^{MKV}}=\mathcal{O}\left(\frac{e^{-b_1}}{b_1}\right)\to 0.
-    \end{equation*}
-    We conclude that $PoA \to 1$ as $b_1 \to \infty$.
-
-    Similarly, for the case $\bar{b}_1 \to \infty$, we find that $\Delta SC=\mathcal{O}\left(\frac{e^{\bar{b}_1}}{\bar{b}_1}\right)$ and $SC^{MKV}=\mathcal{O}(1)$.
-We conclude that $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
-    ToDo: check that we showed all 4 cases.
+    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.
+
+    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
+    \begin{equation*}
+    \begin{split}
+	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
+		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
+		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
+		\left| \bar{x}^{b_1,MFG}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
+    \end{split}
+    \end{equation*}
+    Thus, from Proposition \ref{prop:diff_SC}, we have:
+    \begin{equation*}
+	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
+    \end{equation*}
+
+    We also have the following lower bound:
+    \begin{equation*}
+	\begin{split}
+	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
+	& \geq (q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
+	\end{split}
+    \end{equation*}
+    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. It is easy to check that $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
+    \begin{equation*}
+    \begin{split}
+	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
+	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
+	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
+	    &\xrightarrow[b_1 \to \infty ]{} 0.
+    \end{split}
+    \end{equation*}
+    Therefore,
+    \begin{equation*}
+	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
+    \end{equation*}
+    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
+
 \end{proof}

### 2018-07-19 PoA.tex
update prop 5

@@
 
+%proposition 5
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$ then 
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
+	then 
 	\begin{equation*}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-Let $\epsilon>0$.
-Then there is a $\bar{b}^*_2$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
-We have the following two inequalities for $\bar{b}_2<\bar{b}^*_2$ and $\forall t \in [0,T]$:
+Because $\bar{b}_1 > 0$, we have $A^u < 0$.
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
+We have the following two inequalities for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
 		\begin{IEEEeqnarray*}{rl}
@@
 		\end{IEEEeqnarray}
-	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2 \to 0}_t$ is uniformly bounded over $t \in [0,T]$ for small enough $\bar{b}_2$.
+	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
 
@@
    	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
-	Moreover, $\bar{x}_t^{\bar{b}_2,MFG}$ is uniformly bounded over $\bar{b}_2<\bar{b}^*_2$ and $t \in [0,T]$, i.e. 
+	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$, i.e. 
 	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
@@
 	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
-	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\infty, \bar{b}_2} (r + \bar{r}(1-\bar{s})^2) ,
+	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2),
 	 \end{split} 
@@
 	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.
-	Thus, for $t \in [0,T)$, we have:
-	\begin{equation*}
-	B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
-	\end{equation*}
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
-	$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$	
-	Similarly, we can show that for $t \in [0,T)$:
-	\begin{equation*}
-	\begin{split}
-	(b_2 + \bar{b}_2) w^{\bar{b}_2}_t =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} }\\
-	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w},
-	\end{split}
-	\end{equation*}
-	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$ and therefore $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2}=0$.
+
+	Let's denote $(b_2 + \bar{b}_2)^{\frac{1}{2}} = p$ and $f(p) = p^3 u_{t_2}^{\bar{b}_2}$, then we know that $f(p) \xrightarrow[p\to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1- \bar{s})^2) := c_3 > 0$.
+
+	%Nicolas: Mean Value theorem
+	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, we have then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
+Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that
+	\begin{IEEEeqnarray}{rCl}
+		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
+		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
+		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
+		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
+		&=& \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \left(p^2 e^{- \kappa_2 p f(p)} \right)^2
+	\label{eq:delta_SC_b_2_bar_infty}
+	\end{IEEEeqnarray}
+	where $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$ (or $p$).
+
+	Our next step is to show that $p^2 e^{- \kappa p f(p) } $ tends towards $0$ when $p \to \infty$.
+This can be done fairly easy.
+Since $f(p) \to c_3 >0$, there exists an $\epsilon > 0 $ such that $c_3 - 2 \epsilon >0$ and a constant $p^* := p^*(\epsilon)>0$ so that for all $p \geq p^*$ we have $\vert f(p) - c_3 \vert < \epsilon$.
+Then $f(p) - (c_3 - 2\epsilon) > \epsilon$ and
+	\begin{equation*}
+	\begin{array}{rll}
+		p^2 e^{- \kappa p f(p)} &=& e^{- \kappa p (f(p) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) p + 2 \ln p } \\
+		& \leq & e^{- \kappa p^* \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) p + 2 \ln p} 
+	\end{array}
+	\end{equation*}
+	Then, for any $\epsilon_1>0$, we can choose $p$ large enough, say $p \geq p^*_1 > p^*$, so that
+	\begin{equation}
+		p^2 e^{-\kappa p f(p)} \leq \epsilon_1.
+	\label{eq:limit_p_f(p)}
+	\end{equation}
+
+ 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
+We observe that for any fixed $t_1 \in (0,T_1)$, we have
+ 	$$ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} c_3, $$
+ 	then for any $\epsilon >0$ there exists a $\bar{b}_2^* > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \leq c_3 + \epsilon$.
+Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce
+ 	$$ u_{t_1}^{\bar{b}_2} \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
+ 	$$
+
+ 	Idem, we can show that for $t_1 \in [0,T)$:
+	\begin{equation*}
+	\begin{split}
+	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
+	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} := c_4 >0,
+	\end{split}
+	\end{equation*}
+	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
+Thus $w_{t_1}^{\bar{b}_2}$ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+
+	Hence, together with the equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
+	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon,$$
+	which implies that 
+	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
+
+% error in the proof of proposition 5
+\begin{comment}
+
+	%Thus, for $t \in [0,T)$, we have:
+	%\begin{equation*}
+	%B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
+	%\end{equation*}
+	%From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
+	%$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$
 
@@
 	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$
+\end{comment}
+
 	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,

### 2018-07-19 PoA.tex
update prop 5

@@
 
-	Let's denote $(b_2 + \bar{b}_2)^{\frac{1}{2}} = p$ and $f(p) = p^3 u_{t_2}^{\bar{b}_2}$, then we know that $f(p) \xrightarrow[p\to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1- \bar{s})^2) := c_3 > 0$.
-
 	%Nicolas: Mean Value theorem
@@
 Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that
-	\begin{IEEEeqnarray}{rCl}
+	\begin{IEEEeqnarray*}{rCl}
 		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
@@
 		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
-		&=& \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \left(p^2 e^{- \kappa_2 p f(p)} \right)^2
+	\end{IEEEeqnarray*}
+	where $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ is a positive constant independent of $\bar{b}_2$.
+
+	Let's denote $(b_2 + \bar{b}_2)^{\frac{1}{2}} = p$ and $f(p) = p^3 u_{t_2}^{\bar{b}_2}$, then we know that $f(p) \xrightarrow[p\to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1- \bar{s})^2) := c_3 > 0$.
+Then we have
+	\begin{equation}
+		 \Delta SC = \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \left(p^2 e^{- \kappa p f(p)} \right)^2
 	\label{eq:delta_SC_b_2_bar_infty}
-	\end{IEEEeqnarray}
-	where $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$ (or $p$).
+	\end{equation}
+	where $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $.
 
@@
  	$$ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} c_3, $$
- 	then for any $\epsilon >0$ there exists a $\bar{b}_2^* > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \leq c_3 + \epsilon$.
+ 	then for any $\epsilon >0$ there exists a $\bar{b}_2^* > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
 Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce
- 	$$ u_{t_1}^{\bar{b}_2} \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
+ 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
  	$$
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-Thus $w_{t_1}^{\bar{b}_2}$ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+Thus $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
 
 	Hence, together with the equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
-	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon,$$
+	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2 ,$$
 	which implies that 

### 2018-07-19 PoA.tex
update prop 5

@@
 	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
-	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2),
+	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2)=: c_3,
 	 \end{split} 
@@
 Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that
-	\begin{IEEEeqnarray*}{rCl}
+	\begin{IEEEeqnarray}{rCl}
 		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
@@
 		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
-	\end{IEEEeqnarray*}
-	where $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ is a positive constant independent of $\bar{b}_2$.
-
-	Let's denote $(b_2 + \bar{b}_2)^{\frac{1}{2}} = p$ and $f(p) = p^3 u_{t_2}^{\bar{b}_2}$, then we know that $f(p) \xrightarrow[p\to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1- \bar{s})^2) := c_3 > 0$.
-Then we have
-	\begin{equation}
-		 \Delta SC = \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \left(p^2 e^{- \kappa p f(p)} \right)^2
+		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2)} \right)^2
 		\label{eq:delta_SC_b_2_bar_infty}
-	\end{equation}
-	where $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $.
-
-	Our next step is to show that $p^2 e^{- \kappa p f(p) } $ tends towards $0$ when $p \to \infty$.
+	\end{IEEEeqnarray}
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $f(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+
+	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
 This can be done fairly easy.
-Since $f(p) \to c_3 >0$, there exists an $\epsilon > 0 $ such that $c_3 - 2 \epsilon >0$ and a constant $p^* := p^*(\epsilon)>0$ so that for all $p \geq p^*$ we have $\vert f(p) - c_3 \vert < \epsilon$.
-Then $f(p) - (c_3 - 2\epsilon) > \epsilon$ and
+Since $f(\bar{b}_2) \to c_3 >0$, there exists an $\epsilon > 0 $ such that $c_3 - 2 \epsilon >0$ and a constant $\bar{b}_2^* := \bar{b}_2^*(\epsilon)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2) - c_3 \vert < \epsilon$.
+Then $f(\bar{b}_2) - (c_3 - 2\epsilon) > \epsilon$ and
 	\begin{equation*}
 	\begin{array}{rll}
-		p^2 e^{- \kappa p f(p)} &=& e^{- \kappa p (f(p) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) p + 2 \ln p } \\
-		& \leq & e^{- \kappa p^* \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) p + 2 \ln p} 
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) }  &=& e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
+		& \leq & e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} 
 	\end{array}
 	\end{equation*}
-	Then, for any $\epsilon_1>0$, we can choose $p$ large enough, say $p \geq p^*_1 > p^*$, so that
-	\begin{equation}
-		p^2 e^{-\kappa p f(p)} \leq \epsilon_1.
+	Then, for any $\epsilon_1>0$, we can choose $\bar{b}_2$ large enough, say $\bar{b}_2 \geq \bar{b}_2^{**} > \bar{b}_2^*$, so that
+	\begin{equation}
+	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) }   \leq \epsilon_1.
 	\label{eq:limit_p_f(p)}
@@
 	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
-	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} := c_4 >0,
+	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
 	\end{split}

### 2018-07-20 PoA.tex
small edits proposition 5

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
 	then 
@@
 	%Nicolas: Mean Value theorem
-	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, we have then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that
+	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
+Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
 	\begin{IEEEeqnarray}{rCl}
@@
 		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
-		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2)} \right)^2
+		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2)} \right)^2,
 		\label{eq:delta_SC_b_2_bar_infty}
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $f(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
-
-	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
-This can be done fairly easy.
-Since $f(\bar{b}_2) \to c_3 >0$, there exists an $\epsilon > 0 $ such that $c_3 - 2 \epsilon >0$ and a constant $\bar{b}_2^* := \bar{b}_2^*(\epsilon)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2) - c_3 \vert < \epsilon$.
-Then $f(\bar{b}_2) - (c_3 - 2\epsilon) > \epsilon$ and
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $f(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.
+
+	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
+We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$.
+Thus, for any $0<\epsilon <\frac{c_3}{2} $, there exists $\bar{b}_2^* := \bar{b}_2^*(\epsilon,t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < \epsilon$.
+Then $f(\bar{b}_2,t_2) - c_3 + 2\epsilon > \epsilon$ and
 	\begin{equation*}
 	\begin{array}{rll}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) }  &=& e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &=& e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
 		& \leq & e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} 
@@
 	\end{equation*}
+	(ToDo: problem here. What is the limit of $e^{- \kappa (b_2+\bar{b}_2^*(\epsilon))^{\frac{1}{2}} \cdot \epsilon}$ as $\epsilon$ goes to 0?)
 	Then, for any $\epsilon_1>0$, we can choose $\bar{b}_2$ large enough, say $\bar{b}_2 \geq \bar{b}_2^{**} > \bar{b}_2^*$, so that
 	\begin{equation}
-	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2) }   \leq \epsilon_1.
+	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }   \leq \epsilon_1.
 	\label{eq:limit_p_f(p)}
@@
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-We observe that for any fixed $t_1 \in (0,T_1)$, we have
- 	$$ (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_1}^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} c_3, $$
- 	then for any $\epsilon >0$ there exists a $\bar{b}_2^* > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
-Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce
+As before, and recycling notation, for any $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
+Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
  	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.

### 2018-07-20 PoA.tex
limit top of page 22 more clear

@@
 We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$.
-Thus, for any $0<\epsilon <\frac{c_3}{2} $, there exists $\bar{b}_2^* := \bar{b}_2^*(\epsilon,t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < \epsilon$.
-Then $f(\bar{b}_2,t_2) - c_3 + 2\epsilon > \epsilon$ and
-	\begin{equation*}
-	\begin{array}{rll}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &=& e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
-		& \leq & e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} 
+Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.
+Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$.
+Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
+	\begin{equation*}
+	\begin{array}{rl}
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
+		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
 	\end{array}
 	\end{equation*}
-	(ToDo: problem here. What is the limit of $e^{- \kappa (b_2+\bar{b}_2^*(\epsilon))^{\frac{1}{2}} \cdot \epsilon}$ as $\epsilon$ goes to 0?)
-	Then, for any $\epsilon_1>0$, we can choose $\bar{b}_2$ large enough, say $\bar{b}_2 \geq \bar{b}_2^{**} > \bar{b}_2^*$, so that
-	\begin{equation}
-	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }   \leq \epsilon_1.
-	\label{eq:limit_p_f(p)}
-	\end{equation}
 

### 2018-07-20 PoA.tex
proposition 5 finished!

@@
 	\end{equation*}
+	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{**}>\bar{b}_2^{*}$, such that for all $\bar{b}_2>\bar{b}_2^{**}$, we have:
+	\begin{equation}
+	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }|<\epsilon.
+	\label{eq:limit_p_f(p)}
+	\end{equation}
 
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-As before, and recycling notation, for any $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
+Given $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
 Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-Thus $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
-
-	Hence, together with the equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
-	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2 ,$$
-	which implies that 
+Thus, $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+
+	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
+	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
+	Thus, by taking $\epsilon \to 0$, we have:
 	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$

### 2018-07-20 PoA.tex
minor edits

@@
 \end{equation}
-where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$. We have analogous expressions for $w_t$ and $\eta_t$ in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively. Note that $B^u=B^w=:B$.
+where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$.
+Note that under the above conditions, we have $\delta^-_u<0<\delta^+_u$ and thus, $u_t \geq 0$ for all $t\in[0,T]$.
+We have analogous expressions for $w_t$ and $\eta_t$, which are also nonnegative, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively.
+Note that $B^u=B^w=:B$, and the above conditions on the parameters $B$, $C^u$, $D^u$, $C^w$, $D^w$, $B^\eta$, $C^\eta$, and $D^\eta$ are exactly the conditions in assumption (\ref{eq:assumptions}).
 
@@
 	\begin{equation}
-		\dot{\left({u}^{r \to \infty}_t\right)} - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
+		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
 	\end{equation}
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$, i.e. 
-	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
+	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
 
@@
    	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
-	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$, i.e. 
-	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 + c_1 c_2) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
 
@@
 		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
-		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2)} \right)^2,
+		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2)} \right)^2,
 		\label{eq:delta_SC_b_2_bar_infty}
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $f(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.
-
-	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
-We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$.
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+
+	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
+We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$.
 Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.
-Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$.
-Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
+Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\vert h(\bar{b}_2) - c_3 \vert < c_{b_2}$.
+Then $h(\bar{b}_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
 	\begin{equation*}
 	\begin{array}{rl}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
-		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (h(\bar{b}_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
+		& \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
 		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
@@
 	\end{equation*}
-	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{**}>\bar{b}_2^{*}$, such that for all $\bar{b}_2>\bar{b}_2^{**}$, we have:
-	\begin{equation}
-	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }|<\epsilon.
+	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{*,2}>\bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$, we have:
+	\begin{equation}
+	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
 	\label{eq:limit_p_f(p)}
@@
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-Given $\epsilon>0$, there exists a $\bar{b}_2^*:=\bar{b}_2^*(\epsilon,t_1) > 1$ such that for any $\bar{b}_2 \geq \bar{b}_2^*$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
-Thus, for any $\bar{b}_2 \geq \bar{b}_2^*$ we deduce:
+Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
+Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we deduce:
  	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
@@
 
-	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have
+	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 > \bar{b}_2^*$ we have
 	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
@@
 	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
-
-% error in the proof of proposition 5
-\begin{comment}
-
-	%Thus, for $t \in [0,T)$, we have:
-	%\begin{equation*}
-	%B^{\bar{b}_2} u^{\bar{b}_2}_t=\frac{\sqrt{b_2+\bar{b}_2}}{r+\bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{}\infty.
-	%\end{equation*}
-	%From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we deduce:
-	%$$\lim_{\bar{b}_2 \to \infty} \bar{x}_t^{\bar{b}_2 \to \infty,MFG} = 0,\ \forall t \in (0,T]. $$
-
-	Next, our goal is to derive bounds for the functions $\frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}}$, $(b_2 + \bar{b}_2) w^{\bar{b}_2}_t$, and $\bar{x}_t^{\bar{b}_2,MFG}$.
-Let $0<\epsilon<\delta^{\bar{b}_2 \to \infty}$.
-It is easy to check that there exists a $\bar{b}_2^*$ such that $ C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} <\epsilon$, $\left| \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-\delta^{\bar{b}_2 \to \infty}\right|< \epsilon$, and $\left| \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}-(-\delta^{\bar{b}_2 \to \infty})\right|< \epsilon$ for $\bar{b}_2>\bar{b}_2^*$.
-Then we have for $\bar{b}_2>\bar{b}^*_2$ and $\forall t\in[0,T]$:
-		\begin{equation*}
-		\begin{split}
-		\left| \frac{(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t}{\sqrt{b_2+\bar{b}_2}} \right| &\leq \frac{
-			C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \left(\frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} -\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}\right)}{-\frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}}\\
-		&\leq \frac{\epsilon + 2\epsilon\zeta}{\delta^{\bar{b}_2 \to \infty}-\epsilon} \\
-		&=:c_1.
-		\end{split} 
-		\end{equation*}
-	ToDo setup
-	\begin{equation*}
-	\begin{split}
-		\left| (b_2 + \bar{b}_2) w^{\bar{b}_2}_t \right| &\leq \frac{ \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot\left( \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}-\frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2} \right)}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t)} } \\
-		& \leq \frac{}{0!!!}
-	\end{split}
-	\end{equation*}
-
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and the non-negativity of $u^{\bar{b}_2}_t$, we have:
-	\begin{equation*}
-		\left| \bar{x}^{\bar{b}_2,MFG,}_t \right| \leq \left|\mathbb{E}(\xi)\right|e^{(b_1+\bar{b}_1)T}.
-	\end{equation*}
-
-	Hence, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	$$ \lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} =  \frac{1}{2(r+ \bar{r}(1-\bar{s})^2)} \int_0^T \lim_{\bar{b}_2 \to \infty}\left[ \left( \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t }{\sqrt{b_2 + \bar{b}_2}} - (b_2 + \bar{b}_2)w^{\bar{b}_2}_t \right)^2 \cdot \left(\bar{x}_t^{\bar{b}_2,MFG} \right)^2\right] dt = 0.$$
-\end{comment}
 

### 2018-07-20 PoA.tex
minor edits again

@@
 \bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
-\label{eq:x_bar_MKV}
 \end{equation}
@@
 
-% proposition r infinity
 \begin{proposition}
@@
 
-	% modification Main point 5 (nicolas)
 	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
@@
 		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-		&\geq(-A^u + \vert A_u \vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
+		&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
 		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
@@
 	\begin{IEEEeqnarray}{rCl}
-		\vert u_t^{r} \vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
+		\left\vert u_t^{r} \right\vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
 		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
@@
 	\begin{equation*}
-		\lim_{r\to \infty}\bar{x}_t^{r,MFG} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{r\to \infty,MFG}.
-	\end{equation*}
-	Moreover, $\bar{x}_t^{r,MFG}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
-	$$ \vert \bar{x}^{r,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
+		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
+	\end{equation*}
+	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
 
@@
 	\begin{equation*}
-	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{r,MFG})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{r\to \infty,MFG})^2 dt \  < \infty,
+	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
 	\end{equation*}
@@
 	\begin{equation*}
-	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{r,MFG})^2 dt = 0.
-	\end{equation*}
-
-	%---------------------------
+	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
+	\end{equation*}
+
 	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
@@
 
-% proposition b_2
 \begin{proposition}
@@
 
-	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.
+	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$.
 Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
@@
 	\begin{split}
-	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
+	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
 	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
@@
 	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
-\frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u .
-\frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
+		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
 		{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \nonumber \\
@@
 		\Delta SC &=& \frac{1}{2} \frac{(b_2+\bar{b}_2)^2}{\zeta_1} \int_0^T (u_t - w_t)^2 (\bar{x}_t^{MFG})^2 dt \\
-		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 .
-e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
+		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 \cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
 		&=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
-		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right].
-e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
+		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
 	\end{IEEEeqnarray*}
@@
 	For the second term, we know that 
-	$$ \vert e^{-2\int_0^t h_s(b_2) ds} - 1 \vert \leq \vert e^{ \mathcal{O}(b_2^{-1}) } -1 \vert = \mathcal{O}(b_2^{-1}).$$
+	$$ \left\vert e^{-2\int_0^t h_s(b_2) ds} - 1 \right\vert \leq \left\vert e^{ \mathcal{O}(b_2^{-1}) } -1 \right\vert = \mathcal{O}(b_2^{-1}).$$
 	Together with the estimation of the first term above, we have 
-	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right].
-e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
+	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
 	Hence, we deduce that
@@
 
-%proposition 5
 \begin{proposition}
@@
 For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
-We have the following two inequalities for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
-		\begin{IEEEeqnarray*}{rl}
-			&\left\vert (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{+,\bar{b}_2}_u) - (C^{u,\bar{b}_2} + D^{u,\bar{b}_2} \delta^{-,\bar{b}_2}_u) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u) (T-t)} \right\vert\\
-			&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
-			&< \infty,
-		\end{IEEEeqnarray*}
-		and 
-		\begin{IEEEeqnarray*}{rl}
-			& \left\vert ( -\delta^{-,\bar{b}_2}_u + D^{u,\bar{b}_2} B^{\bar{b}_2} ) + (\delta^{+,\bar{b}_2}_u - D^{u,\bar{b}_2} B^{\bar{b}_2} ) e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right\vert \\
-			&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
-			&>  0.
-		\end{IEEEeqnarray*}
-		Thus, we can deduce that:
-		\begin{IEEEeqnarray}{rCl}
-			\vert u_t^{\bar{b}_2} \vert  &\leq& c_2,\ \forall t \in [0,T],\ \bar{b}_2<\bar{b}^*_2.  \nonumber
-		\end{IEEEeqnarray}
+Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
+	\begin{equation*}
+	\begin{split}
+		\left| u_t^{\bar{b}_2} \right| &\leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} \\
+		&=:c_2.
+	\end{split}
+	\end{equation*}
+
 	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
@@
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{\bar{b}_2,MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{\bar{b}_2 \to 0,MFG}_t>0.$$
-	Moreover, $\bar{x}^{\bar{b}_2,MFG}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
-	$$ \vert \bar{x}^{\bar{b}_2,MFG}_t \vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t>0.$$
+	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
 
@@
 Thus, from Proposition \ref{prop:diff_SC}, and by the bounded convergence theorem, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{\bar{b}_2 \to 0,MFG} \right)^2 dt \  > 0.
+	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
 $$
@@
 
-	%Nicolas: Mean Value theorem
-	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{\bar{b}_2,MFG}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{\bar{b}_2,MFG} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
+	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
 Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
 	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{\bar{b}_2,MFG} )^2 dt  \nonumber \\
-		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
+		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{MFG,\bar{b}_2} )^2 dt  \nonumber \\
+		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot T \nonumber \\
 		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
@@
 Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.
-Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\vert h(\bar{b}_2) - c_3 \vert < c_{b_2}$.
+Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < c_{b_2}$.
 Then $h(\bar{b}_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
@@
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \vert u_{t_1}^{\bar{b}_2} \vert \leq c_3 + \epsilon$.
+Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
 Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we deduce:
- 	$$ \vert u_{t_1}^{\bar{b}_2} \vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
+ 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
  	$$
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-Thus, $ \vert w_{t_1}^{\bar{b}_2} \vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
 
@@
 	\begin{equation*}
-	\lim_{b_1\to 0}\bar{x}_t^{b_1,MFG} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{b_1\to 0,MFG}>0.
-	\end{equation*}
-	Moreover, $\bar{x}_t^{b_1\to 0,MFG}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
-	$$ \left| \bar{x}^{b_1,MFG}_t \right| \leq \vert \mathbb{E}(\xi) \vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$
+	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}>0.
+	\end{equation*}
+	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
+	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$
 
@@
 		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
-		\left| \bar{x}^{b_1,MFG}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
+		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
     \end{split}
@@
 In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-For all three cases, as $b_1 \to 0$, we see that $PoA \to PoA^{0,b_1}>1$ and as $\bar{b}_1 \to 0$, we see that $PoA \to PoA^{0,\bar{b}_1}>1$.
+For all three cases, as $b_1 \to 0$, we see that $PoA \to PoA^{b_1\to 0}>1$ and as $\bar{b}_1 \to 0$, we see that $PoA \to PoA^{\bar{b}_1 \to 0}>1$.
 We also see that $PoA\to 1$ as $b_1 \to \infty$ and $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
@@
 When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $PoA \to 1$ as $b_2 \to 0$.
-When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $PoA \to PoA^{0,b_2}>1$ as $b_2 \to 0$.
+When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $PoA \to PoA^{b_2 \to 0}>1$ as $b_2 \to 0$.
 For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $PoA \to 1$ as $b_2 \to \infty$.
-For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $PoA \to PoA^{0,\bar{b}_2}>1$ as $\bar{b}_2 \to 0$ and $PoA \to 1$ as $\bar{b}_2 \to \infty$.
+For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $PoA \to PoA^{\bar{b}_2 \to 0}>1$ as $\bar{b}_2 \to 0$ and $PoA \to 1$ as $\bar{b}_2 \to \infty$.
 Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $PoA \to 1$ as $r \to \infty$ or $\bar{r} \to \infty$.

### 2018-07-21 PoA.tex
update prop 4

--- 2018-07-20 PoA.tex
@@
 
-% proposition b_2
+% proposition 4 related to b_2
 \begin{proposition}
@@
 	\end{equation*}
-	Moreover, if
-		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	then
-	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
-	otherwise
+
+%	Moreover, if
+%		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
+%	then
+%	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
+%	otherwise
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 
+	% case when b_2 tends towards infinity
 	Now we consider the case when $b_2 \to \infty$.
@@
 In order to study the limit of $PoA$,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
+
+	When $b_2 \to \infty$, we have 
+	\begin{equation*}
+	\begin{array}{l}
+	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
+	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
+	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
+	\end{array}
+	\end{equation*}
+	Moreover
+	\begin{IEEEeqnarray*}{rCl}
+	\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
+	&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{b_2 \to \infty}_u
+	\end{IEEEeqnarray*}
+	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
+	$$ e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
+
+	Since $u^{b_2}$, $w^{b_2}$ and $\bar{x}^{b_2,MFG}$ are continuous functions on $[0,T]$, we have that the functions $t \mapsto \int_0^t u_s^{b_2} ds$ and $t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{b_2, MFG})^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
+Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value Theorem and deduce that there exists two fixed times $0 < t_2 < t_1 < T$ such that:
+		\begin{IEEEeqnarray}{rCl}
+		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{b_2,MFG} )^2 dt  \nonumber \\
+		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{\bar{b}_2,MFG} )^2  \cdot T \nonumber \\
+		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{\bar{b}_2} ds } \nonumber \\
+		&=&  \kappa_1 (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{b_2} u_{t_2}^{b_2} \cdot t_1}  \right]^2 \nonumber \\
+		&= & \kappa_1 (u_{t_1}^{b_2} - w_{t_1}^{b_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) f(b_2,t_2)} \right)^2,
+		\label{eq:delta_SC_b_2_infty}
+	\end{IEEEeqnarray}
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $b_2$, and $f(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$.
+
+	-----------------------------
 
@@
 	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
-We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$.
+We showed above that for all $0 \leq t<T$, $f(\bar{b}_2,t) \to c_3 >0$.
 Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.

### 2018-07-21 PoA.tex
prop 4 second half

--- 2018-07-20 PoA.tex
@@
 	\end{equation*}
-	Moreover, if
-		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	then
-	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
-	otherwise
+
+	%Moreover, if
+	%	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + %\bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
+	%then
+	%$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
+	%otherwise
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 
+	% b_2 to infty
+
 	Now we consider the case when $b_2 \to \infty$.
@@
 
-	For the sake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
-	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
-	\begin{equation*}
-	\begin{array}{rclcrcl}
-	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
-	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
-	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
-	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
+	When $b_2 \to \infty$, we have 
+	\begin{equation*}
+	\begin{array}{l}
+	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
+	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
+	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
 	\end{array}
 	\end{equation*}
-	and 
+	Moreover
 	\begin{IEEEeqnarray*}{rCl}
-		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
-		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
-		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
+		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
 	\end{IEEEeqnarray*}
-
-	Thus, for $b_2$ tends to infinity, we have $$e^{-(\delta_u^+ - \delta_u^-) (T-t)} = e^{-( (2 b_2+\bar{b}_2)\kappa_u (T-t) + \mathcal{O}(b_2^{-1}) }$$
-	which is uniformly bounded over $[0,T]$. Clearly, $e^{-(\delta_u^+ - \delta_u^-) (T-t)} = \mathcal{O}(b_2^{-2}) \to 0$ for $t \in [0, T)$.
-
-	The next step is to give an estimation of $\Delta SC$. To do so, we need to expand the product $B u_t$ up till $b_2^{-2}$. We first notice that for $t \in [0,T)$, 
+	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
+	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
+	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
 	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
-		{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \nonumber \\
-		&=& \frac{ - (\mathcal{O}(b_2^{-1}) + \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \kappa_u + \mathcal{O}(b_2^{-1}) ) + \mathcal{O}(b_2^{-2})}{(\mathcal{O}(b_2^{-1})- \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} ) - \mathcal{O}(b_2^{-2}) } \nonumber \\
-		&=& \zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})
+		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
+		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
+		&&\\
+		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_3
 	\end{IEEEeqnarray*}
-	Then, we can continue do the expansion and obtain
+	Idem, we can have for any $t \in [0,T)$,
+	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_4,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} };$$
+	and for any $t \in [0,T)$,
+	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
+	$$
+
+	The next step is to provide an estimation of the order of magnitude of $\Delta SC$ and $SC^{MKV}$.
+For all $t \in [0,T)$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$, $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$ and $h_\eta(b_2,t) = b_2 \eta_t^{b_2}$.\\
+
+	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$.
+Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ for which
+	\begin{IEEEeqnarray}{rCl}
+		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
+		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
+		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
+		&=&  \kappa_1 \left[ (b_2 + \bar{b}_2) (u_{t_1}^{b_2}- w_{t_1}^{b_2} ) \right]^2\cdot  \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
+		&= & \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)},
+		\label{eq:delta_SC_b_2_infty}
+	\end{IEEEeqnarray}
+	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\
+
+	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$.
+Then the Mean Value Theorem yields that there exists a time  $t_3 \in (0,T)$ so that
+	\begin{equation}
+	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = \left(q + \bar{q} + \frac{1}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} \cdot T,
+	\label{eq:vt_int_b_2_infinity}
+	\end{equation}
+	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
+	\begin{IEEEeqnarray}{rCl}
+		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
+		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
+		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
+		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
+	\label{eq:vt_b_2_infinity} 
+	\end{IEEEeqnarray}
+	where
+	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.
+
+	\begin{comment}
+	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
+	\begin{equation}
+		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
+	\label{eq:v_{t_3}_b_2_expansion}
+	\end{equation}
+	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
+	\end{comment}
+
+	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
+	\begin{IEEEeqnarray}{rCl}
+		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)} }{\displaystyle \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
+		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2) e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_\eta(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_1(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
+	\label{eq:delta_SC_SC^MKV_b_2_infinity}
+	\end{IEEEeqnarray}
+	where 
+	$\displaystyle l_{u,v}(b_2) = \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 , \  l_\eta(b_2) =  \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) \frac{b_2 + \bar{b}_2}{b_2}$
+	and $\displaystyle l_1(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}$.	
+	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
+	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
+
+	Finally, we will show that for any fixed $t \in [0,T)$ and $\kappa >0$, we have
+	\begin{equation}
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2 \to \infty]{} 0 \qquad \text{and} \qquad b_2 e^{-\kappa b_2 h_\eta(b_2, t)} \xrightarrow[b_2 \to \infty]{} 0.
+	\label{eq:b_2_vt_limit}
+	\end{equation}
+	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ whilst the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$ because equation (\ref{eq:vt_b_2_infinity}) gives raise to
+	$$ b_2 v_T^{b_2} = \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \xrightarrow[b_2 \to \infty]{} 0,$$
+	and so $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
+	Together with the limits of $l_{u,v}(b_2), l_\eta(b_2)$ and $l_1(b_2)$, we have
+	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$
+
+	Take $(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)}$ as an example.
+For any $t \in [0,T)$, we previously showed that $\lim_{b_2 \to \infty} h(b_2,t) = c_3 >0$.
+Let $\epsilon_1 >0$ such that $c_3 - 2 \epsilon_1 >0$.
+Then there exists $b_2^* > 0$ so that for all $b_2 \geq b_2^{*}$ we have $\vert h_u(b_2,t) - c_3 \vert \leq \epsilon_1$.
+Thus $h_u(b_2,t) - c_2 + 2 \epsilon_1 > \epsilon_1$ and
 	\begin{IEEEeqnarray*}{rCl}
-		&&(b_2 + \bar{b}_2) ( (b_2 + \bar{b}_2) u_t - \zeta_1 \kappa_u ) \nonumber\\
-		&=& \frac{-(C^u + D^u \delta^+_u) + \mathcal{O}(b_2^{-2}) }{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) + \mathcal{O}(b_2^{-2}) } - (b_2 + \bar{b}_2) \zeta_1 \kappa_u \nonumber \\
-		&=& \frac{-\left( C^u + D^u \delta_u^+ + (b_2 + \bar{b}_2) \zeta_1 \kappa_u \left( \frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right) \right) + \mathcal{O}(b_2^{-2})}{  \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right)-  \mathcal{O}(b_2^{-2})} \nonumber \\
-		&=& \frac{  -\left( C^u +\zeta_1 \kappa_u \frac{\delta_u^-}{b_2 + \bar{b}_2} +  D^u (b_2 + \bar{b}_2)(\frac{\delta^+_u}{b_2 + \bar{b}_2} - \kappa_u) \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1}) } \nonumber \\
-		&=& \frac{- \left( \zeta_1 \kappa_u^2 (1 -\frac{\bar{b}_2}{b_2} )  + \zeta_1 \kappa_u (- \kappa_u + (A^u + \frac{\bar{b}_2}{2} \kappa_u) \frac{1}{b_2}) ) + D^u (b_2 + \bar{b}_2) \left[ (A^u - \frac{\bar{b}_2}{2} \kappa_u )\frac{1}{b_2} + \mathcal{O}(b_2^{-2}) \right] \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1})} \nonumber \\
-		&=& \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u ) + \mathcal{O}(b_2^{-1})
+		(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2, t)} &=& e^{- \kappa (b_2 + \bar{b}_2) (h_u(b_2,t) - c_3 + 2\epsilon_1)} \cdot e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) } \\
+		&\leq & e^{- \kappa (b_2^* + \bar{b}_2) \epsilon_1} \cdot \exp \left( - \kappa(c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) \right).
 	\end{IEEEeqnarray*}
-	Thus, we have for any given $t \in [0,T)$,
-	\begin{equation*}
-		(b_2+\bar{b}_2)^2 u_t = \zeta_1 \kappa_u (b_2 + \bar{b}_2) + \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u) + h_t(b_2)
-	\end{equation*}
-	where $h_t(b_2) = \mathcal{O}(b_2^{-1})$.
-	Since for any $t \in [0,T)$, $\int_0^t h_s(b_2) ds = \mathcal{O}(b_2^{-1})$ and $B = (b_2+ \bar{b}_2)^2 / \zeta_1$, we deduce that 
-	\begin{equation*}
-	\bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t + \mathcal{O}(b_2^{-1}) }
-	\end{equation*}
-	which tends uniformly to $0$ over $[0,T)$ as $b_2 \to \infty$.
-	Moreover, since 
-	\begin{equation*}
-	\begin{split}
-		(b_2 + \bar{b}_2) (u_t - w_t) 
-	= (\zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})) - (\sqrt{\zeta_1 (q+\bar{q}(1-s)^2)} + \mathcal{O}(b_2^{-1}) )\\
-	= \sqrt{\zeta_1} (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})
-	\end{split}
-	\end{equation*}
-	Thus
-	\begin{IEEEeqnarray*}{rCl}
-		\Delta SC &=& \frac{1}{2} \frac{(b_2+\bar{b}_2)^2}{\zeta_1} \int_0^T (u_t - w_t)^2 (\bar{x}_t^{MFG})^2 dt \\
-		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 \cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
-		&=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
-		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
-	\end{IEEEeqnarray*}
-
-	For the first term, a direct computation yields that
-	\begin{equation*}
-	\begin{array}{rl}
-	&\frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
-	&= \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
-	&= \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
-	\end{array}
-	\end{equation*}
-	For the second term, we know that 
-	$$ \left\vert e^{-2\int_0^t h_s(b_2) ds} - 1 \right\vert \leq \left\vert e^{ \mathcal{O}(b_2^{-1}) } -1 \right\vert = \mathcal{O}(b_2^{-1}).$$
-	Together with the estimation of the first term above, we have 
-	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
-	Hence, we deduce that
-	\begin{equation}
-		\Delta SC = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2}).
-	\end{equation}
-
-	Similarly, we can have $SC^{MKV} =  \frac{\zeta_2}{b_2} + \mathcal{O}(b_2^{-2})$
-	for some constant $\zeta_2 \neq 0$. Thus,
-	\begin{equation}
-		\frac{\Delta SC}{SC^{MKV}} = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{\zeta_2} + \mathcal{O}(b_2^{-1})
-	\end{equation}
-	Therefore, if $ \zeta_1 \kappa_u^2 \neq q + \bar{q}(1-s)^2$, i.e.
-	$$\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	we have
-	$$ \lim_{b_2 \to \infty} PoA =: PoA^{\infty,b_2} > 1;$$
-	otherwise $$ \lim_{b_2 \to \infty} PoA = 1.$$
-
+	Since the first term in the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$, then we must have
+	$$ (b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2\to \infty]{} 0, \quad \forall\   0 \leq t < T. $$
+	Thus, the limits in (\ref{eq:b_2_vt_limit}) hold true and following the previous analysis we conclude that 
+	$$ \lim_{b_2 \to \infty} PoA = 1.$$
 \end{proof}
@@
 	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u_t- w_t)^2 (\bar{x}_t^{MFG,\bar{b}_2} )^2 dt  \nonumber \\
+		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
 		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot T \nonumber \\
-		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
-		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
+		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
+		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) \exp\left( - B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right)  \right]^2 \nonumber \\
 		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2)} \right)^2,
@@
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
 
@@
 We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$.
-Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.
-Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < c_{b_2}$.
-Then $h(\bar{b}_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
+Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$.
+Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$.
+Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and
 	\begin{equation*}
 	\begin{array}{rl}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (h(\bar{b}_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
-		& \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
-		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
+		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot e^{- \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+		& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
 		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
@@
 	\end{equation*}
-	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{*,2}>\bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$, we have:
+	Namely, for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
 	\begin{equation}
@@
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
-Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we deduce:
- 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
+Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} \geq 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
+Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3} \geq 1$ we deduce:
+ 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq \frac{c_3+ \epsilon}{(b_2 + \bar{b}^{*,3}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
  	$$
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for large enough $\bar{b}_2$.
 

### 2018-07-21 PoA.tex
update prop 4 b_2 infty

@@
 
-% proposition b_2
+% proposition b_2 to \infty
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
-	\begin{equation*}
-	 \lim_{b_2 \to 0} PoA = 1,
-	\end{equation*}
-	whereas if $\bar{b}_2 > 0$, then:
-	\begin{equation*}
-	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
-	\end{equation*}
-
-	%Moreover, if
-	%	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + %\bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	%then
-	%$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
-	%otherwise
+	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 
+\begin{remark}
+	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
+The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
+Indeed, we will show that $\Delta SC$ decreases exponentially fast when $b_2$ tends towards infinity while $SC^{MKV}$ decreases as fast as $1/b_2$.
+Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter.
+\end{remark}
+
 \begin{proof}
-    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
-    As $b_2 \to 0$, we have $\lambda \to 0 $ and
-	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
-	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $.
-Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
-	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$
-
-	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$.
-Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
-
-	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
-	\begin{equation*}
-	\begin{split}
-	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
-	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
-	\end{split}
-	\end{equation*}
-
-	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
-	\begin{equation*}
-	\begin{split}
-	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
-	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
-	\end{split}
-	\end{equation*}
-	which are bounded over $[0,T]$.
-Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
-	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
-
-	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
-
-	% b_2 to infty
-
-	Now we consider the case when $b_2 \to \infty$.
-It can be seen later in the proof that both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
-In order to study the limit of $PoA$,  the idea becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
 
@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+\end{proof}
+
+%proposition b_2 \to 0
+\begin{proposition}
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
+	\begin{equation*}
+	\lim_{b_2 \to 0} PoA = 1,
+	\end{equation*}
+	whereas if $\bar{b}_2 > 0$, then:
+	\begin{equation*}
+	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
+	\end{equation*}
+\end{proposition}
+
+\begin{proof}
+	    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
+	As $b_2 \to 0$, we have $\lambda \to 0 $ and
+	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
+	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $.
+Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
+	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$
+
+	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$.
+Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
+
+	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
+	\begin{equation*}
+	\begin{split}
+	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
+	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
+	\end{split}
+	\end{equation*}
+
+	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
+	\begin{equation*}
+	\begin{split}
+	\text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
+	\text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
+	\end{split}
+	\end{equation*}
+	which are bounded over $[0,T]$.
+Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
+	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
+
+	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
+
 \end{proof}

### 2018-07-21 PoA.tex
update prop 6

@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
-	\label{prop:b2}
+\label{prop:b2_to_infty}
 \end{proposition}
@@
 	\end{equation*}
+\label{prop:b2_to_0}
 \end{proposition}
@@
 \begin{proof}
-	    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
+	If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
+
 	As $b_2 \to 0$, we have $\lambda \to 0 $ and
@@
 	and
-	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
+	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
 	and therefore,
-	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
-	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
+	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
 	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
@@
 	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
-	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2)=: c_3,
+	 	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_3,
 	 \end{split} 
@@
 	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
-		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot e^{- \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
-		& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
-		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
+		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot \exp \left( - \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)\right) \\
+		%& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
+		%& \xrightarrow[\bar{b}_2 \to \infty]{}0.
 	\end{array}
 	\end{equation*}
-	Namely, for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
+	The first term on the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$.
+Thus,  for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
 	\begin{equation}
@@
 
+ 	\begin{comment}	
  	Idem, we can show that for $t_1 \in [0,T)$:
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. 
-Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+	\end{comment}
+	Idem we can show that for any $t_1 \in [0,T)$:
+	\begin{equation*}
+		(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} \xrightarrow[\bar{b}_2 \to \infty]{} (r+ \bar{r}(1-\bar{s})^2) c_{\delta_w^{\bar{b}_2 \to \infty}} =: c_4, \qquad \text{where } \quad c_{\delta_w^{\bar{b}_2 \to \infty}} = \sqrt{\frac{q+ \bar{q}(1-s)^2}{r + \bar{r}(1 - \bar{s})^2} }.
+	\end{equation*}
+	Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for any $\bar{b}_2$ large enough.
 
@@
 
-	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
-	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
+	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$.
+Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $w^{\bar{b}_2}_0 \xrightarrow[\bar{b}_2 \to \infty]{} 0$.
+Thus, together with equation (\ref{eq:v_t_new_notation}) we obtain
+	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV} <\infty.$$
 	Therefore, we conclude that:
-	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
+	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
 \end{proof}

### 2018-07-22 PoA.tex
minor edits, problem in Proposition 5

--- 2018-07-21 PoA.tex
@@
 \dot{\bar{x}}^{MFG}_t&=(b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t)\bar{x}^{MFG}_t, \\
-\bar{x}^{MFG}_0&=\mathbb{E}(\xi).
+\bar{x}^{MFG}_0&=\mathbb{E}(\xi),
 \end{split}
@@
 \end{equation}
-And thus,
+where the dot is the standard ODE notation for a derivative. And thus,
 \begin{equation}
@@
 &\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
-&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
-\end{split}
-\end{equation*}
-Then by integration by parts:
+&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \right].\\
+\end{split}
+\end{equation*}
+Then we use integration by parts:
 \begin{equation*}
@@
 = & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
-& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
-\end{split}
-\end{equation*}
-Then using equation (\ref{eq:x_bar_MFG}):
+& + \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg]. \\
+\end{split}
+\end{equation*}
+Then by using equation (\ref{eq:x_bar_MFG}), we have:
 \begin{equation*}
@@
 = & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
-&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
+&+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
 \end{split}
@@
 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
-&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
+&+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
 \end{split}
@@
 \int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
-&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
+&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg].
 \end{split}
@@
 \begin{proposition}
-	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
+	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by:
 	\begin{equation*}
@@
 
-Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by 
+Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by:
 \begin{equation}
@@
 
-We study in the following the variation of $PoA$ by letting one of the coefficients tend to $0$ or to $\infty$.
+We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity.
 It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
@@
 	\end{equation}
-	where
+	where:
 	\begin{IEEEeqnarray*}{rClcrClcrCl}
-		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right) & \qquad & 
-		A^w &=& - (b_1 + \bar{b}_1) & \qquad & 
-		A^\eta &=& - b_1 \nonumber \\
-		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} & \qquad &	
-		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} &\qquad & 
-		B^\eta &=& \frac{b_2^2}{r+ \bar{r}} \nonumber \\
-		C^u &=& \lambda (q + \bar{q}(1-s))& \qquad & 
-		C^w &=& q + \bar{q}(1-s)^2 & \qquad &
-		C^\eta &=& q + \bar{q} \nonumber \\
-		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)) & \qquad & 
-		D^w &=& q_T + \bar{q}_T(1-s_T)^2 & \qquad & 
-		D^\eta &=& q_T + \bar{q}_T 
+		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
+		A^w &=& - (b_1 + \bar{b}_1), & \qquad & 
+		A^\eta &=& - b_1, \nonumber \\
+		B^u &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, & \qquad &	
+		B^w &=& \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}, &\qquad & 
+		B^\eta &=& \frac{b_2^2}{r+ \bar{r}}, \nonumber \\
+		C^u &=& \lambda (q + \bar{q}(1-s)),& \qquad & 
+		C^w &=& q + \bar{q}(1-s)^2, & \qquad &
+		C^\eta &=& q + \bar{q}, \nonumber \\
+		D^u &=& \lambda(q_T + \bar{q}_T(1-s_T)), & \qquad & 
+		D^w &=& q_T + \bar{q}_T(1-s_T)^2, & \qquad & 
+		D^\eta &=& q_T + \bar{q}_T .
 	\end{IEEEeqnarray*}
@@
 \begin{equation}
-		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}
+		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}},
 	\label{eq:riccati_ut_sol}
@@
 \end{equation}
+Also for convenience, recall the definition:
+\begin{equation*}
+\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}.
+\end{equation*}
 
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$,
+	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$, then:
 	\begin{equation*}
@@
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$.	 $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
 	\begin{equation*}
@@
 	\end{equation*}
-
-	%Moreover, if
-	%	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + %\bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
-	%then
-	%$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
-	%otherwise
+	Moreover, if
+		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
+	then
+	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
+	otherwise
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 
-	% b_2 to infty
-
 	Now we consider the case when $b_2 \to \infty$.
@@
 
-	When $b_2 \to \infty$, we have 
-	\begin{equation*}
-	\begin{array}{l}
-	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
-	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
-	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
-	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
+	For the sake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
+	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
+	\begin{equation*}
+	\begin{array}{rclcrcl}
+	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
+	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
+	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
+	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
 	\end{array}
 	\end{equation*}
-	Moreover
+	and 
 	\begin{IEEEeqnarray*}{rCl}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
-		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
+		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
+		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
+		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
 	\end{IEEEeqnarray*}
-	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
-	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
-	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
+
+	Thus, for $b_2$ tends to infinity, we have $$e^{-(\delta_u^+ - \delta_u^-) (T-t)} = e^{-( (2 b_2+\bar{b}_2)\kappa_u (T-t) + \mathcal{O}(b_2^{-1}) }$$
+	which is uniformly bounded over $[0,T]$. Clearly, $e^{-(\delta_u^+ - \delta_u^-) (T-t)} = \mathcal{O}(b_2^{-2}) \to 0$ for $t \in [0, T)$.
+
+	The next step is to give an estimation of $\Delta SC$. To do so, we need to expand the product $B u_t$ up till $b_2^{-2}$. We first notice that for $t \in [0,T)$, 
 	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
-		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
-		&&\\
-		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_3
+		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
+		{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \nonumber \\
+		&=& \frac{ - (\mathcal{O}(b_2^{-1}) + \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \kappa_u + \mathcal{O}(b_2^{-1}) ) + \mathcal{O}(b_2^{-2})}{(\mathcal{O}(b_2^{-1})- \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} ) - \mathcal{O}(b_2^{-2}) } \nonumber \\
+		&=& \zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})
 	\end{IEEEeqnarray*}
-	Idem, we can have for any $t \in [0,T)$,
-	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_4,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} };$$
-	and for any $t \in [0,T)$,
-	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
-	$$
-
-	The next step is to provide an estimation of the order of magnitude of $\Delta SC$ and $SC^{MKV}$.
-For all $t \in [0,T)$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$, $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$ and $h_\eta(b_2,t) = b_2 \eta_t^{b_2}$.\\
-
-	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ for which
-	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
-		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
-		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
-		&=&  \kappa_1 \left[ (b_2 + \bar{b}_2) (u_{t_1}^{b_2}- w_{t_1}^{b_2} ) \right]^2\cdot  \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
-		&= & \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)},
-		\label{eq:delta_SC_b_2_infty}
-	\end{IEEEeqnarray}
-	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\
-
-	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then the Mean Value Theorem yields that there exists a time  $t_3 \in (0,T)$ so that
-	\begin{equation}
-	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = \left(q + \bar{q} + \frac{1}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} \cdot T,
-	\label{eq:vt_int_b_2_infinity}
-	\end{equation}
-	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
-	\begin{IEEEeqnarray}{rCl}
-		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
-		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
-		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
-		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
-	\label{eq:vt_b_2_infinity} 
-	\end{IEEEeqnarray}
-	where
-	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.
-
-	\begin{comment}
-	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
-	\begin{equation}
-		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
-	\label{eq:v_{t_3}_b_2_expansion}
-	\end{equation}
-	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
-	\end{comment}
-
-	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
-	\begin{IEEEeqnarray}{rCl}
-		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)} }{\displaystyle \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
-		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2) e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_\eta(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_1(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
-	\label{eq:delta_SC_SC^MKV_b_2_infinity}
-	\end{IEEEeqnarray}
-	where 
-	$\displaystyle l_{u,v}(b_2) = \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 , \  l_\eta(b_2) =  \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) \frac{b_2 + \bar{b}_2}{b_2}$
-	and $\displaystyle l_1(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}$.	
-	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
-	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
-
-	Finally, we will show that for any fixed $t \in [0,T)$ and $\kappa >0$, we have
-	\begin{equation}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2 \to \infty]{} 0 \qquad \text{and} \qquad b_2 e^{-\kappa b_2 h_\eta(b_2, t)} \xrightarrow[b_2 \to \infty]{} 0.
-	\label{eq:b_2_vt_limit}
-	\end{equation}
-	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ whilst the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$ because equation (\ref{eq:vt_b_2_infinity}) gives raise to
-	$$ b_2 v_T^{b_2} = \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \xrightarrow[b_2 \to \infty]{} 0,$$
-	and so $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
-	Together with the limits of $l_{u,v}(b_2), l_\eta(b_2)$ and $l_1(b_2)$, we have
-	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$
-
-	Take $(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)}$ as an example.
-For any $t \in [0,T)$, we previously showed that $\lim_{b_2 \to \infty} h(b_2,t) = c_3 >0$.
-Let $\epsilon_1 >0$ such that $c_3 - 2 \epsilon_1 >0$.
-Then there exists $b_2^* > 0$ so that for all $b_2 \geq b_2^{*}$ we have $\vert h_u(b_2,t) - c_3 \vert \leq \epsilon_1$.
-Thus $h_u(b_2,t) - c_2 + 2 \epsilon_1 > \epsilon_1$ and
+	Then, we can continue do the expansion and obtain
 	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2, t)} &=& e^{- \kappa (b_2 + \bar{b}_2) (h_u(b_2,t) - c_3 + 2\epsilon_1)} \cdot e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) } \\
-		&\leq & e^{- \kappa (b_2^* + \bar{b}_2) \epsilon_1} \cdot \exp \left( - \kappa(c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) \right).
+		&&(b_2 + \bar{b}_2) ( (b_2 + \bar{b}_2) u_t - \zeta_1 \kappa_u ) \nonumber\\
+		&=& \frac{-(C^u + D^u \delta^+_u) + \mathcal{O}(b_2^{-2}) }{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) + \mathcal{O}(b_2^{-2}) } - (b_2 + \bar{b}_2) \zeta_1 \kappa_u \nonumber \\
+		&=& \frac{-\left( C^u + D^u \delta_u^+ + (b_2 + \bar{b}_2) \zeta_1 \kappa_u \left( \frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right) \right) + \mathcal{O}(b_2^{-2})}{  \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right)-  \mathcal{O}(b_2^{-2})} \nonumber \\
+		&=& \frac{  -\left( C^u +\zeta_1 \kappa_u \frac{\delta_u^-}{b_2 + \bar{b}_2} +  D^u (b_2 + \bar{b}_2)(\frac{\delta^+_u}{b_2 + \bar{b}_2} - \kappa_u) \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1}) } \nonumber \\
+		&=& \frac{- \left( \zeta_1 \kappa_u^2 (1 -\frac{\bar{b}_2}{b_2} )  + \zeta_1 \kappa_u (- \kappa_u + (A^u + \frac{\bar{b}_2}{2} \kappa_u) \frac{1}{b_2}) ) + D^u (b_2 + \bar{b}_2) \left[ (A^u - \frac{\bar{b}_2}{2} \kappa_u )\frac{1}{b_2} + \mathcal{O}(b_2^{-2}) \right] \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1})} \nonumber \\
+		&=& \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u ) + \mathcal{O}(b_2^{-1})
 	\end{IEEEeqnarray*}
-	Since the first term in the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$, then we must have
-	$$ (b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2\to \infty]{} 0, \quad \forall\   0 \leq t < T. $$
-	Thus, the limits in (\ref{eq:b_2_vt_limit}) hold true and following the previous analysis we conclude that 
-	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+	Thus, we have for any given $t \in [0,T)$,
+	\begin{equation*}
+		(b_2+\bar{b}_2)^2 u_t = \zeta_1 \kappa_u (b_2 + \bar{b}_2) + \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u) + h_t(b_2)
+	\end{equation*}
+	where $h_t(b_2) = \mathcal{O}(b_2^{-1})$.
+	Since for any $t \in [0,T)$, $\int_0^t h_s(b_2) ds = \mathcal{O}(b_2^{-1})$ and $B = (b_2+ \bar{b}_2)^2 / \zeta_1$, we deduce that 
+	\begin{equation*}
+	\bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t + \mathcal{O}(b_2^{-1}) }
+	\end{equation*}
+	which tends uniformly to $0$ over $[0,T)$ as $b_2 \to \infty$.
+	Moreover, since 
+	\begin{equation*}
+	\begin{split}
+		(b_2 + \bar{b}_2) (u_t - w_t) 
+	= (\zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})) - (\sqrt{\zeta_1 (q+\bar{q}(1-s)^2)} + \mathcal{O}(b_2^{-1}) )\\
+	= \sqrt{\zeta_1} (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})
+	\end{split}
+	\end{equation*}
+	Thus
+	\begin{IEEEeqnarray*}{rCl}
+		\Delta SC &=& \frac{1}{2} \frac{(b_2+\bar{b}_2)^2}{\zeta_1} \int_0^T (u_t - w_t)^2 (\bar{x}_t^{MFG})^2 dt \\
+		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 \cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
+		&=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
+		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
+	\end{IEEEeqnarray*}
+
+	For the first term, a direct computation yields that
+	\begin{equation*}
+	\begin{array}{rl}
+	&\frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
+	&= \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
+	&= \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
+	\end{array}
+	\end{equation*}
+	For the second term, we know that 
+	$$ \left\vert e^{-2\int_0^t h_s(b_2) ds} - 1 \right\vert \leq \left\vert e^{ \mathcal{O}(b_2^{-1}) } -1 \right\vert = \mathcal{O}(b_2^{-1}).$$
+	Together with the estimation of the first term above, we have 
+	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
+	Hence, we deduce that
+	\begin{equation}
+		\Delta SC = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2}).
+	\end{equation}
+
+	Similarly, we can have $SC^{MKV} =  \frac{\zeta_2}{b_2} + \mathcal{O}(b_2^{-2})$
+	for some constant $\zeta_2 \neq 0$. Thus,
+	\begin{equation}
+		\frac{\Delta SC}{SC^{MKV}} = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{\zeta_2} + \mathcal{O}(b_2^{-1})
+	\end{equation}
+	Therefore, if $ \zeta_1 \kappa_u^2 \neq q + \bar{q}(1-s)^2$, i.e.
+	$$\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
+	we have
+	$$ \lim_{b_2 \to \infty} PoA =: PoA^{\infty,b_2} > 1;$$
+	otherwise $$ \lim_{b_2 \to \infty} PoA = 1.$$
+
 \end{proof}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$
-	then 
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, then:
 	\begin{equation*}
@@
 	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
-
 From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
    	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
-Thus, from Proposition \ref{prop:diff_SC}, and by the bounded convergence theorem, we deduce:
+Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
 	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
@@
 	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
+Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the mean value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
 	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
+		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG,\bar{b}_2} )^2 dt  \nonumber \\
 		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot T \nonumber \\
-		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
-		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) \exp\left( - B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right)  \right]^2 \nonumber \\
+		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot (\mathbb{E}\xi)^2 e^{ 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds } \nonumber \\
+		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) e^{- B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1}  \right]^2 \nonumber \\
 		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2)} \right)^2,
@@
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T (\mathbb{E}\xi)^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+(ToDo: $t_1(\bar{b}_2)$ and $t_2(\bar{b}_2))$.)
 
@@
 We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$.
-Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$.
-Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$.
-Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and
+Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $.
+Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < c_{b_2}$.
+Then $h(\bar{b}_2) - c_3 + 2c_{b_2} > c_{b_2}$ and
 	\begin{equation*}
 	\begin{array}{rl}
-	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
-		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot e^{- \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
-		& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
+		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (h(\bar{b}_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
+		& \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
+		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
 		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
@@
 	\end{equation*}
-	Namely, for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
+	Let $\epsilon>0$. Then there exists a $\bar{b}_2^{*,2}>\bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$, we have:
 	\begin{equation}
@@
  	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} \geq 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
-Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3} \geq 1$ we deduce:
- 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq \frac{c_3+ \epsilon}{(b_2 + \bar{b}^{*,3}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
+Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} > 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
+Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we deduce:
+ 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
  	$$
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for large enough $\bar{b}_2$.
+Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded $c_4 + \epsilon$ for large enough $\bar{b}_2$.
 
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then:
 	\begin{equation*}
@@
   type control.
-\newblock {\em arXiv preprint arXiv:1503.05044}, 2015.
+\newblock {\em arXiv:1503.05044}, 2015.
 
@@
 \newblock On the (in)efficiency of {MFG} equilibria.
-\newblock Technical report, 2018.
+\newblock {\em arXiv:1802.06637}, 2018.
 
@@
   stochastic maximum principle and a transport perspective.
-\newblock Technical report, 2018.
+\newblock {\em arXiv:1802.05754}, 2018.
 
@@
 
+\bibitem{nourian2011mean}
+M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
+\newblock Mean field analysis of controlled {C}ucker-{S}male type flocking:
+Linear analysis and perturbation equations.
+\newblock {\em IFAC Proceedings Volumes}, 44(1):4471--4476, 2011.
+
 \bibitem{nourian2010synthesis}
@@
 
-\bibitem{nourian2011mean}
-M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
-\newblock Mean field analysis of controlled {C}ucker-{S}male type flocking:
-  Linear analysis and perturbation equations.
-\newblock {\em IFAC Proceedings Volumes}, 44(1):4471--4476, 2011.
-
 \bibitem{nourian2013nash}
@@
         \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t\\
-        \bar{y}_T&=(c^x+c^{\bar{x}})\bar{x}_T
+        \bar{y}_T&=(c^x+c^{\bar{x}})\bar{x}_T,
 \end{split}
@@
     \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t \\
-    \bar{x}_0&=\mathbb{E}(\xi)
+    \bar{x}_0&=\mathbb{E}(\xi),
 \end{split}
@@
         dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t \\
-        Y_T&=c^xX_T+c^0
+        Y_T&=c^xX_T+c^0,
 \end{split}
@@
 \end{equation*}
-
 Now we make the ansatz: $Y_t=\eta_t X_t+\chi_t$, which reduces the problem to the ODE system:
@@
 It will also be useful to compute $Var(X_t)$, which we denote by $v_t$.
-After we have solved the above equations, we have
+After we have solved the above equations, we have:
 \begin{equation*}
@@
 		C=&-(b^x+b^{\bar{x}}) \\
-		D=&\ c^x+c^{\bar{x}}
+		D=&\ c^x+c^{\bar{x}}.
 	\end{array}
@@
 		-(b^x+b^{\bar{x}})&>0 \\
-		c^x+c^{\bar{x}}& \geq 0
+		c^x+c^{\bar{x}}& \geq 0.
 	\end{array}

### 2018-07-22 PoA.tex

--- 2018-07-21 PoA.tex
@@
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T (\mathbb{E}\xi)^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+(ToDo: $t_1(\bar{b}_2)$ and $t_2(\bar{b}_2)$.)
 

### 2018-07-22 PoA.tex
update proposition 5

--- 2018-07-21 PoA.tex
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $b_1 > 0$.
+
+	If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 \begin{proof}
-	If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
-
-	As $b_2 \to 0$, we have $\lambda \to 0 $ and
-	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
-	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $.
+	If $\bar{b}_2 =0$, we have 
+	\begin{equation*}
+		B^{b_2} \xrightarrow[b_2 \to 0]{} 0, \quad B^{\eta,b_2} \xrightarrow[b_2 \to 0]{} 0, \quad \lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}
+	\end{equation*}
+	and $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that 
+	$$\lim_{b_2 \to 0} PoA = 1.$$
+
+	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have 
+	\begin{equation*}
+	\begin{array}{l}
+		\lambda \longrightarrow 0\\
+		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
+		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0 
+	\end{array}
+	\end{equation*}
+	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
+	Moreover, we have $\delta^{+,b_2}_u \xrightarrow{} -2A^u >0 $ and $\delta^{-,b_2}_u \to 0$, so that $\delta^{+}_u - \delta^{-}_u \xrightarrow{} -2 A^u > 0$.
 Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
-	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$
-
-	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$.
-Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.
-
-	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
-	\begin{equation*}
-	\begin{split}
-	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
-	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
-	\end{split}
-	\end{equation*}
-
-	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
-	\begin{equation*}
-	\begin{split}
-	\text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
-	\text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
-	\end{split}
-	\end{equation*}
-	which are bounded over $[0,T]$.
-Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
-	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .
-
-	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
+	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
+	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive an uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
+Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
+	\begin{equation*}
+	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
+	\end{equation*}
+
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we have $\displaystyle \bar{x}_t^{MFG,b_2}=\mathbb{E}(\xi) \exp \left( \int_0^t(b_1+\bar{b}_1-B^{b_2} u^{b_2}_s)ds\right)$, and by the bounded convergence theorem we derive that for any fixed $t \in [0,T]$:
+	$$\bar{x}_t^{MFG,b_2} \xrightarrow[b_2 \to \infty]{} \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} > 0$$
+
+	Moreover, since $B^{b_2 \to 0}>0, B^{b_2 \to 0}C^w >0, B^{b_2\to 0}D^w \geq 0$, the limiting solution for $w_t^{b_2}$ is still well defined, denoted by $w_t^{b_2 \to 0}$, which is strictly positive over $[0,T]$.
+We also have $w_t^{b_2}$ is uniformly bounded over $[0,T]$ for all $b_2$ small enough.
+
+	Hence, from Proposition \ref{prop:diff_SC}, the Bounded Convergence theorem, and the assumption on $\xi$, we deduce
+	\begin{equation*}
+	\lim_{b_2 \to 0} \Delta SC = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
+	\end{equation*}
+
+	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
+	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for any $b_2$ small enough and $\eta_t^{b_2}$ converge pointwisely to a strictly positive function $\eta_t^{b_2 \to 0}$.
+More precisely, we can have
+	$$\eta_t^{b_2 \to 0} := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }.$$
+	Again, with equation (\ref{eq:v_t_new_notation}) and the Bounded Convergence theorem, the variance function $v_t^{b_2}$ converges pointwisely to some strictly positive continuous function $\displaystyle v_t^{b_2 \to 0} := Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds$.
+We can then obtain that
+	$$ 0 < \lim_{b_2 \to 0} SC^{MKV} < \infty.$$
+
+	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{b_2 \to 0} > 1.$$
 

### 2018-07-22 PoA.tex
proofreading Proposition 7

--- 2018-07-22 PoA.tex
@@
 From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t>0.$$
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
 	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then:
+	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
 	\begin{equation*}
@@
 	\end{equation*}
-	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. By the assumption on $\lambda$, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
+By our assumption on $\bar{b}_1$, we have $A^{u,b_1\to 0} \neq A^{w,b_1\to 0}$ and thus, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
 
@@
 	\begin{equation*}
-	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}>0.
+	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
 	\end{equation*}
@@
 	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
-	& \geq (q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
+	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
 	\end{split}

### 2018-07-23 PoA.tex
finished Proposition 7 case 3, limit of h(b_1)
update prop 6 second half

--- 2018-07-22 PoA.tex
@@
 	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ for which
+Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ depending on $b_2$ for which
 	\begin{IEEEeqnarray}{rCl}
@@
 		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
-		&=&  \kappa_1 \left[ (b_2 + \bar{b}_2) (u_{t_1}^{b_2}- w_{t_1}^{b_2} ) \right]^2\cdot  \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
-		&= & \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)},
+		&=&  \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2\cdot   (b_2 + \bar{b}_2)^2 \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
+		&=& \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)}
 		\label{eq:delta_SC_b_2_infty}
@@
 	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then the Mean Value Theorem yields that there exists a time  $t_3 \in (0,T)$ so that
-	\begin{equation}
-	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = \left(q + \bar{q} + \frac{1}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} \cdot T,
+Then the Mean Value Theorem yields that there exists a time point $t_3 \in (0,T)$ depending on $b_2$ so that
+	\begin{equation}
+	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2},
 	\label{eq:vt_int_b_2_infinity}
@@
 	\begin{IEEEeqnarray}{rCl}
-		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)} }{\displaystyle \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
-		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2) e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_\eta(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_1(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
+		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)} }{\displaystyle (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
+		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2)^3 e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_{\eta,1}(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_{\eta,2}(b_2)\cdot b_2^3 v_{t_3}^{b_2}+ l_{\eta,3}(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
 	\label{eq:delta_SC_SC^MKV_b_2_infinity}
@@
 	where 
-	$\displaystyle l_{u,v}(b_2) = \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 , \  l_\eta(b_2) =  \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) \frac{b_2 + \bar{b}_2}{b_2}$
-	and $\displaystyle l_1(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}$.	
+	$\displaystyle l_{u,v}(b_2) = \kappa_1   \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 $, and
+	$$ \displaystyle l_{\eta,1}(b_2) =  (q + \bar{q})T  \frac{b_2 + \bar{b}_2}{b_2},\quad 
+	l_{\eta,2}(b_2) = \frac{T}{r+ \bar{r}} (\eta_{t_3}^{b_2})^2 \frac{b_2 + \bar{b}_2}{b_2}, \quad 
+	l_{\eta,3}(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}.$$
+
+	It is not hard to show that $u_t^{b_2}, w_t^{b_2}$ and $\eta_t^{b_2}$ are uniformly bounded over $[0,T]$ for any $b_2$ being large enough.
+One way is to follow the same technique shown in Proposition \ref{prop:r_bar_r} to derive these uniform upper bounds.
+Indeed, for any fixed $b_2$, the solution $(u_t^{b_2})_{0\leq t \leq T}$ is increasing along $[0,T]$ when $B^{b_2} (D^{u,b_2})^2 + 2 A^{u} D^{u,b_2} - C^{u,b_2} > 0$.
+As $B^{b_2} \to \infty, C^{u,b_2} \to C^{u,b_2 \to \infty}$ and $D^{u,b_2} \to D^{u,b_2\to \infty}$, there must exist $b_2^*> 0 $ so that
+	$$\sup_{b_2 \geq b_2^*} \sup_{0 \leq t \leq T} \{ u_t^{b_2}\} \leq \sup_{b_2 \geq b_2^*} \{ u_T^{b_2} \} = \sup_{b_2 \geq b_2^*} \{ D^{u,b_2} \} \leq D^{u,b_2\to \infty} + 1.$$
+	Thus, there exists a constant $M$ independent of $b_2$ such that for any large enough $b_2$:
+	$$ \max \{ l_{u,v}(b_2), \  l_{\eta,1}(b_2), \  l_{\eta,2}(b_2), \  l_{\eta,3}(b_2) \} \leq M.$$
+
+	\begin{comment}
 	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
 	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
-
-	Finally, we will show that for any fixed $t \in [0,T)$ and $\kappa >0$, we have
-	\begin{equation}
-		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2 \to \infty]{} 0 \qquad \text{and} \qquad b_2 e^{-\kappa b_2 h_\eta(b_2, t)} \xrightarrow[b_2 \to \infty]{} 0.
+	\end{comment}
+
+	Finally, we will show that for any $p > 0$ and $\kappa >0$, we have
+	\begin{equation}
+	\begin{array}{ll}
+		& \displaystyle (b_2 + \bar{b}_2)^p \exp \left( - \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t) \right) \xrightarrow[b_2 \to \infty]{} 0 \\
+		and \quad & \displaystyle b_2^p \exp \left( -\kappa b_2 \min_{0 \leq t \leq T} h_\eta(b_2, t) \right) \xrightarrow[b_2 \to \infty]{} 0.
+	\end{array}
 	\label{eq:b_2_vt_limit}
 	\end{equation}
-	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ whilst the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$ because equation (\ref{eq:vt_b_2_infinity}) gives raise to
-	$$ b_2 v_T^{b_2} = \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \xrightarrow[b_2 \to \infty]{} 0,$$
-	and so $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
-	Together with the limits of $l_{u,v}(b_2), l_\eta(b_2)$ and $l_1(b_2)$, we have
+	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ because
+	$$ (b_2 + \bar{b}_2)^3 e^{-\kappa_2 (b_2+ \bar{b}_2) h_u(b_2,t_2)} \leq (b_2 + \bar{b}_2)^3 e^{- \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t)}.
+	$$
+	Meanwhile, the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$, because 
+	$$ h_w(b_2,0) = b_2 \eta_0^{b_2} \xrightarrow[b_2 \to \infty]{} c_4,$$
+	and equation (\ref{eq:vt_b_2_infinity}) gives raise to
+	\begin{IEEEeqnarray*}{rCl} 
+		b_2 v_T^{b_2} &=& \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \\
+		& \leq & (\kappa_3 + \kappa_5) b_2 e^{- \min\{\kappa_4, \kappa_6\} \cdot b_2  \min_{0 \leq t \leq T} h_\eta(b_2, t) } \\
+		& \xrightarrow[b_2 \to \infty]{}& 0,
+	\end{IEEEeqnarray*}
+	and so as for $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$ and $b_2^{3} v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
+	Together with the  we have
 	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$
@@
 	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
-	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive an uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
+	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
 Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
@@
 
+% proposition b2 bar
 \begin{proposition}
@@
 
-	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
-	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
-	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
-	and
+	Now, for the case when $\bar{b}_2 \to \infty$,  we have 
+	\begin{equation*}
+	\begin{array}{l}
+		\lambda^{\bar{b}_2} \to 0;\\
+		B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0
+	\end{array}
+	\end{equation*}
+	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
+	We can show that 
 	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
-	and therefore,
-	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
-	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
-	\begin{equation*}
-	\begin{split}
-	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
-	 	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_3,
-	 \end{split} 
-	\end{equation*}
-	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.
-
-	Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[0,T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[0,T]$ and differentiable over $(0,T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $0< t_2 < t_1 < T$ such that:
+	Idem, we can deduce that 
+	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}}.$$
+
+%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
+	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough.
+Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
+	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1.
+$$
+	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
+	\begin{IEEEeqnarray*}{rCl}
+		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + \left( - \delta_u^{-,\bar{b}_2} + \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) } \\
+		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
+		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
+	\end{IEEEeqnarray*}
+	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough.
+There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
+	\begin{equation*}
+		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
+	\end{equation*}
+	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
+	\begin{equation}
+	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,1}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
+	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
+	\end{equation}
+
+	Our next step is to study the convergence rate of $u_t^{\bar{b}_2}$ and $w_t^{\bar{b}_2}$ for all $t \in [0,T]$.
+First of all, we notice that when $t =T$, $u_T^{\bar{b}_2} = D^{u,\bar{b}_2}$ and $w_T^{\bar{b}_2} = D^w$.
+Thus, note from the assumptions  $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have
+	$$ (b_2 + \bar{b}_2) u_T^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} \frac{b_2 (r+ \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)} =: \zeta > 0.$$
+	and $ w_T^{\bar{b}_2} >0$ being a constant independent of $\bar{b}_2$.
+
+	For any $t \in [0,T)$, equation (\ref{eq:riccati_ut_sol}) yields that
+	\begin{equation*}
+	\begin{split}
+	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \zeta \cdot \frac{1}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} -  \zeta \cdot \frac{1}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
+	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_u,
+	\end{split} 
+	\end{equation*}
+	where the limits is justified by $ \lim_{\bar{b}_2 \to \infty} C^{u,\bar{b}_2} \sqrt{b_2 + \bar{b}_2} = 0$ and $\lim_{\bar{b}_2 \to \infty} (\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} ) = \infty$.
+
+	Idem, for $t \in [0,T)$ we have:
+	$$ (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w. $$
+
+	Recall that when we derive the uniform bound for $u_t^{\bar{b}_2}$ over $[0,T]$, we have chosen $\bar{b}_2^{*,u}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$, $\frac{\delta_u^{+,\bar{b}_2} }{\sqrt{b_2 + \bar{b}_2}} \geq c_{\delta_u^{\bar{b}_2 \to \infty} } - \epsilon_1 > 0$ and $\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \leq 2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1 $.
+Thus, there exists $\bar{b}_2^{*,lower} > \bar{b}_2^{*,u}$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ we can have furthermore $\frac{1}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon_1$.
+
+	Hence, we get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$, namely for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,lower}$:
 	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{\bar{b}_2} \int_0^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
-		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot T \nonumber \\
-		&=& \frac{T  B^{\bar{b}_2} }{2} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
-		&=&  \kappa_1 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot \left[ (b_2 + \bar{b}_2) \exp\left( - B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right)  \right]^2 \nonumber \\
-		&= & \kappa_1 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot \left((b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2)} \right)^2,
-		\label{eq:delta_SC_b_2_bar_infty}
+		\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert &\geq&   (b_2 + \bar{b}_2)^{\frac{3}{2}} \frac{D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }  \nonumber \\
+		&= & \frac{\zeta \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} }{\frac{1}{\sqrt{b_2 + \bar{b}_2}} \cdot \frac{\delta_u^{+,\bar{b}_2}- \delta_u^{-,\bar{b}_2} }{\sqrt{b_2 + \bar{b}_2} } + \frac{\zeta}{r + \bar{r}(1- \bar{s})^2}  } \nonumber \\
+		&\geq & \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1)}{ \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
+	\label{eq:u_t_lower_bound_b2_bar_infty}
 	\end{IEEEeqnarray}
-	where  $\kappa = \frac{t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ and $\kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t_2}^{\bar{b}_2}$.
+
+	Now, we are ready to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
+	%we split the interval $[0,T]$ into two parts $[0,t_\epsilon]$ and $ [t_\epsilon, T]$ in which $0< t_\epsilon < T$ is a time point depending on $\epsilon$, 
+	we split the interval $[0,T]$ into two parts $[0,\frac{T}{2}]$ and $ [\frac{T}{2}, T]$,
+	and then we bound separately the following terms in terms of $\epsilon$:
+	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
+$$
+
+	% the term I_1
+	We first look at the term $I_1$.
+We notice that for any given $\bar{b}_2$, the function $t \mapsto u_t^{\bar{b}_2}$ is increasing over $[0,T]$ when $B^{\bar{b}_2} (D^{u,\bar{b}_2})^2 + 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$.
+	Because the limit $$ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} = \frac{\zeta^2}{r+ \bar{r}(1-\bar{s})^2} >0,$$
+	we can deduce there exists $\bar{b}_2^{*,u,inc}>0$ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,u,inc}$, the function $t \mapsto u_t^{\bar{b}_2}$ is increasing.
+Similarly, there exists $\bar{b}^{*,w,inc}_2$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,w,inc}$ the function $t \mapsto w_t^{\bar{b}_2}$ is increasing.
+
+	Let $\epsilon_2 >0$ such that $ c_u > \epsilon_2$, there must exist $\bar{b}_2^{*,1} :=\bar{b}_2^{*,1}(\epsilon_2) > \max\{\bar{b}_2^{*,u,inc}, \bar{b}_2^{*,w,inc} \} $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,1}$ and all $s \in [0,\frac{T}{2}]$ we have:
+	$$ c_u - \epsilon_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \epsilon_2$$
+	$$ \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \epsilon_2, \quad and \quad 
+	\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \epsilon_2.$$
+	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,1}$ we have
+	\begin{IEEEeqnarray}{rCl}
+		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds  \nonumber \\
+		&=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds} dt \nonumber \\
+		&\leq& \frac{\mathbb{E}(\xi)^2 [2 \epsilon_2^2 + 2 (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2( r + \bar{r}(1-\bar{s})^2)} \int_0^{\frac{T}{2}} \exp \left(- \frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
+		&=& \kappa_1(\epsilon_2) \frac{1}{(b_2 + \bar{b}_2)^{\frac{1}{2}} } \left( 1 - e^{- \kappa_2(\epsilon_2) (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right)\nonumber \\
+		&\leq& \frac{\kappa_1(\epsilon_2)}{\sqrt {b_2 + \bar{b}_2} } \nonumber
+	\end{IEEEeqnarray} 
+	where $\displaystyle \kappa_1(\epsilon_2) = \frac{\mathbb{E}(\xi)^2 [\epsilon_2^2 + (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \epsilon_2)}$ and $ \displaystyle \kappa_2(\epsilon_2) = \frac{(c_u - \epsilon_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are two positive constant independent of $\bar{b}_2$.
+	We can then choose $\bar{b}_2^{*,I_1} := \max \{ \bar{b}_2^{*,1}(\epsilon_2), \left( \frac{\kappa_1(\epsilon_2)}{\epsilon} \right)^2 - b_2 \} $ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have
+	\begin{equation}
+	I_1 \leq \frac{\kappa_1(\epsilon_2)}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon.
+	\label{eq:I_1_b2_bar_infinity}
+	\end{equation}
+
+	% the term I_2
+	Now, we look the term $I_2$.
+Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
+Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
+	\begin{IEEEeqnarray}{rCl}
+		I_2 &=& \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
+		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot \frac{T}{2} \nonumber \\
+		&=& \frac{T  B^{\bar{b}_2} }{4} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
+		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right) \nonumber \\
+		&\leq & \kappa_3 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2,t_2) \right),
+		\label{eq:I_2_b2_bar_inequality}
+	\end{IEEEeqnarray}
+	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ and $\displaystyle \kappa_4 = \frac{T}{(r + \bar{r}(1-\bar{s})^2)} $ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.
+
+	We are going to bound that the last term in (\ref{eq:I_2_b2_bar_inequality}).
+To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} h(\bar{b}_2,s) \geq m_u(\epsilon_1)$.
+	Let $\epsilon_3>0$ such that $m_u(\epsilon_1) -  \epsilon_3 >0$.
+Then there exists $\bar{b}_2^{*,2} = \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3)$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have:
+	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
+	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,2}, \bar{b}_2^{*,lower} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
+	\begin{IEEEeqnarray*}{rCl}
+		I_2 &\leq& \kappa_3 \cdot 4 M(\epsilon_1)^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} m_u(\epsilon_1) \right) \nonumber \\
+		&=& 4\kappa_3 M(\epsilon_1)^2 e^{ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3 \kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}}} \cdot \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)   \nonumber \\
+		&\leq & \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)
+	\end{IEEEeqnarray*}
+	where $\kappa_5 = 4 \kappa_3 M(\epsilon_1)^2$ is independent of $\bar{b}_2$.
+Now, we set $\bar{b}^{*,I_2}_2 := \max\{ \bar{b}_2^{*,3},  \left( \frac{ \ln( \kappa_5(\epsilon_1) / \epsilon)}{ \kappa_4 (m_u(\epsilon_1) - \epsilon_3)} \right)^2 - b_2 \}$, then we have for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$,
+	\begin{equation}
+		I_2 \leq \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right) \leq \epsilon.
+	\label{eq:I_2_b2_bar_infinity}
+	\end{equation}
+
+	Hence, from inequality (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
+	\begin{equation*}
+		\Delta SC = I_1 + I_2 \leq 2\epsilon.
+	\end{equation*} 
+	Therefore, by taking $\epsilon \to 0$, we obtain:
+	\begin{equation*}
+		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
+	\end{equation*}
+
+% comment out: error in using Mean Value theorem	
+\begin{comment}
+	-----------------
 
@@
 	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-	\end{comment}
+
 	Idem we can show that for any $t_1 \in [0,T)$:
@@
 	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
+\end{comment}
 

### 2018-07-23 PoA.tex

@@
 	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
-
 From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t>0.$$
+   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
 	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
@@
 
-% comment out: error in using Mean Value theorem	
-\begin{comment}
-	-----------------
-
-	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$.
-We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$.
-Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$.
-Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$.
-Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and
-	\begin{equation*}
-	\begin{array}{rl}
-	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
-		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot \exp \left( - \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)\right) \\
-		%& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
-		%& \xrightarrow[\bar{b}_2 \to \infty]{}0.
-	\end{array}
-	\end{equation*}
-	The first term on the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$.
-Thus,  for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
-	\begin{equation}
-	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
-	\label{eq:limit_p_f(p)}
-	\end{equation}
-
- 	Now, in order to show that $\Delta SC$ tends to $0$, we need to bound the terms $u_{t_1}^{\bar{b}_2}$ and $w_{t_1}^{\bar{b}_2}$ for large enough $\bar{b}_2$.
-Given $\epsilon>0$, there exists a $\bar{b}_2^{*,3} \geq 1$ such that for any $\bar{b}_2 > \bar{b}_2^{*,3}$ we have $ (b_2 + \bar{b}_2)^{\frac{3}{2}} \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq c_3 + \epsilon$.
-Thus, for any $\bar{b}_2 > \bar{b}_2^{*,3} \geq 1$ we deduce:
- 	$$ \left\vert u_{t_1}^{\bar{b}_2} \right\vert \leq \frac{c_3 + \epsilon}{(b_2 + \bar{b}_2)^{\frac{3}{2}} } \leq \frac{c_3+ \epsilon}{(b_2 + \bar{b}^{*,3}_2)^{\frac{3}{2}} } \leq c_3 + \epsilon.
- 	$$
-
- 	\begin{comment}	
- 	Idem, we can show that for $t_1 \in [0,T)$:
-	\begin{equation*}
-	\begin{split}
-	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
-	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
-	\end{split}
-	\end{equation*}
-	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$.
-
-	Idem we can show that for any $t_1 \in [0,T)$:
-	\begin{equation*}
-		(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} \xrightarrow[\bar{b}_2 \to \infty]{} (r+ \bar{r}(1-\bar{s})^2) c_{\delta_w^{\bar{b}_2 \to \infty}} =: c_4, \qquad \text{where } \quad c_{\delta_w^{\bar{b}_2 \to \infty}} = \sqrt{\frac{q+ \bar{q}(1-s)^2}{r + \bar{r}(1 - \bar{s})^2} }.
-	\end{equation*}
-	Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for any $\bar{b}_2$ large enough.
-
-	Hence, together with equation (\ref{eq:delta_SC_b_2_bar_infty}) and  (\ref{eq:limit_p_f(p)}), we obtain that for any $\epsilon > 0$, there exists a $\bar{b}_2^*$ large enough so that for all $\bar{b}_2 > \bar{b}_2^*$ we have
-	$$ \Delta SC \leq \kappa_1 (c_3 + c_4 + 2 \epsilon)^2 \epsilon^2.$$
-	Thus, by taking $\epsilon \to 0$, we have:
-	$$\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.$$
-\end{comment}
-
 	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$.
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $Var(\xi)>0$, and $\lambda \neq 1$, then
+	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
 	\begin{equation*}
@@
     \end{equation*}
-
     We also have the following lower bound:
@@
 	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
-	& \geq (q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
-	\end{split}
-    \end{equation*}
-    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. It is easy to check that $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
+	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
+	\end{split}
+    \end{equation*}
+
+    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. Since $\lim_{b_1 \to \infty} |A^{u,b_1}|=\infty$, we have:
+    \begin{equation*}
+    \begin{split}
+	    \delta^{+,b_1}_u-\delta^{-,b_1}_u&=2 \sqrt{(A^{u,b_1})^2+BC^u} \\
+	    &\xrightarrow[b_1 \to \infty]{}\infty,
+    \end{split}
+    \end{equation*}
+    and
+    \begin{equation*}
+    \begin{split}
+    -\delta^{-,b_1}_u&=A^{u,b_1}+\sqrt{(A^{u,b_1})^2+BC^u} \\
+    &\xrightarrow[b_1 \to \infty]{}0.
+    \end{split}
+    \end{equation*}    
+    Thus, $\lim_{b_1 \to \infty}h_u(b_1)=\infty$, which implies $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
+
     \begin{equation*}

### 2018-07-23 PoA.tex
update prop 6 second half

@@
 	\begin{equation}
-	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,1}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
+	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
 	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
@@
 	we split the interval $[0,T]$ into two parts $[0,\frac{T}{2}]$ and $ [\frac{T}{2}, T]$,
-	and then we bound separately the following terms in terms of $\epsilon$:
+	and then we bound separately the following two quantities in terms of $\epsilon$:
 	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
@@
 	\begin{IEEEeqnarray}{rCl}
-		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds  \nonumber \\
+		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
 		&=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds} dt \nonumber \\
@@
 	Now, we look the term $I_2$.
-Since $u_t^{\bar{b}_2}$, $w_t^{\bar{b}_2}$ and $\bar{x}_t^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed times $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
+Since $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[T/2,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[T/2,T]$ and differentiable over $(T/2,T)$.
+Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed time points $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
 	\begin{IEEEeqnarray}{rCl}
@@
 	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
-	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,2}, \bar{b}_2^{*,lower} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
+	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,lower}, \bar{b}_2^{*,2} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
 	\begin{IEEEeqnarray*}{rCl}
@@
 
-	Hence, from inequality (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
+	Hence, from inequalities (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
 	\begin{equation*}

### 2018-07-23 PoA.tex
update prop 6 second half

@@
 	\end{equation*} 
-	Therefore, by taking $\epsilon \to 0$, we obtain:
+	Therefore, we can set $\epsilon_1, \epsilon_2,\epsilon_3$ as the following constants:
+	$$ \epsilon_1 := \frac{1}{2} \min \left\{c_{\delta_u^{\bar{b}_2 \to \infty}}, c_{\delta_w^{\bar{b}_2 \to \infty}} \right\}, \quad  \epsilon_2 := \frac{c_u}{2}, \quad \epsilon_3 = \frac{m_u(\epsilon_1)}{2},$$ and following the previous analysis by taking $\epsilon \to 0$, we obtain:
 	\begin{equation*}

### 2018-07-23 PoA.tex
update prop 4 to be continue

@@
 		&&\\
-		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_3
+		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
 	\end{IEEEeqnarray*}
 	Idem, we can have for any $t \in [0,T)$,
-	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_4,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} };$$
-	and for any $t \in [0,T)$,
-	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
+	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
+%	and for any $t \in [0,T)$,
+%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
+%	$$
+
+	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}).
+Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$.
+Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$ we have:
 	$$ 
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
+	$$ 
+	so that
+	\begin{IEEEeqnarray}{rCl}
+		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
+		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
+	\end{IEEEeqnarray}
+
+	% upper bound for u_t, w_t
+	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
+	\begin{equation}
+		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }
+	\end{equation}
+	Hence $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
+	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
+	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$ we have $t \mapsto u_t^{b_2}$ being an increasing function and 
+	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
+	Idem for $t \mapsto w_t^{b_2}$.
+Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we have a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2$ large enough,namely
+	\begin{equation}
+	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
+	\label{eq:ut_wt_upper_bound_b2_infty}
+	\end{equation}
 

### 2018-07-23 PoA.tex
update prop 4 to be continue

@@
 \begin{proof}
-
-	When $b_2 \to \infty$, we have 
+	If $\bar{b}_2 = 0$ then 
+	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
+	otherwise when $b_2 \to \infty$, we still have
+	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
+	For other coefficients, in the case when $b_2 \to \infty$ we have 
 	\begin{equation*}
 	\begin{array}{l}
-	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
 	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
-	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
-	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty}
 	\end{array}
 	\end{equation*}
+	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$.
+
 	Moreover
-	\begin{IEEEeqnarray*}{rCl}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
-		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
-	\end{IEEEeqnarray*}
-	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
+	\begin{equation*}
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
+	\end{equation*}
+	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
 	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$

### 2018-07-24 PoA.tex
minor edits proposition 5

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
+	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $b_1 > 0$.
-
-	If $\bar{b}_2= 0$, then:
+	Assume (\ref{eq:assumptions}), $b_1 > 0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$. If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 	\begin{equation*}
-	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
+	\lim_{b_2 \to 0} PoA =: PoA^{b_2\to 0} > 1.
 	\end{equation*}
@@
 \begin{proof}
-	If $\bar{b}_2 =0$, we have 
-	\begin{equation*}
-		B^{b_2} \xrightarrow[b_2 \to 0]{} 0, \quad B^{\eta,b_2} \xrightarrow[b_2 \to 0]{} 0, \quad \lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}
-	\end{equation*}
-	and $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that 
+	First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
+	\begin{equation*}
+		B^{b_2} \to 0, \quad B^{\eta,b_2} \to 0,
+	\end{equation*}
+	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$.
+We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that:
 	$$\lim_{b_2 \to 0} PoA = 1.$$
 
-	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have 
+	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
 	\begin{equation*}
@@
 		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
-		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0 
+		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
 	\end{array}
@@
 	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
-	Moreover, we have $\delta^{+,b_2}_u \xrightarrow{} -2A^u >0 $ and $\delta^{-,b_2}_u \to 0$, so that $\delta^{+}_u - \delta^{-}_u \xrightarrow{} -2 A^u > 0$.
+	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$.
 Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
-	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
-	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
-Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
+	$$\lim_{b_2 \to 0}u^{b_2}_t = 0 .$$
+	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
+Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
 	\begin{equation*}
@@
 
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we have $\displaystyle \bar{x}_t^{MFG,b_2}=\mathbb{E}(\xi) \exp \left( \int_0^t(b_1+\bar{b}_1-B^{b_2} u^{b_2}_s)ds\right)$, and by the bounded convergence theorem we derive that for any fixed $t \in [0,T]$:
-	$$\bar{x}_t^{MFG,b_2} \xrightarrow[b_2 \to \infty]{} \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} > 0$$
-
-	Moreover, since $B^{b_2 \to 0}>0, B^{b_2 \to 0}C^w >0, B^{b_2\to 0}D^w \geq 0$, the limiting solution for $w_t^{b_2}$ is still well defined, denoted by $w_t^{b_2 \to 0}$, which is strictly positive over $[0,T]$.
-We also have $w_t^{b_2}$ is uniformly bounded over $[0,T]$ for all $b_2$ small enough.
-
-	Hence, from Proposition \ref{prop:diff_SC}, the Bounded Convergence theorem, and the assumption on $\xi$, we deduce
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we derive that for any fixed $t \in [0,T]$:
+	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
+
+	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$.
+It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for $b_2$ small enough.
+Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
 	\begin{equation*}
@@
 	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
-	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for any $b_2$ small enough and $\eta_t^{b_2}$ converge pointwisely to a strictly positive function $\eta_t^{b_2 \to 0}$.
-More precisely, we can have
-	$$\eta_t^{b_2 \to 0} := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }.$$
-	Again, with equation (\ref{eq:v_t_new_notation}) and the Bounded Convergence theorem, the variance function $v_t^{b_2}$ converges pointwisely to some strictly positive continuous function $\displaystyle v_t^{b_2 \to 0} := Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds$.
-We can then obtain that
+	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for any $b_2$ small enough and for each $t \in[0,T]$:
+	$$\lim_{b_2 \to 0}\eta_t^{b_2}=\left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }=:\eta_t^{b_2 \to 0}.$$
+
+	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
+	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0.$$
+	and thus,
 	$$ 0 < \lim_{b_2 \to 0} SC^{MKV} < \infty.$$
-
 	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{b_2 \to 0} > 1.$$

### 2018-07-24 PoA.tex
update prop 4 finish

--- 2018-07-23 PoA.tex
@@
 
-\begin{remark}
-	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
+%\begin{remark}
+%	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
 The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
@@
 Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter.
-\end{remark}
+%\end{remark}
 
@@
 	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
-	otherwise when $b_2 \to \infty$, we still have
+	otherwise when $b_2 \to \infty$ we have
 	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
-	For other coefficients, in the case when $b_2 \to \infty$ we have 
+	For other coefficients, as long as $b_2 \to \infty$ we have 
 	\begin{equation*}
@@
 
-	Moreover
-	\begin{equation*}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
-	\end{equation*}
-	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
+	Moreover, we notice that
+	\begin{equation*}
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
+	\end{equation*}
+	Thus $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
 	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
@@
 	\end{IEEEeqnarray*}
-	Idem, we can have for any $t \in [0,T)$,
+	Idem, for any $t \in [0,T)$,
 	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
@@
 
+	% lower bound for (b_2 + b2 bar) u_t
 	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}).
-Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$.
-Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$ we have:
+Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$.
+Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
 	$$ 
@@
 		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
+	\label{eq:ut_uniform_lower_bound_b2_infinity}
 	\end{IEEEeqnarray}
@@
 	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
-	\begin{equation}
-		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }
-	\end{equation}
-	Hence $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
+	\begin{equation*}
+		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }.
+	\end{equation*}
+	Hence, the function $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
 	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
-	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$ we have $t \mapsto u_t^{b_2}$ being an increasing function and 
+	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ being increasing and 
 	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
 	Idem for $t \mapsto w_t^{b_2}$.
-Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we have a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2$ large enough,namely
+Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we get a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2\geq b_2^{*,upper}$, namely
 	\begin{equation}
@@
 
-	The next step is to provide an estimation of the order of magnitude of $\Delta SC$ and $SC^{MKV}$.
-For all $t \in [0,T)$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$, $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$ and $h_\eta(b_2,t) = b_2 \eta_t^{b_2}$.\\
+	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. The idea is to split the whole interval into two parts $[0,T] =[0,t^*] \cup [t^*,T]$.	
+	Since $v_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV} \geq w_0^{b_2} \mathbb{E}(\xi)^2$.	For the sake of simplicity, for all $t \in [0,T]$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$.
+Thus by multiplying $(b_2 + \bar{b}_2)$ both on the numerator and denominator we get
+	\begin{IEEEeqnarray*}{rCl}
+		0 \leq \frac{\Delta SC}{SC^{MKV}} &\leq& \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{[0,t^*]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{[t^*, T]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
+		&=&  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1 + I_2 \right)
+	\end{IEEEeqnarray*}
+	where
+	\begin{IEEEeqnarray*}{rCl}
+	I_1 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
+	\right) dt \\
+	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt
+	\end{IEEEeqnarray*}
+	and 
+	$$
+		I_2 = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
+	$$	
+	The time point $t^*$ is chosen afterwards in order to make $I_1$ small enough.
+For any given $\epsilon>0$, we want to show that $I_1 \leq \epsilon$ and $I_2 \leq \epsilon$ for any $b_2$ large enough.\\
+
+	% the term I_1
+	We look at the term $I_1$ first.
+Recall that on the closed sub-interval $[0,T/2]$, we have pointwise convergence $(b_2 + \bar{b}_2) u_t^{b_2} \to c_u$ and $(b_2 + \bar{b}_2) w_t^{b_2} \to c_w$.
+Because we have shown that for all $b_2 \geq b_w^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing.
+Consequently, for any positive constant $\epsilon_2 < \min \{ c_u, c_w \} $, saying for example $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w \}$, there exists $b_2^{*,I_1} := b_2^{*,I_1}(\epsilon_2) > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	\begin{equation*}
+	\left\{
+	\begin{array}{lclclclcl}
+		c_u - \epsilon_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \epsilon_2 \\
+		c_w - \epsilon_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \epsilon_2 
+	\end{array}
+	\right.
+	\end{equation*}
+	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*] \subset [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$,
+	$$
+		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \epsilon_2)^2 + (c_w+ \epsilon_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \epsilon_2) t,
+	$$
+	which implies
+	\begin{IEEEeqnarray}{rCl}
+		I_1 &=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt \nonumber \\
+		&\leq& \frac{e^{(b_1 + \bar{b}_1) T}\cdot  2[ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{r+ \bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2) \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
+		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 \cdot (b_2 + \bar{b}_2) t^* } \right) 
+	\label{eq:I1_ineq_b2_infinity}
+	\end{IEEEeqnarray}
+	where the coefficients $ \displaystyle \kappa_1 := \kappa_1(\epsilon_2) = \frac{e^{(b_1 + \bar{b}_1) T}\cdot  [ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{c_u - \epsilon_2}$ and $\displaystyle \kappa_2 := \kappa_2(\epsilon_2) = \frac{2 (c_u - \epsilon_2)}{r + \bar{r}(1-\bar{s})^2} $ independent of $b_2$.
+	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we let $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}$ as previous, and choose the time point $t^*$ as following
+	\begin{equation}
+	 t^* := t^*(\epsilon) = \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
+	\label{eq:t^*_b2_infty} 
+	\end{equation}
+	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that
+	\begin{equation}
+		I_1 \leq \kappa_1 \left[1 - e^{- \kappa_2 \cdot (b_2^{*,I_2} + \bar{b}_2) \cdot t^*}  \right] = \epsilon.\\
+	\label{eq:I1_b2_infty}
+	\end{equation}
+
+	% check I_2
+	Now we look at the term $I_2$ with the above given $t^*(\epsilon)$. 
+	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$.
+We can apply the Mean Value theorem and deduce that there exists a time points $t_1$ depending on $b_2$ which satisfy $t^* < t_1 < T$ such that:
+	\begin{IEEEeqnarray}{rCl}
+		I_2 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt \nonumber \\
+		&=&  \frac{(u_{t_1}^{b_2} - w_{t_1}^{b_2})^2 e^{2(b_1 + \bar{b}_1)t_1} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1} h_u(b_2,s) ds }.
+	\label{eq:I2_b2_infity_Mean_Value}
+	\end{IEEEeqnarray}	
+	We know from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max \{b_2^{*,upper}, b_2^{*,lower} \}$ and all $t \in [0,T]$:
+	\begin{equation*}
+		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M
+	\end{equation*}
+	and 
+	\begin{equation*}
+		\int_0^{t_1} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq m_u(\epsilon_1) \cdot t^*.
+	\end{equation*}
+	Together with equation (\ref{eq:I2_b2_infity_Mean_Value}) give raise to
+	\begin{equation*}
+		I_2 \leq  \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)}
+	\end{equation*}
+	where $\kappa_3 = \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} $ and $\kappa_4 := \kappa_4(\epsilon, \epsilon_1) =  \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2}$ are two positive constants independent of $b_2$.
+	Hence, there exists $b_2^{*,I_2} := b_2^{*,I_2}(\epsilon, \epsilon_1) > \max \{b_2^{*,upper}, b_2^{*,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$, 
+	\begin{equation}
+		I_2 \leq \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon.
+	\label{eq:I2_b2_infty}
+	\end{equation}
+
+	Let $\epsilon_1, \epsilon_2$ be two constants as follow:
+	$$ \epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}\quad \text{and} \quad \epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}.$$ Hence, 
+	for any $\epsilon>0$, we can choose $t^*$ as shown in equation (\ref{eq:t^*_b2_infty}) so that for all $b_2 \geq b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}(\epsilon) \}$, the inequalities (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) yield
+	\begin{equation*}
+		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \epsilon_2} 
+	\end{equation*}
+	Therefore, by letting $\epsilon \to 0$, we conclude that:
+	\begin{equation*}
+		\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0, 
+	\end{equation*}
+	which implies immediately
+	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+
+\begin{comment}
 
@@
 	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
-	\end{comment}
+	%%%%%%% end{comment}
 
@@
 	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
-	\end{comment}
+	%%%%%%% end{comment}
 
@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+\end{comment}
+
 \end{proof}
@@
 Since $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[T/2,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[T/2,T]$ and differentiable over $(T/2,T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists two fixed time points $t_1$ and $t_2$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ and $0 < t_2 < t_1 <T$ such that:
+Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists a time points $t_1$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ such that:
 	\begin{IEEEeqnarray}{rCl}
@@
 		&=& \frac{T  B^{\bar{b}_2} }{4} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
-		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} u_{t_2}^{\bar{b}_2} \cdot t_1 \right) \nonumber \\
-		&\leq & \kappa_3 (u_{t_1}^{\bar{b}_2} - w_{t_1}^{\bar{b}_2} )^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2,t_2) \right),
+		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} \int_0^{\frac{T}{2}} u_s^{\bar{b}_2} ds \right)
 		\label{eq:I_2_b2_bar_inequality}
 	\end{IEEEeqnarray}
-	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ and $\displaystyle \kappa_4 = \frac{T}{(r + \bar{r}(1-\bar{s})^2)} $ are two positive constants independent of $\bar{b}_2$, and $ \displaystyle h(\bar{b}_2,t) = (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{t}^{\bar{b}_2}$.
+	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ is a constant independent of $\bar{b}_2$.
 
 	We are going to bound that the last term in (\ref{eq:I_2_b2_bar_inequality}).
-To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} h(\bar{b}_2,s) \geq m_u(\epsilon_1)$.
+To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} \geq m_u(\epsilon_1)$.
 	Let $\epsilon_3>0$ such that $m_u(\epsilon_1) -  \epsilon_3 >0$.
-Then there exists $\bar{b}_2^{*,2} = \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3)$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have:
+Then there exists $\bar{b}_2^{*,2} := \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3) >0 $ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have:
 	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
-	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,lower}, \bar{b}_2^{*,2} \}$ and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
+	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,lower}, \bar{b}_2^{*,2} \}$ and $\kappa_4 = \frac{T}{r + \bar{r}(1-\bar{s})^2}$, and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
 	\begin{IEEEeqnarray*}{rCl}

### 2018-07-24 PoA.tex
update again prop 4 & 5

@@
 	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
+	We can also have $\bar{x}_t^{MFG,b_2}$ being uniformly bounded by the constant $\vert \mathbb{E}(\xi) \vert e^{(b_1 + \bar{b}_1) T}$ for any $t \in [0,T]$ and $b_2 > 0$.
 

### 2018-07-24 PoA.tex
update again prop 4 & 5

@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$
-
-\begin{comment}
-
-	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ depending on $b_2$ for which
-	\begin{IEEEeqnarray}{rCl}
-		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
-		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
-		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
-		&=&  \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2\cdot   (b_2 + \bar{b}_2)^2 \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
-		&=& \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)}
-		\label{eq:delta_SC_b_2_infty}
-	\end{IEEEeqnarray}
-	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\
-
-	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$.
-Then the Mean Value Theorem yields that there exists a time point $t_3 \in (0,T)$ depending on $b_2$ so that
-	\begin{equation}
-	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2},
-	\label{eq:vt_int_b_2_infinity}
-	\end{equation}
-	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
-	\begin{IEEEeqnarray}{rCl}
-		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
-		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
-		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
-		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
-	\label{eq:vt_b_2_infinity} 
-	\end{IEEEeqnarray}
-	where
-	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.
-
-	\begin{comment}
-	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
-	\begin{equation}
-		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
-	\label{eq:v_{t_3}_b_2_expansion}
-	\end{equation}
-	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
-	%%%%%%% end{comment}
-
-	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
-	\begin{IEEEeqnarray}{rCl}
-		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 \cdot (b_2 + \bar{b}_2)^2 e^{-\kappa_2 (b_2+ \bar{b}_2)h_u(b_2,t_2)} }{\displaystyle (q + \bar{q} ) T v_{t_3}^{b_2} +  \frac{T}{r + \bar{r}} (\eta_{t_3}^{b_2})^2 \cdot b_2^2 v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
-		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2)^3 e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_{\eta,1}(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_{\eta,2}(b_2)\cdot b_2^3 v_{t_3}^{b_2}+ l_{\eta,3}(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
-	\label{eq:delta_SC_SC^MKV_b_2_infinity}
-	\end{IEEEeqnarray}
-	where 
-	$\displaystyle l_{u,v}(b_2) = \kappa_1   \left(u_{t_1}^{b_2}- w_{t_1}^{b_2} \right)^2 $, and
-	$$ \displaystyle l_{\eta,1}(b_2) =  (q + \bar{q})T  \frac{b_2 + \bar{b}_2}{b_2},\quad 
-	l_{\eta,2}(b_2) = \frac{T}{r+ \bar{r}} (\eta_{t_3}^{b_2})^2 \frac{b_2 + \bar{b}_2}{b_2}, \quad 
-	l_{\eta,3}(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}.$$
-
-	It is not hard to show that $u_t^{b_2}, w_t^{b_2}$ and $\eta_t^{b_2}$ are uniformly bounded over $[0,T]$ for any $b_2$ being large enough.
-One way is to follow the same technique shown in Proposition \ref{prop:r_bar_r} to derive these uniform upper bounds.
-Indeed, for any fixed $b_2$, the solution $(u_t^{b_2})_{0\leq t \leq T}$ is increasing along $[0,T]$ when $B^{b_2} (D^{u,b_2})^2 + 2 A^{u} D^{u,b_2} - C^{u,b_2} > 0$.
-As $B^{b_2} \to \infty, C^{u,b_2} \to C^{u,b_2 \to \infty}$ and $D^{u,b_2} \to D^{u,b_2\to \infty}$, there must exist $b_2^*> 0 $ so that
-	$$\sup_{b_2 \geq b_2^*} \sup_{0 \leq t \leq T} \{ u_t^{b_2}\} \leq \sup_{b_2 \geq b_2^*} \{ u_T^{b_2} \} = \sup_{b_2 \geq b_2^*} \{ D^{u,b_2} \} \leq D^{u,b_2\to \infty} + 1.$$
-	Thus, there exists a constant $M$ independent of $b_2$ such that for any large enough $b_2$:
-	$$ \max \{ l_{u,v}(b_2), \  l_{\eta,1}(b_2), \  l_{\eta,2}(b_2), \  l_{\eta,3}(b_2) \} \leq M.$$
-
-	\begin{comment}
-	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
-	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$
-	%%%%%%% end{comment}
-
-	Finally, we will show that for any $p > 0$ and $\kappa >0$, we have
-	\begin{equation}
-	\begin{array}{ll}
-		& \displaystyle (b_2 + \bar{b}_2)^p \exp \left( - \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t) \right) \xrightarrow[b_2 \to \infty]{} 0 \\
-		and \quad & \displaystyle b_2^p \exp \left( -\kappa b_2 \min_{0 \leq t \leq T} h_\eta(b_2, t) \right) \xrightarrow[b_2 \to \infty]{} 0.
-	\end{array}
-	\label{eq:b_2_vt_limit}
-	\end{equation}
-	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ because
-	$$ (b_2 + \bar{b}_2)^3 e^{-\kappa_2 (b_2+ \bar{b}_2) h_u(b_2,t_2)} \leq (b_2 + \bar{b}_2)^3 e^{- \kappa (b_2 + \bar{b}_2) \min_{0 \leq t \leq T} h_u(b_2,t)}.
-	$$
-	Meanwhile, the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$, because 
-	$$ h_w(b_2,0) = b_2 \eta_0^{b_2} \xrightarrow[b_2 \to \infty]{} c_4,$$
-	and equation (\ref{eq:vt_b_2_infinity}) gives raise to
-	\begin{IEEEeqnarray*}{rCl} 
-		b_2 v_T^{b_2} &=& \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \\
-		& \leq & (\kappa_3 + \kappa_5) b_2 e^{- \min\{\kappa_4, \kappa_6\} \cdot b_2  \min_{0 \leq t \leq T} h_\eta(b_2, t) } \\
-		& \xrightarrow[b_2 \to \infty]{}& 0,
-	\end{IEEEeqnarray*}
-	and so as for $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$ and $b_2^{3} v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
-	Together with the  we have
-	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$
-
-	Take $(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)}$ as an example.
-For any $t \in [0,T)$, we previously showed that $\lim_{b_2 \to \infty} h(b_2,t) = c_3 >0$.
-Let $\epsilon_1 >0$ such that $c_3 - 2 \epsilon_1 >0$.
-Then there exists $b_2^* > 0$ so that for all $b_2 \geq b_2^{*}$ we have $\vert h_u(b_2,t) - c_3 \vert \leq \epsilon_1$.
-Thus $h_u(b_2,t) - c_2 + 2 \epsilon_1 > \epsilon_1$ and
-	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2, t)} &=& e^{- \kappa (b_2 + \bar{b}_2) (h_u(b_2,t) - c_3 + 2\epsilon_1)} \cdot e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) } \\
-		&\leq & e^{- \kappa (b_2^* + \bar{b}_2) \epsilon_1} \cdot \exp \left( - \kappa(c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) \right).
-	\end{IEEEeqnarray*}
-	Since the first term in the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$, then we must have
-	$$ (b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2\to \infty]{} 0, \quad \forall\   0 \leq t < T. $$
-	Thus, the limits in (\ref{eq:b_2_vt_limit}) hold true and following the previous analysis we conclude that 
-	$$ \lim_{b_2 \to \infty} PoA = 1.$$
-\end{comment}
 

### 2018-07-24 PoA.tex
update again prop 4 finish
stylistic edits

@@
 \begin{equation}
-		u_t= \frac{(C^u+D^u \delta^+_u) - (C^u+D^u \delta^-_u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}}{(-\delta^-_u + D^u B^u) + (\delta^+_u - D^u B^u) e^{-(\delta_u^+ - \delta_u^-)(T-t)}},
+		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{D^u B^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
 	\label{eq:riccati_ut_sol}
@@
 where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$.
-Note that under the above conditions, we have $\delta^-_u<0<\delta^+_u$ and thus, $u_t \geq 0$ for all $t\in[0,T]$.
-We have analogous expressions for $w_t$ and $\eta_t$, which are also nonnegative, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively.
-Note that $B^u=B^w=:B$, and the above conditions on the parameters $B$, $C^u$, $D^u$, $C^w$, $D^w$, $B^\eta$, $C^\eta$, and $D^\eta$ are exactly the conditions in assumption (\ref{eq:assumptions}).
+Under assumption (\ref{eq:assumptions}), the above conditions on $B^u$, $C^u$, and $D^u$ are satisfied, and we have $\delta^-_u<0<\delta^+_u$, $u_t > 0$ for all $t\in[0,T)$, and $u_T \geq 0$.
+We have analogous expressions for $w_t$ and $\eta_t$, in terms of $\delta^\pm_w$ and $\delta^\pm_{\eta}$, respectively.
+Note that $B^u=B^w=:B$.
 
@@
 	\begin{IEEEeqnarray*}{rl}
-		&\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert\\
-		&= C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
+		C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +& D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )\\
 		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
@@
 	\begin{IEEEeqnarray*}{rl}
-		& \left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert \\
-		&=  D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\		
+		D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)})& + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
 		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
@@
 	\begin{IEEEeqnarray}{rCl}
-		\left\vert u_t^{r} \right\vert  &=& \frac{\left\vert (C^{u,r} + D^{u,r} \delta^{+,r}_u) - (C^{u,r} + D^{u,r} \delta^{-,r}_u) e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} \right\vert}{\left\vert ( -\delta^{-,r}_u + D^{u,r} B^{r} ) + (\delta^{+,r}_u - D^{u,r} B^{r} ) e^{-(\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} \right\vert } \nonumber \\
+		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
 		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
@@
 	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
 	$$ 
@@
 		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
-		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
+		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
 	\label{eq:ut_uniform_lower_bound_b2_infinity}
@@
 	\begin{IEEEeqnarray*}{rCl}
-		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + \left( - \delta_u^{-,\bar{b}_2} + \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) } \\
+		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right)+ \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} - \delta_u^{-,\bar{b}_2} } \\
 		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
@@
 \begin{equation}
-		\rho_t= \frac{(C+D \delta^+) - (C+D \delta^-) e^{-(\delta^+ - \delta^-)(T-t)}}{(-\delta^- + D B) + (\delta^+ - D B) e^{-(\delta^+ - \delta^-)(T-t)}}
+		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{D B(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- }
 	\label{eq:riccati_ut_sol_app}

### 2018-07-24 PoA.tex
minor edits

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
+	Assuming (\ref{eq:assumptions}), $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 \begin{proof}
-	If $\bar{b}_2 = 0$ then 
-	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
-	otherwise when $b_2 \to \infty$ we have
-	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
-	For other coefficients, as long as $b_2 \to \infty$ we have 
+	When $b_2 \to \infty$, we have:
 	\begin{equation*}
 	\begin{array}{l}
+	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
 	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
-	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty}
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty},
 	\end{array}
 	\end{equation*}
-	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$.
-
-	Moreover, we notice that
-	\begin{equation*}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
-	\end{equation*}
-	Thus $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
-	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
-	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
+	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
+	\begin{equation*}
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
+	\end{equation*}
+	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
+	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
 	\begin{IEEEeqnarray*}{rCl}

### 2018-07-24 PoA.tex
minor edits again

@@
 	% lower bound for (b_2 + b2 bar) u_t
-	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}).
-Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$.
+	Next, we derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
+Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
 Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
 	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
 	$$ 
-	so that
+	and thus,
 	\begin{IEEEeqnarray}{rCl}
@@
 	% upper bound for u_t, w_t
-	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
-	\begin{equation*}
-		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }.
-	\end{equation*}
-	Hence, the function $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
+	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
+	\begin{equation*}
+		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
+	\end{equation*}
+	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
 	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
-	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ being increasing and 
-	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
+	there exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
+	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$ (ToDo: why 1 and not $\epsilon_1$?)
 	Idem for $t \mapsto w_t^{b_2}$.
-Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we get a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2\geq b_2^{*,upper}$, namely
+Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w\}$.
+Then for $b_2\geq b_2^{*,upper}$, we have the uniform upper bound:
 	\begin{equation}
@@
 	\end{equation}
+	(ToDo: why should we write the uniform upper bounds together? We can give them individually.)
 

### 2018-07-25 PoA.tex
minor edits again 2

@@
 Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
-Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
+Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$,
 	$$ 
@@
 
-	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. The idea is to split the whole interval into two parts $[0,T] =[0,t^*] \cup [t^*,T]$.	
-	Since $v_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV} \geq w_0^{b_2} \mathbb{E}(\xi)^2$.	For the sake of simplicity, for all $t \in [0,T]$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$.
-Thus by multiplying $(b_2 + \bar{b}_2)$ both on the numerator and denominator we get
+	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts, $[0,t^*] \cup [t^*,T]$.	
+	Since $v_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
+We have:
 	\begin{IEEEeqnarray*}{rCl}
-		0 \leq \frac{\Delta SC}{SC^{MKV}} &\leq& \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{[0,t^*]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{[t^*, T]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
+		0 \leq \frac{\Delta SC}{SC^{MKV}} &\leq& \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{t^*} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{t^*}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
 		&=&  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1 + I_2 \right)
 	\end{IEEEeqnarray*}
-	where
+	where:
 	\begin{IEEEeqnarray*}{rCl}
@@
 	\right) dt \\
-	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt
+	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt,
 	\end{IEEEeqnarray*}
-	and 
+	and:
 	$$
@@
 	$$	
-	The time point $t^*$ is chosen afterwards in order to make $I_1$ small enough.
-For any given $\epsilon>0$, we want to show that $I_1 \leq \epsilon$ and $I_2 \leq \epsilon$ for any $b_2$ large enough.\\
+	The time point $t^*$ will be chosen such that for any given $\epsilon>0$, we will have $I_1 \leq \epsilon$ and $I_2 \leq \epsilon$ for large $b_2$.
 
 	% the term I_1
-	We look at the term $I_1$ first.
-Recall that on the closed sub-interval $[0,T/2]$, we have pointwise convergence $(b_2 + \bar{b}_2) u_t^{b_2} \to c_u$ and $(b_2 + \bar{b}_2) w_t^{b_2} \to c_w$.
-Because we have shown that for all $b_2 \geq b_w^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing.
-Consequently, for any positive constant $\epsilon_2 < \min \{ c_u, c_w \} $, saying for example $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w \}$, there exists $b_2^{*,I_1} := b_2^{*,I_1}(\epsilon_2) > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	First, consider $I_1$.
+Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_w^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing.
+Consequently, for any $\epsilon_2>0$ with $\epsilon_2 < \min \{ c_u, c_w \} $, there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
 	\begin{equation*}
@@
 	\end{equation*}
-	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*] \subset [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$,
+	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*] \subset [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
 	$$
@@
 	$$
-	which implies
+	which implies:
 	\begin{IEEEeqnarray}{rCl}
-		I_1 &=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt \nonumber \\
-		&\leq& \frac{e^{(b_1 + \bar{b}_1) T}\cdot  2[ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{r+ \bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2) \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
-		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 \cdot (b_2 + \bar{b}_2) t^* } \right) 
+		I_1 &\leq& \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  2[ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{r+ \bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2) \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
+		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 (b_2 + \bar{b}_2) t^* } \right), 
 	\label{eq:I1_ineq_b2_infinity}
 	\end{IEEEeqnarray}
-	where the coefficients $ \displaystyle \kappa_1 := \kappa_1(\epsilon_2) = \frac{e^{(b_1 + \bar{b}_1) T}\cdot  [ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{c_u - \epsilon_2}$ and $\displaystyle \kappa_2 := \kappa_2(\epsilon_2) = \frac{2 (c_u - \epsilon_2)}{r + \bar{r}(1-\bar{s})^2} $ independent of $b_2$.
-	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we let $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}$ as previous, and choose the time point $t^*$ as following
+	where the coefficients $ \displaystyle \kappa_1 := \kappa_1(\epsilon_2) = \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  [ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{c_u - \epsilon_2}>0$ and $\displaystyle \kappa_2 := \kappa_2(\epsilon_2) = \frac{2 (c_u - \epsilon_2)}{r + \bar{r}(1-\bar{s})^2}>0$ are independent of $b_2$.
+	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we choose the time point $t^*$ as follows:
 	\begin{equation}
@@
 	\end{equation}
-	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that
-	\begin{equation}
-		I_1 \leq \kappa_1 \left[1 - e^{- \kappa_2 \cdot (b_2^{*,I_2} + \bar{b}_2) \cdot t^*}  \right] = \epsilon.\\
+	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that:
+	\begin{equation}
+		I_1 \leq \kappa_1 \left(1 - e^{- \kappa_2 (b_2^{*,I_2} + \bar{b}_2) t^*}  \right) \leq \epsilon.\\
 	\label{eq:I1_b2_infty}

### 2018-07-25 PoA.tex
minor edits again 3

@@
 		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)>0
 	\label{eq:ut_uniform_lower_bound_b2_infinity}
@@
 	% check I_2
-	Now we look at the term $I_2$ with the above given $t^*(\epsilon)$. 
-	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$.
-We can apply the Mean Value theorem and deduce that there exists a time points $t_1$ depending on $b_2$ which satisfy $t^* < t_1 < T$ such that:
-	\begin{IEEEeqnarray}{rCl}
-		I_2 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt \nonumber \\
-		&=&  \frac{(u_{t_1}^{b_2} - w_{t_1}^{b_2})^2 e^{2(b_1 + \bar{b}_1)t_1} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1} h_u(b_2,s) ds }.
+	Next, consider $I_2$ with $t^*(\epsilon)$ as in equation (\ref{eq:t^*_b2_infty}). 
+	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_{t^*}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{t^*}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$.
+We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1$ with $t^* < t_1 < T$ such that:
+	\begin{equation}
+		I_2 = (T-t^*) \cdot \frac{(u_{t_1}^{b_2} - w_{t_1}^{b_2})^2 e^{2(b_1 + \bar{b}_1)t_1} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1} h_u(b_2,s) ds }.
 	\label{eq:I2_b2_infity_Mean_Value}
-	\end{IEEEeqnarray}	
+	\end{equation}	
 	We know from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max \{b_2^{*,upper}, b_2^{*,lower} \}$ and all $t \in [0,T]$:
 	\begin{equation*}
-		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M
+		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M,
 	\end{equation*}
@@
 	\begin{equation*}
-		\int_0^{t_1} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq m_u(\epsilon_1) \cdot t^*.
-	\end{equation*}
-	Together with equation (\ref{eq:I2_b2_infity_Mean_Value}) give raise to
-	\begin{equation*}
-		I_2 \leq  \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)}
-	\end{equation*}
-	where $\kappa_3 = \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} $ and $\kappa_4 := \kappa_4(\epsilon, \epsilon_1) =  \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2}$ are two positive constants independent of $b_2$.
-	Hence, there exists $b_2^{*,I_2} := b_2^{*,I_2}(\epsilon, \epsilon_1) > \max \{b_2^{*,upper}, b_2^{*,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$, 
-	\begin{equation}
-		I_2 \leq \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon.
+		\int_0^{t_1} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq t^* m_u(\epsilon_1).
+	\end{equation*}
+	Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
+	\begin{equation*}
+		I_2 \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
+	\end{equation*}
+	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} $ and $\kappa_4 := \kappa_4(\epsilon, \epsilon_1) =  \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2}$ are two positive constants independent of $b_2$.
+	Hence, there exists $b_2^{*,I_2} := b_2^{*,I_2}(\epsilon, \epsilon_1) > \max \{b_2^{*,upper}, b_2^{*,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
+	\begin{equation}
+		I_2 \leq \epsilon.
 	\label{eq:I2_b2_infty}
@@
 	$$ \epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}\quad \text{and} \quad \epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}.$$ Hence, 
-	for any $\epsilon>0$, we can choose $t^*$ as shown in equation (\ref{eq:t^*_b2_infty}) so that for all $b_2 \geq b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}(\epsilon) \}$, the inequalities (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) yield
-	\begin{equation*}
-		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \epsilon_2} 
+	for any $\epsilon>0$, we can choose $t^*$ as in equation (\ref{eq:t^*_b2_infty}) so that for all $b_2 \geq b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}(\epsilon) \}$, the inequalities (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) yield:
+	\begin{equation*}
+		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \epsilon_2}.
 	\end{equation*}
@@
 	\end{equation*}
-	which implies immediately
+	and thus,
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$

### 2018-07-25 PoA.tex
edits, and mistake found in Proposition 4!

@@
 	Next, we derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
-Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
+Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
 Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$,
 	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \epsilon_1,
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
 	$$ 
@@
 		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ \epsilon_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)>0
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
 	\label{eq:ut_uniform_lower_bound_b2_infinity}
@@
 	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
-	there exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
-	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$ (ToDo: why 1 and not $\epsilon_1$?)
-	Idem for $t \mapsto w_t^{b_2}$.
-Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w\}$.
-Then for $b_2\geq b_2^{*,upper}$, we have the uniform upper bound:
-	\begin{equation}
-	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
-	\label{eq:ut_wt_upper_bound_b2_infty}
-	\end{equation}
-	(ToDo: why should we write the uniform upper bounds together? We can give them individually.)
-
-	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts, $[0,t^*] \cup [t^*,T]$.	
-	Since $v_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
+	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
+	there exists $b_2^{*,u,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
+	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + \zeta_1.$$
+	Thus,
+	\begin{equation}
+	\left| u_t^{b_2}\right|\leq D^{u,b_2 \to \infty} + \zeta_1 ,\ t\in[0,T],\ b_2 > b_2^{*,u,upper},
+	\label{eq:u_t_bound}
+	\end{equation}
+	and by the same argument,
+	\begin{equation}	
+	\left| w_t^{b_2}\right|\leq D^{w} ,\ t\in[0,T],\ b_2 > b_2^{*,w,upper}.
+	\label{eq:w_t_bound}
+	\end{equation}
+	Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$.
+
+	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,t^*]$ and $[t^*,T]$.	
+	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
 We have:
-	\begin{IEEEeqnarray*}{rCl}
-		0 \leq \frac{\Delta SC}{SC^{MKV}} &\leq& \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{t^*} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{t^*}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
-		&=&  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1 + I_2 \right)
-	\end{IEEEeqnarray*}
+	\begin{equation}
+	\begin{split}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{t^*} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{t^*}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
+		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
+	\end{split}
+	\label{eq:I_1_plus_I_2}
+	\end{equation}
 	where:
 	\begin{IEEEeqnarray*}{rCl}
-	I_1 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
+	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
 	\right) dt \\
@@
 	$$
-		I_2 = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
+		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
 	$$
-	The time point $t^*$ will be chosen such that for any given $\epsilon>0$, we will have $I_1 \leq \epsilon$ and $I_2 \leq \epsilon$ for large $b_2$.
+
+	Fix $\epsilon>0$. In the following, we show that the time point $t^*$ can be chosen such that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
 
 	% the term I_1
-	First, consider $I_1$.
-Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_w^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing.
-Consequently, for any $\epsilon_2>0$ with $\epsilon_2 < \min \{ c_u, c_w \} $, there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
-	\begin{equation*}
-	\left\{
+	First, consider $I_1^{b_2}$.
+Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
+(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\frac{1}{2} \min \{ c_u, c_w \} $.
+Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	\begin{equation*}
 	\begin{array}{lclclclcl}
-		c_u - \epsilon_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \epsilon_2 \\
-		c_w - \epsilon_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \epsilon_2 
+		c_u - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \zeta_2, \\
+		c_w - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \zeta_2.
 	\end{array}
-	\right.
-	\end{equation*}
-	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*] \subset [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
+	\end{equation*}
+	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*]$ and $b_2 \geq b_2^{*,I_1}$, we have:
 	$$
-		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \epsilon_2)^2 + (c_w+ \epsilon_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \epsilon_2) t,
+		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \zeta_2)^2 + (c_w+ \zeta_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \zeta_2) t.
 	$$
-	which implies:
+	Therefore,
 	\begin{IEEEeqnarray}{rCl}
-		I_1 &\leq& \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  2[ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{r+ \bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2) \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
+		I_1^{b_2} &\leq& e^{2T(b_1 + \bar{b}_1)}[ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ] \cdot\frac{2(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \zeta_2) t \right) dt \nonumber \\
 		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 (b_2 + \bar{b}_2) t^* } \right), 
@@
 	\end{IEEEeqnarray}
-	where the coefficients $ \displaystyle \kappa_1 := \kappa_1(\epsilon_2) = \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  [ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{c_u - \epsilon_2}>0$ and $\displaystyle \kappa_2 := \kappa_2(\epsilon_2) = \frac{2 (c_u - \epsilon_2)}{r + \bar{r}(1-\bar{s})^2}>0$ are independent of $b_2$.
+	where the coefficients $ \displaystyle \kappa_1:= \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  [ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ]}{c_u - \zeta_2}>0$ and $\displaystyle \kappa_2 := \frac{2 (c_u - \zeta_2)}{r + \bar{r}(1-\bar{s})^2}>0$ are independent of $b_2$.
 	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we choose the time point $t^*$ as follows:
 	\begin{equation}
-	 t^* := t^*(\epsilon) = \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
+	 t^* := \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
 	\label{eq:t^*_b2_infty} 
 	\end{equation}
-	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that:
-	\begin{equation}
-		I_1 \leq \kappa_1 \left(1 - e^{- \kappa_2 (b_2^{*,I_2} + \bar{b}_2) t^*}  \right) \leq \epsilon.\\
+	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that: 	(ToDo: there is a mistake here!
+This is only true for $I_1^{b_2^{*,I_2}}$, not for $I_1^{b_2}$ for any $b_2> b_2^{*,I_2}$.)
+	\begin{equation}
+		I_1^{b_2} \leq \kappa_1 \left(1 - e^{- \kappa_2 (b_2^{*,I_2} + \bar{b}_2) t^*}  \right) \leq \epsilon.\\
 	\label{eq:I1_b2_infty}
@@
 	% check I_2
-	Next, consider $I_2$ with $t^*(\epsilon)$ as in equation (\ref{eq:t^*_b2_infty}). 
+	Next, consider $I_2^{b_2}$ with $t^*$ as in equation (\ref{eq:t^*_b2_infty}). 
 	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_{t^*}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{t^*}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$.
-We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1$ with $t^* < t_1 < T$ such that:
-	\begin{equation}
-		I_2 = (T-t^*) \cdot \frac{(u_{t_1}^{b_2} - w_{t_1}^{b_2})^2 e^{2(b_1 + \bar{b}_1)t_1} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1} h_u(b_2,s) ds }.
+We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $t^* < t_1^{b_2} < T$ such that:
+	\begin{equation}
+		I_2^{b_2} = (T-t^*) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
 	\label{eq:I2_b2_infity_Mean_Value}
 	\end{equation}	
-	We know from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max \{b_2^{*,upper}, b_2^{*,lower} \}$ and all $t \in [0,T]$:
+	We know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [0,T]$:
 	\begin{equation*}
@@
 	\begin{equation*}
-		\int_0^{t_1} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq t^* m_u(\epsilon_1).
+		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq t^* m_u.
 	\end{equation*}
@@
 	\begin{equation*}
-		I_2 \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
-	\end{equation*}
-	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} $ and $\kappa_4 := \kappa_4(\epsilon, \epsilon_1) =  \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2}$ are two positive constants independent of $b_2$.
-	Hence, there exists $b_2^{*,I_2} := b_2^{*,I_2}(\epsilon, \epsilon_1) > \max \{b_2^{*,upper}, b_2^{*,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
-	\begin{equation}
-		I_2 \leq \epsilon.
+		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
+	\end{equation*}
+	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
+	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
+	\begin{equation}
+		I_2^{b_2} \leq \epsilon.
 	\label{eq:I2_b2_infty}
@@
 
-	Let $\epsilon_1, \epsilon_2$ be two constants as follow:
-	$$ \epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}\quad \text{and} \quad \epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}.$$ Hence, 
-	for any $\epsilon>0$, we can choose $t^*$ as in equation (\ref{eq:t^*_b2_infty}) so that for all $b_2 \geq b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}(\epsilon) \}$, the inequalities (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) yield:
-	\begin{equation*}
-		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \epsilon_2}.
-	\end{equation*}
-	Therefore, by letting $\epsilon \to 0$, we conclude that:
+	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) give:
+	\begin{equation*}
+		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
+	\end{equation*}
+	Since the proof holds for arbitrary $\epsilon>0$, we conclude:
 	\begin{equation*}

### 2018-07-25 PoA.tex
edits, and mistake found in Proposition 4!
fixed mistake in prop 4

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
+	Assuming (\ref{eq:assumptions}),
+	\begin{equation*}
+	\begin{split}
+	q_T+\bar{q}_T(1-s_T)&>0 \\
+	q_T+\bar{q}_T(1-s_T)^2&>0 \\
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}&=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{split}
+	\end{equation*}
+	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
-%	and for any $t \in [0,T)$,
-%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
-%	$$
+	From the assumption:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	we have $c_w=c_u=:c$.
 
@@
 
-	Fix $\epsilon>0$. In the following, we show that the time point $t^*$ can be chosen such that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
-
+	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
 	% the term I_1
@@
 Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
-(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\frac{1}{2} \min \{ c_u, c_w \} $.
+(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}$.
 Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
@@
 	\begin{array}{lclclclcl}
-		c_u - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \zeta_2, \\
-		c_w - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \zeta_2.
+		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
+		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
 	\end{array}
@@
 	$$
-		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \zeta_2)^2 + (c_w+ \zeta_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \zeta_2) t.
+		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
 	$$
@@
 	\begin{IEEEeqnarray}{rCl}
-		I_1^{b_2} &\leq& e^{2T(b_1 + \bar{b}_1)}[ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ] \cdot\frac{2(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \zeta_2) t \right) dt \nonumber \\
-		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 (b_2 + \bar{b}_2) t^* } \right), 
+		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
+		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  t^* } \right) \\
+		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
+		&\leq&\epsilon, 
 	\label{eq:I1_ineq_b2_infinity}
 	\end{IEEEeqnarray}
-	where the coefficients $ \displaystyle \kappa_1:= \frac{e^{2T(b_1 + \bar{b}_1)}\cdot  [ (c_u+ \zeta_2)^2 + (c_w + \zeta_2)^2 ]}{c_u - \zeta_2}>0$ and $\displaystyle \kappa_2 := \frac{2 (c_u - \zeta_2)}{r + \bar{r}(1-\bar{s})^2}>0$ are independent of $b_2$.
-	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we choose the time point $t^*$ as follows:
-	\begin{equation}
-	 t^* := \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
-	\label{eq:t^*_b2_infty} 
-	\end{equation}
-	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that: 	(ToDo: there is a mistake here!
-This is only true for $I_1^{b_2^{*,I_2}}$, not for $I_1^{b_2}$ for any $b_2> b_2^{*,I_2}$.)
-	\begin{equation}
-		I_1^{b_2} \leq \kappa_1 \left(1 - e^{- \kappa_2 (b_2^{*,I_2} + \bar{b}_2) t^*}  \right) \leq \epsilon.\\
-	\label{eq:I1_b2_infty}
-	\end{equation}
+	where the last inequality comes from the definition of $\zeta_2$.
 
@@
 
-	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) give:
-	\begin{equation*}
-		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
+	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
+	\begin{equation*}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
 	\end{equation*}
@@
 	\begin{equation*}
-		\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0, 
+		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
 	\end{equation*}
 	and thus,
-	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
 

### 2018-07-25 PoA.tex
removed t* in prop 4

@@
 
-	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,t^*]$ and $[t^*,T]$.	
+	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 	\begin{split}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{t^*} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{t^*}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
 		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
@@
 	\begin{IEEEeqnarray*}{rCl}
-	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
+	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
 	\right) dt \\
-	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt,
+	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt,
 	\end{IEEEeqnarray*}
@@
 	$$
-		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
+		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
 	$$
@@
 	\end{equation*}
-	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*]$ and $b_2 \geq b_2^{*,I_1}$, we have:
+	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
 	$$
@@
 	\begin{IEEEeqnarray}{rCl}
-		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
-		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  t^* } \right) \\
+		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
+		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \\
 		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
@@
 	% check I_2
-	Next, consider $I_2^{b_2}$ with $t^*$ as in equation (\ref{eq:t^*_b2_infty}). 
-	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_{t^*}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{t^*}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$.
-We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $t^* < t_1^{b_2} < T$ such that:
-	\begin{equation}
-		I_2^{b_2} = (T-t^*) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
+	Next, consider $I_2^{b_2}$. 
+	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $\displaystyle t \mapsto \int_{\frac{T}{2}}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
+We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $\frac{T}{2} < t_1^{b_2} < T$ such that:
+	\begin{equation}
+		I_2^{b_2} = (T-\frac{T}{2}) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
 	\label{eq:I2_b2_infity_Mean_Value}
@@
 	\begin{equation*}
-		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq t^* m_u.
+		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u.
 	\end{equation*}
@@
 	\begin{equation*}
-		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
-	\end{equation*}
-	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 t^*  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
+		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
+	\end{equation*}
+	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
 	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,I_2}$: 

### 2018-07-26 PoA.tex
fixed below (37) in prop 4
simplify prop 4, removing Mean Value Theorem

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}),
-	\begin{equation*}
-	\begin{split}
-	q_T+\bar{q}_T(1-s_T)&>0 \\
-	q_T+\bar{q}_T(1-s_T)^2&>0 \\
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}&=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{split}
-	\end{equation*}
-	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then:
-	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
+	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$.
+	If 
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
+	\end{equation*}
+	then 
+	$$ \lim_{b_2 \to \infty} PoA = 1,$$	
+	otherwise, 
+	$$ \lim_{b_2 \to \infty} PoA >1$$.
 \label{prop:b2_to_infty}
@@
 	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
-	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty},
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
 	\end{array}
@@
 	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
-	From the assumption:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{equation*}
-	we have $c_w=c_u=:c$.
 
 	% lower bound for (b_2 + b2 bar) u_t
-	Next, we derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
+	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
 Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
@@
 	$$ 
-	and thus,
+	and thus for all $t \in [0,T]$,
 	\begin{IEEEeqnarray}{rCl}
@@
 	\end{IEEEeqnarray}
+	Idem, we can have a strictly positive uniform lower bound for $b_2 \eta_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $b^{*,\eta,lower}_2 >0$ such that for all $b_2 \geq b^{*,\eta,lower}$,
+	\begin{equation}
+		b_2 \eta_t^{b_2} \geq m_\eta > 0.
+	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
+	\end{equation}
 
@@
 	\end{equation}
-	Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$.
-
-	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
+	Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$.\\
+
+	In the case when
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
+	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 	First, consider $I_1^{b_2}$.
-Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = c_u$ and $\lim_{b_2 \to \infty}h_w(b_2,t) = c_w$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
-(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let $\zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}$.
+Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
+(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
+	$$ \zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}.$$
 	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
@@
 		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
-		&=& 2\zeta_2^2 \cdot \frac{e^{2T(b_1 + \bar{b}_1)}}{\frac{c}{2}} \left( 1 - e^{ - \frac{2(b_2 + \bar{b}_2) \frac{c}{2}}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \\
-		&\leq& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot \zeta_2^2\\
-		&\leq&\epsilon, 
+		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
 	\label{eq:I1_ineq_b2_infinity}
@@
 	Next, consider $I_2^{b_2}$. 
-	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $\displaystyle t \mapsto \int_{\frac{T}{2}}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
+%	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $\displaystyle t \mapsto \int_{\frac{T}{2}}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
 We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $\frac{T}{2} < t_1^{b_2} < T$ such that:
-	\begin{equation}
-		I_2^{b_2} = (T-\frac{T}{2}) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
-	\label{eq:I2_b2_infity_Mean_Value}
-	\end{equation}	
-	We know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [0,T]$:
+%	\begin{equation}
+%		I_2^{b_2} = (T-\frac{T}{2}) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
+%	\label{eq:I2_b2_infity_Mean_Value}
+%	\end{equation}	
+	Since $u_t^{b_2}$ is positive over $[0,T]$, we know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [\frac{T}{2},T]$:
 	\begin{equation*}
@@
 	\begin{equation*}
-		\int_0^{t_1^{b_2}} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u.
-	\end{equation*}
-	Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
-	\begin{equation*}
-		I_2^{b_2} \leq  \frac{4 T M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
-	\end{equation*}
-	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{2 \frac{T}{2}  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
-	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
+		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
+	\end{equation*}
+	%Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
+	Therefore,
+	\begin{IEEEeqnarray*}{rCl}
+		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \frac{T}{2} \right) dt\\
+		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
+	\end{IEEEeqnarray*}
+	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
+	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
 	\begin{equation}
@@
 	\begin{equation*}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \zeta_2}.
-	\end{equation*}
-	Since the proof holds for arbitrary $\epsilon>0$, we conclude:
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4}{c}\epsilon.
+	\end{equation*}
+	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $\epsilon$, we conclude:
 	\begin{equation*}
@@
 
-% proposition b2 bar
+% proposition b2 bar infinity
 \begin{proposition}

### 2018-07-26 PoA.tex
simplify prop 4 & prop 6

@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$.
+	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$.
+Moreover, we assume that $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$ and $q_T + \bar{q}_T > 0$.
+
 	If 
@@
 	otherwise, 
-	$$ \lim_{b_2 \to \infty} PoA >1$$.
+	$$ \lim_{b_2 \to \infty} PoA >1.$$
 \label{prop:b2_to_infty}
@@
 	\end{IEEEeqnarray*}
-	Idem, for any $t \in [0,T)$,
-	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
+	Idem, for all $t \in [0,T)$,
+	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	and
+	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
 
@@
 Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
-Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$,
+Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
 	$$ 
@@
 		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
-		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{1}{b_2 + \bar{b}_2} \cdot \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
 		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
@@
 	\end{IEEEeqnarray}
-	Idem, we can have a strictly positive uniform lower bound for $b_2 \eta_t^{b_2}$ over $[0,T]$ and large $b_2$. Let $b^{*,\eta,lower}_2 >0$ such that for all $b_2 \geq b^{*,\eta,lower}$,
-	\begin{equation}
-		b_2 \eta_t^{b_2} \geq m_\eta > 0.
+	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
+	\begin{equation}
+	   b_2 \eta_t^{b_2} \geq m_\eta.
 	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
@@
 	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
-	there exists $b_2^{*,u,upper}>b_2^{*,lower}$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
-	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + \zeta_1.$$
+	there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
+	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
 	Thus,
-	\begin{equation}
-	\left| u_t^{b_2}\right|\leq D^{u,b_2 \to \infty} + \zeta_1 ,\ t\in[0,T],\ b_2 > b_2^{*,u,upper},
+	\begin{equation*}
+	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper},
 	\label{eq:u_t_bound}
-	\end{equation}
-	and by the same argument,
-	\begin{equation}	
-	\left| w_t^{b_2}\right|\leq D^{w} ,\ t\in[0,T],\ b_2 > b_2^{*,w,upper}.
-	\label{eq:w_t_bound}
-	\end{equation}
-	Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$.\\
-
-	In the case when
+	\end{equation*}
+	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
+	%for all $t \in [0,T]$ and $b_2 \geq b_2^{*,w,upper}$,
+	%\begin{equation*}	
+	%$\left| w_t^{b_2}\right|\leq D^{w}.$
+	%\label{eq:w_t_bound}
+	%\end{equation*}
+
+	%Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$, then\\
+	\begin{equation}
+	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M.
+	\label{eq:ut_wt_upper_bound_b2_infty}
+	\end{equation}
+	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing along $[0,T]$. \\
+
+	\textbf{Case 1:} when
 	\begin{equation*}
@@
 	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
-	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,\frac{T}{2}]$ and $[\frac{T}{2},T]$.	
+	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
-	$$ \zeta_2 =\min \{\frac{1}{2}\sqrt{\epsilon c}e^{-T(b_1+\bar{b}_2)},\frac{c}{2}\}.$$
+	$$ \zeta_2 = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
 	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
@@
 %	\end{equation}	
-	Since $u_t^{b_2}$ is positive over $[0,T]$, we know from equations (\ref{eq:u_t_bound}) and (\ref{eq:w_t_bound}) that for all $b_2 \geq b_2^{*,upper}>b_2^{*,lower}$ and all $t \in [\frac{T}{2},T]$:
-	\begin{equation*}
-		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M,
-	\end{equation*}
-	and 
-	\begin{equation*}
+	Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
+	\begin{equation*}
+		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
+		\qquad \text{and} \qquad
 		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
@@
 	%Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
-	Therefore,
-	\begin{IEEEeqnarray*}{rCl}
-		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \frac{T}{2} \right) dt\\
-		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \xrightarrow[b_2 \to \infty]{} 0,
-	\end{IEEEeqnarray*}
-	where $\kappa_3 = \frac{4 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$. 	
-	Hence, there exists $b_2^{*,I_2} > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_2}$: 
-	\begin{equation}
-		I_2^{b_2} \leq \epsilon.
+	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
+	\begin{IEEEeqnarray}{rCl}
+		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \frac{T}{2} \right) dt \nonumber\\
+		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon
 	\label{eq:I2_b2_infty}
-	\end{equation}
+	\end{IEEEeqnarray}
+	where $\kappa_3 = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
 
@@
 	and thus,
-	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
-
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$\\
+
+	Todo: 
+	\textbf{Case 2}: when \begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
+	\end{equation*}
 \end{proof}
@@
 \begin{proof}
-	First, we consider $\bar{b}_2 \to 0$.
+	%First, we consider $\bar{b}_2 \to 0$.
 For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
@@
 	When $\bar{b}_2 \to 0$, we have:
-	$$\displaystyle \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})},$$
-	and 
-	$$B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\ C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,$$
-	$$D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0.$$
-
+	\begin{equation*}
+	\begin{array}{l}
+		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
+		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
+		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
+		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0,
+	\end{array}
+	\end{equation*}
+	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
 	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
@@
 	\begin{equation*}
-	\begin{split}
-		\left| u_t^{\bar{b}_2} \right| &\leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} \\
-		&=:c_2.
-	\end{split}
+		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} =:c_2.
 	\end{equation*}
@@
 	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
-
+	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$\\
+
+	% case when b2 bar \to infty
 	Now, for the case when $\bar{b}_2 \to \infty$,  we have 
@@
 	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
-	We can show that 
-	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
-	Idem, we can deduce that 
-	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}}.$$
-
-%	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
-	We first provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough.
-Let $\epsilon_1 > 0$ satisfy $\epsilon_1 < \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$, there exists $\bar{b}_2^{*,u} := \bar{b}^{*,u}_2(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
-	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert \right\} \leq \epsilon_1.
+	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that 
+	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
+	\qquad
+	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}}.$$
+	and, for all $0 \leq t < T$,
+	\begin{equation*}
+	\left\{
+	\begin{array}{l}
+	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \longrightarrow (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u \\
+	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \longrightarrow (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
+	\end{array}
+	\right. 
+	\end{equation*}
+
+% uniform upper bound for u_t and w_t
+	Next we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
+Let $\zeta_1 = \frac{1}{2} \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$.
+Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
+	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1.
 $$
-	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$:
-	\begin{IEEEeqnarray*}{rCl}
-		\vert u_t^{\bar{b}_2} \vert &=& \frac{\displaystyle C^{u,\bar{b}_2} \left(1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) + D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right) }{\displaystyle B^{\bar{b}_2} D^{u,\bar{b}_2} \left( 1 - e^{-(\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} \right)+ \delta_u^{+,\bar{b}_2} e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} - \delta_u^{-,\bar{b}_2} } \\
-		&\leq & \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
-		&\leq & \frac{\epsilon_1 + \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_u(\epsilon_1)
-	\end{IEEEeqnarray*}
-	Idem, we can also have a uniform bound for $w_t^{\bar{b}_2}$ over $[0,T]$ when $\bar{b}_2$ is large enough.
-There exists $\bar{b}_2^{*,w} := \bar{b}_2^{*,w}(\epsilon_1)$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,w}$ we have:
-	\begin{equation*}
-		\vert w_t^{\bar{b}_2} \vert \leq \frac{\epsilon_1 + D^w (2 c_{\delta_w^{\bar{b}_2\to \infty}} + 2 \epsilon_1)}{c_{\delta_w^{\bar{b}_2 \to \infty}} - \epsilon_1} =: M_w(\epsilon_1).		
-	\end{equation*}
-	Let $\bar{b}^{*,upper}_2 = \max\{ \bar{b}_2^{*,u}, \bar{b}_2^{*,w} \}$ and $M(\epsilon_1) = \max\{ M_u(\epsilon_1), M_v(\epsilon_1) \}$, then we have
-	\begin{equation}
-	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M(\epsilon_1).
-	 \label{eq:u_t_w_t_uniform_bound_b2_bar_infty}
-	\end{equation}
-
-	Our next step is to study the convergence rate of $u_t^{\bar{b}_2}$ and $w_t^{\bar{b}_2}$ for all $t \in [0,T]$.
-First of all, we notice that when $t =T$, $u_T^{\bar{b}_2} = D^{u,\bar{b}_2}$ and $w_T^{\bar{b}_2} = D^w$.
-Thus, note from the assumptions  $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have
-	$$ (b_2 + \bar{b}_2) u_T^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} \frac{b_2 (r+ \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)} =: \zeta > 0.$$
-	and $ w_T^{\bar{b}_2} >0$ being a constant independent of $\bar{b}_2$.
-
-	For any $t \in [0,T)$, equation (\ref{eq:riccati_ut_sol}) yields that
-	\begin{equation*}
-	\begin{split}
-	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \zeta \cdot \frac{1}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} -  \zeta \cdot \frac{1}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
-	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_u,
-	\end{split} 
-	\end{equation*}
-	where the limits is justified by $ \lim_{\bar{b}_2 \to \infty} C^{u,\bar{b}_2} \sqrt{b_2 + \bar{b}_2} = 0$ and $\lim_{\bar{b}_2 \to \infty} (\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} ) = \infty$.
-
-	Idem, for $t \in [0,T)$ we have:
-	$$ (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w. $$
-
-	Recall that when we derive the uniform bound for $u_t^{\bar{b}_2}$ over $[0,T]$, we have chosen $\bar{b}_2^{*,u}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$, $\frac{\delta_u^{+,\bar{b}_2} }{\sqrt{b_2 + \bar{b}_2}} \geq c_{\delta_u^{\bar{b}_2 \to \infty} } - \epsilon_1 > 0$ and $\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \leq 2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1 $.
-Thus, there exists $\bar{b}_2^{*,lower} > \bar{b}_2^{*,u}$ such that for any $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ we can have furthermore $\frac{1}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon_1$.
-
-	Hence, we get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$, namely for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,lower}$:
-	\begin{IEEEeqnarray}{rCl}
-		\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert &\geq&   (b_2 + \bar{b}_2)^{\frac{3}{2}} \frac{D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }  \nonumber \\
-		&= & \frac{\zeta \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} }{\frac{1}{\sqrt{b_2 + \bar{b}_2}} \cdot \frac{\delta_u^{+,\bar{b}_2}- \delta_u^{-,\bar{b}_2} }{\sqrt{b_2 + \bar{b}_2} } + \frac{\zeta}{r + \bar{r}(1- \bar{s})^2}  } \nonumber \\
-		&\geq & \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \epsilon_1)}{ \epsilon_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \epsilon_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
-	\label{eq:u_t_lower_bound_b2_bar_infty}
-	\end{IEEEeqnarray}
-
-	Now, we are ready to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
-	%we split the interval $[0,T]$ into two parts $[0,t_\epsilon]$ and $ [t_\epsilon, T]$ in which $0< t_\epsilon < T$ is a time point depending on $\epsilon$, 
-	we split the interval $[0,T]$ into two parts $[0,\frac{T}{2}]$ and $ [\frac{T}{2}, T]$,
-	and then we bound separately the following two quantities in terms of $\epsilon$:
+	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
+	\begin{equation}
+		\left\vert u_t^{\bar{b}_2} \right\vert 
+		\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
+		\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 6 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2
+	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
+	\end{equation}
+	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper}$,
+	\begin{equation}
+	 \sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M.
+	 \label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
+	\end{equation}
+	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Namely for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$:
+	\begin{equation}
+		\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
+		\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u
+	\label{eq:ut_lower_bound_b2_bar_infty}
+	\end{equation}
+	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
+
+	Now, we can adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
+	we intend to bound separately the following two quantities $I_1, I_2$:
 	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
 $$
+	so that for all $b_2$ large enough we have $\Delta SC = I_1 + I_2 \leq 2\epsilon.$
 
 	% the term I_1
-	We first look at the term $I_1$.
-We notice that for any given $\bar{b}_2$, the function $t \mapsto u_t^{\bar{b}_2}$ is increasing over $[0,T]$ when $B^{\bar{b}_2} (D^{u,\bar{b}_2})^2 + 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$.
-	Because the limit $$ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} = \frac{\zeta^2}{r+ \bar{r}(1-\bar{s})^2} >0,$$
-	we can deduce there exists $\bar{b}_2^{*,u,inc}>0$ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,u,inc}$, the function $t \mapsto u_t^{\bar{b}_2}$ is increasing.
-Similarly, there exists $\bar{b}^{*,w,inc}_2$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,w,inc}$ the function $t \mapsto w_t^{\bar{b}_2}$ is increasing.
-
-	Let $\epsilon_2 >0$ such that $ c_u > \epsilon_2$, there must exist $\bar{b}_2^{*,1} :=\bar{b}_2^{*,1}(\epsilon_2) > \max\{\bar{b}_2^{*,u,inc}, \bar{b}_2^{*,w,inc} \} $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,1}$ and all $s \in [0,\frac{T}{2}]$ we have:
-	$$ c_u - \epsilon_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \epsilon_2$$
-	$$ \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \epsilon_2, \quad and \quad 
-	\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \epsilon_2.$$
-	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,1}$ we have
+	For the term $I_1$.
+Let $\zeta_2 = c_u / 2$.
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there must exists $\bar{b}_2^{*,I_1} >0$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and for all $s \in [0, T/2]$,
+	\begin{IEEEeqnarray*}{c}
+		 c_u - \zeta_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_2,\\
+		 \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_2, \quad and \quad 
+		 \left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_2.
+	\end{IEEEeqnarray*}
+	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have
 	\begin{IEEEeqnarray}{rCl}
-		I_1 &=& \frac{1}{2} B^{\bar{b}_2} \int_0^{\frac{T}{2}}  (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
-		&=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds} dt \nonumber \\
-		&\leq& \frac{\mathbb{E}(\xi)^2 [2 \epsilon_2^2 + 2 (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2( r + \bar{r}(1-\bar{s})^2)} \int_0^{\frac{T}{2}} \exp \left(- \frac{2}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^{\frac{1}{2}} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
-		&=& \kappa_1(\epsilon_2) \frac{1}{(b_2 + \bar{b}_2)^{\frac{1}{2}} } \left( 1 - e^{- \kappa_2(\epsilon_2) (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right)\nonumber \\
-		&\leq& \frac{\kappa_1(\epsilon_2)}{\sqrt {b_2 + \bar{b}_2} } \nonumber
+		I_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
+		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \leq \epsilon,
+	\label{eq:I1_b2_bar_infinity}
 	\end{IEEEeqnarray} 
-	where $\displaystyle \kappa_1(\epsilon_2) = \frac{\mathbb{E}(\xi)^2 [\epsilon_2^2 + (c_w + \epsilon_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \epsilon_2)}$ and $ \displaystyle \kappa_2(\epsilon_2) = \frac{(c_u - \epsilon_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are two positive constant independent of $\bar{b}_2$.
-	We can then choose $\bar{b}_2^{*,I_1} := \max \{ \bar{b}_2^{*,1}(\epsilon_2), \left( \frac{\kappa_1(\epsilon_2)}{\epsilon} \right)^2 - b_2 \} $ so that for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have
-	\begin{equation}
-	I_1 \leq \frac{\kappa_1(\epsilon_2)}{\sqrt{b_2 + \bar{b}_2}} \leq \epsilon.
-	\label{eq:I_1_b2_bar_infinity}
-	\end{equation}
+	where $\kappa_1 = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 = \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$.
 
@@
 	Now, we look the term $I_2$.
-Since $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[T/2,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[T/2,T]$ and differentiable over $(T/2,T)$.
-Then with the equation (\ref{eq:x_bar_MFG_explicit_new_notation}) we can apply the Mean Value theorem and deduce that there exists a time points $t_1$ depending on $\bar{b}_2$ which satisfy $\frac{T}{2} < t_1 < T$ such that:
-	\begin{IEEEeqnarray}{rCl}
-		I_2 &=& \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_t- w^{\bar{b}_2}_t)^2 (\bar{x}_t^{MFG, \bar{b}_2} )^2 dt  \nonumber \\
-		&=& \frac{1}{2} B^{\bar{b}_2}  (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 (\bar{x}_{t_1}^{MFG,\bar{b}_2} )^2  \cdot \frac{T}{2} \nonumber \\
-		&=& \frac{T  B^{\bar{b}_2} }{4} \cdot (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{\bar{b}_2} u_s^{\bar{b}_2} ds \right) \nonumber \\
-		&\leq &  \kappa_3 (u_{t_1}^{\bar{b}_2}- w_{t_1}^{\bar{b}_2} )^2\cdot (b_2 + \bar{b}_2)^2 \exp\left( - 2 B^{\bar{b}_2} \int_0^{\frac{T}{2}} u_s^{\bar{b}_2} ds \right)
-		\label{eq:I_2_b2_bar_inequality}
-	\end{IEEEeqnarray}
-	where   $\displaystyle \kappa_3 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) T}}{4 (r + \bar{r}(1-\bar{s})^2)}$ is a constant independent of $\bar{b}_2$.
-
-	We are going to bound that the last term in (\ref{eq:I_2_b2_bar_inequality}).
-To do so, we recall that from equation (\ref{eq:u_t_lower_bound_b2_bar_infty}), we have for all $t \in [0,T]$ and all $\bar{b}_2 \geq \bar{b}_2^{*,lower}$ the inequality $ \inf_{0 \leq s \leq T} (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} \geq m_u(\epsilon_1)$.
-	Let $\epsilon_3>0$ such that $m_u(\epsilon_1) -  \epsilon_3 >0$.
-Then there exists $\bar{b}_2^{*,2} := \bar{b}_2^{*,2}(\epsilon_1,\epsilon_3) >0 $ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,2}$ we have:
-	$$ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3\kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \leq 0.$$ 
-	Hence, let $\bar{b}_2^{*,3} = \max \{\bar{b}_2^{*,upper}, \bar{b}_2^{*,lower}, \bar{b}_2^{*,2} \}$ and $\kappa_4 = \frac{T}{r + \bar{r}(1-\bar{s})^2}$, and together with inequality (\ref{eq:u_t_w_t_uniform_bound_b2_bar_infty}) and (\ref{eq:I_2_b2_bar_inequality}), we obtain that for all $\bar{b}_2 \geq \bar{b}_2^{*,3}$:
-	\begin{IEEEeqnarray*}{rCl}
-		I_2 &\leq& \kappa_3 \cdot 4 M(\epsilon_1)^2 \cdot (b_2 + \bar{b}_2)^2 \exp \left( - \kappa_4 (b_2 + \bar{b}_2)^{\frac{1}{2}} m_u(\epsilon_1) \right) \nonumber \\
-		&=& 4\kappa_3 M(\epsilon_1)^2 e^{ 2 \ln(b_2 + \bar{b}_2) - \epsilon_3 \kappa_4 \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}}} \cdot \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)   \nonumber \\
-		&\leq & \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right)
-	\end{IEEEeqnarray*}
-	where $\kappa_5 = 4 \kappa_3 M(\epsilon_1)^2$ is independent of $\bar{b}_2$.
-Now, we set $\bar{b}^{*,I_2}_2 := \max\{ \bar{b}_2^{*,3},  \left( \frac{ \ln( \kappa_5(\epsilon_1) / \epsilon)}{ \kappa_4 (m_u(\epsilon_1) - \epsilon_3)} \right)^2 - b_2 \}$, then we have for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$,
-	\begin{equation}
-		I_2 \leq \kappa_5(\epsilon_1) \exp\left(- \kappa_4 (m_u(\epsilon_1) - \epsilon_3) \cdot (b_2 + \bar{b}_2)^{\frac{1}{2}} \right) \leq \epsilon.
-	\label{eq:I_2_b2_bar_infinity}
-	\end{equation}
-
-	Hence, from inequalities (\ref{eq:I_1_b2_bar_infinity}) and (\ref{eq:I_2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
+Since $u_t^{\bar{b}_2}$ is positive over $[0,T]$ and from inequalities (\ref{eq:ut_wt_uniform_upper_bound_b2_bar_infty}) and (\ref{eq:ut_lower_bound_b2_bar_infty}), we know that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $t \in [T/2,T]$,
+	\begin{equation*}
+	\vert u_t^{\bar{b}_2} - w_t^{\bar{b}_2} \vert \leq 2M,\qquad \text{and} \qquad \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds \geq m_u \cdot \frac{T}{2}.
+	\end{equation*}
+	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$, 
+	\begin{equation}
+	I_2  \leq  \kappa_3 (b_2 + \bar{b}_2)^2 e^{ - \kappa_4 \sqrt{b_2 + \bar{b}_2} } \leq \epsilon
+	\label{eq:I2_b2_bar_infinity}
+	\end{equation}
+	where  $\kappa_3 =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 = \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$.
+
+	Hence, from inequalities (\ref{eq:I1_b2_bar_infinity}) and (\ref{eq:I2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
 	\begin{equation*}
@@
 	\end{equation*} 
-	Therefore, we can set $\epsilon_1, \epsilon_2,\epsilon_3$ as the following constants:
-	$$ \epsilon_1 := \frac{1}{2} \min \left\{c_{\delta_u^{\bar{b}_2 \to \infty}}, c_{\delta_w^{\bar{b}_2 \to \infty}} \right\}, \quad  \epsilon_2 := \frac{c_u}{2}, \quad \epsilon_3 = \frac{m_u(\epsilon_1)}{2},$$ and following the previous analysis by taking $\epsilon \to 0$, we obtain:
+	By taking $\epsilon \to 0$ we obtain:
 	\begin{equation*}
@@
 	\end{equation*}
-
 	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$.
@@
 
+% proposition b1 bar
 \begin{proposition}\label{prop:b1_b1bar}

### 2018-07-26 PoA.tex
simplify prop 3

@@
 
+% proposition r to infty
 \begin{proposition}
@@
 We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
-	\begin{IEEEeqnarray*}{rl}
-		C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +& D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )\\
-		&\leq  C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
-		&=  C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}} \\
-		&\leq  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} \\
-		&< \infty,
+	\begin{IEEEeqnarray*}{RL}
+		& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
+		\leq & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
+	%	= & C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}}  \\
+		\leq &  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} < \infty,
+	%	< & \infty,
 	\end{IEEEeqnarray*}
@@
 	\begin{IEEEeqnarray*}{rl}
-		D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)})& + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
-		&\geq \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-		&=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-		&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
-		&\geq -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} }\\
-		&>  0.
+	&	D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
+	\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
+	%=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
+	%	&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
+	\geq & -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } >  0.
 	\end{IEEEeqnarray*}
 	Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
-	\begin{IEEEeqnarray}{rCl}
-		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
-		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } \nonumber \\
-		&=:&c_2.  \nonumber
-	\end{IEEEeqnarray}
+	\begin{equation*}
+			\left\vert u_t^{r} \right\vert  \leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
+	\end{equation*}
+%	\begin{IEEEeqnarray*}{rCl}
+%		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
+%		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
+		% &=:&c_2. 
+%	\end{IEEEeqnarray*}
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	\end{equation}
-	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Namely for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$:
+	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$.
+Denote $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$, then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
 	\begin{equation}
 		\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
-		\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u
+		\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
 	\label{eq:ut_lower_bound_b2_bar_infty}
 	\end{equation}
-	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
 

### 2018-07-26 PoA.tex
minor change prop 7
added assumptions D_u \neq D_w for Prop 6 Case 1 and Prop 7 Cases 1 and 2

@@
 	&	D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
-	\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
+	\geq &  \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}\\
+	%\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
 	%=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, then:
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, and:
+	\begin{equation*}
+		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
+	\end{equation*}
+	then:
 	\begin{equation*}
@@
 
-   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
+   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w,\bar{b}_2 \to 0}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), $b_1>0$, $\bar{b}_1>0$, the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, then:
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
+	\begin{equation*}
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
+	\end{equation*}
+	then:
 	\begin{equation*}
@@
 	\begin{equation*}
-	\begin{split}
-		\left|u^{b_1}_t\right| &\leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
-		&\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon}\\
-		&=:c,
-	\end{split}
+		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
+		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
 	\end{equation*}
 	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
-By our assumption on $\bar{b}_1$, we have $A^{u,b_1\to 0} \neq A^{w,b_1\to 0}$ and thus, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
 
@@
 
+    \begin{comment}
     Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
@@
     and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
-
+\end{comment}
+
+	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.
 \end{proof}

### 2018-07-26 PoA.tex
minor edit prop 7 assumption

@@
 	\begin{equation*}
-	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2
 	\end{equation*}
@@
 	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
-From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
 

### 2018-07-26 PoA.tex
sketch of Prop 7 Case 4

@@
 \end{equation*}
+
+It will also be useful to compute the derivative of $u_t$ with respect to time $t$ from the explicit form in equation (\ref{eq:riccati_ut_sol}):
+\begin{equation}
+\frac{d u_t}{dt} = \frac{\left(B (D^{u})^2 + 2 A^u D^{u} - C^{u} \right) \cdot \left(\delta_u^{+} - \delta_u^{-}\right)^2 e^{- (\delta_u^{+} - \delta_u^{-})(T-t) } }{\left[B D^{u}(1-e^{- (\delta_u^{+} - \delta_u^{-})(T-t)})   + \delta_u^{+}e^{- (\delta_u^{+} - \delta_u^{-})(T-t)}- \delta_u^{-}  \right]^2 }.
+\label{eq:riccati_ut_sol_deriv}
+\end{equation}
+Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.
 
@@
 	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
 	\end{equation*}
 	then 
-	$$ \lim_{b_2 \to \infty} PoA = 1,$$	
-	otherwise, 
+	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
+	Otherwise, 
 	$$ \lim_{b_2 \to \infty} PoA >1.$$
@@
 	% upper bound for u_t, w_t
-	Also, from equation (\ref{eq:riccati_ut_sol}), for any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$:
-	\begin{equation*}
-		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot \left(\delta_u^{+,b_2} - \delta_u^{-,b_2}\right)^2 e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[B^{b_2} D^{u,b_2}(1-e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)})   + \delta_u^{+,b_2}e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)}- \delta_u^{-,b_2}  \right]^2 }.
-	\end{equation*}
-	Hence, the function $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
+	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
 	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
@@
 	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.
+
+	Now, consider $\bar{b}_1 \to \infty$.
+	Since $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have:
+	\begin{equation*}
+	\begin{split}
+	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
+	&\xrightarrow[\bar{b}_1 \to \infty]{}\infty,
+	\end{split}
+	\end{equation*}
+	and
+	\begin{equation*}
+	\begin{split}
+	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
+	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
+	\end{split}
+	\end{equation*}
+	Therefore, it can be shown that for $t \in [0,T)$:
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
+	\end{equation*}
+	Similarly, for $t \in [0,T)$:
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
+	\end{equation*}
+	Thus,
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty} \left(\frac{u^{\bar{b}_1}_t}{\bar{b}_1}-\frac{w^{\bar{b}_1}_t}{\bar{b}_1}\right)^2=\frac{1}{B^2}.
+	\end{equation*}
+
+	Note that $\eta_t$, and therefore $v_t$, are independent of $\bar{b}_1$. Thus,
+	\begin{equation*}
+	\begin{split}
+	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}&=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2\\
+	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
+	\end{split}
+	\end{equation*}
+
+	Now, consider:
+	\begin{equation*}
+	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
+	\end{equation*}
+	(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$.
+OR show both are uniformly bounded and use the bounded convergence theorem.)
+
+	Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
+	\begin{equation*}
+	\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
+	\end{equation*}
+	Then,
+	\begin{equation*}
+	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
+	\end{equation*}
+
+	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$.
+
+	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)
+
+	Let $\zeta_2>0$.
+Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
+	\begin{equation*}
+	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
+	\end{equation*}
+	and therefore:
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
+	\end{equation*}
+	Thus, we conclude:
+	\begin{equation*}
+	\begin{split}
+	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
+	\end{split}
+	\end{equation*}
+	and therefore,
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
+	\end{equation*}
+
 \end{proof}

### 2018-07-26 PoA.tex
sketch of Prop 7 Case 4

@@
 
-	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)
+	(ToDo: Show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$.)
+
+	Next, we show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$. We have: (ToDo don't use $\xi$, add superscripts)
+	\begin{equation*} 
+	\bar{b}_1-Bu^{\bar{b}_1}_0=\frac{BD(\bar{b}_1-\delta^+_u)-\delta^-_u\bar{b}_1-BC+(BC+BD\delta^-_u+\delta^+_u\bar{b}_1-BD\bar{b}_1)e^{-(\delta^+_u-\delta^-_u)T}}{-\delta^-_u+BD+(\delta^+_u-BD) e^{-(\delta^+_u-\delta^-_u)T}}
+	\end{equation*}
 
 	Let $\zeta_2>0$.
-Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
+Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) \geq 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
 	\begin{equation*}

### 2018-07-27 PoA.tex
Prop 7 Case 4 finished

--- 2018-07-26 PoA.tex
@@
 	\begin{equation*}
-	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2,
+	\end{equation*}
+	\begin{equation*}
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0,
 	\end{equation*}
@@
 
-	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.
+	Todo: case $b_1 \to \infty$.
 
 	Now, consider $\bar{b}_1 \to \infty$.
-	Since $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have:
-	\begin{equation*}
-	\begin{split}
-	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
-	&\xrightarrow[\bar{b}_1 \to \infty]{}\infty,
-	\end{split}
-	\end{equation*}
-	and
-	\begin{equation*}
-	\begin{split}
-	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
-	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
-	\end{split}
-	\end{equation*}
-	Therefore, it can be shown that for $t \in [0,T)$:
+	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
+	\begin{equation*}
+	\begin{split}
+	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty,\\
+	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,\\
+	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}&=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1
+	\end{split}
+	\end{equation*}
+	We also have for $t\in [0,T)$:
+	\begin{equation*}
+	\begin{split}
+	\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
+	\xrightarrow[\bar{b}_1 \to \infty]{}0,
+	\end{split}
+	\end{equation*}
+	which implies:
+	\begin{equation*}
+	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
+	\end{equation*}
+	Therefore, for $t \in [0,T)$:
 	\begin{equation*}
@@
 	\end{equation*}
-	Similarly, for $t \in [0,T)$:
+	By the same arguments, we have for $t \in [0,T)$:
 	\begin{equation*}
@@
 	Now, consider:
-	\begin{equation*}
+	\begin{equation}
 	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
-	\end{equation*}
-	(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$.
+	\label{eq:prop_7_case_4_numerator}
+	\end{equation}
+	%(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$.
 OR show both are uniformly bounded and use the bounded convergence theorem.)
 
-	Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
-	\begin{equation*}
-	\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
-	\end{equation*}
-	Then,
-	\begin{equation*}
-	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
-	\end{equation*}
-
+	%Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
+	%\begin{equation*}
+	%\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
+	%\end{equation*}
+	%Then,
+	%\begin{equation*}
+	%\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
+	%\end{equation*}
 	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$.
-
-	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)
-
-	Let $\zeta_2>0$.
-Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
-	\begin{equation*}
-	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
-	\end{equation*}
-	and therefore:
-	\begin{equation*}
-	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
-	\end{equation*}
-	Thus, we conclude:
-	\begin{equation*}
-	\begin{split}
-	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
-	\end{split}
-	\end{equation*}
-	and therefore,
+Next, we will show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1})=c$.
+We have the following limits for $t\in[0,T)$:
+	\begin{equation*}
+	\begin{split}
+	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u&=-2b_1\\
+	\lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1&=BC^u\\
+	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0\\
+	\lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0,
+	\end{split}
+	\end{equation*}
+	and thus, with the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0$ which implies $D^u>0$,
+	\begin{equation*}
+	\begin{split}
+	\bar{b}_1-Bu^{\bar{b}_1}_0&=\frac{-BC^u+BD^u(\bar{b}_1-\delta^{+,\bar{b}_1}_u)-\delta^{-,\bar{b}_1}_u\bar{b}_1+(\delta^{+,\bar{b}_1}_u\bar{b}_1+BC^u+BD^u(\delta^{-,\bar{b}_1}_u-\bar{b}_1))e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}}{BD^u-\delta^{-,\bar{b}_1}_u+(\delta^{+,\bar{b}_1}_u-BD^u) e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}} \\
+	&\xrightarrow[\bar{b}_1 \to \infty]{}-2b_1.
+	\end{split}
+	\end{equation*}
+
+	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) =-2b_1$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,dec}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
+Returning to equation (\ref{eq:prop_7_case_4_numerator}), we have for $\bar{b}_1 \geq \bar{b}^*_1$:
+	\begin{equation*}
+	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2(b_1-3b_1)t}dt.
+	\end{equation*}
+	By the bounded convergence theorem,
+	\begin{equation*}
+	=\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \frac{1}{B^2} e^{-4b_1t}dt=:c>0.
+	\end{equation*}	
+	Therefore,
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0,
+	\end{equation*}
+	and thus,
+	\begin{equation*}
+	\begin{split}
+	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty.
+	\end{split}
+	\end{equation*}
+	We conclude:
 	\begin{equation*}

### 2018-07-27 PoA.tex
update prop 7 case 4 drop BCT

@@
 	\end{equation*}
-	Thus,
-	\begin{equation*}
-	\lim_{\bar{b}_1 \to \infty} \left(\frac{u^{\bar{b}_1}_t}{\bar{b}_1}-\frac{w^{\bar{b}_1}_t}{\bar{b}_1}\right)^2=\frac{1}{B^2}.
+	%Thus,
+	%\begin{equation*}
+	%\lim_{\bar{b}_1 \to \infty} \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1}  = \frac{1}{B} > 0.
+	%\end{equation*}
+	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing, and all $t \in [0, T/2]$ we have
+	\begin{equation*}
+	    0< \frac{u_t^{\bar{b}_1}}{\bar{b}_1} \leq \frac{u_0^{\bar{b}_1}}{\bar{b}_1} \leq \frac{1}{B} + \frac{1}{4B}  \leq \frac{2}{B} - \frac{1}{4 B} \leq \frac{w_{T/2}^{\bar{b}_1}}{ \bar{b}_1} \leq \frac{w_t^{\bar{b}_1}}{\bar{b}_1}
+	\end{equation*}
+	Thus, for all $\bar{b}_1 \geq \bar{b}_1^{*,lower}$ and all $t \in [0,T/2]$,
+	\begin{equation*}
+	 (\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1}), \quad \text{and} \quad \left\vert  \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \right\vert \geq \frac{1}{2B}.
 	\end{equation*}
@@
 	\begin{split}
-	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}&=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2\\
+	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}&=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2 \\
 	&\xrightarrow[\bar{b}_1 \to \infty]{}0.	
@@
 	%\end{equation*}
-	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$.
-Next, we will show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1})=c$.
-We have the following limits for $t\in[0,T)$:
+
+	Next, we will show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1})=c$. We have the following limits for $t\in[0,T)$:
 	\begin{equation*}
@@
 	\bar{b}_1-Bu^{\bar{b}_1}_0&=\frac{-BC^u+BD^u(\bar{b}_1-\delta^{+,\bar{b}_1}_u)-\delta^{-,\bar{b}_1}_u\bar{b}_1+(\delta^{+,\bar{b}_1}_u\bar{b}_1+BC^u+BD^u(\delta^{-,\bar{b}_1}_u-\bar{b}_1))e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}}{BD^u-\delta^{-,\bar{b}_1}_u+(\delta^{+,\bar{b}_1}_u-BD^u) e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}} \\
-	&\xrightarrow[\bar{b}_1 \to \infty]{}-2b_1.
-	\end{split}
-	\end{equation*}
-
-	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) =-2b_1$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,dec}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
+	&\xrightarrow[\bar{b}_1 \to \infty]{} -2b_1 .
+	\end{split}
+	\end{equation*}
+
+	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
 Returning to equation (\ref{eq:prop_7_case_4_numerator}), we have for $\bar{b}_1 \geq \bar{b}^*_1$:
-	\begin{equation*}
-	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2(b_1-3b_1)t}dt.
-	\end{equation*}
-	By the bounded convergence theorem,
-	\begin{equation*}
-	=\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \frac{1}{B^2} e^{-4b_1t}dt=:c>0.
-	\end{equation*}	
+	\begin{equation}
+	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}
+	\geq \frac{B}{2}\mathbb{E}(\xi)^2 \cdot \frac{1}{4B^2} \cdot \int_{0}^{\frac{T}{2}} e^{2b_1 t + 2(\bar{b}_1 - B u_0^{\bar{b}_1}) t } dt \geq \frac{\mathbb{E}(\xi)^2}{8 B} \int_0^{\frac{T}{2}} e^{-4b_1 t} dt  > 0.
+	\end{equation}
 	Therefore,

### 2018-07-27 PoA.tex
update prop 7 case 3

@@
 
-    \begin{comment}
-    Now we consider $b_1 \to \infty$. For each $b_1>0$, we have the following bounds over $t\in[0,T]$:
-    \begin{equation*}
-    \begin{split}
-	    \left| u^{b_1}_t\right| &\leq \frac{C^u+D^u(\delta^{+,b_1}_u-\delta^{-,b_1}_u)}{-\delta^{-,b_1}_u}=:h_u(b_1) \\
-		\left| w^{b_1}_t\right| &\leq \frac{C^w+D^w(\delta^{+,b_1}_w-\delta^{-,b_1}_w)}{-\delta^{-,b_1}_w}=:h_w(b_1) \\
-		\left| \eta^{b_1}_t\right| &\leq \frac{C^{\eta}+D^{\eta}(\delta^{+,b_1}_{\eta}-\delta^{-,b_1}_{\eta})}{-\delta^{-,b_1}_{\eta}}=:h_{\eta}(b_1) \\
-		\left| \bar{x}^{MFG,b_1}_t \right| &\leq \left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)}=:h_{\bar{x}}(b_1).
-    \end{split}
-    \end{equation*}
-    Thus, from Proposition \ref{prop:diff_SC}, we have:
-    \begin{equation*}
-	    \Delta SC^{b_1} \leq \frac{1}{2}BT(h_u(b_1)+h_w(b_1))^2 (h_{\bar{x}}(b_1))^2.
-    \end{equation*}
-    We also have the following lower bound:
-    \begin{equation*}
-	\begin{split}
-	SC^{MKV,b_1} &\geq \frac{1}{2}(q_T+\bar{q}_T)v^{b_1}_T \\
-	& \geq \frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h_{\eta}(b_1))}.
-	\end{split}
-    \end{equation*}
-
-    Let $h(b_1)=\max \{h_u(b_1),h_w(b_1),h_{\eta}(b_1) \}$. Since $\lim_{b_1 \to \infty} |A^{u,b_1}|=\infty$, we have:
-    \begin{equation*}
-    \begin{split}
-	    \delta^{+,b_1}_u-\delta^{-,b_1}_u&=2 \sqrt{(A^{u,b_1})^2+BC^u} \\
-	    &\xrightarrow[b_1 \to \infty]{}\infty,
-    \end{split}
-    \end{equation*}
-    and
-    \begin{equation*}
-    \begin{split}
-    -\delta^{-,b_1}_u&=A^{u,b_1}+\sqrt{(A^{u,b_1})^2+BC^u} \\
-    &\xrightarrow[b_1 \to \infty]{}0.
-    \end{split}
-    \end{equation*}    
-    Thus, $\lim_{b_1 \to \infty}h_u(b_1)=\infty$, which implies $\lim_{b_1 \to \infty}h(b_1)=\infty$. Combining the above bounds and using the assumption $Var(\xi)>0$, we have:
-
-    \begin{equation*}
-    \begin{split}
-	    \frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}&\leq \frac{2BT(h(b_1))^2 (h_{\bar{x}}(b_1))^2}{\frac{1}{2}(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
-	    &= \frac{4BT(h(b_1))^2 (\left| \mathbb{E}(\xi)\right| e^{T(b_1+\bar{b}_1)})^2}{(q_T+\bar{q}_T)Var(\xi)e^{2T(b_1-B^{\eta}h(b_1))}}\\
-	    &= \frac{4BTe^{2T(\bar{b}_1)}(\mathbb{E}(\xi))^2  }{(q_T+\bar{q}_T)Var(\xi)} \cdot \frac{(h(b_1))^2}{e^{-2TB^{\eta}h(b_1))}}\\
-	    &\xrightarrow[b_1 \to \infty ]{} 0.
-    \end{split}
-    \end{equation*}
-    Therefore,
-    \begin{equation*}
-	    \lim_{b_1 \to \infty}\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}}=0,
-    \end{equation*}
-    and thus, $\lim_{b_1 \to \infty} PoA^{b_1}=1$. ToDo: last case.
-\end{comment}
-
-	Todo: case $b_1 \to \infty$.
-
-	Now, consider $\bar{b}_1 \to \infty$.
+	% case 3: b1 to infinity
+	\textbf{Case 3:} consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
+	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$,
+	\begin{equation}
+		\lim_{b_1 \to \infty} \frac{u_t^{b_1}}{b_1} =  	\lim_{b_1 \to \infty} \frac{w_t^{b_1}}{b_1} = \frac{2}{B}.
+	\label{eq:ut_wt_lim_b1_infty}
+	\end{equation}
+	Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$.
+From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing, and
+	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq B \left(\frac{2}{B} +\frac{1}{B} \right) = 3.$$
+
+	Moreover, for any fixed $\epsilon$, there exists $b^{*,I_1}_1(\epsilon) \geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1}(\epsilon) $, and for all $t \in [0, 3/4 T]$,
+	$$ \vert h_u(b_1, t) - h_u(b_1,t) \vert  \leq \epsilon, \quad h_w(b_1,0) \geq B \left( \frac{2}{B} - \frac{1}{3B} \right) = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, \frac{3}{4} T) \geq \frac{5}{3}.$$
+	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3/4 T]$ and $[3/4 T, T]$.
+For all $b_2 \geq b_2^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have
+	\begin{equation*}
+		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)}
+	\end{equation*}
+	where
+	\begin{IEEEeqnarray*}{rCl}
+	I_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
+	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
+	& \leq & \kappa_1 \epsilon^2 
+	\end{IEEEeqnarray*} 	
+	in which $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
+	\begin{IEEEeqnarray*}{rCl}
+		 I_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
+		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
+		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
+		 &=& \kappa_2 b_1 e^{- \frac{1}{2} b_1 T}
+	\end{IEEEeqnarray*}
+	in which $\kappa_2 = 9 T e^{2 \bar{b}_1 T}$.	
+	We can continue to choose $b_2$ being even larger, say for example $b_2 \geq b_2^{*}$ with $b_2^{*}(\epsilon) \geq b_2^{*,I_1}(\epsilon)$, so that $ I_2 \leq \epsilon$.
+Hence, for any given $\epsilon >0$ we obtain that for all $b_1 \geq b_1^{*}(\epsilon)$,
+	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon),$$
+	thus by letting $\epsilon \to 0$ we conclude that 
+	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$
+
+	% case 4: b1 bar to infinity
+	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
 	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:

### 2018-07-27 PoA.tex
minor edit prop 4 drop case 2
removed comments for readability

@@
 		\leq & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
-	%	= & C^{u,r} + 2 D^{u,r} \sqrt{ (A^u)^2 + B^{r} C^{u,r}}  \\
 		\leq &  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} < \infty,
-	%	< & \infty,
 	\end{IEEEeqnarray*}
@@
 	\geq &  \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}\\
-	%\geq & \delta_u^{+,r} e^{-2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-	%=(-A^u + \sqrt{ (A^u)^2 + B^{r} C^{u,r} } )  e^{- 2 \sqrt{(A^u)^2 + B^{r} C^{u,r}} (T-t) } \\
-	%	&\geq(-A^u + \left\vert A_u \right\vert) e^{-2T \sqrt{(A^u)^2 + c_1^2}}\\
 	\geq & -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } >  0.
@@
 	\end{equation*}
-%	\begin{IEEEeqnarray*}{rCl}
-%		\left\vert u_t^{r} \right\vert  &=& \frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) +D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \nonumber \\
-%		& \leq & \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
-		% &=:&c_2. 
-%	\end{IEEEeqnarray*}
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$.
-Moreover, we assume that $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$ and $q_T + \bar{q}_T > 0$.
-
-	If 
+Moreover, we assume that $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$, $q_T + \bar{q}_T > 0$ and
 	\begin{equation*}
@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
-	Otherwise, 
-	$$ \lim_{b_2 \to \infty} PoA >1.$$
+	%Otherwise, 
+	%$$ \lim_{b_2 \to \infty} PoA >1.$$
 \label{prop:b2_to_infty}
 \end{proposition}
-
-%\begin{remark}
-%	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$.
-The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$.
-Indeed, we will show that $\Delta SC$ decreases exponentially fast when $b_2$ tends towards infinity while $SC^{MKV}$ decreases as fast as $1/b_2$.
-Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter.
-%\end{remark}
 
@@
 
-	% lower bound for (b_2 + b2 bar) u_t
 	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
@@
 
-	% upper bound for u_t, w_t
 	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
@@
 	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
-	%for all $t \in [0,T]$ and $b_2 \geq b_2^{*,w,upper}$,
-	%\begin{equation*}	
-	%$\left| w_t^{b_2}\right|\leq D^{w}.$
-	%\label{eq:w_t_bound}
-	%\end{equation*}
-
-	%Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+\zeta_1, D^w\}$, then\\
 	\begin{equation}
@@
 
-	\textbf{Case 1:} when
+	%\textbf{Case 1:} when
+	Since we have assume that
 	\begin{equation*}
@@
 	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
-	We would like to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
+	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
-	% the term I_1
+
 	First, consider $I_1^{b_2}$.
@@
 
-	% check I_2
 	Next, consider $I_2^{b_2}$.
-%	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[\frac{T}{2},T]$, then the functions $\displaystyle t \mapsto \int_{\frac{T}{2}}^T u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[\frac{T}{2},T]$ and differentiable over $(\frac{T}{2},T)$.
-We can apply the mean value theorem and deduce that for a fixed $b_2$, there exists a time point $t_1^{b_2}$ with $\frac{T}{2} < t_1^{b_2} < T$ such that:
-%	\begin{equation}
-%		I_2^{b_2} = (T-\frac{T}{2}) \cdot \frac{\left(u_{t_1^{b_2}}^{b_2} - w_{t_1^{b_2}}^{b_2}\right)^2 e^{2(b_1 + \bar{b}_1)t_1^{b_2}} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1^{b_2}} h_u(b_2,s) ds }.
-%	\label{eq:I2_b2_infity_Mean_Value}
-%	\end{equation}	
 Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
@@
 	\end{equation*}
-	%Combining this with (\ref{eq:I2_b2_infity_Mean_Value}) gives:
 	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
@@
 \begin{proof}	
-	%First, we consider $\bar{b}_2 \to 0$.
-For every given $\bar{b}_2 >0$, we have existence and uniqueness of the solutions $u^{\bar{b}_2}_t$, $w^{\bar{b}_2}_t$ and $\eta^{\bar{b}_2}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}).
-Note that, as before, we have added the superscript $\bar{b}_2$ to emphasize the dependence on this parameter.
-
 	When $\bar{b}_2 \to 0$, we have:
@@
 
-% uniform upper bound for u_t and w_t
 	Next we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
@@
 
-	% the term I_1
 	For the term $I_1$.
@@
 
-	% the term I_2
 	Now, we look the term $I_2$.
@@
 	\end{equation*}
-	%Thus,
-	%\begin{equation*}
-	%\lim_{\bar{b}_1 \to \infty} \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1}  = \frac{1}{B} > 0.
-	%\end{equation*}
+
 	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing, and all $t \in [0, T/2]$ we have
@@
 	\end{equation}
-	%(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$.
-OR show both are uniformly bounded and use the bounded convergence theorem.)
-
-	%Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
-	%\begin{equation*}
-	%\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
-	%\end{equation*}
-	%Then,
-	%\begin{equation*}
-	%\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
-	%\end{equation*}
 

### 2018-07-27 PoA.tex
minor changes Prop 7 Case 4, added Case labels to all propositions

@@
 \begin{proof}
-	First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
+	\textbf{Case 1:} First, consider the case $\bar{b}_2 =0$. As $b_2 \to 0$, we have:
 	\begin{equation*}
@@
 
-	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
+	\textbf{Case 2:} Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
 	\begin{equation*}
@@
 \begin{proof}	
-	When $\bar{b}_2 \to 0$, we have:
+	\textbf{Case 1:} When $\bar{b}_2 \to 0$, we have:
 	\begin{equation*}
@@
 	% case when b2 bar \to infty
-	Now, for the case when $\bar{b}_2 \to \infty$,  we have 
+	\textbf{Case 2:}Now, for the case when $\bar{b}_2 \to \infty$,  we have 
 	\begin{equation*}
@@
 \begin{proof}
-	First, we consider $b_1 \to 0$.
+	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$.
 We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
@@
 
-	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing, and all $t \in [0, T/2]$ we have
+	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have:
+	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} <\frac{1}{4B},$$
+	and the functions $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing. Thus, for all $t \in [0, T/2]$ we have:
 	\begin{equation*}
@@
 	Thus, for all $\bar{b}_1 \geq \bar{b}_1^{*,lower}$ and all $t \in [0,T/2]$,
-	\begin{equation*}
-	 (\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1}), \quad \text{and} \quad \left\vert  \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \right\vert \geq \frac{1}{2B}.
-	\end{equation*}
+	\begin{equation}
+	  \left\vert  \frac{w^{\bar{b}_1}_t}{\bar{b}_1}-\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \right\vert \geq \frac{1}{2B}.
+	\label{eq:lower_bound_u_w}
+	\end{equation}
 
@@
 
-	Next, we will show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1})=c$. We have the following limits for $t\in[0,T)$:
+	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1> \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
 	\begin{equation*}
@@
 	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
-Returning to equation (\ref{eq:prop_7_case_4_numerator}), we have for $\bar{b}_1 \geq \bar{b}^*_1$:
+Returning to equation (\ref{eq:prop_7_case_4_numerator}), and using equation (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
 	\begin{equation}

### 2018-07-27 PoA.tex
minor edits Prop 4

@@
 	\begin{equation*}
-	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper},
+	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
 	\label{eq:u_t_bound}
 	\end{equation*}
-	and by the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
-	\begin{equation}
-	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M.
+	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
+	\begin{equation}
+	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M,
 	\label{eq:ut_wt_upper_bound_b2_infty}
 	\end{equation}
-	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing along $[0,T]$. \\
+	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$. \\
 
 	%\textbf{Case 1:} when
-	Since we have assume that
+	From the assumption:
 	\begin{equation*}
@@
 	\end{equation*}
-	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and so that $c_u = c_w =: c$. 
+	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
 	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
@@
 	\begin{IEEEeqnarray}{rCl}
-		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \frac{T}{2} \right) dt \nonumber\\
-		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon
+		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
+		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
 	\label{eq:I2_b2_infty}
@@
 
-	Let $b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
+	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
 	\begin{equation*}
@@
 	% case when b2 bar \to infty
-	\textbf{Case 2:}Now, for the case when $\bar{b}_2 \to \infty$,  we have 
+	\textbf{Case 2:} Now, for the case when $\bar{b}_2 \to \infty$,  we have 
 	\begin{equation*}

### 2018-07-27 PoA.tex
minor edits Prop 7 Case 3

@@
 	% case 3: b1 to infinity
-	\textbf{Case 3:} consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
-	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$,
+	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
+	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$:
 	\begin{equation}
@@
 	Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$.
-From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing, and
+From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, we have:
+	$$\max \left\{ \left|\frac{u_0^{b_1}}{b_1}-\frac{2}{B} \right|,\left|\frac{w_0^{b_1}}{b_1}-\frac{2}{B} \right| \right\} \leq \frac{1}{B},$$
+	and the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing. Thus,
 	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq B \left(\frac{2}{B} +\frac{1}{B} \right) = 3.$$
 
-	Moreover, for any fixed $\epsilon$, there exists $b^{*,I_1}_1(\epsilon) \geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1}(\epsilon) $, and for all $t \in [0, 3/4 T]$,
+	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3/4 T]$,
 	$$ \vert h_u(b_1, t) - h_u(b_1,t) \vert  \leq \epsilon, \quad h_w(b_1,0) \geq B \left( \frac{2}{B} - \frac{1}{3B} \right) = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, \frac{3}{4} T) \geq \frac{5}{3}.$$
 	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3/4 T]$ and $[3/4 T, T]$.
-For all $b_2 \geq b_2^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have
-	\begin{equation*}
-		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)}
+For all $b_1 \geq b_1^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have:
+	\begin{equation*}
+		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)},
 	\end{equation*}
@@
 	\begin{IEEEeqnarray*}{rCl}
-	I_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
+	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
 	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
-	& \leq & \kappa_1 \epsilon^2 
+	&= & \epsilon^2 e^{\frac{3\bar{b}_1 T}{2} } \cdot \frac{3}{4}(1-e^{-b_1T})  \nonumber \\	
+	& \leq & \kappa_1 \epsilon^2 ,
 	\end{IEEEeqnarray*} 	
@@
 	\begin{IEEEeqnarray*}{rCl}
-		 I_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
+		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
 		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
 		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
-		 &=& \kappa_2 b_1 e^{- \frac{1}{2} b_1 T}
+		 &=&  9 T e^{2 \bar{b}_1 T} b_1 e^{- \frac{1}{2} b_1 T} \xrightarrow[b_1 \to \infty]{}0.
 	\end{IEEEeqnarray*}
-	in which $\kappa_2 = 9 T e^{2 \bar{b}_1 T}$.	
-	We can continue to choose $b_2$ being even larger, say for example $b_2 \geq b_2^{*}$ with $b_2^{*}(\epsilon) \geq b_2^{*,I_1}(\epsilon)$, so that $ I_2 \leq \epsilon$.
-Hence, for any given $\epsilon >0$ we obtain that for all $b_1 \geq b_1^{*}(\epsilon)$,
-	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I_1 + I_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon),$$
-	thus by letting $\epsilon \to 0$ we conclude that 
+	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
+	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
+	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:
 	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$

### 2018-07-27 PoA.tex
more minor edits Prop 7 Case 3

@@
 	\end{equation*}
-	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $\epsilon$, we conclude:
+	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
 	\begin{equation*}
@@
 	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
-	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$. Moreover we have the following limits, for all $t \in [0,T)$:
-	\begin{equation}
-		\lim_{b_1 \to \infty} \frac{u_t^{b_1}}{b_1} =  	\lim_{b_1 \to \infty} \frac{w_t^{b_1}}{b_1} = \frac{2}{B}.
+	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$.
+Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$.
+We have the following limits, for all $t \in [0,T)$:
+	\begin{equation}
+		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
 	\label{eq:ut_wt_lim_b1_infty}
 	\end{equation}
-	Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$.
-From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, we have:
-	$$\max \left\{ \left|\frac{u_0^{b_1}}{b_1}-\frac{2}{B} \right|,\left|\frac{w_0^{b_1}}{b_1}-\frac{2}{B} \right| \right\} \leq \frac{1}{B},$$
-	and the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing. Thus,
-	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq B \left(\frac{2}{B} +\frac{1}{B} \right) = 3.$$
-
-	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3/4 T]$,
-	$$ \vert h_u(b_1, t) - h_u(b_1,t) \vert  \leq \epsilon, \quad h_w(b_1,0) \geq B \left( \frac{2}{B} - \frac{1}{3B} \right) = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, \frac{3}{4} T) \geq \frac{5}{3}.$$
-	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3/4 T]$ and $[3/4 T, T]$.
-For all $b_1 \geq b_1^{*,I_1}(\epsilon)$, similar to equation (\ref{eq:I_1_plus_I_2}), we have:
+	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and
+	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 2+1= 3.$$
+
+	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3T/4]$,
+	\begin{equation*}
+	\begin{split}
+	\vert h_u(b_1, t) - h_w(b_1,t) \vert  &=\max \{h_u(b_1, t)-h_w(b_1, t),h_w(b_1, t)-h_u(b_1, t) \}\\
+	&\leq \max \{h_u(b_1, 0)-h_w(b_1, 3T/4),h_w(b_1, 0)-h_u(b_1, 3T/4) \} \\
+	&\leq \epsilon,
+	\end{split}
+	\end{equation*}
+	and
+	$$h_w(b_1,0) \geq 2 - \frac{1}{3} = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, 3T/4) \geq \frac{5}{3}.$$
+	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3T/4]$ and $[3T/4, T]$.
+For all $b_1 \geq b_1^{*,I_1}$, similar to equation (\ref{eq:I_1_plus_I_2}), we have:
 	\begin{equation*}

### 2018-07-27 PoA.tex
minor edits Prop 6 Case 2

@@
 	% case when b2 bar \to infty
-	\textbf{Case 2:} Now, for the case when $\bar{b}_2 \to \infty$,  we have 
+	\textbf{Case 2:} Now, for the case when $\bar{b}_2 \to \infty$,  we have:
 	\begin{equation*}
 	\begin{array}{l}
-		\lambda^{\bar{b}_2} \to 0;\\
-		B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0
+		\lambda^{\bar{b}_2} \to 0,\\
+		B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
 	\end{array}
@@
 	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
-	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that 
+	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
 	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
 	\qquad
-	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}}.$$
-	and, for all $0 \leq t < T$,
-	\begin{equation*}
-	\left\{
+	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
+	and, for all $0 \leq t < T$:
+	\begin{equation*}
 	\begin{array}{l}
-	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \longrightarrow (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u \\
-	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \longrightarrow (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
+	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
+	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
 	\end{array}
-	\right. 
-	\end{equation*}
-
-	Next we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
-Let $\zeta_1 = \frac{1}{2} \min \{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \}$.
+	\end{equation*}
+
+	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
+Let $\zeta_1 = \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
 Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
@@
 		\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
-		\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 6 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2
+		\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1
 	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
@@
 	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$.
-Denote $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$, then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have
+Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
+Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
 	\begin{equation}
@@
 
-	Now, we can adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. For any given $\epsilon > 0$, 
-	we intend to bound separately the following two quantities $I_1, I_2$:
-	$$ I_1 = \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I_2 = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
-$$
-	so that for all $b_2$ large enough we have $\Delta SC = I_1 + I_2 \leq 2\epsilon.$
-
-	For the term $I_1$.
+	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. Consider the two quantities:
+	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds, $$
+	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$.
+
+	First, consider $I^{\bar{b}_2}_1$.
 Let $\zeta_2 = c_u / 2$.
-Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there must exists $\bar{b}_2^{*,I_1} >0$ large enough so that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and for all $s \in [0, T/2]$,
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
 		 c_u - \zeta_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_2,\\
-		 \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_2, \quad and \quad 
+		 \left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_2, \quad \text{and} \quad 
 		 \left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_2.
 	\end{IEEEeqnarray*}
-	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$ we have
+	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
 	\begin{IEEEeqnarray}{rCl}
-		I_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
-		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \leq \epsilon,
+		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
+		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0,
 	\label{eq:I1_b2_bar_infinity}
 	\end{IEEEeqnarray} 
-	where $\kappa_1 = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 = \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$.
-
-	Now, we look the term $I_2$.
+	where $\kappa_1 = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 = \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
+
+	Now, we consider the quantity $I^{\bar{b}_2}_2$.
 Since $u_t^{\bar{b}_2}$ is positive over $[0,T]$ and from inequalities (\ref{eq:ut_wt_uniform_upper_bound_b2_bar_infty}) and (\ref{eq:ut_lower_bound_b2_bar_infty}), we know that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $t \in [T/2,T]$,
@@
 	\begin{equation}
-	I_2  \leq  \kappa_3 (b_2 + \bar{b}_2)^2 e^{ - \kappa_4 \sqrt{b_2 + \bar{b}_2} } \leq \epsilon
+	I^{\bar{b}_2}_2  \leq  \kappa_3 (b_2 + \bar{b}_2)^2 e^{ - \kappa_4 \sqrt{b_2 + \bar{b}_2} } \leq \epsilon,
 	\label{eq:I2_b2_bar_infinity}
 	\end{equation}
-	where  $\kappa_3 =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 = \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$.
-
-	Hence, from inequalities (\ref{eq:I1_b2_bar_infinity}) and (\ref{eq:I2_b2_bar_infinity}), for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
-	\begin{equation*}
-		\Delta SC = I_1 + I_2 \leq 2\epsilon.
-	\end{equation*} 
-	By taking $\epsilon \to 0$ we obtain:
-	\begin{equation*}
-		\lim_{\bar{b}_2 \to \infty} \Delta SC = 0.
+	where  $\kappa_3 =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 = \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+
+	Hence, for all $\bar{b}_2 \geq \bar{b}_2^* := \max \{ \bar{b}_2^{*,I_1}, \bar{b}_2^{*,I_2}\}$ we have:
+	\begin{equation*}
+		\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon.
+	\end{equation*} 
+	Since the proof holds for arbitrary $\epsilon > 0$, we obtain:
+	\begin{equation*}
+		\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0.
 	\end{equation*}
@@
 Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $w^{\bar{b}_2}_0 \xrightarrow[\bar{b}_2 \to \infty]{} 0$.
-Thus, together with equation (\ref{eq:v_t_new_notation}) we obtain
-	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV} <\infty.$$
+Thus, we obtain:
+	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
 	Therefore, we conclude that:
-	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
+	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
 \end{proof}

### 2018-07-27 PoA.tex
tried removing some white space

@@
 Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$.
-We have the following two inequalities for $r > r^*$ and $\forall t \in [0,T]$:
-	\begin{IEEEeqnarray*}{RL}
-		& C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) \\
-		\leq & C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)\\
-		\leq &  c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2} < \infty,
-	\end{IEEEeqnarray*}
-	and 
-	\begin{IEEEeqnarray*}{rl}
-	&	D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u \\
-	\geq &  \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}\\
-	\geq & -2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } >  0.
-	\end{IEEEeqnarray*}
 Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
 	\begin{equation*}
-			\left\vert u_t^{r} \right\vert  \leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2
+	\begin{split}
+	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
+	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
+	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2.
+	\end{split}
 	\end{equation*}
@@
 
-	Similarly, the solutions $w^r_t$ and $\eta^r_t$ of equations (\ref{eq:riccati_wt}) and (\ref{eq:riccati_etat}) converge for each time $t\in [0,T]$ towards the solutions $w^{r\to \infty}_t$ and $\eta_t^{r\to \infty}$ of some linear first-order differential equations.
-Namely, for every $t\in [0,T]$,
-	$$\lim_{r\to \infty}w^r_t = w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t = \eta_t^{r\to \infty},$$
-	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$.
-
-	Again, by the bounded convergence theorem we have for every $t \in [0,T]$:
+	Similarly, for every $t\in [0,T]$,
+	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
+	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
 	\begin{equation*}
@@
 	\end{equation*}
-
 	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
@@
 Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.
-
 \end{proof}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$.
-Moreover, we assume that $q_T+\bar{q}_T(1-s_T)>0$, $q_T+\bar{q}_T(1-s_T)^2>0$, $q_T + \bar{q}_T > 0$ and
+	Assuming (\ref{eq:assumptions}),
+	$$q_T+\bar{q}_T(1-s_T)>0, \quad q_T+\bar{q}_T(1-s_T)^2>0, \quad q_T + \bar{q}_T > 0,$$
 	\begin{equation*}
@@
 	\end{equation*}
-	then 
+	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 	\begin{array}{l}
-	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \\
-	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
+	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
 	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
@@
 	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
-	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^u>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
+	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^{u,b_2}>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
 	\begin{IEEEeqnarray*}{rCl}
@@
 		&&\\
-		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
+		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
 	\end{IEEEeqnarray*}
@@
 	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$$
-	there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
+	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and
 	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
@@
 	\end{equation}
-	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$. \\
+	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.
 
@@
 
-	Fix $\epsilon>0$. In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
-
+	Fix $\epsilon>0$.
+In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
 First, consider $I_1^{b_2}$.
@@
 	and thus,
-	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$\\
-
-	Todo: 
-	\textbf{Case 2}: when \begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
-	\end{equation*}
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
+	%Todo: 
+	%\textbf{Case 2}: when \begin{equation*}
+	%\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq %\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
+	%\end{equation*}
 \end{proof}
@@
 	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
-	We can also have $\bar{x}_t^{MFG,b_2}$ being uniformly bounded by the constant $\vert \mathbb{E}(\xi) \vert e^{(b_1 + \bar{b}_1) T}$ for any $t \in [0,T]$ and $b_2 > 0$.
+	It can also be shown that $\left| \bar{x}_t^{MFG,b_2}\right| \leq \vert \mathbb{E}(\xi) \vert e^{(b_1 + \bar{b}_1) T}$ for any $t \in [0,T]$ and $b_2 > 0$.
 
 	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$.
-It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for $b_2$ small enough.
+It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$.
 Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
@@
 	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
-	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for any $b_2$ small enough and for each $t \in[0,T]$:
+	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for small $b_2$ and for all $t \in[0,T]$:
 	$$\lim_{b_2 \to 0}\eta_t^{b_2}=\left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }=:\eta_t^{b_2 \to 0}.$$
@@
 	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
-	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0.$$
+	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
 	and thus,
@@
 	\begin{equation*}
-		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}
+		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
 	\end{equation*}
@@
 	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$\\
+	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
 
@@
 	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. Consider the two quantities:
-	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds, $$
-	Fix $\epsilon>0$. In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$.
-
+	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
+$$
+
+	Fix $\epsilon>0$.
+In the following, we will show that $\Delta SC^{\bar{b}_2} = I^{\bar{b}_2}_1 + I^{\bar{b}_2}_2 \leq 2\epsilon$ for large $\bar{b}_2$.
 First, consider $I^{\bar{b}_2}_1$.
@@
 	\end{equation*}
-	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$, 
+	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$:
 	\begin{equation}
@@
 Thus, we obtain:
-	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
-	Therefore, we conclude that:
+	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
+	and conclude that:
 	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
@@
 	\begin{equation*}
-	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0,
+	q_T+\bar{q}_T(1-s_T) >0,
 	\end{equation*}

### 2018-07-28 PoA.tex
minor change prop 3

@@
 	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
+
 	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
-
-	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing.
+Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
+	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
+
+%	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
@@
 Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
-	\begin{equation*}
-	\begin{split}
-	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
-	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
-	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2.
-	\end{split}
-	\end{equation*}
+%	\begin{equation*}
+%	\begin{split}
+%	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
+%	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
+%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2.
+%	\end{split}
+%	\end{equation*}
+
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$.
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have 
+	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
 	Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.

### 2018-07-28 PoA.tex
add a remark after prop 6 for u_t = w_t

@@
 
+In the following propositions, based on assumption (\ref{eq:assumptions}) and the positivity of coefficients, we assume in addition that $b_1 > 0, D^{u} > 0, D^w > 0, D^{\eta} >0$ and the initial condition $\xi$ satisfies $\mathbb{E}(\xi) \neq 0$.
+These assumptions allow us to better understand the main ideas and techniques employed in the following propositions.
+
 % proposition r to infty
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$, then:
+	Assuming (\ref{eq:assumptions}), then:
 	\begin{equation*}
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
-	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
-
+	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
+	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
 	Similarly, for every $t\in [0,T]$,
@@
 	\end{equation*}
-	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
+
+	Again, from equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
 	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
 	\begin{equation*}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}),
-	$$q_T+\bar{q}_T(1-s_T)>0, \quad q_T+\bar{q}_T(1-s_T)^2>0, \quad q_T + \bar{q}_T > 0,$$
+	Assuming (\ref{eq:assumptions}), and if
 	\begin{equation*}
@@
 	\end{equation*}
-	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
+	then
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
-	%Otherwise, 
-	%$$ \lim_{b_2 \to \infty} PoA >1.$$
 \label{prop:b2_to_infty}
@@
 \begin{proposition}
-	Assume (\ref{eq:assumptions}), $b_1 > 0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$. If $\bar{b}_2= 0$, then:
+	Assume (\ref{eq:assumptions}). If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, and:
-	\begin{equation*}
-		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
-	\end{equation*}
-	then:
-	\begin{equation*}
-	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
-	\end{equation*}
+	Assuming (\ref{eq:assumptions}). 
+	If	$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
+	\begin{equation*}
+	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
+	\end{equation*}	
+	When $\bar{b}_2$ tends to infinity, we always have:
+	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
 	\label{prop:b2bar}
 \end{proposition}
+
 \begin{proof}	
-	\textbf{Case 1:} When $\bar{b}_2 \to 0$, we have:
+	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
 	\begin{equation*}
@@
    	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
-	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
 	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
 
-   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w,\bar{b}_2 \to 0}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
+   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
    	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
-$$
+	\begin{equation}
+	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
+	\label{eq:delta_SC_limit_b2_bar_0}
+	\end{equation}
+
 	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
@@
 
-% proposition b1 bar
+\begin{remark}
+	In the case when $\bar{b}_2$ tends to zero, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then since $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$ we must have $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
+Hence, from equation (\ref{eq:delta_SC_limit_b2_bar_0}) we  can derive that that for $t \in [0,T]$,
+	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
+	We know that $u_t^{\bar{b}_2 \to 0}$ and $w_t^{\bar{b}_2 \to 0}$ are solutions to some Riccati equations, the above equality implies $ D^{u,\bar{b}_2 \to \infty} =  u_T^{\bar{b}_2 \to 0} = w_T^{\bar{b}_2 \to 0} = D^w$ and
+	$$ B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
+	In another words, the coefficients have to satisfy the following three equations:
+	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
+	\qquad
+	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} = 1 - \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2},
+	$$
+	and
+	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q_ + \bar{q}(1- s)^2 \right) = 0.$$\\
+\end{remark}
+
+% proposition b1 and b1 bar
 \begin{proposition}\label{prop:b1_b1bar}
@@
 	\begin{equation*}
-	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2,
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
 	\end{equation*}
@@
 	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
-From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
 

### 2018-07-28 PoA.tex
minor change prop 6 remove assumption b1 bar > 0
update prop 5 return back to previous version

@@
 
+%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing.
+Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
+%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
 	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
-	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing.
-Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
-	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
-
-%	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
@@
 %	\begin{split}
-%	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
+%	\left\vert u_t^{r} \right\vert &=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
 %	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
-%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2.
+%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2.
 %	\end{split}
 %	\end{equation*}
-
+	\begin{equation}
+	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
+	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }
+	\end{equation}	
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	\begin{equation*}
-	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
+	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T]
 	\end{equation*}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-Because $\bar{b}_1 > 0$, we have $A^u < 0$.
+Because $b_1 > 0$, we have $A^u < 0$.
 For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
@@
 	\begin{equation*}
-		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} =:c_2.
+		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
 	\end{equation*}

### 2018-07-28 PoA.tex
update prop 3 return back to previous version

@@
 
-	Again, from equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
+	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
 	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
@@
 	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
+
 	Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.

### 2018-07-29 PoA.tex
minor edits from Friday

@@
 A sufficient condition for control problems of McKean-Vlasov type involving the law of the control is derived in \cite{carmona_acciaio}.
-Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition is the following:
+Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition reduces to the following (see section 4 in \cite{carmona_acciaio}):
 $\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
@@
     dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
-    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\mu}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
+    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
 \end{split}
@@
 
-In the following propositions, based on assumption (\ref{eq:assumptions}) and the positivity of coefficients, we assume in addition that $b_1 > 0, D^{u} > 0, D^w > 0, D^{\eta} >0$ and the initial condition $\xi$ satisfies $\mathbb{E}(\xi) \neq 0$.
-These assumptions allow us to better understand the main ideas and techniques employed in the following propositions.
-
 % proposition r to infty
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), then:
+	Assuming (\ref{eq:assumptions}), and assuming $b_1>0$, then:
 	\begin{equation*}
@@
 	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
-
-%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing.
-Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
-%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
 Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
+
 	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
@@
 Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
-%	\begin{equation*}
-%	\begin{split}
-%	\left\vert u_t^{r} \right\vert &=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
-%	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
-%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2.
-%	\end{split}
-%	\end{equation*}
-	\begin{equation}
-	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
-	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }
-	\end{equation}	
+	\begin{equation*}
+	\begin{split}
+	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
+	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
+	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2.
+	\end{split}
+	\end{equation*}
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
-	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
+	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded over $r>r^*$ and $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
+	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T],\ r>r^*. $$
+
 	Similarly, for every $t\in [0,T]$,
@@
 	\end{equation*}
-
-	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$: 
+	From equation (\ref{eq:v_t_new_notation}) and by the bounded convergence theorem, we have for each $t \in [0,T]$: 
 	$$	\lim_{r\to \infty} v^r_t = Var(\xi)e^{2b_1 t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{r \to \infty}_t.
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$ for large $r$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
 	\begin{equation*}
@@
 	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have 
-	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
-
+	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have $\displaystyle \lim_{r \to \infty} PoA^r = 1$.
 Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and if
+	Assuming (\ref{eq:assumptions}),
+	$$q_T+\bar{q}_T(1-s_T)>0, \quad q_T+\bar{q}_T(1-s_T)^2>0, \quad q_T + \bar{q}_T > 0,$$
 	\begin{equation*}
@@
 	\end{equation*}
-	then
+	and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
+	%Otherwise, 
+	%$$ \lim_{b_2 \to \infty} PoA >1.$$
 \label{prop:b2_to_infty}
 \end{proposition}
-
 \begin{proof}
@@
 	and thus,
-	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
+	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
 	%Todo: 
@@
 \begin{proposition}
-	Assume (\ref{eq:assumptions}). If $\bar{b}_2= 0$, then:
+	Assume (\ref{eq:assumptions}), $b_1 > 0$, and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$. If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 	\begin{equation*}
-	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T]
+	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
 	\end{equation*}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}). 
-	If	$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
-	\begin{equation*}
-	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
-	\end{equation*}	
-	When $\bar{b}_2$ tends to infinity, we always have:
-	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
+	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, $q_T+\bar{q}_T(1-s_T)>0$, and $q_T+\bar{q}_T(1-s_T)^2>0$, and:
+	\begin{equation*}
+		\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
+	\end{equation*}
+	then:
+	\begin{equation*}
+	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
+	\end{equation*}
 	\label{prop:b2bar}
 \end{proposition}
-
 \begin{proof}	
-	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
+	\textbf{Case 1:} When $\bar{b}_2 \to 0$, we have:
 	\begin{equation*}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-Because $b_1 > 0$, we have $A^u < 0$.
+Because $\bar{b}_1 > 0$, we have $A^u < 0$.
 For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
@@
 	\begin{equation*}
-		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
+		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} =:c_2.
 	\end{equation*}
@@
    	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
-	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
+	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the nonnegativity of $u_t$, we have:
 	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
 
-   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
+   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w,\bar{b}_2 \to 0}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	\begin{equation}
-	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
-	\label{eq:delta_SC_limit_b2_bar_0}
-	\end{equation}
-
+	$$ \lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
+$$
 	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
@@
 
-\begin{remark}
-	In the case when $\bar{b}_2$ tends to zero, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then since $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$ we must have $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
-Hence, from equation (\ref{eq:delta_SC_limit_b2_bar_0}) we  can derive that that for $t \in [0,T]$,
-	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
-	We know that $u_t^{\bar{b}_2 \to 0}$ and $w_t^{\bar{b}_2 \to 0}$ are solutions to some Riccati equations, the above equality implies $ D^{u,\bar{b}_2 \to \infty} =  u_T^{\bar{b}_2 \to 0} = w_T^{\bar{b}_2 \to 0} = D^w$ and
-	$$ B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
-	In another words, the coefficients have to satisfy the following three equations:
-	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
-	\qquad
-	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} = 1 - \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2},
-	$$
-	and
-	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q_ + \bar{q}(1- s)^2 \right) = 0.$$\\
-\end{remark}
-
-% proposition b1 and b1 bar
+% proposition b1 bar
 \begin{proposition}\label{prop:b1_b1bar}
@@
 	\begin{equation*}
-	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
+	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2,
 	\end{equation*}
@@
 	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
-From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
 

### 2018-07-29 PoA.tex

--- 2018-07-28 PoA.tex
@@
 Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
-%	\begin{equation*}
-%	\begin{split}
-%	\left\vert u_t^{r} \right\vert &=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
-%	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
-%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2.
-%	\end{split}
-%	\end{equation*}
 	\begin{equation}
@@
 \end{proposition}
-
 \begin{proof}

### 2018-07-29 PoA.tex
corrected some superscript notation

@@
 	\begin{equation*}
-	\lim_{b_2 \to 0} \Delta SC = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
+	\lim_{b_2 \to 0} \Delta SC^{b_2} = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
 	\end{equation*}
@@
 	and thus,
-	$$ 0 < \lim_{b_2 \to 0} SC^{MKV} < \infty.$$
-	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{b_2 \to 0} > 1.$$
+	$$ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$$
+	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA^{b_2} = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC^{b_2}}{\displaystyle \lim_{b_2 \to 0} SC^{MKV,b_2} } =: PoA^{b_2 \to 0} > 1.$$
 
@@
 
-	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC = 0$. Consider the two quantities:
+	Now, we adapt the method used in Proposition \ref{prop:b2_to_infty} to prove $\lim_{\bar{b}_2 \to \infty} \Delta SC^{\bar{b}_2} = 0$. Consider the two quantities:
 	$$ I^{\bar{b}_2}_1 := \frac{1}{2} B^{\bar{b}_2} \int_{0}^{\frac{T}{2}} (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds \quad \text{ and } \quad I^{\bar{b}_2}_2: = \frac{1}{2} B^{\bar{b}_2} \int_{\frac{T}{2}}^T (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG, \bar{b}_2} )^2 ds.
@@
 	\begin{split}
-	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
+	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
 	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,b_1\to 0}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
+	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
 	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$

### 2018-07-29 PoA.tex
added assumption 1

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{assumption}{Assumption}
 
@@
 \end{equation}
-Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.
-
-In the following propositions, based on assumption (\ref{eq:assumptions}) and the positivity of coefficients, we assume in addition that $b_1 > 0, D^{u} > 0, D^w > 0, D^{\eta} >0$ and the initial condition $\xi$ satisfies $\mathbb{E}(\xi) \neq 0$.
-These assumptions allow us to better understand the main ideas and techniques employed in the following propositions.
+Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.\\
+
+In the following propositions, we utilize the following assumption.	
+\begin{assumption}\label{assumption}
+	Assume (\ref{eq:assumptions}). In addition, assume: $b_1 > 0$, $D^{u} > 0$, $D^w > 0$, $D^{\eta} >0$ and the initial condition satisfies $\mathbb{E}(\xi) \neq 0$.
+\end{assumption}
 
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), then:
+	Assuming assumption \ref{assumption}, then:
 	\begin{equation*}
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}), and if
+	Assuming assumption \ref{assumption}, and if
 	\begin{equation*}
@@
 	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
-	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^{u,b_2}>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
+	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
 	\begin{IEEEeqnarray*}{rCl}
@@
 	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
-	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
+	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 \begin{proposition}
-	Assume (\ref{eq:assumptions}). If $\bar{b}_2= 0$, then:
+	Assume assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we derive that for any fixed $t \in [0,T]$:
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we derive that for any fixed $t \in [0,T]$:
 	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
@@
 
-	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$.
+	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w > 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$.
 It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$.
@@
 
-	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
+	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} > 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
 	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for small $b_2$ and for all $t \in[0,T]$:
@@
 \begin{proposition}
-	Assuming (\ref{eq:assumptions}). 
-	If	$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
+	Assuming assumption \ref{assumption}, then:
+	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
+	Furthermore, if	$\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
 	\begin{equation*}
@@
 	\end{equation*}	
-	When $\bar{b}_2$ tends to infinity, we always have:
-	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
 	\label{prop:b2bar}
@@
 \begin{proof}
-	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
-	\begin{equation*}
-	\begin{array}{l}
-		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
-		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
-		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
-		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0,
-	\end{array}
-	\end{equation*}
-	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
-	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
-	\begin{equation}
-	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
-	\end{equation}
-	which we recall has an explicit solution.
-It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
-Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-Because $b_1 > 0$, we have $A^u < 0$.
-For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
-Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
-	\begin{equation*}
-		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
-	\end{equation*}
-
-	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
-From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
-	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
-	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
-
-   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
-   	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	\begin{equation}
-	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
-	\label{eq:delta_SC_limit_b2_bar_0}
-	\end{equation}
-
-	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
-It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
-	\begin{equation*}
-	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
-	\end{equation*}
-	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
-
 	% case when b2 bar \to infty
-	\textbf{Case 2:} Now, for the case when $\bar{b}_2 \to \infty$,  we have:
+	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
 	\begin{equation*}
@@
 	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
+
+	\textbf{Case 2: } When $\bar{b}_2 \to 0$, we have:
+	\begin{equation*}
+	\begin{array}{l}
+		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
+		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
+		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
+		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u > 0,
+	\end{array}
+	\end{equation*}
+	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
+	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
+	\begin{equation}
+	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
+	\label{eq:riccati_limiting_u}
+	\end{equation}
+	which we recall has an explicit solution.
+It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
+Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
+Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
+	\begin{equation*}
+		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
+	\end{equation*}
+
+	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
+From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+   	\begin{equation}
+   	\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.
+   	\label{eq:x_bar_neq_0}
+   	\end{equation}
+	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
+	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+
+   	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
+   	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
+	\begin{equation}
+	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
+	\label{eq:delta_SC_limit_b2_bar_0}
+	\end{equation}
+
+	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
+It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
+	\begin{equation*}
+	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
+	\end{equation*}
+	Hence, we deduce:
+	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
 \end{proof}
@@
 \begin{remark}
-	In the case when $\bar{b}_2$ tends to zero, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then since $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$ we must have $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
-Hence, from equation (\ref{eq:delta_SC_limit_b2_bar_0}) we  can derive that that for $t \in [0,T]$,
+	Consider assumption \ref{assumption} and the case when $\bar{b}_2$ tends to zero.
+We have $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$, and therefore, $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$ implies $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
+Hence, from equation (\ref{eq:x_bar_neq_0}) and Proposition \ref{prop:diff_SC}, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then for all $t \in [0,T]$:
 	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
-	We know that $u_t^{\bar{b}_2 \to 0}$ and $w_t^{\bar{b}_2 \to 0}$ are solutions to some Riccati equations, the above equality implies $ D^{u,\bar{b}_2 \to \infty} =  u_T^{\bar{b}_2 \to 0} = w_T^{\bar{b}_2 \to 0} = D^w$ and
+	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality implies $ D^{u,\bar{b}_2 \to \infty} =  u_T^{\bar{b}_2 \to 0} = w_T^{\bar{b}_2 \to 0} = D^w$ and:
 	$$ B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
+	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
 	\begin{equation*}
 	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
-	\end{equation*}
-	\begin{equation*}
-	q_T+\bar{q}_T(1-s_T) >0,
 	\end{equation*}
@@
 
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
 	\begin{equation*}
@@
 	\end{equation*}
-	and thus, with the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0$ which implies $D^u>0$,
+	and thus,
 	\begin{equation*}
@@
 The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
-Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption (\ref{eq:assumptions}).
+Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption \ref{assumption}.
 In particular, when we allow for full interaction (i.e.

### 2018-07-29 PoA.tex
editing remark 6

@@
 	\begin{equation}
-	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
+	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
 	\label{eq:riccati_limiting_u}
@@
 	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
-	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality implies $ D^{u,\bar{b}_2 \to \infty} =  u_T^{\bar{b}_2 \to 0} = w_T^{\bar{b}_2 \to 0} = D^w$ and:
-	$$ B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
-	In another words, the coefficients have to satisfy the following three equations:
+	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, a sufficient condition for the above equality is:
+	$$D^{u,\bar{b}_2 \to \infty} = D^w \quad \text{and} \quad B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
+	In other words, the following three equations provide a sufficient condition for $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
 	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
 	\qquad
-	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} = 1 - \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2},
+	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} =  \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2}-1,
 	$$
 	and
-	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q_ + \bar{q}(1- s)^2 \right) = 0.$$\\
+	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q + \bar{q}(1- s)^2 \right) = 0.$$\\
 \end{remark}

### 2018-07-29 PoA.tex
editing remark 6

@@
 	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
-	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, a sufficient condition for the above equality is:
-	$$D^{u,\bar{b}_2 \to \infty} = D^w \quad \text{and} \quad B^{\bar{b}_2 \to 0} (D^{u,\bar{b}_2 \to 0} )^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} (D^w)^2 + 2 A^{w} D^w - C^w  = 0.$$
-	In other words, the following three equations provide a sufficient condition for $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
+	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality is equivalent to:
+	$$D^{u,\bar{b}_2 \to \infty} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D^w - C^w  = 0.$$
+	In other words, the following three equations imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
 	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
 	\qquad
-	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} =  \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2}-1,
+	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} =  \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2}-1,
 	$$

### 2018-07-29 PoA.tex
removed constant definitions that are not used, checked =:

@@
 	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
-	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }
+	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
 	\end{equation}
@@
 	Idem, for all $t \in [0,T)$,
-	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
 	and
-	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
+	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
 
 	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
-Let $\zeta_1 =\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
+Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
 Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
@@
 (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
-	$$ \zeta_2 = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
+	$$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
 	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
@@
 	\end{IEEEeqnarray}
-	where $\kappa_3 = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
+	where $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
 
@@
 	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
-Let $\zeta_1 = \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
+Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
 Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
@@
 First, consider $I^{\bar{b}_2}_1$.
-Let $\zeta_2 = c_u / 2$.
+Let $\zeta_2 := c_u / 2$.
 Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and for all $s \in [0, T/2]$:
@@
 	\end{IEEEeqnarray} 
-	where $\kappa_1 = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 = \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 := \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
 Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
@@
 	\end{equation}
-	where  $\kappa_3 =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 = \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+	where  $\kappa_3: =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 := \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
 
@@
 		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
-		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
+		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
 	\end{equation*}
@@
 	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$.
-Denote $h_u(b_1,t) = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) = B \frac{w_t^{b_1}}{b_1}$.
+Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$.
 We have the following limits, for all $t \in [0,T)$:
@@
 	\end{IEEEeqnarray*} 	
-	in which $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
+	in which $\kappa_1 := \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} } $, and
 	\begin{IEEEeqnarray*}{rCl}

### 2018-07-29 PoA.tex
removed some white space

@@
 	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$.
-We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that:
-	$$\lim_{b_2 \to 0} PoA = 1.$$
+We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$
 
@@
 	\begin{array}{l}
-		\lambda \longrightarrow 0\\
-		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
-		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
+		\lambda \longrightarrow 0, \quad \displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0, \quad C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
 	\end{array}
@@
 	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$.
-Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
-	$$\lim_{b_2 \to 0}u^{b_2}_t = 0 .$$
+Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$, $\lim_{b_2 \to 0}u^{b_2}_t = 0.$
+
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
@@
 	\begin{equation*}
-	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T]
+	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T].
 	\end{equation*}
@@
 	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
-	and thus,
-	$$ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$$
-	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA^{b_2} = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC^{b_2}}{\displaystyle \lim_{b_2 \to 0} SC^{MKV,b_2} } =: PoA^{b_2 \to 0} > 1.$$
-
+	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$
+	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that: $$\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$$
 \end{proof}
@@
 	\begin{array}{l}
-	\lambda^{\bar{b}_2} \to 0,\\
-	B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
+	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
 	\end{array}
@@
 	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
-	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1
+	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1.
 	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
@@
 Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
-There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$.
+There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1<b_1^*$.
 Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
@@
 
-	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem,
-    \begin{equation*}
-        0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty.
-    \end{equation*}
-    By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus:
-    $$0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$$
+	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$.
+By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
     Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.
@@
 	\begin{equation*}
-	\begin{split}
-	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty,\\
-	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,\\
-	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}&=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1
-	\end{split}
+	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
+	\end{equation*}
+	\begin{equation*}
+	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
 	\end{equation*}
 	We also have for $t\in [0,T)$:
-	\begin{equation*}
-	\begin{split}
-	\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
-	\xrightarrow[\bar{b}_1 \to \infty]{}0,
-	\end{split}
-	\end{equation*}
+	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
+	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
 	which implies:
-	\begin{equation*}
+	$
 	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
-	\end{equation*}
+	$
 	Therefore, for $t \in [0,T)$:
-	\begin{equation*}
-	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
-	\end{equation*}
-	By the same arguments, we have for $t \in [0,T)$:
-	\begin{equation*}
-	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
-	\end{equation*}
+	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$.
+By the same arguments, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.
 
@@
 	\begin{equation*}
-	    0< \frac{u_t^{\bar{b}_1}}{\bar{b}_1} \leq \frac{u_0^{\bar{b}_1}}{\bar{b}_1} \leq \frac{1}{B} + \frac{1}{4B}  \leq \frac{2}{B} - \frac{1}{4 B} \leq \frac{w_{T/2}^{\bar{b}_1}}{ \bar{b}_1} \leq \frac{w_t^{\bar{b}_1}}{\bar{b}_1}
+	    0< \frac{u_t^{\bar{b}_1}}{\bar{b}_1} \leq \frac{u_0^{\bar{b}_1}}{\bar{b}_1} \leq \frac{1}{B} + \frac{1}{4B}  \leq \frac{2}{B} - \frac{1}{4 B} \leq \frac{w_{T/2}^{\bar{b}_1}}{ \bar{b}_1} \leq \frac{w_t^{\bar{b}_1}}{\bar{b}_1}.
 	\end{equation*}
@@
 	\begin{equation*}
-	\begin{split}
-	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}&=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2 \\
-	&\xrightarrow[\bar{b}_1 \to \infty]{}0.	
-	\end{split}
+	\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}=\frac{1}{2\bar{b}_1^2}\left[\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T\right] + \frac{w^{\bar{b}_1}_0}{2\bar{b}_1^2} (\mathbb{E}(\xi))^2 \xrightarrow[\bar{b}_1 \to \infty]{}0.
 	\end{equation*}
@@
 	\begin{equation*}
-	\begin{split}
-	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u&=-2b_1\\
-	\lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1&=BC^u\\
-	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0\\
-	\lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0,
-	\end{split}
+	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u=-2b_1, \quad \lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1=BC^u,
+	\end{equation*}
+	\begin{equation*}
+	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0, \quad \lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0,
 	\end{equation*}
@@
 	Therefore,
-	\begin{equation*}
+	$
 	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0,
-	\end{equation*}
+	$
 	and thus,
@@
 	We conclude:
-	\begin{equation*}
+	$
 	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
-	\end{equation*}
+	$
 

### 2018-07-29 PoA.tex
only cite Proposition 2 in Proposition 3, to be consistent throughout Propositions 4-7

@@
 	\end{equation*}
-	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ_new_notation}), we have 
+	Therefore, from equation (\ref{eq:PoA_LQ_new_notation}), we have 
 	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
@@
 	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
-	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$
-	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that: $$\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$$
+	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$
 \end{proof}

### 2018-07-29 PoA.tex
style edit: remove enough from small/large enough

@@
 %	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
-	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
+	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
 	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
@@
 
-	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough.
+	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
 Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
@@
 It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
-Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
+Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
 For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
@@
 
-	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$.
+	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small $\bar{b}_2$.
 From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:

### 2018-07-29 PoA.tex
style edit: referring to inequalities as inequalities instead of equations

@@
 
-	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then equations (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
+	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
 	\begin{equation*}
@@
 	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3T/4]$ and $[3T/4, T]$.
-For all $b_1 \geq b_1^{*,I_1}$, similar to equation (\ref{eq:I_1_plus_I_2}), we have:
+For all $b_1 \geq b_1^{*,I_1}$, similar to inequality (\ref{eq:I_1_plus_I_2}), we have:
 	\begin{equation*}
@@
 	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
-Returning to equation (\ref{eq:prop_7_case_4_numerator}), and using equation (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
+Returning to inequality (\ref{eq:prop_7_case_4_numerator}), and using inequality (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
 	\begin{equation}

### 2018-07-29 PoA.tex
style edit: removing equation numbers for equations never referred to

@@
 	Let $u^{r \to \infty}:[0,T] \to \mathbb{R}$ be the solution to the linear first-order differential equation:
-	\begin{equation}
+	\begin{equation*}
 		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
-	\end{equation}
+	\end{equation*}
 	Then we have:
@@
 Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
-	\begin{equation}
+	\begin{equation*}
 	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
 	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
-	\end{equation}
+	\end{equation*}
 	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
-	\begin{equation}
+	\begin{equation*}
 	   b_2 \eta_t^{b_2} \geq m_\eta.
-	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
-	\end{equation}
+	\end{equation*}
 
@@
 		I^{\bar{b}_2}_1 &=& \frac{\mathbb{E}(\xi)^2}{2 (r + \bar{r}(1-\bar{s})^2) } \int_0^{\frac{T}{2}} \left( (b_2 + \bar{b}_2) u_t^{\bar{b}_2} - (b_2 + \bar{b}_2) w_t^{\bar{b}_2} \right)^2 e^{2(b_1 + \bar{b}_1) t} \cdot e^{ -\frac{2 (b_2 + \bar{b}_2)^{1/2}}{r + \bar{r}(1-\bar{s})^2}  \int_0^t (b_2 + \bar{b}_2)^{3/2} u_s^{\bar{b}_2} ds} dt \nonumber \\
-		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0,
+		&\leq& \kappa_1  \frac{1}{\sqrt{b_2 + \bar{b}_2} } \left( 1 - e^{- \kappa_2 (b_2 + \bar{b}_2)^{\frac{1}{2}} }\right) \xrightarrow[\bar{b}_2 \to \infty]{} 0, \nonumber
 		\label{eq:I1_b2_bar_infinity}
@@
 	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$:
-	\begin{equation}
+	\begin{equation*}
 	I^{\bar{b}_2}_2  \leq  \kappa_3 (b_2 + \bar{b}_2)^2 e^{ - \kappa_4 \sqrt{b_2 + \bar{b}_2} } \leq \epsilon,
-	\label{eq:I2_b2_bar_infinity}
-	\end{equation}
+	\end{equation*}
 	where  $\kappa_3: =\frac{T \mathbb{E}(\xi)^2 e^{2 (b_1 + \bar{b}_1) T} M^2 }{r + \bar{r}(1-\bar{s})^2}$ and $\kappa_4 := \frac{T m_u}{r + \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
@@
    	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	\begin{equation}
+	\begin{equation*}
 	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
-	\label{eq:delta_SC_limit_b2_bar_0}
-	\end{equation}
+	\end{equation*}
 
@@
 Returning to inequality (\ref{eq:prop_7_case_4_numerator}), and using inequality (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
-	\begin{equation}
+	\begin{equation*}
 	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}
 	\geq \frac{B}{2}\mathbb{E}(\xi)^2 \cdot \frac{1}{4B^2} \cdot \int_{0}^{\frac{T}{2}} e^{2b_1 t + 2(\bar{b}_1 - B u_0^{\bar{b}_1}) t } dt \geq \frac{\mathbb{E}(\xi)^2}{8 B} \int_0^{\frac{T}{2}} e^{-4b_1 t} dt  > 0.
-	\end{equation}
+	\end{equation*}
 	Therefore,

### 2018-07-29 PoA.tex
style edit: replacing 0 \leq t < T with t \in [0,T], and removing sup sup

@@
 	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and
-	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
-	Thus,
+	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing and thus, $ u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1.$
+	Therefore,
 	\begin{equation*}
@@
 	\end{equation*}
-	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
-	\begin{equation}
-	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M,
+	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
+	\begin{equation}
+	\max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
 	\label{eq:ut_wt_upper_bound_b2_infty}
@@
 	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
-	and, for all $0 \leq t < T$:
+	and, for all $t \in [0,T)$:
 	\begin{equation*}
@@
 	\end{equation}
-	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper}$,
-	\begin{equation}
-	\sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M.
+	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
+	\begin{equation}
+	\max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
 	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
@@
 	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$.
-By the same arguments, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.
+By the same argument, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.
 

### 2018-07-29 PoA.tex
style edit: using \leq and \geq instead of < and > in delta-epsilon arguments

@@
 Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$.
-Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
+Thus, we can deduce that for $r \geq r^*$, for every $t \in [0,T]$:
 	\begin{equation*}
@@
 	$$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
-	Then there exists $b_2^{*,I_1}  > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	Then there exists $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
 	\begin{equation*}
@@
 
-	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give:
+	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
 	\begin{equation*}
@@
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
-Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
+Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
 	\begin{equation*}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2 \leq \bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
 Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
@@
    	\end{equation}
-	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
-	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$
+	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2 \leq \bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
+	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2 \leq \bar{b}^*_2. $$
 
@@
 Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
-There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1<b_1^*$.
-Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
+There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$.
+Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
 	\begin{equation*}
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1<b_1^*$ and $t \in [0,T]$, i.e. 
-	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1<b_1^*. $$
+	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1 \leq b_1^*$ and $t \in [0,T]$, i.e. 
+	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1 \leq b_1^*. $$
 
@@
 
-	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1> \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
+	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
 	\begin{equation*}

### 2018-07-29 PoA.tex
style edit: denoting limits using lim_{} and only using \xrightarrow when necessary

@@
 	\end{equation*}
-	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
+	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
 	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
@@
 	Idem, for all $t \in [0,T)$,
-	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
 	and
-	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
+	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
 
@@
 	\begin{array}{l}
-	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
-	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
 	\end{array}
@@
 	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$.
-Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $w^{\bar{b}_2}_0 \xrightarrow[\bar{b}_2 \to \infty]{} 0$.
+Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $\lim_{\bar{b}_2 \to \infty}w^{\bar{b}_2}_0 = 0$.
 Thus, we obtain:

### 2018-07-29 PoA.tex
style edit: making the conditions for choosing * parameters more clear

@@
 	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
-	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u$, $D^{u,r}$, $D^{r \to \infty}_u> 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
-Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$.
-Thus, we can deduce that for $r \geq r^*$, for every $t \in [0,T]$:
+Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$ for $r \geq r^*$.
+Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
 	\begin{equation*}
@@
 	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
+	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$. From the non-negativity of $u^r_t$, we have:
 	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
@@
 	\begin{equation*}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
 	\end{equation*}
@@
 	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing and thus, $ u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1.$
+	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing.
 	Therefore,
 	\begin{equation*}
-	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
+	u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
 	\label{eq:u_t_bound}
@@
 	\end{equation}
-	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.
+	and such that the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.
 
@@
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
-Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
+Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and thus,
 	\begin{equation*}
@@
 	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
-	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1.
+	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1}.
 	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
@@
 Let $\zeta_2 := c_u / 2$.
-Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and for all $s \in [0, T/2]$:
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
@@
 	\begin{equation}
-	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
+	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{\bar{b}_2 \to 0} = D^{\bar{b}_2 \to 0}_u,
 	\label{eq:riccati_limiting_u}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2 \leq \bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$.
-Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$ for all $\bar{b}_2 \leq \bar{b}^*_2$.
+Thus, for all $\bar{b}_2\leq \bar{b}^*_2$ and for every $t \in [0,T]$:
 	\begin{equation*}
@@
 
-	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small $\bar{b}_2$.
+	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ and small $\bar{b}_2$.
 From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
@@
 	\end{equation}
-	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and
-	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 2+1= 3.$$
+	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
+	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$
 
@@
 	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} <\frac{1}{4B},$$
-	and the functions $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing. Thus, for all $t \in [0, T/2]$ we have:
+	and such that the functions $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing. Thus, for all $t \in [0, T/2]$ we have:
 	\begin{equation*}

### 2018-07-29 PoA.tex
style edit: added space between Cases

@@
 	and $\lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$, $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$.
-We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$
+We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that $\lim_{b_2 \to 0} PoA = 1.$\\
 
@@
 	and conclude that:
-	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
+	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$\\
 
@@
 By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
-    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.
+    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.\\
 
@@
 	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:
-	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$
+	$$ \lim_{b_1 \to \infty} PoA^{b_1} = 1.$$ \\
 

### 2018-07-29 PoA.tex
style edit: relabeled Prop 6 Case 1 zeta and zeta_2 to become: zeta_2 and zeta_3

@@
 	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$.
-Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
+Denote $\zeta_2: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
 Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
@@
 	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
-	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
+	\geq  \frac{\zeta_2 (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
 	\label{eq:ut_lower_bound_b2_bar_infty}
@@
 First, consider $I^{\bar{b}_2}_1$.
-Let $\zeta_2 := c_u / 2$.
+Let $\zeta_3 := c_u / 2$.
 Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
-		c_u - \zeta_2 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_2,\\
-		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_2, \quad \text{and} \quad 
-		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_2.
+		c_u - \zeta_3 \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_0^{\bar{b}_2} \leq  (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} \leq (b_2 + \bar{b}_2)^{\frac{3}{2}} u_{\frac{T}{2}}^{\bar{b}_2} \leq c_u + \zeta_3,\\
+		\left\vert (b_2 + \bar{b}_2) u_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) u_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq  \zeta_3, \quad \text{and} \quad 
+		\left\vert (b_2 + \bar{b}_2) w_s^{\bar{b}_2} \right\vert \leq \left\vert (b_2 + \bar{b}_2) w_{\frac{T}{2}}^{\bar{b}_2} \right\vert \leq c_w + \zeta_3.
 	\end{IEEEeqnarray*}
@@
 	\end{IEEEeqnarray} 
-	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_2^2 + (c_w + \zeta_2)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_2)}$ and $ \kappa_2 := \frac{(c_u - \zeta_2)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
 Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.

### 2018-07-29 PoA.tex
removed notation for limits that are >1

@@
 	\begin{equation*}
-	\lim_{b_2 \to 0} PoA =: PoA^{b_2\to 0} > 1.
+	\lim_{b_2 \to 0} PoA > 1.
 	\end{equation*}
@@
 	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
-	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$
+	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} > 1.$
 \end{proof}
@@
 	\begin{equation*}
-	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
+	\lim_{\bar{b}_2 \to 0} PoA > 1. 
 	\end{equation*}	
@@
 It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
-	\begin{equation*}
-	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.
-	\end{equation*}
+	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
 	Hence, we deduce:
-	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
+	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} > 1. $$
 \end{proof}
@@
 	\begin{split}
-	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
+	    \lim_{b_1 \to 0} PoA > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1,\\
 	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
@@
 By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
-    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.\\
+    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.\\
 

### 2018-07-29 PoA.tex
removed notation for limits that are >1 in numerical results

@@
 In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-For all three cases, as $b_1 \to 0$, we see that $PoA \to PoA^{b_1\to 0}>1$ and as $\bar{b}_1 \to 0$, we see that $PoA \to PoA^{\bar{b}_1 \to 0}>1$.
-We also see that $PoA\to 1$ as $b_1 \to \infty$ and $PoA \to \infty$ as $\bar{b}_1 \to \infty$.
+For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA=>1$.
+We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
 Proposition \ref{prop:b2} is confirmed in Figure \ref{fig:b2_b2bar}.
 When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $PoA \to 1$ as $b_2 \to 0$.
-When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $PoA \to PoA^{b_2 \to 0}>1$ as $b_2 \to 0$.
-For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $PoA \to 1$ as $b_2 \to \infty$.
-For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $PoA \to PoA^{\bar{b}_2 \to 0}>1$ as $\bar{b}_2 \to 0$ and $PoA \to 1$ as $\bar{b}_2 \to \infty$.
-Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $PoA \to 1$ as $r \to \infty$ or $\bar{r} \to \infty$.
+When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $\lim_{b_2 \to 0}PoA>1$.
+For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $\lim_{b_2 \to \infty}PoA= 1$.
+For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
+Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
 

### 2018-07-30 PoA.tex
putting B before D in Riccati denominator because Im a perfectionist
removed the word idem (Ive never seen it before so Im unsure of it)

@@
 \begin{equation}
-		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{D^u B^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
+		u_t= \frac{C^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+D^u(\delta^+_u -\delta^-_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} )}{B^uD^u(1-e^{-(\delta_u^+ - \delta_u^-)(T-t)})+ \delta^+_ue^{-(\delta_u^+ - \delta_u^-)(T-t)} -\delta^-_u  },
 	\label{eq:riccati_ut_sol}
@@
 
-	Idem, by replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.
+	By replacing $\lambda^{r \to \infty}$ with $\lambda^{\bar{r} \to \infty}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, the proof can be repeated, and we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA^{\bar{r}} = 1$.
 \end{proof}
@@
 	\end{IEEEeqnarray*}
-	Idem, for all $t \in [0,T)$,
+	Similarly, for all $t \in [0,T)$,
 	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
@@
 \begin{equation}
-		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{D B(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- }
+		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{BD(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- }
 	\label{eq:riccati_ut_sol_app}

### 2018-07-30 PoA.tex
removed comments (Carmona preferred to remove comments when he uploaded to arXiv since you must upload the source as well)
made it clear that the limits come from the explicit solutions, not PDE literature

@@
 	\end{equation*}
-	It is easy to show that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
-
-%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing.
-Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
-%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
+	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
+
 	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
@@
 
-	%\textbf{Case 1:} when
 	From the assumption:
@@
 	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
-	%Todo: 
-	%\textbf{Case 2}: when \begin{equation*}
-	%\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq %\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
-	%\end{equation*}
 \end{proof}
@@
 \begin{proof}
-	% case when b2 bar \to infty
 	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
@@
 	which we recall has an explicit solution.
-It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
+It is easy to show directly from the explicit solutions that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$.
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
@@
 	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
-It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
+Clearly $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
 	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
@@
 
-	% case 3: b1 to infinity
 	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
@@
 
-	% case 4: b1 bar to infinity
 	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.

### 2018-07-30 PoA.tex
fix reference in numerical results

@@
 We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
-Proposition \ref{prop:b2} is confirmed in Figure \ref{fig:b2_b2bar}.
-When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $PoA \to 1$ as $b_2 \to 0$.
+Propositions \ref{prop:b2_to_infty} and \ref{prop:b2_to_0} are confirmed in Figure \ref{fig:b2_b2bar}.
+When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
 When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $\lim_{b_2 \to 0}PoA>1$.

### 2018-07-30 PoA.tex
fixed overflowing equations and avoided line breaks for inline equations

@@
 	\end{equation*}
-	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t$, and thus, $\lim_{r \to \infty}B^ru^r_t=0$.
+	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$
 
@@
 	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
-	\begin{IEEEeqnarray*}{rCl}
-		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
+	\begin{equation*}
+	\begin{split}
+		(b_2 + \bar{b}_2) u^{b_2}_t &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
 		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
-		&&\\
-		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
-	\end{IEEEeqnarray*}
+		\\
+		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
+	\end{split}
+	\end{equation*}
 	Similarly, for all $t \in [0,T)$,
@@
 	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
-	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$.
+	Moreover, we have:
+	$$\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0, \quad \lim_{b_2 \to 0}\delta^{-,b_2}_u = 0, \quad \text{and} \quad \lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0.$$
 	Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$, $\lim_{b_2 \to 0}u^{b_2}_t = 0.$
@@
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
-Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and thus,
-	\begin{equation*}
-	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T].
-	\end{equation*}
+Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, we have:
+	$$\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1, \quad \text{and thus,} \quad
+	\vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\ \forall  \  t \in [0,T].$$
 
@@
 	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
-	\qquad
+	\
 	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
@@
 	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$.
-Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
+
+	\hspace{-7mm} Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
 Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
@@
 	\end{equation}
+
 	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$.
-Denote $\zeta_2: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$.
-Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
+
+	\hspace{-7mm}Denote $\zeta_2: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
 	\begin{equation}
@@
 Thus, we obtain:
-	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$$
+	$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty,$
 	and conclude that:
@@
 
-	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have 
-	$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty$.
-Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$.
-We have the following limits, for all $t \in [0,T)$:
+	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have:
+	$$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty.$$
+	Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. For all $t \in [0,T)$, we have the limits:
 	\begin{equation}

### 2018-07-30 PoA.tex
consistent punctuation around equations

@@
 $\mu_t=\cL(X^{\phi}_t)$, and similarly, we can identify $\bnu$ as the law of the control, such that $\nu_t=\cL(\phi(t,X^{\phi}_t))$.
-Thus, in the $N=\infty$ regime, we rewrite the social cost as
-\begin{equation*}
-SC(\phi)=\int_0^T<f(t,\,\cdot\,,\cL(X^{\phi}_t),\phi(t,\,\cdot\,),\cL(\phi(t,X^{\phi}_t))),\cL(X^{\phi}_t)>\,dt+<g(\,\cdot\,,\cL(X^{\phi}_T)),\cL(X^{\phi}_T)>
+Thus, in the $N=\infty$ regime, we rewrite the social cost as:
+\begin{equation*}
+SC(\phi)=\int_0^T<f(t,\,\cdot\,,\cL(X^{\phi}_t),\phi(t,\,\cdot\,),\cL(\phi(t,X^{\phi}_t))),\cL(X^{\phi}_t)>\,dt+<g(\,\cdot\,,\cL(X^{\phi}_T)),\cL(X^{\phi}_T)>,
 \end{equation*}
@@
 \begin{equation*}
-    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t)
+    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t),
 \end{equation*}
@@
 \begin{equation*}
-    \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t)
+    \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t),
 \end{equation*}
@@
         dX_t&=\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
-        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t
+        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t,
 \end{split}
@@
         dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
-        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t
+        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t,
 \end{split}
@@
 \begin{equation*}
-    (b_1(t), \bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10}
+    (b_1(t), \bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10},
 \end{equation*}
@@
     q+\bar{q} &>& 0 && q + \bar{q}(1-s) &>& 0 & & q+ \bar{q}(1-s)^2 &>& 0 \\
-    q_T + \bar{q}_T &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T) &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T)^2 &\geq& 0
+    q_T + \bar{q}_T &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T) &\geq& 0 & \quad & q_T + \bar{q}_T(1-s_T)^2 &\geq& 0.
 \end{array}
@@
 \end{equation}
-then there exists a unique solution to the LQEMFG problem, and there exists a unique solution to the LQEMKV problem.
+Then there exists a unique solution to the LQEMFG problem, and there exists a unique solution to the LQEMKV problem.
 And therefore, $PoA=\frac{SC^{MFG}}{SC^{MKV}}$ where $SC^{MFG}:=SC(\phi)$ for $\phi$ given by the explicit solution constructed in Appendix \ref{appendix_solving_fbsdes}.
@@
 \begin{split}
-    a^{MFG}&=a^{MKV}=:a \\
-    \eta_t^{MFG}&=\eta_t^{MKV}=:\eta_t \\
-    v_t^{MFG}&=v_t^{MKV}=:v_t
+    a^{MFG}&=a^{MKV}=:a, \\
+    \eta_t^{MFG}&=\eta_t^{MKV}=:\eta_t, \\
+    v_t^{MFG}&=v_t^{MKV}=:v_t.
 \end{split}
@@
 If we denote:
-\begin{equation*}
+\begin{equation}
 \lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
-\end{equation*}
+\label{eq:lambda}
+\end{equation}
 \begin{equation*}
@@
 		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
-		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
+		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV},
 	\end{equation*}
@@
 	\begin{equation*}
-	\left\{
 		\begin{array}{rcl}
@@
 		\end{array}
-	\right.
 	\end{equation*} 
@@
 		\begin{split}
-			& SC^{MFG} - SC^{MKV}\\
-			&= \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
+			SC^{MFG} - SC^{MKV}&= \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
 			&= \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
@@
     \begin{equation}
-		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0 \qquad u_T = D^u
+		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0, \qquad u_T = D^u,
 		\label{eq:riccati_ut}
@@
 	\begin{equation}
-	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0 \qquad w_T = D^w
+	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0, \qquad w_T = D^w,
 	\label{eq:riccati_wt}
@@
 	\begin{equation}
-	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0 \qquad \eta_T = D^\eta
+	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0, \qquad \eta_T = D^\eta,
 	\label{eq:riccati_etat}
 	\end{equation}
-	where:
+	with:
 	\begin{IEEEeqnarray*}{rClcrClcrCl}
@@
 \end{equation}
-Also for convenience, recall the definition:
+Also for convenience, recall the definition from equation (\ref{eq:lambda}):
 \begin{equation*}
@@
 	\end{equation*}
-	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$
+	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t, \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$
 
@@
 	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
-	Similarly, for every $t\in [0,T]$,
+	Similarly, for every $t\in [0,T]$:
 	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
@@
 	\end{equation*}
-	Therefore, from equation (\ref{eq:PoA_LQ_new_notation}), we have 
+	Therefore, from equation (\ref{eq:PoA_LQ_new_notation}), we have: 
 	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
@@
 \begin{proposition}
-	Assuming assumption \ref{assumption}, and if
+	Assuming assumption \ref{assumption}, and if:
 	\begin{equation*}
@@
 	\end{equation*}
-	then
+	then:
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
@@
 	\end{equation*}
-	Similarly, for all $t \in [0,T)$,
+	Similarly, for all $t \in [0,T)$:
 	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
@@
 Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
-Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$,
+Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
 	$$ 
@@
 	$$ 
-	and thus for all $t \in [0,T]$,
+	and thus for all $t \in [0,T]$:
 	\begin{IEEEeqnarray}{rCl}
@@
 	\end{IEEEeqnarray}
-	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$,
+	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$:
 	\begin{equation*}
@@
 	\end{equation}
-	where:
+	with:
 	\begin{IEEEeqnarray*}{rCl}
@@
 (Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
-	$$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$$
+	$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$
 	Then there exists $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
@@
 Clearly $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
-	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
+	$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$
 	Hence, we deduce:
@@
 	\end{equation*}
-	We conclude:
+	We conclude
 	$

### 2018-07-30 PoA.tex
combined equations in appendix to save space

@@
 \end{equation}
-where $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$.
+with $\delta^\pm_u = -A^u \pm \sqrt{(A^u)^2 + B^u C^u}$.
 Under assumption (\ref{eq:assumptions}), the above conditions on $B^u$, $C^u$, and $D^u$ are satisfied, and we have $\delta^-_u<0<\delta^+_u$, $u_t > 0$ for all $t\in[0,T)$, and $u_T \geq 0$.
@@
 	\end{IEEEeqnarray}
-	where $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
+	with $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
 
@@
 	\end{IEEEeqnarray} 
-	where $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
+	with $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
 Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
@@
 \begin{split}
-        dX_t&=\left(a^x_tX_t+a^{\bar{x}}_t \mathbb{E}X_t+a^y_tY_t+a^{\bar{y}}_t \mathbb{E}Y_t\right)dt+\sigma dW_t \\
-        X_0&=\xi \\
-        dY_t&=\left(b^x_tX_t+b^{\bar{x}}_t \mathbb{E}X_t+b^y_tY_t+b^{\bar{y}}_t \mathbb{E}Y_t\right)dt +Z_t dW_t \\
-        Y_T&=c^xX_T+c^{\bar{x}}\mathbb{E}X_T.
+        dX_t&=\left(a^x_tX_t+a^{\bar{x}}_t \mathbb{E}X_t+a^y_tY_t+a^{\bar{y}}_t \mathbb{E}Y_t\right)dt+\sigma dW_t, \quad X_0=\xi, \\
+        dY_t&=\left(b^x_tX_t+b^{\bar{x}}_t \mathbb{E}X_t+b^y_tY_t+b^{\bar{y}}_t \mathbb{E}Y_t\right)dt +Z_t dW_t, \quad Y_T=c^xX_T+c^{\bar{x}}\mathbb{E}X_T.
 \end{split}
@@
 \begin{split}
-        \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t)\bar{x}_t+(a^y_t+a^{\bar{y}}_t)\bar{y}_t\\
-        \bar{x}_0&=\mathbb{E}(\xi) \\
-        \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t\\
-        \bar{y}_T&=(c^x+c^{\bar{x}})\bar{x}_T,
+        \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t)\bar{x}_t+(a^y_t+a^{\bar{y}}_t)\bar{y}_t, \quad \bar{x}_0=\mathbb{E}(\xi), \\
+        \dot{\bar{y}}_t&=(b^x_t+b^{\bar{x}}_t)\bar{x}_t+(b^y_t+b^{\bar{y}}_t)\bar{y}_t, \quad \bar{y}_T=(c^x+c^{\bar{x}})\bar{x}_T,
 \end{split}
@@
 \begin{split}
-    \dot{\bar{\eta}}_t+(a^y_t+a^{\bar{y}}_t) \bar{\eta}_t^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}_t -b^x_t-b^{\bar{x}}_t&=0\\
-    \bar{\eta}_T-c^x-c^{\bar{x}}&=0 \\
-    \dot{\bar{\chi}}_t+(\bar{\eta}_t(a^y_t+a^{\bar{y}}_t)-b^y_t-b^{\bar{y}}_t)\bar{\chi}_t &=0\\
-    \bar{\chi}_T&=0.
+    \dot{\bar{\eta}}_t+(a^y_t+a^{\bar{y}}_t) \bar{\eta}_t^2+(a^x_t+a^{\bar{x}}_t-b^y_t-b^{\bar{y}}_t) \bar{\eta}_t -b^x_t-b^{\bar{x}}_t&=0, \quad \bar{\eta}_T=c^x+c^{\bar{x}}, \\
+    \dot{\bar{\chi}}_t+(\bar{\eta}_t(a^y_t+a^{\bar{y}}_t)-b^y_t-b^{\bar{y}}_t)\bar{\chi}_t &=0, \quad \bar{\chi}_T=0.
 \end{split}
@@
 \begin{split}
-    \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t \\
-    \bar{x}_0&=\mathbb{E}(\xi),
+    \dot{\bar{x}}_t&=(a^x_t+a^{\bar{x}}_t+(a^y_t+a^{\bar{y}}_t)\bar{\eta}_t)\bar{x}_t, \quad \bar{x}_0=\mathbb{E}(\xi),
 \end{split}
@@
 \begin{split}
-        dX_t&=\left(a^x_tX_t+a^y_tY_t+a^0_t\right)dt+\sigma dW_t \\
-        X_0&=\xi \\
-        dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t \\
-        Y_T&=c^xX_T+c^0,
+        dX_t&=\left(a^x_tX_t+a^y_tY_t+a^0_t\right)dt+\sigma dW_t, \quad X_0=\xi, \\
+        dY_t&=\left(b^x_tX_t+b^y_tY_t+b^0_t\right)dt +Z_t dW_t, \quad Y_T=c^xX_T+c^0,
 \end{split}
@@
 \begin{split}
-    a^0_t&=(a^{\bar{x}}_t+a^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t \\
-    b^0_t&=(b^{\bar{x}}_t+b^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t\\
-    c^0&=c^{\bar{x}}\bar{x}_T.
+    a^0_t=(a^{\bar{x}}_t+a^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t, \quad b^0_t=(b^{\bar{x}}_t+b^{\bar{y}}_t \bar{\eta}_t)\bar{x}_t, \quad c^0=c^{\bar{x}}\bar{x}_T.
 \end{split}
@@
 \begin{split}
-    \dot{\eta}_t+a^y_t\eta_t^2+(a^x_t-b^y_t)\eta_t-b^x_t&=0 \\
-    \eta_T&=c^x, \\
-    \dot{\chi}_t+(-b^y_t+a^y_t\eta_t)\chi_t+a^0_t\eta_t-b^0_t&=0, \\
-    \chi_T&=c^0, \\
+    \dot{\eta}_t+a^y_t\eta_t^2+(a^x_t-b^y_t)\eta_t-b^x_t&=0, \quad \eta_T=c^x, \\
+    \dot{\chi}_t+(-b^y_t+a^y_t\eta_t)\chi_t+a^0_t\eta_t-b^0_t&=0, \quad \chi_T=c^0, \\
     Z_t&=\sigma \eta_t.
@@
 Thus,
-\begin{equation*}
-    \chi_t=(\bar{\eta}_t-\eta_t)\bar{x}_t.
-\end{equation*}
+$\chi_t=(\bar{\eta}_t-\eta_t)\bar{x}_t.$
 
@@
 \begin{split}
-        dX_t&=\left((a^x_t+a^y_t \eta_t)X_t+a^y_t \chi_t+a^0_t\right)dt+\sigma dW_t \\
-        X_0&=\xi.
+        dX_t&=\left((a^x_t+a^y_t \eta_t)X_t+a^y_t \chi_t+a^0_t\right)dt+\sigma dW_t, \quad X_0=\xi.
 \end{split}
@@
 
-\subsection*{\textbf{Scalar Riccati Equation}} If the scalar Riccati equation 
-	\begin{equation*}
-		\dot{\rho}_t - B \rho_t^2 - 2A \rho_t  + C = 0 
+\subsection*{\textbf{Scalar Riccati Equation}} If the scalar Riccati equation: 
+	\begin{equation*}
+		\dot{\rho}_t - B \rho_t^2 - 2A \rho_t  + C = 0, 
 	\end{equation*}
@@
 	\begin{equation}
-		B \neq 0, BD \geq 0, BC>0,
+		B \neq 0,\ BD \geq 0,\ BC>0,
 	\label{eq:Riccati_assumptions}
@@
 \begin{equation}
-		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{BD(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- }
+		\rho_t= \frac{C(1-e^{-(\delta^+ - \delta^-)(T-t)})+D( \delta^+ -\delta^-e^{-(\delta^+ - \delta^-)(T-t)}) }{BD(1-e^{-(\delta^+ - \delta^-)(T-t)})+ \delta^+e^{-(\delta^+ - \delta^-)(T-t)}  -\delta^- },
 	\label{eq:riccati_ut_sol_app}
 \end{equation}
-	where $\delta^\pm = -A \pm \sqrt{(A)^2 + B C}$.
+	with $\delta^\pm = -A \pm \sqrt{(A)^2 + B C}$.
 
@@
 	\begin{equation*}
-		\dot{\rho}_t - 2A \rho_t +C = 0 
+		\dot{\rho}_t - 2A \rho_t +C = 0,
 	\end{equation*}
@@
 \begin{equation*}
-	\left\{
 	\begin{array}{rl}
@@
 	\end{array}
-	\right.
-\end{equation*}
-The conditions (\ref{eq:Riccati_assumptions}) are satisfied if:
-\begin{equation*}
-	\left\{
-	\begin{array}{rl}
-		-(a^y+a^{\bar{y}})&>0 \\
-		-(b^x+b^{\bar{x}})&>0 \\
-		c^x+c^{\bar{x}}& \geq 0.
-	\end{array}
-	\right.
-\end{equation*}
+\end{equation*}
+The conditions (\ref{eq:Riccati_assumptions}) are satisfied if $-(a^y+a^{\bar{y}})>0$, $-(b^x+b^{\bar{x}})>0$, and $c^x+c^{\bar{x}} \geq 0$.
+
 For $\eta_t$, we use:
 \begin{equation*}
-	\left\{
 	\begin{array}{rl}
@@
 	\end{array}
-	\right.
-\end{equation*}
-The conditions (\ref{eq:Riccati_assumptions}) are satisfied if:
-\begin{equation*}
-	\left\{
-	\begin{array}{rl}
-		-a^y&>0 \\
-		-b^x&>0 \\
-		c^x& \geq0.
-	\end{array}
-	\right.
-\end{equation*}
+\end{equation*}
+The conditions (\ref{eq:Riccati_assumptions}) are satisfied if $-a^y>0$, $-b^x>0$, and $c^x \geq0$.
 Returning to the LGEMFG and LGEMKV problems, if we assume the coefficients are nonnegative, we see that these conditions are exactly assumption (\ref{eq:assumptions}).

### 2018-07-30 PoA.tex
style edit: replace some () with [] for visibility

@@
 To keep the presentations simple, we assume the state space is $\mathbb{R}$.
-We denote by $\mu^N_t$ the empirical distribution of the states, namely
+We denote by $\mu^N_t$ the empirical distribution of the states, namely:
 \begin{equation*}
@@
 \begin{split}
-    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right), \\
-    g(x,\mu)&=\frac{1}{2}\left(q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right).
+    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left[q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right], \\
+    g(x,\mu)&=\frac{1}{2}\left[q_T x^2+\bar{q}_T (x-s_T \bar{\mu})^2\right].
 \end{split}
@@
 \begin{split}
-    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y \\
-    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right),
+    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&\left[b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu}\right]y \\
+    &+\frac{1}{2}\left[q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right],
 \end{split}
@@
 \begin{split}
-        dX_t&=\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
-        dY_t&=-\left((q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right)dt +Z_t dW_t,
+        dX_t&=\left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\
+        dY_t&=-\left[(q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right]dt +Z_t dW_t,
 \end{split}
@@
 \begin{split}
-\dot{\bar{x}}^{MFG}_t&=(b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t)\bar{x}^{MFG}_t, \\
+\dot{\bar{x}}^{MFG}_t&=\left[b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t\right]\bar{x}^{MFG}_t, \\
 \bar{x}^{MFG}_0&=\mathbb{E}(\xi),
@@
 \begin{equation}
-\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u)du},
+\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t\left[b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u\right]du},
 \label{eq:x_bar_MFG_explicit}
@@
 \begin{equation}
-v^{MFG}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u) du}ds.
+v^{MFG}_t=Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u\right] du}ds.
 \label{eq:v_t}
@@
 \begin{equation*}
-    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left(a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right)\bar{x}_t^{MFG}.
+    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left[a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right]\bar{x}_t^{MFG}.
 \end{equation*}
@@
 \begin{split}
-    SC^{MFG}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
-    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2)v_t^{MFG}\\
-    &+(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2)(\bar{x}_t^{MFG})^2dt],
+    SC^{MFG}=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
+    &+\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2\right]v_t^{MFG}dt\\
+    &+\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt\Big],
 \end{split}
@@
 \begin{split}
-    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&(b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu})y\\
-    &+\frac{1}{2}\left(q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right).
+    H(t,x,\bar{\mu},\alpha,\bar{\nu},y)=&\left[b_1(t)x+\bar{b}_1(t)\bar{\mu}+b_2(t) \alpha+\bar{b}_2(t)\bar{\nu}\right]y\\
+    &+\frac{1}{2}\left[q(t)x^2+\bar{q}(t)(x-s(t)\bar{\mu})^2 +r(t)\alpha^2+\bar{r}(t)(\alpha-\bar{s}(t)\bar{\nu})^2\right].
 \end{split}
@@
 \begin{split}
-        dX_t=&\left(b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right)dt+\sigma dW_t \\
-        dY_t=&-\left((q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right)dt +Z_t dW_t,
+        dX_t=&\left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\
+        dY_t=&-\left[(q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right]dt +Z_t dW_t,
 \end{split}
@@
 \begin{split}
-\dot{\bar{x}}^{MKV}_t&=(b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t)\bar{x}^{MKV}_t, \\
+\dot{\bar{x}}^{MKV}_t&=\left[b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t\right]\bar{x}^{MKV}_t, \\
 \bar{x}^{MKV}_0&=\mathbb{E}(\xi).
@@
 \begin{equation}
-\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)du},
-\end{equation}
-\begin{equation}
-v^{MKV}_t=Var(\xi)e^{\int_0^t 2(b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u) du}ds.
+\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t\left[b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)\right]du},
+\end{equation}
+\begin{equation}
+v^{MKV}_t=Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u\right] du}ds.
 \label{eq:v_t_MKV}
@@
 \begin{equation*}
-    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left(a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right)\bar{x}_t^{MKV}.
+    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left[a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right]\bar{x}_t^{MKV}.
 \end{equation*}
@@
 \begin{split}
-    SC^{MKV}=&\frac{1}{2}[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
-    &+\int_0^T (q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2)v_t^{MKV}dt \\
-    &+\int_0^T(q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2)(\bar{x}_t^{MKV})^2dt],
+    SC^{MKV}=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
+    &+\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2\right]v_t^{MKV}dt \\
+    &+\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2\right](\bar{x}_t^{MKV})^2dt\Big],
 \end{split}
@@
 \begin{split}
-    \left(s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right)\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
+    \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
     \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}\left[(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2\right]&=0,\ \forall t \in [0,T] \\
@@
 \begin{split}
-    SC^{MFG}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MFG})^2+\frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt\\
+    SC^{MFG}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MFG})^2+\frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_tdt\\
     &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MFG}\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt,
@@
 \begin{split}
-    SC^{MKV}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MKV})^2+ \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt \\
+    SC^{MKV}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MKV})^2+ \frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_tdt \\
     &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MKV}\bar{\eta}_t^{MKV})^2\right)](\bar{x}_t^{MKV})^2dt.
@@
 \begin{equation*}
-h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
+h_{var}: = \frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
 \end{equation*}
@@
 SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
-& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
+& + \frac{1}{2} \lambda \left[ \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right] + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
 \end{split}
@@
 		\\
-		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
+		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
 	\end{split}
@@
 	Similarly, for all $t \in [0,T)$:
-	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
 	and
-	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
+	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
 
@@
 	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
 	$$ 
@@
 		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1 \cdot (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
 	\label{eq:ut_uniform_lower_bound_b2_infinity}
@@
 	\begin{equation}
-	\max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
+	\max \left\{ \left\vert u_t^{b_2} \right\vert , \left\vert w_t^{b_2} \right\vert, \left\vert \eta_t^{b_2} \right\vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
 	\label{eq:ut_wt_upper_bound_b2_infty}
@@
 	\end{equation*}
-	Thus, for any $t \in [0,\frac{T}{2}]$ and $b_2 \geq b_2^{*,I_1}$, we have:
+	Thus, for any $t \in [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
 	$$
-		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
+		\left\vert h_u(b_2, t) - h_w(b_2,t) \right\vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
 	$$
@@
 		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
-		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c}\cdot  \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right) \cdot \zeta_2^2 \leq \epsilon, 
+		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c} \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right)\zeta_2^2 \leq \epsilon, 
 	\label{eq:I1_ineq_b2_infinity}
@@
 	\begin{equation*}
-		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq s \leq T} \vert u_s^{b_2} \vert + \vert w_s^{b_2} \vert  \leq 2M,
+		\left\vert u_t^{b_2} - w_t^{b_2} \right\vert \leq \sup_{0 \leq s \leq T} \left\vert u_s^{b_2} \right\vert + \left\vert w_s^{b_2} \right\vert  \leq 2M,
 		\qquad \text{and} \qquad
@@
 	\begin{IEEEeqnarray}{rCl}
-		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 \cdot e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
+		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
 		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
@@
 	\begin{equation*}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4}{c}\epsilon.
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4\epsilon}{c}.
 	\end{equation*}
@@
 Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, we have:
-	$$\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1, \quad \text{and thus,} \quad
+	$$\max \left\{B^{b_2}, C^{u,b_2}, D^{u,b_2} \right\} \leq B^{b_2 \to \infty} + \epsilon =: c_1, \quad \text{and thus,} \quad
 	\vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\ \forall  \  t \in [0,T].$$
@@
 	\begin{array}{l}
-	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
-	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
 	\end{array}
@@
 	\begin{equation}
-	\max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
+	\max \left\{ \left\vert u_t^{\bar{b}_2}\right\vert, \left\vert w_t^{\bar{b}_2} \right\vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
 	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
@@
 	\begin{equation}
-	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
-	\geq  \frac{\zeta_2 (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
+	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
+	\geq  \frac{\zeta_2 \left(c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1\right)}{ \zeta_1 \left(2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1\right) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
 	\label{eq:ut_lower_bound_b2_bar_infty}
@@
 	\begin{equation*}
-	\vert u_t^{\bar{b}_2} - w_t^{\bar{b}_2} \vert \leq 2M,\qquad \text{and} \qquad \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds \geq m_u \cdot \frac{T}{2}.
+	\left\vert u_t^{\bar{b}_2} - w_t^{\bar{b}_2} \right\vert \leq 2M,\qquad \text{and} \qquad \int_0^t (b_2 + \bar{b}_2)^{\frac{3}{2}} u_s^{\bar{b}_2} ds \geq \frac{T}{2}m_u.
 	\end{equation*}
@@
 	\begin{equation*}
-	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
+	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} +\frac{\sqrt{\left(b_1+\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
 	\end{equation*}
@@
 	\end{equation}
-
 	Since $u^{\bar{b}_1}_t$ is decreasing for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have $\bar{b}_1-B u_t^{\bar{b}_1} \geq \bar{b}_1-B u_0^{\bar{b}_1}$. We have the following limits for $t\in[0,T)$:
@@
 	\end{equation*}
-
 	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.

### 2018-07-30 PoA.tex
nonnegative to non-negative

@@
 \subsection{\textbf{Theoretical Results}}
-For the remainder of the paper, we assume the coefficients are independent of time and nonnegative:
+For the remainder of the paper, we assume the coefficients are independent of time and non-negative:
 \begin{equation*}
@@
 The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
-Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, nonnegative, and satisfy assumption \ref{assumption}.
+Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}.
 In particular, when we allow for full interaction (i.e.
@@
 In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA=>1$.
+For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA>1$.
 We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
@@
 The conditions (\ref{eq:Riccati_assumptions}) are satisfied if $-a^y>0$, $-b^x>0$, and $c^x \geq0$.
-Returning to the LGEMFG and LGEMKV problems, if we assume the coefficients are nonnegative, we see that these conditions are exactly assumption (\ref{eq:assumptions}).
+Returning to the LGEMFG and LGEMKV problems, if we assume the coefficients are non-negative, we see that these conditions are exactly assumption (\ref{eq:assumptions}).
 

### 2018-07-30 PoA.tex
added non-negativity assumption for q_T, etc
updated the numerical results descriptions

@@
 \begin{equation*}
-    (b_1(t), \bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10},
-\end{equation*}
+    (b_1(t),\bar{b}_1(t),b_2(t),\bar{b}_2(t),q(t),\bar{q}(t),r(t),\bar{r}(t),s(t),\bar{s}(t))=(b_1,\bar{b}_1,b_2,\bar{b}_2,q,\bar{q},r,\bar{r},s,\bar{s})\in (\mathbb{R}^+)^{10},
+\end{equation*}
+$$    (q_T,\bar{q}_T,s_T)\in(\mathbb{R}^+)^{3},$$
 and therefore,
@@
 	$$D^{u,\bar{b}_2 \to \infty} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D^w - C^w  = 0.$$
-	In other words, the following three equations imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
+	In other words, the following three equations together imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
 	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
@@
 	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q + \bar{q}(1- s)^2 \right) = 0.$$\\
+\label{remark_6}
 \end{remark}
@@
 \begin{split}
-    &\xi\equiv 1,\ T=1 \\
-    &b_1=1,\  \bar{b}_1=1,\ b_2=1,\ \bar{b}_2=1,\ \sigma=1 \\
-    &q=1,\ \bar{q}=1,\ s=0.5,\ r=1,\ \bar{r}=1,\ \bar{s}=0.5 \\
-    &q_T=1,\  \bar{q}_T=1,\ s_T=0.5.
+    &\xi\equiv 1,\ T=1,\ b_1=1,\  \bar{b}_1=1,\ b_2=1,\ \bar{b}_2=1,\ \sigma=1, \\
+    &q=1,\ \bar{q}=1,\ s=0.5,\ r=1,\ \bar{r}=1,\ \bar{s}=0.5,\ q_T=1,\  \bar{q}_T=1,\ s_T=0.5.
 \end{split}
@@
 For results involving only interaction through the controls, we set $\bar{b}_1=0$, $\bar{q}=0$, and $\bar{q}_T=0$.
-Figures \ref{fig:b1_b1bar}-\ref{fig:r_rbar} show the price of anarchy as we vary one parameter at a time for each of three cases: full interaction (i.e.
+Figures \ref{fig:b1_b1bar}-\ref{fig:r_rbar} show the price of anarchy as we vary one parameter at a time for each of three interaction cases: full interaction (i.e.
 through the states and the controls), interaction only through the states, and interaction only through the controls.
@@
 In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-For all three cases, we see that $\lim_{b_1 \to 0}PoA >1$ and $\lim_{\bar{b}_1 \to 0}PoA>1$.
-We also see that $\lim_{b_1 \to \infty}PoA = 1$ and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
-Propositions \ref{prop:b2_to_infty} and \ref{prop:b2_to_0} are confirmed in Figure \ref{fig:b2_b2bar}.
-When there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
-When there is full interaction or only interaction through the controls, then $\bar{b}_2\neq0$ and we see that $\lim_{b_2 \to 0}PoA>1$.
-For all three cases, we note that the condition $\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)}$ is satisfied, and thus, $\lim_{b_2 \to \infty}PoA= 1$.
+The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
+Since we consider $\xi \equiv 1$ and the result still holds, we see that $Var(\xi)>0$ is not a necessary assumption.
+Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}.
+For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
+When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$.
+For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$.
+Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction through the states or interaction through the controls, and is thus an unnecessary assumption.
 For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
+Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is thus an unnecessary assumption.
+This agrees with the conclusion of Remark \ref{remark_6}.
 Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.

### 2018-07-30 PoA.tex
updated the numerical results descriptions

@@
 For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$.
-Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction through the states or interaction through the controls, and is thus an unnecessary assumption.
+Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is thus an unnecessary assumption.
 For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.

### 2018-07-31 PoA_response_to_referee.tex
response to referee: minor points

@@
 
-We would like to thank the reviewer for their remarks. We have addressed each of their points as follows:
+We would like to thank the reviewer for their remarks. We have addressed each of their points as follows:\\
 
-Main Points:
+\hspace{-7mm} \textbf{Main Points:}
 \begin{enumerate}
@@
 
-Minor Points:
+\hspace{-7mm} \textbf{Minor Points:}
+\begin{enumerate}
+	\item We agree that this notation was awkward. We have changed all of the function definitions to the more standard notation.
+	\item We changed `its' to `their' to have consistent pronoun usage.
+	\item We added `game'.
+	\item We have used the pronoun `their' throughout the text, so we will continue to use it here.
+	\item The missing parenthesis have been added.
+	\item We agree. Now page 6 line 10 reads `According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is...'
+	\item Yes, this was a typo.
+On page 6 line 13, we have replaced $x$ by $X_t$.
+At this point, the fixed point is not addressed, and the control is the best response when the mean field is fixed.
+So we should not yet replace $\bar{\mu}$ and $\bar{\nu}$.
+	\item On page 6 line -6, we have added: `Note $c^{MFG}(t)=a^{MFG}(t)+b^{MFG}(t)$.' We also added `Note $c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$.' on page 8 line -12.
+	\item The extra parenthesis has been removed.
+	\item We have added equation (6) and refer to it in the proof of Corollary 2, page 13 line 2. And yes, it should be $\bar{x}_t^{MFG}$.
+	\item We changed `tends' to `tend'.
+	\item In the proof of Proposition 3, page 15 line -6, we replaced the limit of $v^r_t$ with our new notation $v^{r \to \infty}_t$.
+	\item Yes, this was a typo. These values were indeed after taking the limit. The limits in a slightly different presentation now appear in the proof of Proposition 5 Case 2, page 19 line 12.
+\end{enumerate}
+
+\hspace{-7mm} In addition to the suggested revisions, we have also made the following minor modifications:
 \begin{enumerate}
@@
 
-In addition to the suggested revisions, we have also made the following minor modifications:
-\begin{enumerate}
-	\item 
-\end{enumerate}
+Finally, we would like to acknowledge that the length of our paper has increased from 26 pages at submission to 33 pages for the final version.
+The issues in our proofs raised by the reviewer required us to write many more details, and in some cases, new approaches altogether.
+We feel that the increase in length was necessary to address all of the issues pointed out by the reviewer.
+(ToDo: Is this comment necessary?)
 

### 2018-07-31 PoA.tex
response to referee: minor points

@@
 We assume $f$ and $g$ are Lipschitz in each of their arguments.
-The goal of player $i$ is to minimize its expected cost as given by:
+The goal of player $i$ is to minimize their expected cost as given by:
 \begin{equation*}
@@
 \end{equation*}
-So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
+Note that $c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$. So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
 \begin{equation}

### 2018-07-31 PoA_response_to_referee.tex
response to referee: some of the major points

@@
 \begin{enumerate}
+	\item This was a good suggestion.
+We have added equations (3)-(7) on page 7, and equations (9)-(13) on page 8, and we refer to these equations often.
+In the same vein we have added equations (26)-(29) on pages 13-14, which are used frequently in Propositions 3-7.
+	\item Since the Hamiltonian depends on the scalars $\bar{\mu}$ and $\bar{\nu}$, instead of the full measures, the derivative in the measure argument greatly simplifies.
+On page 8 line 6, we refer to section 4 in [5], where they write what this condition should be in the linear quadratic case.
+On page 8 lines 7 and 8, the derivative is a standard derivative and does not need explaining further.
+There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
 	\item 
+	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$.
+This was overlooked by the authors.
+If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
+	\item
+	\item
+	\item We added a sentence at the beginning of section 2.4 on page 27 stating that we use a simple rectangular integration rule to numerically compute integrals.
 \end{enumerate}

### 2018-07-31 PoA.tex
response to referee: some of the major points

@@
 The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
-Using the simple rectangle rule to evaluate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}.
+Using the simple rectangle rule to estimate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}.
 In particular, when we allow for full interaction (i.e.

### 2018-07-31 PoA_response_to_referee.tex
response to referee: major point 3

@@
 There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
-	\item 
+	\item We have made many modifications in the computation of $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt$ on pages 10-11 to make it much more readable.
+Whereas we previously dropped the superscripts $MFG$ and $MKV$ to address both simultaneously, we now show the computation fully for the $MFG$ case.
+Then after the computation, we state on page 11 line -5: `Repeating the calculation for $\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2dt$...
+we arrive at...' and we provide the result for the $MKV$ case.
+We now only use the notation introduced thus far, instead of mixing in the notation from the appendix, which could cause confusion.
+We also take the suggestion from the reviewer of explicitly writing the end result of our computation.
+Also, we now give an explanation for each step of the calculation.
+Finally, we separated the equations in the former equation (7) and give more explanation for how they are derived.
+They are now equations (18) and (19) in the final version.
+And yes, there should not have been a $t$ in $h_{var}$.
+We believe pages 10-11 should be much easier to follow in their present form.
 	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$.
@@
 	\item The extra parenthesis has been removed.
-	\item We have added equation (6) and refer to it in the proof of Corollary 2, page 13 line 2. And yes, it should be $\bar{x}_t^{MFG}$.
+	\item We have added equation (6) and refer to it in the proof of Corollary 2, page 13 line 2. And yes, it should have been $\bar{x}_t^{MFG}$.
 	\item We changed `tends' to `tend'.

### 2018-07-31 PoA.tex
response to referee: major point 3

@@
 \end{equation*}
-and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
+and use the terminal condition for $\bar{\eta}^{MFG}_T$ (see equation (\ref{eq:eta_bar_MFG})), then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
 \begin{equation}
@@
 \end{equation*}
-Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
+Using the terminal condition for $\bar{\eta}^{MKV}_T$ (see equation (\ref{eq:eta_bar_MKV})), equation (\ref{eq:SC_MKV_1}) can be rewritten as:
 \begin{equation}

### 2018-07-31 PoA.tex
minor edit remark 6

--- 2018-07-31 PoA.tex
@@
 We assume $f$ and $g$ are Lipschitz in each of their arguments.
-The goal of player $i$ is to minimize their expected cost as given by:
+The goal of player $i$ is to minimize its expected cost as given by:
 \begin{equation*}
@@
 \end{equation*}
-Note that $c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$. So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
+So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
 \begin{equation}
@@
 	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality is equivalent to:
-	$$D^{u,\bar{b}_2 \to \infty} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D^{u,\bar{b}_2 \to 0} - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D^w - C^w  = 0.$$
+	$$D^{u,\bar{b}_2 \to \infty} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D - C^w  = 0.$$
 	In other words, the following three equations together imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
@@
 	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have:
-	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} <\frac{1}{4B},$$
+	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} \leq \frac{1}{4B},$$
 	and such that the functions $t \mapsto u_t^{\bar{b}_1}$ and $ t \mapsto w_t^{\bar{b}_1}$ are decreasing. Thus, for all $t \in [0, T/2]$ we have:

### 2018-08-01 PoA.tex
almost finished with lemma 1 for Prop 4 Case 2

--- 2018-07-31 PoA.tex
@@
 \begin{proposition}
-	Assuming assumption \ref{assumption}, then:
+	Assuming Assumption \ref{assumption}, then:
 	\begin{equation*}
@@
 
+The following lemma will be used in Proposition \ref{prop:b2_to_infty}.
+\begin{lemma}
+	There exists a $b_2^{*,l}>0$ and $M>0$, such that for all $b_2 \geq b_2^{*,l}$:
+	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M.$$
+\end{lemma}
+
+\begin{proof}
+	First, we show that for $t\in[0,T)$: (ToDo: This is already stated in Proposition 4.)
+	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
+	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$:
+	$$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$$
+	Clearly there exists $b_2^{*,2}$ such that for $b_2 \geq b_2^{*,2}$:
+	$$b_2\eta^{b_2}_T=b_2D^\eta=b_2(q_T+\bar{q}_T)\geq c_\eta+2.$$
+	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing.
+Since for any $b_2$, the function $t \mapsto b_2 \eta^{b_2}_t$ is continuous, by the intermediate value theorem we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, there exists a $t^*_{b_2}\in[0,T]$ such that:
+	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$$
+	and:
+	$$b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
+	Thus,
+	$$1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta=\frac{\frac{1}{b_2} \left[ToDO \right]}{\frac{1}{b_2^2} \left[ToDo \right]}-c_\eta=\frac{ToDo}{ToDo}.$$
+	After rearranging terms:
+	\begin{equation}
+	\begin{split}
+	\frac{D}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
+	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)} \\
+	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)}.
+	\end{split}
+	\label{eq:lemma_1}
+	\end{equation}
+	Since we have: (ToDo: show these limits)
+	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$$
+	there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
+	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
+	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
+	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
+	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
+	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
+	\begin{equation}
+	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).
+	\label{eq:lemma_2}
+	\end{equation}
+	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta^{b_2 \to \infty}}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
+	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{\delta^{+,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, $$
+	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2},$$
+	and thus,
+	$$c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	
+	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
+	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
+	Finally, for $b_2 \geq b_2^{*,l}$, we have:
+	\begin{equation*}
+	\begin{split}
+	\int_0^T b_2 \eta^{b_2}_t dt&=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \\
+	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
+	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
+	\end{split}
+	\end{equation*}
+\end{proof}
+
 % proposition b_2 to \infty
 \begin{proposition}
-	Assuming assumption \ref{assumption}, and if:
+	Assume Assumption \ref{assumption}. If:
 	\begin{equation*}
@@
 	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+	Otherwise,
+	$$ \lim_{b_2 \to \infty} PoA > 1.$$
 \label{prop:b2_to_infty}
@@
 	\end{equation}
-	and such that the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.
-
-	From the assumption:
+	and such that the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$. \\
+
+	\textbf{Case 1:} When:
 	\begin{equation*}
@@
 	and thus,
-	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
+	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$\\
+
+	%Todo: 
+	\textbf{Case 2}: When:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
+	\end{equation*}
+
 \end{proof}
@@
 \begin{proposition}
-	Assume assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
+	Assume Assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
 	\begin{equation*}
@@
 \begin{proposition}
-	Assuming assumption \ref{assumption}, then:
+	Assuming Assumption \ref{assumption}, then:
 	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
@@
 Let $\zeta_3 := c_u / 2$.
-Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, from equation (\ref{eq:riccati_ut_sol_deriv}), there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
@@
 \begin{remark}
-	Consider assumption \ref{assumption} and the case when $\bar{b}_2$ tends to zero.
+	Consider Assumption \ref{assumption} and the case when $\bar{b}_2$ tends to zero.
 We have $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$, and therefore, $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$ implies $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
+	Assuming Assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
 	\begin{equation*}
@@
 The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
-Using the simple rectangle rule to estimate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy assumption \ref{assumption}.
+Using the simple rectangle rule to estimate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy Assumption \ref{assumption}.
 In particular, when we allow for full interaction (i.e.

### 2018-08-01 PoA.tex
edit second case prop 4 progress 1/8

--- 2018-07-31 PoA.tex
@@
 	   b_2 \eta_t^{b_2} \geq m_\eta.
+	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
 	\end{equation*}
@@
 	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% case 2: c_u \neq c_w
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\textbf{Case 2:} If
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	then $c_u \neq c_w$.
+In this situation, we will show that the Price of Anarchy tends to a number strictly greater than $1$ as $b_2$ tends to infinity.
+To do so, we will show that in this asymptotic regime, $\Delta SC^{b_2}$ is lower bounded by a strictly positive constant and $SC^{MKV,b_2}$ is upper bounded by another constant, in which both of them are independent of $b_2$.\\
+
+	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$.
+We know directly that  $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
+Moreover, from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), we have the uniform lower bounds $m_u$ and $m_\eta$ for $u_t^{b_2}$ and $\eta_t^{b_2}$.\\
+
+	Step 1: We provide a lower bound for $\Delta SC^{b_2}$ with the similar techniques used for the term $I_1$, see inequality (\ref{eq:I1_ineq_b2_infinity}).
+For every $0 \leq t <T$, we have $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
+Let $\zeta_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
+Thus, there exists $b_2^{*,nominator} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,nominator}$ and all $s \in [0, T/2]$ we have:
+	\begin{equation*}
+	\begin{array}{lclclclcl}
+		c_u - \left\vert c_u - c_w  \right\vert /4 &\leq& h_u(b_2, 0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2) &\leq& c_u + \left\vert c_u - c_w \right\vert /4, \\
+		c_w -  \left\vert c_u - c_w  \right\vert /4 &\leq& h_w(b_2, 0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2) &\leq& c_w + \left\vert c_u - c_w  \right\vert /4,
+	\end{array}
+	\end{equation*}
+	which implies that
+	$$ \left\vert h_u(b_2, s) - h_w(b_2,s)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t.
+	$$
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,nominator}$ we deduce
+	\begin{IEEEeqnarray}{rCl}
+		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B \int_0^{\frac{T}{2}} (u_t - w_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
+		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \cdot \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t \right) dt \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}	
+	\label{eq:nominator_ineq_b2_infinity}	
+	\end{IEEEeqnarray}
+	where the last inequality is justified by the choice of $\zeta_3$ so that
+	$  1 - e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)}  \geq \frac{1}{2}$. \\
+
+	Step 2: We would like to provide an upper bound for $b_2\cdot SC^{MKV,b_2}$. From equation (\ref{eq:v_t_new_notation}), we have 
+	\begin{equation}
+	\begin{array}{rl}
+		& \displaystyle b_2 \cdot SC^{MKV,b_2}   \\
+		= & \displaystyle \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{b_2+ \bar{b}_2} h_w(b_2, 0) (\mathbb{E}(\xi) )^2 \right] }_\text{\large{:= $J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{:= $J_2$}}
+	\end{array}		
+	\end{equation}
+
 \end{proof}

### 2018-08-01 PoA.tex

--- 2018-08-01 PoA.tex
@@
 	and thus,
-	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$\\
-
-	%Todo: 
-	\textbf{Case 2}: When:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
-	\end{equation*}
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% case 2: c_u \neq c_w
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\textbf{Case 2:} When
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	we have $c_u \neq c_w$.
+In this situation, we will show that the Price of Anarchy tends to a number strictly greater than $1$ as $b_2$ tends to infinity.
+To do so, we will show that in this asymptotic regime, $\Delta SC^{b_2}$ is lower bounded by a strictly positive constant and $SC^{MKV,b_2}$ is upper bounded by another constant, in which both of them are independent of $b_2$.\\
+
+	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$.
+We know directly that  $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
+Moreover, from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), we have the uniform lower bounds $m_u$ and $m_\eta$ for $u_t^{b_2}$ and $\eta_t^{b_2}$.\\
+
+	Step 1: We provide a lower bound for $\Delta SC^{b_2}$ with the similar techniques used for the term $I_1$, see inequality (\ref{eq:I1_ineq_b2_infinity}).
+For every $0 \leq t <T$, we have $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
+Let $\zeta_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
+Thus, there exists $b_2^{*,nominator} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,nominator}$ and all $s \in [0, T/2]$ we have:
+	\begin{equation*}
+	\begin{array}{lclclclcl}
+		c_u - \left\vert c_u - c_w  \right\vert /4 &\leq& h_u(b_2, 0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2) &\leq& c_u + \left\vert c_u - c_w \right\vert /4, \\
+		c_w -  \left\vert c_u - c_w  \right\vert /4 &\leq& h_w(b_2, 0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2) &\leq& c_w + \left\vert c_u - c_w  \right\vert /4,
+	\end{array}
+	\end{equation*}
+	which implies that
+	$$ \left\vert h_u(b_2, s) - h_w(b_2,s)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t.
+	$$
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,nominator}$ we deduce
+	\begin{IEEEeqnarray}{rCl}
+		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B \int_0^{\frac{T}{2}} (u_t - w_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
+		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \cdot \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t \right) dt \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}	
+	\label{eq:nominator_ineq_b2_infinity}	
+	\end{IEEEeqnarray}
+	where the last inequality is justified by the choice of $\zeta_3$ so that
+	$  1 - e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)}  \geq \frac{1}{2}$. \\
+
+	Step 2: We would like to provide an upper bound for $b_2\cdot SC^{MKV,b_2}$. From equation (\ref{eq:v_t_new_notation}), we have 
+	\begin{equation}
+	\begin{array}{rl}
+		& \displaystyle b_2 \cdot SC^{MKV,b_2}   \\
+		= & \displaystyle \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{b_2+ \bar{b}_2} h_w(b_2, 0) (\mathbb{E}(\xi) )^2 \right] }_\text{\large{:= $J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{:= $J_2$}}
+	\end{array}		
+	\end{equation}
 

### 2018-08-01 PoA.tex
2nd case prop 4 progression 75%

--- 2018-08-01 PoA.tex
@@
 
-The following lemma will be used in Proposition \ref{prop:b2_to_infty}.
+% proposition b_2 to \infty
+\begin{proposition}
+	Assume Assumption \ref{assumption}. If:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	then:
+	$$ \lim_{b_2 \to \infty} PoA = 1.$$
+	Otherwise,
+	$$ \lim_{b_2 \to \infty} PoA > 1.$$
+\label{prop:b2_to_infty}
+\end{proposition}
+\begin{proof}
+	When $b_2 \to \infty$, we have:
+	\begin{equation*}
+	\begin{array}{l}
+	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
+	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
+	\end{array}
+	\end{equation*}
+	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
+	\begin{equation*}
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
+	\end{equation*}
+	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
+	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
+	\begin{equation*}
+	\begin{split}
+		(b_2 + \bar{b}_2) u^{b_2}_t &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
+		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
+		\\
+		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
+	\end{split}
+	\end{equation*}
+	Similarly, for all $t \in [0,T)$:
+	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	and
+	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
+
+	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
+Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
+Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
+	$$ 
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
+	$$ 
+	and thus for all $t \in [0,T]$:
+	\begin{IEEEeqnarray}{rCl}
+		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
+	\label{eq:ut_uniform_lower_bound_b2_infinity}
+	\end{IEEEeqnarray}
+	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$:
+	\begin{equation}
+	   b_2 \eta_t^{b_2} \geq m_\eta.
+	\label{eq:eta_t_uniform_lower_bound_b2_infinity}
+	\end{equation}
+
+	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
+	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing.
+	Therefore,
+	\begin{equation*}
+	u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
+	\label{eq:u_t_bound}
+	\end{equation*}
+	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
+	\begin{equation}
+	\max \left\{ \left\vert u_t^{b_2} \right\vert , \left\vert w_t^{b_2} \right\vert, \left\vert \eta_t^{b_2} \right\vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
+	\label{eq:ut_wt_upper_bound_b2_infty}
+	\end{equation}
+	and such that the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$. \\
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	% Case 1: c_u = c_w
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
+	\textbf{Case 1:} When:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
+	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
+	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
+We have:
+	\begin{equation}
+	\begin{split}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
+		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
+	\end{split}
+	\label{eq:I_1_plus_I_2}
+	\end{equation}
+	with:
+	\begin{IEEEeqnarray*}{rCl}
+	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
+	\right) dt \\
+	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt,
+	\end{IEEEeqnarray*}
+	and:
+	$$
+		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
+	$$
+
+	Fix $\epsilon>0$.
+In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
+First, consider $I_1^{b_2}$.
+Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
+(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
+	$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$
+	Then there exists $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	\begin{equation*}
+	\begin{array}{lclclclcl}
+		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
+		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
+	\end{array}
+	\end{equation*}
+	Thus, for any $t \in [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
+	$$
+		\left\vert h_u(b_2, t) - h_w(b_2,t) \right\vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
+	$$
+	Therefore,
+	\begin{IEEEeqnarray}{rCl}
+		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
+		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c} \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right)\zeta_2^2 \leq \epsilon, 
+	\label{eq:I1_ineq_b2_infinity}
+	\end{IEEEeqnarray}
+	where the last inequality comes from the definition of $\zeta_2$.
+
+	Next, consider $I_2^{b_2}$.
+Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
+	\begin{equation*}
+		\left\vert u_t^{b_2} - w_t^{b_2} \right\vert \leq \sup_{0 \leq s \leq T} \left\vert u_s^{b_2} \right\vert + \left\vert w_s^{b_2} \right\vert  \leq 2M,
+		\qquad \text{and} \qquad
+		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
+	\end{equation*}
+	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
+	\begin{IEEEeqnarray}{rCl}
+		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
+		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
+	\label{eq:I2_b2_infty}
+	\end{IEEEeqnarray}
+	with $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
+
+	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
+	\begin{equation*}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4\epsilon}{c}.
+	\end{equation*}
+	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
+	\begin{equation*}
+		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
+	\end{equation*}
+	and thus,
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	% case 2: c_u \neq c_w
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\textbf{Case 2:} When
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
+	\end{equation*}
+	we have $c_u \neq c_w$.
+In this situation, we will show that the Price of Anarchy tends to a number strictly greater than $1$ as $b_2$ tends to infinity.
+To do so, we will show that in this asymptotic regime, $(b_2 + \bar{b_2}) \Delta SC^{b_2}$ is lower bounded by a strictly positive constant $c_{nom}$, and meanwhile $b_2 \cdot SC^{MKV,b_2}$ is upper bounded by another constant $M_{den}$.
+Both of these constants are independent of $b_2$.\\
+
+	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$.
+As what have been discussed previously, we know that  $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
+Moreover, from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), we have the uniform lower bounds $m_u$ and $m_\eta$ for $u_t^{b_2}$ and $\eta_t^{b_2}$.
+Also, for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$, we have $\eta_t^{b_2} \leq M$\\
+
+	Step 1: we derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
+It has been shown that for every $0 \leq t <T$,  $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
+Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
+Then, there exists $b_2^{*,nominator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,nominator}$ and all $s \in [0, T/2]$ we have:
+	\begin{equation*}
+	\begin{array}{lclclclcl}
+		c_u - \left\vert c_u - c_w  \right\vert /4 &\leq& h_u(b_2, 0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2) &\leq& c_u + \left\vert c_u - c_w \right\vert /4, \\
+		c_w -  \left\vert c_u - c_w  \right\vert /4 &\leq& h_w(b_2, 0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2) &\leq& c_w + \left\vert c_u - c_w  \right\vert /4,
+	\end{array}
+	\end{equation*}
+	which implies that for all $t \in [0,T/2]$
+	$$ \left\vert h_u(b_2, t) - h_w(b_2,t)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t.
+	$$
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,nominator}$ we deduce
+	\begin{IEEEeqnarray}{rCl}
+		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B \int_0^{\frac{T}{2}} (u_t - w_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
+		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \cdot \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t \right) dt \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)} \right) \nonumber \\
+		&\geq & (2 c_{nom} ) \cdot \frac{1}{2} = c_{nom}
+	\label{eq:nominator_ineq_b2_infinity}	
+	\end{IEEEeqnarray}
+	where $c_{nom} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified by the choice of $b_2 \geq c_3$. \\
+
+	Step 2: We would like to provide an upper bound for $b_2\cdot SC^{MKV,b_2}$. From formula (\ref{eq:SC_MKV_2}), we have 
+	\begin{equation}
+	b_2 \cdot SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + b_2 w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{:= $J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{:= $J_2$}}
+	\label{eq:J1_plus_J2_b2_infinity}
+	\end{equation}	
+	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
+	Let $\kappa_5 = \frac{2 m_{\eta}}{r + \bar{r}}$ and $\displaystyle l(t) = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta_u du} ds$.
+Because for all $b_2 \geq b_2^{*,basic}$ we have $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, then
+	\begin{equation}
+		b_2 \cdot l(t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
+	\label{eq:l(t)_upper_bound_b2_infinity}
+	\end{equation}
+	Besides, with Riccati equation (\ref{eq:riccati_etat}) of $\eta_t^{b_2}$ and the formula of integration by parts, we deduce:
+	\begin{IEEEeqnarray*}{rCL}
+		 \int_0^T B^{\eta, b_2} (\eta_t^{b_2} )^2 \cdot l(t) dt 
+		&= & \int_0^T  (\eta_t^{b_2})' \cdot l(t) dt + \int_0^T \left( -2A^{\eta} \eta_t^{b_2} + C^{\eta} \right) \cdot l(t) dt \nonumber \\
+		&\geq & \left[ \eta_T^{b_2} l(T) - \eta_0^{b_2} l(0) - \int_0^T \eta_t^{b_2} \cdot (l(t))' dt \right]  \nonumber \\
+		&= & - \int_0^T \eta_t^{b_2} \cdot \left[ l(t)\cdot( - 2 B^{\eta,b_2} \eta_t^{b_2} ) + 1 \right] dt + l(T) D^{\eta} \nonumber \\
+		&\geq& 2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot l(t) dt - \int_0^T \eta_t^{b_2} dt.
+	\end{IEEEeqnarray*}
+	where the inequalities are justified by the fact that $-A^{\eta}$, $C^{\eta}$, $D^{\eta} $, $t \mapsto \eta_t^{b_2}$ and $t \mapsto l(t)$ are all positive.	By rearranging the terms we obtain:
+	\begin{equation}
+		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
+	\label{eq:l(t)_transformation_b2_infinity}
+	\end{equation}
+
+	Let's look at $J_1$ first.
+	From the expression of $v_t$ (equation (\ref{eq:v_t_new_notation})) and inequality (\ref{eq:l(t)_upper_bound_b2_infinity}), we have that for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$:
+	\begin{IEEEeqnarray*}{rCl}
+		b_2 v_t &= & Var(\xi) e^{2b_1 t} \cdot b_2 e^{- 2 B^{\eta,b_2} \int_0^t \eta_s ds } + \sigma^2 \cdot b_2 \int_0^t e^{2b_1 (t-s)} \cdot e^{-2B^{\eta,b_2} \int_s^t \eta_u du} ds \nonumber \\	
+		&\leq& Var(\xi) e^{2b_1 T}\cdot b_2 e^{- \frac{2 b_2}{r + \bar{r}} m_\eta \cdot t} + \sigma^2 e^{2 b_1 T} b_2 \cdot l(t)  \nonumber \\
+		&\leq& e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right).
+	\end{IEEEeqnarray*}
+	Hence, if we choose $b^{*,J_1} \geq b^{*,basic}$ such that
+	for all $b_2 \geq b_2^{*,J_1}$ we have 
+	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad and \quad b_2 \cdot e^{- \kappa_5 b_2 \cdot T} \leq \frac{1}{\kappa_5} $$
+	we can derive an upper bound for $J_1$. Namely, for all $b_2 \geq b_2^{*,J_1}$:
+	\begin{IEEEeqnarray}{rCl}
+		J_1 &\leq& \frac{q+\bar{q}}{2}  \cdot e^{2b_1 T} \int_0^T \left( Var(\xi) \cdot b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right) dt  \nonumber \\
+		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 T \cdot b_2 } + \frac{\sigma^2}{\kappa_5} \right) + \frac{b_2}{b_2 + \bar{b}_2} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
+		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_5}  + \frac{\sigma^2 T}{\kappa_5} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_5} + \frac{\sigma^2}{\kappa_5} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{2} \nonumber \\
+		& =:& M_{J_1}
+	\label{eq:J1_upper_bound_b2_infinity}
+	\end{IEEEeqnarray}
+
+	As for the term $J_2$, we can expand it like the following:
+	\begin{IEEEeqnarray*}{rCl}
+		J_2 &=& \frac{1}{2 (r + \bar{r}) }\int_0^T \left(b_2 \eta_t^{b_2} \right)^2 \cdot Var(\xi) e^{2b_1 t} \cdot b_2 \exp \left( - 2 B^{\eta,b_2} \int_0^t \eta_s ds \right) dt \nonumber \\
+		&& \hspace{10em}  + \frac{\sigma^2}{2} \cdot  b_2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot \left( \int_0^t e^{2b_1(t-s) - 2B^{\eta,b_2} \int_s^t \eta_u^{b_2} du} ds \right)  dt .
+	\end{IEEEeqnarray*}
+	The first integration on the right-hand side of the above equation can be treated using similar techniques in Case 1.
+Whilst, for the second integration, we will use a result which says that there exists $b^{*,integral}>0$ and a constant $M_{intgl}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*, integral}$ we have:
+	\begin{equation}
+	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{intgl}
+	\label{eq:intgeral_b2_eta_t_bound_b2_infinity}
+	\end{equation}
+	In order to keep the flow of idea fluent, we defer temporarily the proof of the above claim into Lemma \ref{lemma:int_b2_eta_t}.
+
+	Since $b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} c_\eta$ for all $t \in [0, T/2]$, we can choose $b_2^{*,J_2} \geq \max\{ b_2^{*,integral}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$ we have
+	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0, \frac{T}{2}]  \qquad and \quad b_2^{3} \cdot e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
+	Thus, together with inequalities (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}) and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), let $\kappa_6 = \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$ we deduce that
+	\begin{IEEEeqnarray}{rCl}
+		J_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta_t \right)^2 \cdot b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 \cdot b_2^3 \cdot e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
+		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{intgl} \nonumber \\
+		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{intgl}}{2} =: M_{J_2}
+	\label{eq:J2_upper_bound_b2_infinity}
+	\end{IEEEeqnarray}
+
+	Now, from inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), and the fact that $M_{J_1}$ and $M_{J_2}$ are independent of $b_2$, equation (\ref{eq:J1_plus_J2_b2_infinity}) gives raise to an upper bound: for all $b_2 \geq b_2^{*,denumerator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
+	\begin{equation} 
+		b_2 \cdot SC^{MKV, b_2}  = J_1 + J_2 \leq M_{J_1} + M_{J_2} =: M_{den}
+	\label{eq:demumerator_ineq_b2_infinity}
+	\end{equation}
+
+	Finally, together with inequalities (\ref{eq:nominator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,nominator}, b_2^{*,denumerator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
+	\begin{equation}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) \cdot (b_2 \cdot SC^{MKV,b_2} ) } \geq \frac{c_{nom}}{ 2 M_{den}} > 0.
+	\end{equation}
+	Therefore, we can draw the conclusion that in case when $\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}$, we have 
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} > 1.$$ 
+\end{proof}
+
+The following lemma has been used in Proposition \ref{prop:b2_to_infty}.
 \begin{lemma}
@@
 	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M.$$
+	\label{lemma:int_b2_eta_t}
 \end{lemma}
@@
 	\end{equation*}
-\end{proof}
-
-% proposition b_2 to \infty
-\begin{proposition}
-	Assume Assumption \ref{assumption}. If:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{equation*}
-	then:
-	$$ \lim_{b_2 \to \infty} PoA = 1.$$
-	Otherwise,
-	$$ \lim_{b_2 \to \infty} PoA > 1.$$
-\label{prop:b2_to_infty}
-\end{proposition}
-\begin{proof}
-	When $b_2 \to \infty$, we have:
-	\begin{equation*}
-	\begin{array}{l}
-	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
-	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
-	\end{array}
-	\end{equation*}
-	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
-	\begin{equation*}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
-	\end{equation*}
-	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
-	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
-	\begin{equation*}
-	\begin{split}
-		(b_2 + \bar{b}_2) u^{b_2}_t &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
-		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
-		\\
-		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
-	\end{split}
-	\end{equation*}
-	Similarly, for all $t \in [0,T)$:
-	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
-	and
-	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
-
-	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
-Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
-Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
-	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
-	$$ 
-	and thus for all $t \in [0,T]$:
-	\begin{IEEEeqnarray}{rCl}
-		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
-	\label{eq:ut_uniform_lower_bound_b2_infinity}
-	\end{IEEEeqnarray}
-	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$:
-	\begin{equation*}
-	   b_2 \eta_t^{b_2} \geq m_\eta.
-	\end{equation*}
-
-	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing.
-	Therefore,
-	\begin{equation*}
-	u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
-	\label{eq:u_t_bound}
-	\end{equation*}
-	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
-	\begin{equation}
-	\max \left\{ \left\vert u_t^{b_2} \right\vert , \left\vert w_t^{b_2} \right\vert, \left\vert \eta_t^{b_2} \right\vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
-	\label{eq:ut_wt_upper_bound_b2_infty}
-	\end{equation}
-	and such that the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$. \\
-
-	\textbf{Case 1:} When:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{equation*}
-	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
-	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
-	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
-We have:
-	\begin{equation}
-	\begin{split}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\
-		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
-	\end{split}
-	\label{eq:I_1_plus_I_2}
-	\end{equation}
-	with:
-	\begin{IEEEeqnarray*}{rCl}
-	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
-	\right) dt \\
-	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt,
-	\end{IEEEeqnarray*}
-	and:
-	$$
-		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
-	$$
-
-	Fix $\epsilon>0$.
-In the following, we show that $I_1^{b_2} \leq \epsilon$ and $I_2^{b_2} \leq \epsilon$ for large $b_2$.
-First, consider $I_1^{b_2}$.
-Recall that for $t \in[0,T/2]$, we have $\lim_{b_2 \to \infty}h_u(b_2,t) = \lim_{b_2 \to \infty}h_w(b_2,t) = c$, and for all $b_2 \geq b_2^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing, and thus, $[0,T/2] \ni s \mapsto h_u(b_2,t)$ and $[0,T/2] \ni s \mapsto h_w(b_2,t)$ are increasing.
-(Note that $T/2<T$ is chosen arbitrarily, since the above limits do not hold at $T$.) Let
-	$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$
-	Then there exists $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
-	\begin{equation*}
-	\begin{array}{lclclclcl}
-		c - \zeta_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c + \zeta_2, \\
-		c - \zeta_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c + \zeta_2.
-	\end{array}
-	\end{equation*}
-	Thus, for any $t \in [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
-	$$
-		\left\vert h_u(b_2, t) - h_w(b_2,t) \right\vert^2 \leq  4 \zeta_2^2 \quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c - \zeta_2) t \geq \frac{c}{2}\cdot t.
-	$$
-	Therefore,
-	\begin{IEEEeqnarray}{rCl}
-		I_1^{b_2} &\leq& 4\zeta_2^2e^{2T(b_1 + \bar{b}_1)} \cdot\frac{(b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot \frac{c}{2}\cdot t \right) dt \nonumber \\
-		&=& \frac{4e^{2T(b_1 + \bar{b}_1)}}{c} \left( 1 - e^{ - \frac{(b_2 + \bar{b}_2) c}{r + \bar{r}(1-\bar{s})^2}  \frac{T}{2} } \right)\zeta_2^2 \leq \epsilon, 
-	\label{eq:I1_ineq_b2_infinity}
-	\end{IEEEeqnarray}
-	where the last inequality comes from the definition of $\zeta_2$.
-
-	Next, consider $I_2^{b_2}$.
-Since $u_t^{b_2}$ is positive over $[0,T]$, we know from the inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max\{ b_2^{*,upper}, b_2^{*,u,lower} \}$ and all $t \in [T/2,T]$:
-	\begin{equation*}
-		\left\vert u_t^{b_2} - w_t^{b_2} \right\vert \leq \sup_{0 \leq s \leq T} \left\vert u_s^{b_2} \right\vert + \left\vert w_s^{b_2} \right\vert  \leq 2M,
-		\qquad \text{and} \qquad
-		\int_0^{t} h_u(b_2,s) ds \geq \int_0^{\frac{T}{2}} h_u(b_2,s) ds \geq \frac{T}{2} m_u >0.
-	\end{equation*}
-	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
-	\begin{IEEEeqnarray}{rCl}
-		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
-		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
-	\label{eq:I2_b2_infty}
-	\end{IEEEeqnarray}
-	with $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
-
-	Let $b_2^* := \max \{ b_2^{*,I_1}, b_2^{*,I_2}\}$. Then inequalities (\ref{eq:I_1_plus_I_2}), (\ref{eq:I1_ineq_b2_infinity}) and (\ref{eq:I2_b2_infty}) give for $b_2 \geq b_2^*$:
-	\begin{equation*}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} \leq \frac{I_1^{b_2} + I_2^{b_2}}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c/2}=\frac{4\epsilon}{c}.
-	\end{equation*}
-	Since the proof holds for arbitrary $\epsilon>0$, and $c=\sqrt{(q+\bar{q}(1-s)^2)(r+\bar{r}(1-\bar{s})^2)}>0$ is independent of $b_2$ and $\epsilon$, we conclude:
-	\begin{equation*}
-		\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0, 
-	\end{equation*}
-	and thus,
-	$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$\\
-
-	%Todo: 
-	\textbf{Case 2}: When:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}
-	\end{equation*}
-
 \end{proof}

### 2018-08-01 PoA.tex
almost finished with lemma 1

@@
 	and thus,
-	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$
+	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$\\
 
@@
 	Thus,
-	$$1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta=\frac{\frac{1}{b_2} \left[ToDO \right]}{\frac{1}{b_2^2} \left[ToDo \right]}-c_\eta=\frac{ToDo}{ToDo}.$$
+	\begin{equation*}
+	\begin{split}
+	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,
+	\end{split}
+	\end{equation*}
+	$$
+	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-c_\eta \left(\frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2}\right)+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -c_\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right)\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}.
+	$$
+
 	After rearranging terms:
@@
 	\begin{split}
-	\frac{D}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
-	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)} \\
-	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)}.
+	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
+	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
+	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
 	\end{split}
@@
 	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
-	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
-	\begin{equation}
-	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).
+	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
+	\begin{equation}
+	b_2(T-t^*_{b_2})\leq \frac{1}{\frac{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)}{b_2}} \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right).
 	\label{eq:lemma_2}
@@
 	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
-	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
+	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
 	Finally, for $b_2 \geq b_2^{*,l}$, we have:
@@
 	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
-	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
+	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
 	\end{split}

### 2018-08-01 PoA.tex
almost finished with lemma 1
minor edits, condensing lemma 1

--- 2018-08-01 PoA.tex
@@
 \begin{proof}
-	First, we show that for $t\in[0,T)$: (ToDo: This is already stated in Proposition 4.)
+	As noted in the proof of Proposition \ref{prop:b2_to_infty}, for $t\in[0,T)$, we have:
 	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
-	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$:
-	$$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$$
+	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have
+	$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$
 	Clearly there exists $b_2^{*,2}$ such that for $b_2 \geq b_2^{*,2}$:
@@
 	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing.
-Since for any $b_2$, the function $t \mapsto b_2 \eta^{b_2}_t$ is continuous, by the intermediate value theorem we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, there exists a $t^*_{b_2}\in[0,T]$ such that:
-	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$$
-	and:
-	$$b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
-	Thus,
-	$$1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta=\frac{\frac{1}{b_2} \left[ToDO \right]}{\frac{1}{b_2^2} \left[ToDo \right]}-c_\eta=\frac{ToDo}{ToDo}.$$
-	After rearranging terms:
-	\begin{equation}
-	\begin{split}
-	\frac{D}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
-	&= \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta)+ToDo \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)} \\
-	&\leq  \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t)}.
+Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that:
+	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1, \quad \text{and} \quad b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
+	Thus for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, we have:
+	\begin{equation*}
+	\begin{split}
+	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,
+	\end{split}
+	\end{equation*}
+	$$
+	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},
+	$$
+	\begin{equation}
+	\begin{split}
+	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
+	&= \left[-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
+	&\leq  \left[-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
 	\end{split}
@@
 	\end{equation}
-	Since we have: (ToDo: show these limits)
-	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$$
-	there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
-	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}+c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
+	It is easy to derive the following limits:
+	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0.$$
+	Therefore, there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
+	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
 	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
@@
 	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta^{b_2 \to \infty}}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
-	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{\delta^{+,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, $$
-	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2},$$
-	and thus,
-	$$c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$	
+	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, \quad \text{and} \quad c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$
 	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
-	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right).$$
+	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(5c_\eta+2 \right).$$
 	Finally, for $b_2 \geq b_2^{*,l}$, we have:
@@
 	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
-	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} ln \left( c_{\delta_\eta^{b_2 \to \infty}}+5c_\eta+2 \right)=:M.	
+	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M.	
 	\end{split}

### 2018-08-01 PoA.tex
adjusting [] and () lemma 1
minor edits Prop 4 Case 2, numerator not nominator

@@
 	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
-	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
+	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
 	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\textbf{Case 2:} When
+	\textbf{Case 2:} When:
 	\begin{equation*}
@@
 	we have $c_u \neq c_w$.
-In this situation, we will show that the Price of Anarchy tends to a number strictly greater than $1$ as $b_2$ tends to infinity.
-To do so, we will show that in this asymptotic regime, $(b_2 + \bar{b_2}) \Delta SC^{b_2}$ is lower bounded by a strictly positive constant $c_{nom}$, and meanwhile $b_2 \cdot SC^{MKV,b_2}$ is upper bounded by another constant $M_{den}$.
-Both of these constants are independent of $b_2$.\\
+We want to show that $\lim_{b_2 \to \infty}PoA^{b_2}>1$.
+To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$.
 
@@
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,nominator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,nominator}$ and all $s \in [0, T/2]$ we have:
+Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$ we have:
 	\begin{equation*}
@@
 	$$
-	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,nominator}$ we deduce
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$ we deduce
 	\begin{IEEEeqnarray}{rCl}
@@
 		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)} \right) \nonumber \\
-		&\geq & (2 c_{nom} ) \cdot \frac{1}{2} = c_{nom}
-	\label{eq:nominator_ineq_b2_infinity}	
+		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num}
+	\label{eq:numerator_ineq_b2_infinity}	
 	\end{IEEEeqnarray}
-	where $c_{nom} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified by the choice of $b_2 \geq c_3$. \\
+	where $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified by the choice of $b_2 \geq c_3$. \\
 
@@
 
-	Finally, together with inequalities (\ref{eq:nominator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,nominator}, b_2^{*,denumerator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
-	\begin{equation}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) \cdot (b_2 \cdot SC^{MKV,b_2} ) } \geq \frac{c_{nom}}{ 2 M_{den}} > 0.
+	Finally, together with inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denumerator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
+	\begin{equation}
+		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) \cdot (b_2 \cdot SC^{MKV,b_2} ) } \geq \frac{c_{num}}{ 2 M_{den}} > 0.
 	\end{equation}
@@
 	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
-	&= \left[-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
-	&\leq  \left[-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
+	&= \left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
+	&\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
 	\end{split}
@@
 	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
-	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left[-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right] e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
+	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left(-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
 	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$

### 2018-08-01 PoA.tex
minor edits Prop 4 Case 2

@@
 	\end{IEEEeqnarray}
-	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$:
+	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$ and all $t\in[0,T]$:
 	\begin{equation}
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
-	\textbf{Case 1:} When:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{equation*}
-	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
+	\textbf{Case 1:} Assume:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
+	\end{equation*}
+	Then $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
 	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
@@
 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\textbf{Case 2:} When:
-	\begin{equation*}
-	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
-	\end{equation*}
-	we have $c_u \neq c_w$.
+	\textbf{Case 2:} Assume:
+	\begin{equation*}
+	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}.
+	\end{equation*}
+	Then $c_u \neq c_w$.
 We want to show that $\lim_{b_2 \to \infty}PoA^{b_2}>1$.
-To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$.
-
-	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$.
-As what have been discussed previously, we know that  $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
-Moreover, from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), we have the uniform lower bounds $m_u$ and $m_\eta$ for $u_t^{b_2}$ and $\eta_t^{b_2}$.
-Also, for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$, we have $\eta_t^{b_2} \leq M$\\
-
-	Step 1: we derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
+To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}<\infty$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$.
+
+	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1.
+Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
+Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u$, $b_2 \eta_t^{b_2} \geq m_\eta$, and $\eta_t^{b_2} \leq M$, for all $t\in[0,T]$.\\
+
+	Step 1: We derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
 It has been shown that for every $0 \leq t <T$,  $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
@@
 
-	Now, from inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), and the fact that $M_{J_1}$ and $M_{J_2}$ are independent of $b_2$, equation (\ref{eq:J1_plus_J2_b2_infinity}) gives raise to an upper bound: for all $b_2 \geq b_2^{*,denumerator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
+	Now, from inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), and the fact that $M_{J_1}$ and $M_{J_2}$ are independent of $b_2$, equation (\ref{eq:J1_plus_J2_b2_infinity}) gives raise to an upper bound: for all $b_2 \geq b_2^{*,denominator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
 	\begin{equation} 
@@
 
-	Finally, together with inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denumerator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
+	Finally, together with inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denominator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, we can draw the conclusion that in case when $\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} \neq \frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2}$, we have 
+	Therefore, we conclude: 
 	$$ \lim_{b_2 \to \infty} PoA^{b_2} > 1.$$ 
@@
 
-The following lemma has been used in Proposition \ref{prop:b2_to_infty}.
+The following lemma was used in Proposition \ref{prop:b2_to_infty}.
 \begin{lemma}
-	There exists a $b_2^{*,l}>0$ and $M>0$, such that for all $b_2 \geq b_2^{*,l}$:
-	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M.$$
+	There exists a $b_2^{*,l}>0$ and $M^l>0$, such that for all $b_2 \geq b_2^{*,l}$:
+	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M^l.$$
 	\label{lemma:int_b2_eta_t}
@@
 	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, \quad \text{and} \quad c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$
-	Returning to equation (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
+	Returning to inequality (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
 	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(5c_\eta+2 \right).$$
@@
 	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
-	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M.	
+	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.	
 	\end{split}

### 2018-08-01 PoA.tex
removed Var assumption Prop 7, reordered cases in prop 7

@@
 \begin{proposition}\label{prop:b1_b1bar}
-	Assuming Assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
+	Assuming Assumption \ref{assumption}, then:
+	\begin{equation*}
+	\lim_{b_1 \to \infty} PoA = 1 \qquad \text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
+	\end{equation*}	
+	Furthermore, if:
 	\begin{equation*}
@@
 	\begin{equation*}
-	\begin{split}
-	    \lim_{b_1 \to 0} PoA > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1,\\
-	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
-	\end{split}
+	    \lim_{b_1 \to 0} PoA > 1\qquad \text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1.
 	\end{equation*}
@@
 \begin{proof}
-	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$.
-We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
-Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
-Next, we show that the three sequences are uniformly bounded.
-Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
-There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$.
-Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
-	\begin{equation*}
-		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
-		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
-	\end{equation*}
-	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
-From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
-
-	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
-	\begin{equation*}
-	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
-	\end{equation*}
-	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1 \leq b_1^*$ and $t \in [0,T]$, i.e. 
-	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1 \leq b_1^*. $$
-
-	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$.
-By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
-    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.\\
-
-	\textbf{Case 3:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have:
+	\textbf{Case 1:} Consider $b_1 \to \infty$. Since $\lim_{b_1 \to \infty} A^{u,b_1} = \lim_{b_1 \to \infty} A^{w,b_1} = - \infty$ we have:
 	$$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty.$$
@@
 
-	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
+	\textbf{Case 2:} Now, consider $\bar{b}_1 \to \infty$.
 	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
@@
 	\end{equation*}
-	We conclude
-	$
-	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
-	$
-
+	We conclude $\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.$\\
+
+	\textbf{Cases 3 and 4:} First, we consider $b_1 \to 0$.
+We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
+Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
+Next, we show that the three sequences are uniformly bounded.
+Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
+There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$.
+Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
+	\begin{equation*}
+	\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
+	\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
+	\end{equation*}
+	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$.
+From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.
+
+	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
+	\begin{equation*}
+	\lim_{b_1\to 0}\bar{x}_t^{MFG,b_1} = \mathbb{E}(\xi) e^{\int_0^t(\bar{b}_1-B u^{b_1\to 0}_s)ds} =: \bar{x}_t^{MFG,b_1\to 0}\neq 0.
+	\end{equation*}
+	Moreover, $\bar{x}_t^{MFG,b_1}$ is uniformly bounded over $b_1 \leq b_1^*$ and $t \in [0,T]$, i.e. 
+	$$ \left\vert \bar{x}^{MFG,b_1}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ \bar{b}_1 T }, \quad \forall t \in [0,T],\ b_1 \leq b_1^*. $$
+
+	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$.
+By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
+	Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.
 \end{proof}

### 2018-08-01 PoA.tex
minor edits prop 4 case 2 Step 1

@@
 	Step 1: We derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
-It has been shown that for every $0 \leq t <T$,  $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
+We have shown that every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$ we have:
+Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$, we have:
 	\begin{equation*}
@@
 	\end{equation*}
-	which implies that for all $t \in [0,T/2]$
-	$$ \left\vert h_u(b_2, t) - h_w(b_2,t)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t.
+	which implies that for all $t \in [0,T/2]$:
+	$$ \left\vert h_u(b_2, t) - h_w(b_2,t)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) t.
 	$$
-	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$ we deduce
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$, we deduce:
 	\begin{IEEEeqnarray}{rCl}
-		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B \int_0^{\frac{T}{2}} (u_t - w_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
-		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \cdot \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t \right) dt \nonumber \\
-		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)} \right) \nonumber \\
-		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num}
+		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B^{b_2} \int_0^{\frac{T}{2}} (u^{b_2}_t - w^{b_2}_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
+		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left[- \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) t \right] dt \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \vert c_u - c_w \vert/4 )}{r+\bar{r}(1-\bar{s})^2}(b_2 + \bar{b}_2)} \right) \nonumber \\
+		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num},
 	\label{eq:numerator_ineq_b2_infinity}	
 	\end{IEEEeqnarray}
-	where $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified by the choice of $b_2 \geq c_3$. \\
+	with $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified because $b_2 \geq c_3$. \\
 
@@
 The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
-Since we consider $\xi \equiv 1$ and the result still holds, we see that $Var(\xi)>0$ is not a necessary assumption.
 Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}.

### 2018-08-01 PoA.tex
minor edits prop 4 case 2 Step 2

@@
 
-	Step 1: We derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
+	Step 1: We derive a lower bound for $(b_2+\bar{b}_2)\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
 We have shown that every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
@@
 
-	Step 2: We would like to provide an upper bound for $b_2\cdot SC^{MKV,b_2}$. From formula (\ref{eq:SC_MKV_2}), we have 
-	\begin{equation}
-	b_2 \cdot SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + b_2 w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{:= $J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{:= $J_2$}}
+	Step 2: We derive an upper bound for $b_2 SC^{MKV,b_2}$. From equation (\ref{eq:SC_MKV_2}), we have: 
+	\begin{equation}
+	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J_2$}}
 	\label{eq:J1_plus_J2_b2_infinity}
@@
 	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
-	Let $\kappa_5 = \frac{2 m_{\eta}}{r + \bar{r}}$ and $\displaystyle l(t) = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta_u du} ds$.
+	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}$ and $\displaystyle l(t) = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta_u du} ds$.
 Because for all $b_2 \geq b_2^{*,basic}$ we have $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, then

### 2018-08-01 PoA.tex
minor edits prop 4 case 2 Step 2

@@
 Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
-Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u$, $b_2 \eta_t^{b_2} \geq m_\eta$, and $\eta_t^{b_2} \leq M$, for all $t\in[0,T]$.\\
+Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.\\
 
@@
 	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
-	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}$ and $\displaystyle l(t) = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta_u du} ds$.
-Because for all $b_2 \geq b_2^{*,basic}$ we have $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, then
-	\begin{equation}
-		b_2 \cdot l(t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
+	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
+Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, we have:
+	\begin{equation}
+		b_2 \cdot l(b_2,t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa_5 b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
 	\label{eq:l(t)_upper_bound_b2_infinity}

### 2018-08-01 PoA.tex
add theorem 2 equivalent conditions for PoA =1

--- 2018-08-01 PoA.tex
@@
 \end{equation}
-Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.\\
+Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.
+
+\begin{theorem}
+	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ satisfies that $\mathbb{E}(\xi)  \neq 0$, then 
+	\begin{itemize}
+		\item when $\bar{b}_1 > 0$, we have $PoA = 1$ if and only if
+		\begin{equation}
+		D^u = D^w =:D \quad \text{and} \quad B D^2 + 2 A^{u} D - C^{u} = B D^2 + 2 A^{w} D - C^w  = 0,
+		\label{eq:PoA=1_condition_b1_bar>0}
+		\end{equation}
+		\item when $\bar{b}_1 = 0$, then $A^u = A^w$ and we have $PoA = 1$ if and only if 
+		\begin{equation}
+			D^u = D^w \quad \text{and} \quad C^u = C^w, 
+		\label{eq:PoA=1_condition_b1_bar=0}
+		\end{equation}
+	\end{itemize}
+	Namely, $PoA = 1$ if and only if the following two or three conditions hold true:
+	\begin{equation*}
+	\left\{
+	\begin{array}{rcl}
+	\displaystyle \lambda \cdot (q_T + \bar{q}_T(1-s_T) )  &=& q_T + \bar{q}_T (1- s_T)^2\\
+	\displaystyle \lambda \cdot (q+ \bar{q}(1-s)) &=& (q + \bar{q}(1-s)^2) + \bar{b}_1 \cdot (q_T + \bar{q}_T (1 - s_T)^2) 
+	\end{array}
+	\right.
+	\end{equation*}
+	where $\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}$, and in the case when $\bar{b}_1 > 0$, the third condition becomes
+	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  + ( q + \bar{q}(1-s)^2 ) = 0. $$
+
+	\label{thm:PoA_equivalent_1}
+\end{theorem}
+
+\begin{proof}
+	Under assumption (\ref{eq:assumptions}), we know from equation (\ref{eq:riccati_wt}) and from the explicit formula (\ref{eq:riccati_ut_sol}) for solution to scalar Riccati equation that $w_0$ is strictly positive.
+Thus, with the assumption $\mathbb{E}(\xi) \neq 0$, we have $SC^{MKV} > 0$.
+Hence, $PoA =1$ if and only if $\Delta SC = 0$.
+Since $\bar{x}_t^{MFG} \neq 0$ for all $t \in [0,T]$, from proposition \ref{prop:diff_SC} and the continuity of $u_t$ and $w_t$, we derive that
+	\begin{equation}
+		PoA = 1 \qquad iff \qquad u_t = w_t, \quad \forall  t \in [0,T].
+	\label{eq:PoA_equivalence_ut=w_t} 
+	\end{equation}
+
+	From equation (\ref{eq:riccati_ut_sol_deriv}) and the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$.
+Thus, $PoA = 1$.
+
+	Suppose now that $PoA =1$.
+Then by taking $t=T$ in equation (\ref{eq:PoA_equivalence_ut=w_t}), we obtain the first condition in both (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}):
+	$$D^u = u_T = w_T = D^w.$$
+	Moreover, if we make the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by taking $u_t = w_t$ for all $t in [0,T]$ into account, we obtain:
+	\begin{equation}
+		2 (A^u - A^w) w_t = C^u - C^w, \quad \forall \  t \in [0,T]
+	\label{eq:wt=constant}
+	\end{equation}
+	Since $2(A^u - A^w) = \bar{b}_1$, so that in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$.
+Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, which are constants for all $t \in [0,T]$.
+Thus, the derivatives with respect to time $t$ for $u_t$ and $w_t$ should be zero.
+From equation (\ref{eq:riccati_ut_sol_deriv}), and the fact that $\delta_u^+ - \delta_u^- > 0$, we deduce:
+	$$ B (D^{u})^2 + 2 A^u D^u - C^u = 0.$$
+	Similarly we also have $B (D^{w})^2 + 2 A^w D^w - C^w = 0$.
+
+	By replacing $(A^u,B, C^u, D^u)$ and $(A^w, B, C^w, D^w)$ with their explicit expressions, we obtain henceforth an equivalent condition for $PoA = 1$ in term of the coefficients of Linear Quadratic model.
+
+\end{proof}
 
@@
 	Step 1: We derive a lower bound for $\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
-We have shown that every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
+It has been shown that for every $0 \leq t <T$,  $h_u(b_2, t) \xrightarrow[b_2 \to \infty]{} c_u$ and $h_w(b_2, t) \xrightarrow[b_2 \to \infty]{} c_w$.
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$, we have:
+Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$ we have:
 	\begin{equation*}
@@
 	\end{equation*}
-	which implies that for all $t \in [0,T/2]$:
-	$$ \left\vert h_u(b_2, t) - h_w(b_2,t)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) t.
+	which implies that for all $t \in [0,T/2]$
+	$$ \left\vert h_u(b_2, t) - h_w(b_2,t)\right\vert \geq \frac{1}{2} \left\vert c_u - c_w \right\vert, \qquad \int_0^t h_u(b_2, s) ds \leq \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t.
 	$$
-	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$, we deduce:
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$ we deduce
 	\begin{IEEEeqnarray}{rCl}
-		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B^{b_2} \int_0^{\frac{T}{2}} (u^{b_2}_t - w^{b_2}_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
-		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left[- \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) t \right] dt \nonumber \\
-		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \vert c_u - c_w \vert/4 )}{r+\bar{r}(1-\bar{s})^2}(b_2 + \bar{b}_2)} \right) \nonumber \\
-		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num},
+		(b_2 + \bar{b}_2) \Delta SC ^{b_2} &\geq & \frac{b_2 + \bar{b}_2}{2} B \int_0^{\frac{T}{2}} (u_t - w_t)^2 (\bar{x}^{MFG, b_2})^2 dt \nonumber \\
+		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \cdot \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) \cdot t \right) dt \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \frac{1}{4} \vert c_u - c_w \vert )}{r+\bar{r}(1-\bar{s})^2}\cdot (b_2 + \bar{b}_2)} \right) \nonumber \\
+		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num}
 	\label{eq:numerator_ineq_b2_infinity}	
 	\end{IEEEeqnarray}
-	with $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified because $b_2 \geq c_3$. \\
+	where $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified by the choice of $b_2 \geq c_3$. \\
 

### 2018-08-02 PoA.tex
finished editing prop 4 case 2

--- 2018-08-01 PoA.tex
@@
 	\begin{equation}
-	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J_2$}}
+	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J^{b_2}_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J^{b_2}_2$}}
 	\label{eq:J1_plus_J2_b2_infinity}
 	\end{equation}	
-	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
-	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
+	We also notice the following two technical results which are useful for deriving upper bounds for $J^{b_2}_1$ and $J^{b_2}_2$.
+First, let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
 Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, we have:
@@
 	\end{equation}
-	Besides, with Riccati equation (\ref{eq:riccati_etat}) of $\eta_t^{b_2}$ and the formula of integration by parts, we deduce:
+	Next, using equation (\ref{eq:riccati_etat}), integration by parts, and since $-A^\eta,\eta^{b_2}_t,C^\eta,l(b_2,t)\geq 0$ we deduce:
 	\begin{IEEEeqnarray*}{rCL}
-		 \int_0^T B^{\eta, b_2} (\eta_t^{b_2} )^2 \cdot l(t) dt 
-		&= & \int_0^T  (\eta_t^{b_2})' \cdot l(t) dt + \int_0^T \left( -2A^{\eta} \eta_t^{b_2} + C^{\eta} \right) \cdot l(t) dt \nonumber \\
-		&\geq & \left[ \eta_T^{b_2} l(T) - \eta_0^{b_2} l(0) - \int_0^T \eta_t^{b_2} \cdot (l(t))' dt \right]  \nonumber \\
-		&= & - \int_0^T \eta_t^{b_2} \cdot \left[ l(t)\cdot( - 2 B^{\eta,b_2} \eta_t^{b_2} ) + 1 \right] dt + l(T) D^{\eta} \nonumber \\
-		&\geq& 2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot l(t) dt - \int_0^T \eta_t^{b_2} dt.
+		 \int_0^T B^{\eta, b_2} (\eta_t^{b_2} )^2 \cdot l(b_2,t) dt 
+		&= & \int_0^T  (\eta_t^{b_2})' \cdot l(b_2,t) dt + \int_0^T \left( -2A^{\eta} \eta_t^{b_2} + C^{\eta} \right) \cdot l(b_2,t) dt \nonumber \\
+		&\geq & \left[ \eta_T^{b_2} l(b_2,T) - \eta_0^{b_2} l(b_2,0) - \int_0^T \eta_t^{b_2} \cdot \frac{\partial(l(b_2,t))}{\partial t} dt \right]  \nonumber \\
+		&= & - \int_0^T \eta_t^{b_2} \cdot \left[ l(b_2,t)\cdot( - 2 B^{\eta,b_2} \eta_t^{b_2} ) + 1 \right] dt + l(b_2,T) D^{\eta} \nonumber \\
+		&\geq& 2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot l(b_2,t) dt - \int_0^T \eta_t^{b_2} dt.
 	\end{IEEEeqnarray*}
-	where the inequalities are justified by the fact that $-A^{\eta}$, $C^{\eta}$, $D^{\eta} $, $t \mapsto \eta_t^{b_2}$ and $t \mapsto l(t)$ are all positive.	By rearranging the terms we obtain:
-	\begin{equation}
-		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
+	After rearranging terms, we obtain:
+	\begin{equation}
+		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta^{b_2}_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
 	\label{eq:l(t)_transformation_b2_infinity}
@@
 
-	Let's look at $J_1$ first.
-	From the expression of $v_t$ (equation (\ref{eq:v_t_new_notation})) and inequality (\ref{eq:l(t)_upper_bound_b2_infinity}), we have that for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$:
+	First, consider $J^{b_2}_1$. From equation (\ref{eq:v_t_new_notation}) and inequality (\ref{eq:l(t)_upper_bound_b2_infinity}), we have that for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$:
 	\begin{IEEEeqnarray*}{rCl}
@@
 	Hence, if we choose $b^{*,J_1} \geq b^{*,basic}$ such that
-	for all $b_2 \geq b_2^{*,J_1}$ we have 
-	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad and \quad b_2 \cdot e^{- \kappa_5 b_2 \cdot T} \leq \frac{1}{\kappa_5} $$
-	we can derive an upper bound for $J_1$. Namely, for all $b_2 \geq b_2^{*,J_1}$:
+	for all $b_2 \geq b_2^{*,J_1}$:
+	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad \text{and} \quad b_2 e^{- \kappa_5 b_2 T} \leq \frac{1}{\kappa_5}, $$
+	then we can derive an upper bound for $J^{b_2}_1$. Namely, for all $b_2 \geq b_2^{*,J_1}$:
 	\begin{IEEEeqnarray}{rCl}
-		J_1 &\leq& \frac{q+\bar{q}}{2}  \cdot e^{2b_1 T} \int_0^T \left( Var(\xi) \cdot b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right) dt  \nonumber \\
-		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 T \cdot b_2 } + \frac{\sigma^2}{\kappa_5} \right) + \frac{b_2}{b_2 + \bar{b}_2} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
+		J^{b_2}_1 &\leq& \frac{q+\bar{q}}{2}  \cdot e^{2b_1 T} \int_0^T \left( Var(\xi) b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right) dt  \nonumber \\
+		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 T \cdot b_2 } + \frac{\sigma^2}{\kappa_5} \right) + \frac{b_2}{2(b_2 + \bar{b}_2)} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
 		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_5}  + \frac{\sigma^2 T}{\kappa_5} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_5} + \frac{\sigma^2}{\kappa_5} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{2} \nonumber \\
-		& =:& M_{J_1}
+		& =:& M_{J_1}.
 	\label{eq:J1_upper_bound_b2_infinity}
@@
 
-	As for the term $J_2$, we can expand it like the following:
+	Next, consider the quantity $J^{b_2}_2$:
 	\begin{IEEEeqnarray*}{rCl}
-		J_2 &=& \frac{1}{2 (r + \bar{r}) }\int_0^T \left(b_2 \eta_t^{b_2} \right)^2 \cdot Var(\xi) e^{2b_1 t} \cdot b_2 \exp \left( - 2 B^{\eta,b_2} \int_0^t \eta_s ds \right) dt \nonumber \\
-		&& \hspace{10em}  + \frac{\sigma^2}{2} \cdot  b_2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot \left( \int_0^t e^{2b_1(t-s) - 2B^{\eta,b_2} \int_s^t \eta_u^{b_2} du} ds \right)  dt .
+		J^{b_2}_2 &=& \frac{1}{2 (r + \bar{r}) }\int_0^T \left(b_2 \eta_t^{b_2} \right)^2 Var(\xi) e^{2b_1 t} \cdot b_2 \exp \left( - 2 B^{\eta,b_2} \int_0^t \eta_s ds \right) dt \nonumber \\
+		&& \hspace{10em}  + \frac{\sigma^2}{2} \cdot  b_2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \left( \int_0^t e^{2b_1(t-s) - 2B^{\eta,b_2} \int_s^t \eta_u^{b_2} du} ds \right)  dt .
 	\end{IEEEeqnarray*}
-	The first integration on the right-hand side of the above equation can be treated using similar techniques in Case 1.
-Whilst, for the second integration, we will use a result which says that there exists $b^{*,integral}>0$ and a constant $M_{intgl}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*, integral}$ we have:
-	\begin{equation}
-	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{intgl}
+	The first integration on the right-hand side of the above equation can be treated using similar techniques as in Case 1.
+For the second integration, we will use Lemma \ref{lemma:int_b2_eta_t}, which appears below.
+From Lemma \ref{lemma:int_b2_eta_t}, there exists $b^{*,integral}>0$ and a constant $M_{intgl}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*, integral}$ we have:
+	\begin{equation}
+	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{intgl}.
 	\label{eq:intgeral_b2_eta_t_bound_b2_infinity}
 	\end{equation}
-	In order to keep the flow of idea fluent, we defer temporarily the proof of the above claim into Lemma \ref{lemma:int_b2_eta_t}.
-
-	Since $b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} c_\eta$ for all $t \in [0, T/2]$, we can choose $b_2^{*,J_2} \geq \max\{ b_2^{*,integral}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$ we have
-	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0, \frac{T}{2}]  \qquad and \quad b_2^{3} \cdot e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
-	Thus, together with inequalities (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}) and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), let $\kappa_6 = \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$ we deduce that
+
+	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,integral}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
+	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
+	Thus, together with inequalities (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}) and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
 	\begin{IEEEeqnarray}{rCl}
-		J_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta_t \right)^2 \cdot b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 \cdot b_2^3 \cdot e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
+		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
 		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{intgl} \nonumber \\
-		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{intgl}}{2} =: M_{J_2}
+		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{intgl}}{2} =: M_{J_2}.
 	\label{eq:J2_upper_bound_b2_infinity}
@@
 
-	Now, from inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), and the fact that $M_{J_1}$ and $M_{J_2}$ are independent of $b_2$, equation (\ref{eq:J1_plus_J2_b2_infinity}) gives raise to an upper bound: for all $b_2 \geq b_2^{*,denominator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
-	\begin{equation} 
-		b_2 \cdot SC^{MKV, b_2}  = J_1 + J_2 \leq M_{J_1} + M_{J_2} =: M_{den}
+	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,denominator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
+	\begin{equation} 
+		b_2 SC^{MKV, b_2}  = J^{b_2}_1 + J^{b_2}_2 \leq M_{J_1} + M_{J_2} =: M_{den}.
 	\label{eq:demumerator_ineq_b2_infinity}
@@
 
-	Finally, together with inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}), let $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denominator} \}$ so that we have for all $b_2 \geq b_2^{*,case 2}$ the inequalities $ b_2 + \bar{b}_2 \leq 2 b_2$ and
-	\begin{equation}
-		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) \cdot (b_2 \cdot SC^{MKV,b_2} ) } \geq \frac{c_{num}}{ 2 M_{den}} > 0.
+	Finally, putting together inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}) and for $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denominator} \}$, we have for all $b_2 \geq b_2^{*,case 2}$:
+	\begin{equation}
+		\frac{b_2+\bar{b}_2}{b_2} \leq 2, \quad \text{and thus,} \quad \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) (b_2 SC^{MKV,b_2} ) } \geq \frac{c_{num}}{ 2 M_{den}} > 0.
 	\end{equation}

### 2018-08-02 PoA.tex

@@
 	where $\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}$, and in the case when $\bar{b}_1 > 0$, the third condition becomes
-	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  + ( q + \bar{q}(1-s)^2 ) = 0. $$
+	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  - ( q + \bar{q}(1-s)^2 ) = 0. $$
 
@@
 	$$D^u = u_T = w_T = D^w.$$
-	Moreover, if we make the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by taking $u_t = w_t$ for all $t in [0,T]$ into account, we obtain:
+	Moreover, if we make the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by taking $u_t = w_t$ for all $t \in [0,T]$ into account, we obtain:
 	\begin{equation}
@@
 	Step 1: We derive a lower bound for $(b_2+\bar{b}_2)\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
-We have shown that every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
+We have shown that for every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
@@
 	\end{IEEEeqnarray}
-	with $c_{num} =  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified because $b_2 \geq c_3$. \\
+	with $c_{num} :=  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified because $b_2 \geq c_3$. \\
 

### 2018-08-02 PoA.tex
minor change in Theorem 2

@@
 
-	From equation (\ref{eq:riccati_ut_sol_deriv}) and the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$.
+	From equation (\ref{eq:riccati_ut_sol_deriv}) and the uniqueness of solutions to Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$.
 Thus, $PoA = 1$.

### 2018-08-02 PoA.tex
minor change in Theorem 2 statement

@@
 	\end{equation*}
-	where $\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}$, and in the case when $\bar{b}_1 > 0$, the third condition becomes
+	where $\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}$, and in the case when $\bar{b}_1 > 0$, there is an additional condition:
 	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  - ( q + \bar{q}(1-s)^2 ) = 0. $$

### 2018-08-02 PoA.tex
stylistic edit for section 2.1

@@
 and whenever the flows $\bmubar=(\bar{\mu}_t)_{0\leq t\leq T}$ and $\bnubar=(\bar{\nu}_t)_{0\leq t\leq T}$ are fixed, we consider for each control process $\balpha=(\alpha_t)_{0\leq t\leq T}$ the adjoint equation:
-
-\begin{equation*}
-\begin{split}
-    dY_t&=- \partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)dt+Z_tdW_t \\
-    Y_T&=\partial_xg(X_T, \cL(X_T)).
-\end{split}
+\begin{equation*}
+    dY_t=- \partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)dt+Z_tdW_t,
+    \qquad
+    Y_T=\partial_xg(X_T, \cL(X_T)).
 \end{equation*}
 According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. We introduce the function:
-\begin{equation*}
+\begin{equation}
     \hat{\alpha}(t,x,\bar{\mu},\bar{\nu},y)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)y}{r(t)+\bar{r}(t)},
-\end{equation*}
+\label{eq:MFG_opt_alpha_Pontryagin}
+\end{equation}
 and use the control $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$.
@@
 \begin{equation*}
-    \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t),
-\end{equation*}
-with:
-\begin{equation*}
+    \bar{\nu}_t = \mathbb{E}(\hat{\alpha}_t)=c^{MFG}(t)\mathbb{E}(Y_t),
+	\qquad 
+	\text{with} 
+	\quad
     c^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))}.
 \end{equation*}
-Thus, necessarily we must have:
-\begin{equation*}
+Thus, from equation (\ref{eq:MFG_opt_alpha_Pontryagin}) we must have:
+\begin{equation}
     \hat{\alpha}_t=a^{MFG}(t) Y_t+b^{MFG}(t)\mathbb{E}(Y_t),
-\end{equation*}
-with:
-\begin{equation*}
-    a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)},
-\end{equation*}
-and:
-\begin{equation*}
+\label{eq:MFG_opt_alpha_Y_expY}
+\end{equation}
+where
+\begin{equation*}
+	a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)}
+	\qquad
+	\text{and}
+	\qquad
 	b^{MFG}(t)=-\frac{\bar{r}(t)\bar{s}(t)b_2(t)}{(r(t)+\bar{r}(t))(r(t)+\bar{r}(t)(1-\bar{s}(t)))}.
@@
 \begin{equation}
-\begin{split}
-        dX_t&=\left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\
-        dY_t&=-\left[(q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right]dt +Z_t dW_t,
-\end{split}
+\left\{
+\begin{array}{lcl}
+      \displaystyle  dX_t&=& \left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MFG}(t)b_2(t)Y_t+(b^{MFG}(t)b_2(t)+c^{MFG}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\[5pt]
+        dY_t&=& -\left[(q(t)+\bar{q}(t))X_t-\bar{q}(t)s(t)\mathbb{E}X_t+b_1(t)Y_t \right]dt +Z_t dW_t,
+\end{array}
+\right.
 \label{eq:FBSDE_EMFG}
@@
 See Appendix \ref{appendix_solving_fbsdes}).
-Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that $Y_t=\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MFG}\bar{x}_t^{MFG}$, $\mathbb{E}(X_t)=\bar{x}_t^{MFG}$, and $Var(X_t)=v^{MFG}_t$ provide a solution to the LQEMFG problem.
-Then from the appendix, we have:
-\begin{equation}
-\begin{split}
-\dot{\bar{\eta}}^{MFG}_t+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MFG}_t)^2+(2b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t))&=0,\\
-\bar{\eta}^{MFG}_T-(q_T+\bar{q}_T(1-s_T))&=0,
-\end{split}
+Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that
+\begin{align*}
+Y_t =\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}, \quad &\mathbb{E}(Y_t) =\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},\\
+\mathbb{E}(X_t) =\bar{x}_t^{MFG}, \quad &Var(X_t)=v^{MFG}_t
+\end{align*}
+provide a solution to the LQEMFG problem. Then from the appendix, we have 
+\begin{itemize}
+	\item a scalar Riccati equation for $\bar{\eta}_t^{MFG}$:
+	\begin{equation}
+	\dot{\bar{\eta}}^{MFG}_t+ \left[ c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MFG}_t)^2+ \left(2b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t)) =0
 	\label{eq:eta_bar_MFG}
 	\end{equation}
-\begin{equation}
-\begin{split}
-\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)(\eta^{MFG}_t)^2+2b_1(t)\eta^{MFG}_t+q(t)+\bar{q}(t)&=0, \\
-\eta^{MFG}_T-(q_T+\bar{q}_T)&=0,
-\end{split}
-\end{equation}
-\begin{equation}
-\begin{split}
-\dot{\bar{x}}^{MFG}_t&=\left[b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MFG}_t\right]\bar{x}^{MFG}_t, \\
-\bar{x}^{MFG}_0&=\mathbb{E}(\xi),
-\end{split}
+	with terminal condition $\bar{\eta}^{MFG}_T = q_T+\bar{q}_T(1-s_T)$; 
+	\item a first order equation for $\bar{x}_t^{MFG}$:
+	\begin{equation}
+	\dot{\bar{x}}^{MFG}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MFG}_t \right] \cdot \bar{x}^{MFG}_t
 	\label{eq:x_bar_MFG}
 	\end{equation}
-where the dot is the standard ODE notation for a derivative. And thus,
-\begin{equation}
-\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t\left[b_1(u)+\bar{b}_1(u)+c^{MFG}(u)(b_2(u)+\bar{b}_2(u))\bar{\eta}^{MFG}_u\right]du},
-\label{eq:x_bar_MFG_explicit}
-\end{equation}
-\begin{equation}
-v^{MFG}_t=Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MFG}(s)b_2(s)\eta^{MFG}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u\right] du}ds.
+	with initial condition $\bar{x}^{MFG}_0=\mathbb{E}(\xi)$;
+	\item a scalar Riccati equation for $\eta_t^{MFG}$:
+	\begin{equation}
+	\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)\cdot (\eta^{MFG}_t)^2 + 2b_1(t) \cdot \eta^{MFG}_t+q(t)+\bar{q}(t)=0
+	\end{equation}
+	with terminal condition $\eta^{MFG}_T = q_T+\bar{q}_T$,
+\end{itemize}
+where the dot is the standard ODE notation for a derivative. 
+And thus, we obtain explicit solutions for $\bar{x}_t^{MFG}$ and $v_t^{MFG}$:
+\begin{IEEEeqnarray}{rCl}
+	\bar{x}^{MFG}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MFG}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MFG}_s\right) ds} \label{eq:x_bar_MFG_explicit} \\ 
+	v^{MFG}_t &=& Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MFG}(s)b_2(s) \cdot \eta^{MFG}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u\right] du}ds.
 	\label{eq:v_t}
-\end{equation}
-Let $SC^{MFG}:=SC(\phi)$ for the feedback function specified by this solution, i.e.
+\end{IEEEeqnarray}
+Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have
 \begin{equation*}
@@
 \begin{equation*}
-    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},
-\end{equation*}
-and:
-\begin{equation*}
-    Var(\phi(t,X_t))=(a^{MFG}(t)\eta_t^{MFG})^2v^{MFG}_t.
+    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\cdot \bar{\eta}_t^{MFG}\bar{x}_t^{MFG}
+	\qquad 
+	\text{and}
+	\qquad
+    Var(\phi(t,X_t))=\left(a^{MFG}(t)\eta_t^{MFG} \right)^2 \cdot v^{MFG}_t.
 \end{equation*}
@@
 \begin{equation*}
-\begin{split}
-    dY_t&=-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\
-    Y_T&=\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
-\end{split}
-\end{equation*}
-and $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
+\left\{
+\begin{array}{lcl}
+    dY_t&=&-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\[8pt]
+    Y_T&=&\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
+\end{array}
+\right.
+\end{equation*}
+where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
 In the present LQ case, the sufficient condition can be used to solve for:

### 2018-08-02 PoA.tex
stylistic edit for section 2.1
rearranging the position of Theorem 2, make it before the new notation of xt_bar and vt_bar

@@
 \end{equation*}
-According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$. We introduce the function:
+According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$.
+By solving this equation, we introduce the function:
 \begin{equation}
@@
 \end{equation}
-and use the control $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$.
+and pick an optimal control as $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$.
 When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$.
@@
 \end{equation}
-where
+with
 \begin{equation*}
@@
 
-We study in the following the variation of $PoA$ by letting one of the coefficients tend to zero or to infinity.
 It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
-    \begin{equation}
-		\dot{u}_t - 2A^u u_t - B u_t^2 + C^u =0, \qquad u_T = D^u,
-		\label{eq:riccati_ut}
-	\end{equation}	
-	\begin{equation}
-	    \dot{w}_t - 2A^w w_t - B w_t^2 + C^w =0, \qquad w_T = D^w,
-	\label{eq:riccati_wt}
-	\end{equation}
-	\begin{equation}
-	    \dot{\eta}_t - 2A^\eta \eta_t - B^\eta \eta_t^2 + C^\eta =0, \qquad \eta_T = D^\eta,
+    \begin{IEEEeqnarray}{lLLLClClCl}
+		\dot{u}_t &- 2A^u u_t &- B u_t^2 &+ C^u &= & 0, &\qquad& u_T &=& D^u,
+		\label{eq:riccati_ut} \\
+	    \dot{w}_t &- 2A^w w_t &- B w_t^2 &+ C^w &=&0, &\qquad &w_T &= & D^w,
+		\label{eq:riccati_wt}\\
+	    \dot{\eta}_t &- 2A^\eta \eta_t &- B^\eta \eta_t^2 &+ C^\eta &= & 0, &\qquad& \eta_T &= &D^\eta,
 	\label{eq:riccati_etat}
-	\end{equation}
+	\end{IEEEeqnarray}
 	with:
@@
 
-To make the following computations easier to follow, we repeat equations (\ref{eq:PoA_LQ}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations:
-\begin{equation}
-PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle B\int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
-\label{eq:PoA_LQ_new_notation}
-\end{equation}
-\begin{equation}
-\bar{x}^{MFG}_t=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds},
-\label{eq:x_bar_MFG_explicit_new_notation}
-\end{equation}
-\begin{equation}
-v_t=Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds.
-\label{eq:v_t_new_notation}
-\end{equation}
-Also for convenience, recall the definition from equation (\ref{eq:lambda}):
-\begin{equation*}
-\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}.
-\end{equation*}
-
 It will also be useful to compute the derivative of $u_t$ with respect to time $t$ from the explicit form in equation (\ref{eq:riccati_ut_sol}):
@@
 
-In the following propositions, we utilize the following assumption.	
+We study in the following the variation of $PoA$ by letting only one of the coefficients tend to zero or to infinity.
+In order to make the following computations easier to follow, we repeat equations (\ref{eq:PoA_LQ}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations:
+\begin{IEEEeqnarray}{l}
+	PoA = 1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle B\int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
+\label{eq:PoA_LQ_new_notation} \\[3pt]
+	\displaystyle \bar{x}^{MFG}_t =\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds},
+\label{eq:x_bar_MFG_explicit_new_notation} \\[3pt]	
+	v_t = Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds.
+\label{eq:v_t_new_notation}
+\end{IEEEeqnarray}
+Also for convenience, recall the definition from equation (\ref{eq:lambda}):
+$
+\displaystyle
+\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}.
+$
+
+\noindent In the following propositions, we utilize the following assumption to make their proofs simpler.	
 \begin{assumption}\label{assumption}

### 2018-08-02 PoA.tex
minor edits, put equations for Delta SC and SC^MKV in new notation so that we dont need to refer to the earlier equations; I will add more references to these new equations later

@@
 \end{equation*}
-Thus, from equation (\ref{eq:MFG_opt_alpha_Pontryagin}) we must have:
+Thus, from equation (\ref{eq:MFG_opt_alpha_Pontryagin}) we have:
 \begin{equation}
@@
 \end{equation}
-with
-\begin{equation*}
-	a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)}
+with:
+\begin{equation*}
+	a^{MFG}(t)=-\frac{b_2(t)}{r(t)+\bar{r}(t)},
 	\qquad
@@
 See Appendix \ref{appendix_solving_fbsdes}).
-Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that
+Let $\bar{\eta}_t^{MFG}$, $\eta_t^{MFG}$, $\bar{x}_t^{MFG}$, and $v^{MFG}_t$ denote the solutions for this problem as described in the appendix so that:
 \begin{align*}
 Y_t =\eta_t^{MFG}X_t+(\bar{\eta}_t^{MFG}-\eta_t^{MFG})\bar{x}_t^{MFG}, \quad &\mathbb{E}(Y_t) =\bar{\eta}_t^{MFG}\bar{x}_t^{MFG},\\
-\mathbb{E}(X_t) =\bar{x}_t^{MFG}, \quad &Var(X_t)=v^{MFG}_t
+\mathbb{E}(X_t) =\bar{x}_t^{MFG}, \quad &Var(X_t)=v^{MFG},
 \end{align*}
-provide a solution to the LQEMFG problem. Then from the appendix, we have 
+provide a solution to the LQEMFG problem. Then from the appendix, we have:
 \begin{itemize}
@@
 	\end{equation}
-	with terminal condition $\bar{\eta}^{MFG}_T = q_T+\bar{q}_T(1-s_T)$; 
+	with terminal condition $\bar{\eta}^{MFG}_T = q_T+\bar{q}_T(1-s_T)$, 
 	\item a first order equation for $\bar{x}_t^{MFG}$:
@@
 	\end{equation}
-	with initial condition $\bar{x}^{MFG}_0=\mathbb{E}(\xi)$;
+	with initial condition $\bar{x}^{MFG}_0=\mathbb{E}(\xi)$,
 	\item a scalar Riccati equation for $\eta_t^{MFG}$:
@@
 \end{IEEEeqnarray}
-Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have
+Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
 \begin{equation*}
@@
 \begin{equation}
-	\Delta \bar{\eta}_t = \lambda \bar{\eta}_t^{MFG} - \bar{\eta}_t^{MKV} .
+	\Delta \bar{\eta}_t := \lambda \bar{\eta}_t^{MFG} - \bar{\eta}_t^{MKV} .
 \label{eq:delta_eta}
@@
 	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by:
-	\begin{equation*}
+	\begin{equation}
 		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2}\cdot \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
-	\end{equation*}
+	\label{eq:prop_2}
+	\end{equation}
 \label{prop:diff_SC}
@@
 
-Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by:
-\begin{equation}
-PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} (\mathbb{E}(\xi))^2}.
+Note that we can write:
+\begin{equation}
+PoA =1+ \frac{\Delta SC}{SC^{MKV}}.
 \label{eq:PoA_LQ}
-\end{equation}\\
+\end{equation}
 
@@
 Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
-We conclude that $PoA=1$.
+We conclude from equation (\ref{eq:PoA_LQ}) that $PoA=1$.
 \end{proof}
@@
 We study in the following the variation of $PoA$ by letting only one of the coefficients tend to zero or to infinity.
-In order to make the following computations easier to follow, we repeat equations (\ref{eq:PoA_LQ}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations:
+In order to make the following computations easier to follow, we repeat equations (\ref{eq:prop_2}), (\ref{eq:SC_MKV_2}), (\ref{eq:x_bar_MFG_explicit}), and (\ref{eq:v_t}), which we recall is equivalent to  equation (\ref{eq:v_t_MKV}), using the above notations.
+Assuming (\ref{eq:assumptions}), we have:
 \begin{IEEEeqnarray}{l}
-	PoA = 1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle B\int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + w_0 (\mathbb{E}(\xi))^2},
-\label{eq:PoA_LQ_new_notation} \\[3pt]
-	\displaystyle \bar{x}^{MFG}_t =\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds},
-\label{eq:x_bar_MFG_explicit_new_notation} \\[3pt]	
-	v_t = Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds.
-\label{eq:v_t_new_notation}
+	\displaystyle \Delta SC= \frac{1}{2}B\int_0^T (u_t-w_t)^2 \cdot (\bar{x}_t^{MFG})^2 dt, \label{eq:Delta_SC_LQ_new_notation} \\[3pt]
+	\displaystyle SC^{MKV}= \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{(q_T + \bar{q}_T)}{2} v_T + \frac{1}{2}w_0 (\mathbb{E}(\xi))^2, \label{eq:SC_MKV_LQ_new_notation} \\[3pt]
+	\displaystyle \bar{x}^{MFG}_t =\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}, \label{eq:x_bar_MFG_explicit_new_notation} \\[3pt]	
+	\displaystyle v_t = Var(\xi)e^{\int_0^t 2(b_1-B^{\eta} \eta_s)ds}+\sigma^2 \int_0^t e^{2 \int_s^t (b_1-B^{\eta}\eta_u) du}ds. \label{eq:v_t_new_notation}
 \end{IEEEeqnarray}
@@
 	\end{equation*}
-	Therefore, from equation (\ref{eq:PoA_LQ_new_notation}), we have: 
+	Therefore, from equation (\ref{eq:PoA_LQ}), we have: 
 	$$\displaystyle \lim_{r \to \infty} PoA^r = 1.$$
@@
 
-	Step 2: We derive an upper bound for $b_2 SC^{MKV,b_2}$. From equation (\ref{eq:SC_MKV_2}), we have: 
+	Step 2: We derive an upper bound for $b_2 SC^{MKV,b_2}$. From equation (\ref{eq:SC_MKV_LQ_new_notation}), we have: 
 	\begin{equation}
@@
 For the second integration, we will use Lemma \ref{lemma:int_b2_eta_t}, which appears below.
-From Lemma \ref{lemma:int_b2_eta_t}, there exists $b^{*,integral}>0$ and a constant $M_{intgl}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*, integral}$ we have:
-	\begin{equation}
-	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{intgl}.
+From Lemma \ref{lemma:int_b2_eta_t}, there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$ we have:
+	\begin{equation}
+	\int_0^T b_2 \eta_t^{b_2} dt \leq M_{l}.
 	\label{eq:intgeral_b2_eta_t_bound_b2_infinity}
@@
 
-	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,integral}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
+	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
 	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
@@
 		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
-		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{intgl} \nonumber \\
-		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{intgl}}{2} =: M_{J_2}.
+		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{l} \nonumber \\
+		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{l}}{2} =: M_{J_2}.
 	\label{eq:J2_upper_bound_b2_infinity}
@@
 	Finally, putting together inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}) and for $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denominator} \}$, we have for all $b_2 \geq b_2^{*,case 2}$:
-	\begin{equation}
+	\begin{equation*}
 		\frac{b_2+\bar{b}_2}{b_2} \leq 2, \quad \text{and thus,} \quad \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = \frac{(b_2 + \bar{b}_2) \Delta SC^{b_2} }{\left(\frac{b_2 + \bar{b}_2}{b_2} \right) (b_2 SC^{MKV,b_2} ) } \geq \frac{c_{num}}{ 2 M_{den}} > 0.
-	\end{equation}
+	\end{equation*}
 	Therefore, we conclude: 
@@
 \begin{lemma}
-	There exists a $b_2^{*,l}>0$ and $M^l>0$, such that for all $b_2 \geq b_2^{*,l}$:
+	Assume Assumption \ref{assumption}. There exists a $b_2^{*,l}>0$ and $M^l>0$, such that for all $b_2 \geq b_2^{*,l}$:
 	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M^l.$$

### 2018-08-02 PoA.tex
condensing Lemma 1

@@
 	\end{equation*}
-	It is easy to show directly from their explicit solutions that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t, \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$
+	It is easy to show directly from their explicit solutions (see equation (\ref{eq:riccati_ut_sol})) that for every time $t\in [0,T]$, $$\lim_{r \to \infty}u^r_t=u^{r \to \infty}_t, \quad \text{and thus,} \quad \lim_{r \to \infty}B^ru^r_t=0.$$
 
@@
 \begin{proof}
-	As noted in the proof of Proposition \ref{prop:b2_to_infty}, for $t\in[0,T)$, we have:
-	$$\lim_{b_2 \to \infty}b_2\eta^{b_2}_t=(r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}}=\sqrt{(r+\bar{r})(q+\bar{q})} =: c_\eta.$$
-	And thus, there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have
+	Since $\lim_{b_2 \to \infty}b_2\eta^{b_2}_t= c_\eta,$ there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have
 	$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$
@@
 	$$b_2\eta^{b_2}_T=b_2D^\eta=b_2(q_T+\bar{q}_T)\geq c_\eta+2.$$
-	Since $\lim_{b_2 \to \infty} B^\eta (D^\eta)^2+2A^\eta D^\eta-C^\eta=\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing.
-Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that:
-	$$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1, \quad \text{and} \quad b_2 \eta^{b_2}_t \leq c_\eta+1,\ \forall t\leq t^*_{b_2}.$$
-	Thus for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, we have:
-	\begin{equation*}
-	\begin{split}
-	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta&=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} \right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}-c_\eta,
-	\end{split}
-	\end{equation*}
+	Let $b_2^{*,3}$ such that for $b_2 \geq b_2^{*,3}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing.
+Since for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$, the function $t \mapsto b_2 \eta^{b_2}_t$ is increasing and continuous, by the intermediate value theorem, there exists a $t^*_{b_2}\in[0,T]$ such that
+	$b_2 \eta^{b_2}_{t^*_{b_2}} =c_\eta+1$, and $b_2 \eta^{b_2}_t \leq c_\eta+1$, for all $t\leq t^*_{b_2}.$
+	From an analogous equation to (\ref{eq:riccati_ut_sol}) for $\eta^{b_2}_{t^*_{b_2}}$, we have for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3} \}$:
 	$$
-	1=\frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} +\left(\frac{\delta^{+,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}}\right) e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},
+	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta\leq \frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}} e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},
 	$$
-	\begin{equation}
-	\begin{split}
-	\frac{D^\eta}{r+\bar{r}}-&\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \\
-	&= \left(-\frac{C^\eta}{b_2}-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} -\frac{\delta^{+,b_2}_\eta}{b_2^2}c_\eta +\frac{D^\eta}{r+\bar{r}}c_\eta -\frac{\delta^{+,b_2}_\eta}{b_2^2} +\frac{D^\eta}{r+\bar{r}} \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})} \\
-	&\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
+	After rearranging terms:
+	\begin{equation}
+	\begin{split}
+	\frac{D^\eta}{r+\bar{r}}-\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right]\\
+	\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
 	\end{split}
@@
 	\end{equation}
-	It is easy to derive the following limits:
-	$$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0.$$
-	Therefore, there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$, we have:
-	$$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}+\frac{C^\eta}{b_2}+\frac{\delta^{-,b_2}_\eta c_\eta}{b_2^2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$$
+	Since we have
+	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$ there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$,
+	$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$
 	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
-	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left(-\frac{\delta^{-,b_2}_\eta D^\eta}{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}, $$
-	$$e^{\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}\leq -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) , $$
-	$$\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})\leq \ln \left( -\frac{2\delta^{-,b_2}_\eta(r+\bar{r})}{b_2}+2(1+c_\eta) \right) , $$
+	$$\frac{D^\eta}{2(r+\bar{r})}\leq \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.$$
+	After rearranging terms:
 	\begin{equation}
@@
 	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(5c_\eta+2 \right).$$
-	Finally, for $b_2 \geq b_2^{*,l}$, we have:
-	\begin{equation*}
-	\begin{split}
-	\int_0^T b_2 \eta^{b_2}_t dt&=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \\
-	&\leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta\\
-	&\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.	
+	Finally, for $b_2 \geq b_2^{*,l}$:
+	\begin{equation*}
+	\begin{split}
+	\int_0^T b_2 \eta^{b_2}_t dt=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta \\
+	\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.
 	\end{split}

### 2018-08-02 PoA.tex
condensing Prop 4 Case 2

@@
 To do so, we will show that $(b_2 + \bar{b_2}) \Delta SC^{b_2}\geq c_{num}>0$ and $b_2 SC^{MKV,b_2} \leq M_{den}<\infty$ for large $b_2$, where $c_{num}$ and $M_{den}$ are two constants independent of $b_2$.
-
 We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1.
 Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
-Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.\\
+Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.
 
@@
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,numerator} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,numerator}$ and all $s \in [0, T/2]$, we have:
+Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$, we have:
 	\begin{equation*}
@@
 	$$
-	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,numerator}$, we deduce:
+	Thus, similar to inequality (\ref{eq:I1_ineq_b2_infinity}), for all $b_2 \geq b_2^{*,num}$, we deduce:
 	\begin{IEEEeqnarray}{rCl}
@@
 		&\geq& \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{8 (r+ \bar{r}(1-\bar{s})^2 )} \cdot (b_2 + \bar{b}_2) \int_0^{\frac{T}{2}} \exp \left[- \frac{2 (b_2 + \bar{b}_2)}{r +\bar{r}(1-\bar{s})^2} \left( c_u + \frac{1}{4} \left\vert c_u - c_w \right\vert \right) t \right] dt \nonumber \\
-		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \vert c_u - c_w \vert/4 )}{r+\bar{r}(1-\bar{s})^2}(b_2 + \bar{b}_2)} \right) \nonumber \\
-		&\geq & (2 c_{num} ) \cdot \frac{1}{2} = c_{num},
+		&= & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)} \left( 1- e^{- \frac{T (c_u + \vert c_u - c_w \vert/4 )}{r+\bar{r}(1-\bar{s})^2}(b_2 + \bar{b}_2)} \right) \nonumber \\
+		&\geq & \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{16 (c_u +  \vert c_u - c_w \vert / 4)}\cdot \frac{1}{2} =: c_{num}.
 	\label{eq:numerator_ineq_b2_infinity}	
 	\end{IEEEeqnarray}
-	with $c_{num} :=  \frac{\left\vert c_u - c_w \right\vert^2 (\mathbb{E}(\xi))^2}{32 (c_u +  \vert c_u - c_w \vert / 4)}$ and the last inequality is justified because $b_2 \geq c_3$. \\
 
@@
 	\begin{equation}
-	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J^{b_2}_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J^{b_2}_2$}}
+	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J^{b_2}_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J^{b_2}_2$}}.
 	\label{eq:J1_plus_J2_b2_infinity}
 	\end{equation}	
-	We also notice the following two technical results which are useful for deriving upper bounds for $J^{b_2}_1$ and $J^{b_2}_2$.
+	We derive the following two results which are useful for deriving upper bounds for $J^{b_2}_1$ and $J^{b_2}_2$.
 First, let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
@@
 	\begin{equation}
-		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta^{b_2}_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
+		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta^{b_2}_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt.
 	\label{eq:l(t)_transformation_b2_infinity}
@@
 	\end{IEEEeqnarray*}
-	Hence, if we choose $b^{*,J_1} \geq b^{*,basic}$ such that
+	Let $b^{*,J_1} \geq b^{*,basic}$ such that
 	for all $b_2 \geq b_2^{*,J_1}$:
-	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad \text{and} \quad b_2 e^{- \kappa_5 b_2 T} \leq \frac{1}{\kappa_5}, $$
-	then we can derive an upper bound for $J^{b_2}_1$. Namely, for all $b_2 \geq b_2^{*,J_1}$:
+	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad \text{and} \quad b_2 e^{- \kappa_5 b_2 T} \leq \frac{1}{\kappa_5}.$$
+	Then for all $b_2 \geq b_2^{*,J_1}$:
 	\begin{IEEEeqnarray}{rCl}
@@
 
-	Next, consider the quantity $J^{b_2}_2$:
+	Next, consider the quantity $J^{b_2}_2$, which we can write as:
 	\begin{IEEEeqnarray*}{rCl}
@@
 	\end{IEEEeqnarray*}
-	The first integration on the right-hand side of the above equation can be treated using similar techniques as in Case 1.
-For the second integration, we will use Lemma \ref{lemma:int_b2_eta_t}, which appears below.
-From Lemma \ref{lemma:int_b2_eta_t}, there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$ we have:
+	We will make use of Lemma \ref{lemma:int_b2_eta_t}, which appears below, and states that there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$:
 	\begin{equation}
@@
 
-	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,denominator} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
+	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,den} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
 	\begin{equation} 
@@
 
-	Finally, putting together inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}) and for $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,numerator}, b_2^{*,denominator} \}$, we have for all $b_2 \geq b_2^{*,case 2}$:
+	Finally, putting together inequalities (\ref{eq:numerator_ineq_b2_infinity}) and (\ref{eq:demumerator_ineq_b2_infinity}) and for $b_2^{*,case 2} := \max \{ \bar{b}_2,  b_2^{*,num}, b_2^{*,den} \}$, we have for all $b_2 \geq b_2^{*,case 2}$:
 	\begin{equation*}

### 2018-08-02 PoA.tex
changed h_u and h_w in Prop 7 to g_u and g_w

@@
 	Step 1: We derive a lower bound for $(b_2+\bar{b}_2)\Delta SC^{b_2}$ by adapting the techniques used in inequality (\ref{eq:I1_ineq_b2_infinity}).
-We have shown that for every $t \in[0,T]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
+We have shown that for every $t \in[0,T/2]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
 Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
@@
 
-	First, consider $J^{b_2}_1$. From equation (\ref{eq:v_t_new_notation}) and inequality (\ref{eq:l(t)_upper_bound_b2_infinity}), we have that for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$:
+	First, consider $J^{b_2}_1$.
+From equation (\ref{eq:v_t_new_notation}) and inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}) and (\ref{eq:l(t)_upper_bound_b2_infinity}), we have that for all $b_2 \geq b_2^{*,basic}$ and for all $t \in [0,T]$:
 	\begin{IEEEeqnarray*}{rCl}
@@
 
-	Next, consider the quantity $J^{b_2}_2$, which we can write as:
+	Next, consider the quantity $J^{b_2}_2$, which can be written as:
 	\begin{IEEEeqnarray*}{rCl}
@@
 	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
-	Thus, together with inequalities (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}) and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
+	Thus, together with inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}), and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
 	\begin{IEEEeqnarray}{rCl}
@@
 	\end{IEEEeqnarray} 
-
 	Now, from equation (\ref{eq:J1_plus_J2_b2_infinity}) and inequalities (\ref{eq:J1_upper_bound_b2_infinity}) and (\ref{eq:J2_upper_bound_b2_infinity}), we have for all $b_2 \geq b_2^{*,den} := \max \{ b_2^{*,J_1}, b_2^{*,J_2} \}$:
@@
 	$$\lim_{b_1 \to \infty}B (D^{u})^2 + 2 A^{u,b_1} D^{u} - C^{u} = \lim_{b_1 \to \infty}B (D^{w})^2 + 2 A^{w,b_1} D^{w} - C^{w}=-\infty.$$
-	Denote $h_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $h_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. For all $t \in [0,T)$, we have the limits:
-	\begin{equation}
-		\lim_{b_1 \to \infty} h_u(b_1,t) =  \lim_{b_1 \to \infty} h_w(b_1,t) = 2.
+	Denote $g_u(b_1,t): = B \frac{u_t^{b_1}}{b_1}$ and $g_w(b_1,t) := B \frac{w_t^{b_1}}{b_1}$. For all $t \in [0,T)$, we have the limits:
+	\begin{equation}
+		\lim_{b_1 \to \infty} g_u(b_1,t) =  \lim_{b_1 \to \infty} g_w(b_1,t) = 2.
 	\label{eq:ut_wt_lim_b1_infty}
@@
 	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
-	$$ \sup_{0 \leq t \leq T} \left\{ h_u(b_1, t), h_w(b_1,t)\right\} \leq \max \left\{ h_u(b_1, 0), h_w(b_1,0) \right\} \leq 3.$$
+	$$ \sup_{0 \leq t \leq T} \left\{ g_u(b_1, t), g_w(b_1,t)\right\} \leq \max \left\{ g_u(b_1, 0), g_w(b_1,0) \right\} \leq 3.$$
 
@@
 	\begin{split}
-	\vert h_u(b_1, t) - h_w(b_1,t) \vert  &=\max \{h_u(b_1, t)-h_w(b_1, t),h_w(b_1, t)-h_u(b_1, t) \}\\
-	&\leq \max \{h_u(b_1, 0)-h_w(b_1, 3T/4),h_w(b_1, 0)-h_u(b_1, 3T/4) \} \\
+	\vert g_u(b_1, t) - g_w(b_1,t) \vert  &=\max \{g_u(b_1, t)-g_w(b_1, t),g_w(b_1, t)-g_u(b_1, t) \}\\
+	&\leq \max \{g_u(b_1, 0)-g_w(b_1, 3T/4),g_w(b_1, 0)-g_u(b_1, 3T/4) \} \\
 	&\leq \epsilon,
@@
 	and
-	$$h_w(b_1,0) \geq 2 - \frac{1}{3} = \frac{5}{3},\quad  h_u(b_1,t) \geq h_u(b_1, 3T/4) \geq \frac{5}{3}.$$
+	$$g_w(b_1,0) \geq 2 - \frac{1}{3} = \frac{5}{3},\quad  g_u(b_1,t) \geq g_u(b_1, 3T/4) \geq \frac{5}{3}.$$
 	We adapt the methodology in Proposition \ref{prop:b2_to_infty} and split the interval $[0,T]$ into two parts: $[0, 3T/4]$ and $[3T/4, T]$.
@@
 	\begin{equation*}
-		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)},
+		\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{g_w(b_1,0)},
 	\end{equation*}
@@
 	\begin{IEEEeqnarray*}{rCl}
-	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
+	I^{b_1}_1 &=& b_1 \int_0^{\frac{3}{4}T} \left( g_u(b_1,t) - g_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t g_u(b_1,s) ds \right) dt \nonumber \\
 	&\leq & \epsilon^2 e^{2\bar{b}_1 \cdot \frac{3}{4} T } \cdot b_1 \int_0^{\frac{3}{4}T} \exp \left( 2b_1 t - 2 b_1 \cdot \frac{5}{3} t \right) dt  \nonumber \\
@@
 	\begin{IEEEeqnarray*}{rCl}
-		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( h_u(b_1,t) - h_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t h_u(b_1,s) ds \right) dt \nonumber \\
-		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} h_u(b_1,s) ds \right) dt \nonumber \\
+		 I^{b_1}_2 &=& b_1 \int_{\frac{3}{4}T}^T \left( g_u(b_1,t) - g_w(b_1,t) \right)^2 e^{2\bar{b}_1 t} \cdot \exp \left( 2b_1 t - 2 b_1 \int_0^t g_u(b_1,s) ds \right) dt \nonumber \\
+		 &\leq & b_1 (3+3)^2 e^{2 \bar{b}_1 T} \cdot \int_{\frac{3}{4}T}^{T}  \exp \left( 2b_1 t - 2b_1 \int_0^{\frac{3}{4}T} g_u(b_1,s) ds \right) dt \nonumber \\
 		 &\leq & 36 e^{2 \bar{b}_1 T} b_1 \cdot \frac{T}{4} \exp\left(2b_1 \cdot T - 2 b_1 \cdot  \frac{3}{4} T \cdot \frac{5}{3} \right) \nonumber \\
@@
 	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
-	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{h_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
+	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{g_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
 	Since the proof holds for arbitrary $\epsilon>0$, and $\kappa_1 = \frac{3}{4} e^{\frac{3\bar{b}_1 T}{2} }$ is independent of $b_1$ and $\epsilon$, we conclude that:

### 2018-08-02 PoA.tex
moved h_u, h_w definitions earlier in Prop 4

@@
 	and thus, $\lim_{b_2 \to \infty}\delta^{+,b_2}_u - \delta^{-,b_2}_u = +\infty$.
+	For the sake of simplicity, denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
 From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
@@
 	\begin{split}
-		(b_2 + \bar{b}_2) u^{b_2}_t &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
+		h_u(b_2,t) &= \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
 		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
@@
 	Similarly, for all $t \in [0,T)$:
-	$$\lim_{b_2 \to \infty} (b_2 + \bar{b}_2) w_t^{b_2} =  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	$$\lim_{b_2 \to \infty} h_w(b_2,t)=  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
 	and
@@
 	\begin{IEEEeqnarray}{rCl}
-		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
+		h_u(b_2,t) &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
 		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
@@
 	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
-	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
-We have:
+	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$ and thus:
 	\begin{equation}
@@
 Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions.
-Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.
+Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $h_u(b_2,t) \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.
 
@@
 	\end{equation}
-
 	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:

### 2018-08-02 PoA.tex
minor edit in defining alpha in 2.1

@@
 \end{equation*}
-According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,y)=0$.
-By solving this equation, we introduce the function:
-\begin{equation}
-    \hat{\alpha}(t,x,\bar{\mu},\bar{\nu},y)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)y}{r(t)+\bar{r}(t)},
+According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha},\bar{\nu}_t,Y_t)=0$.
+Thus, we find the optimal control:
+\begin{equation}
+    \hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)Y_t}{r(t)+\bar{r}(t)},
 \label{eq:MFG_opt_alpha_Pontryagin}
 \end{equation}
-and pick an optimal control as $\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$.
-When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$.
-By taking the expectation, we find:
+When solving the fixed point step, we identify $\bar{\nu}_t=\mathbb{E}(\hat{\alpha}_t)$. By taking the expectation, we find:
 \begin{equation*}

### 2018-08-02 PoA.tex
clarifying differences between 2.2 and 2.1

@@
 	with terminal condition $\bar{\eta}^{MFG}_T = q_T+\bar{q}_T(1-s_T)$, 
-	\item a first order equation for $\bar{x}_t^{MFG}$:
+	\item a linear first order ODE for $\bar{x}_t^{MFG}$:
 	\begin{equation}
@@
 \end{IEEEeqnarray}
-Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
+Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely, from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
 \begin{equation*}
@@
 Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition reduces to the following (see section 4 in \cite{carmona_acciaio}):
-$\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
+$\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
 \begin{equation*}
@@
 In the present LQ case, the sufficient condition can be used to solve for:
-\begin{equation*}
+\begin{equation}
     \hat{\alpha}_t=a^{MKV}(t)Y_t+b^{MKV}(t)\mathbb{E}(Y_t),
-\end{equation*}
-and:
-\begin{equation*}
-    \mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t),
-\end{equation*}
+    \label{eq:alpha_hat_MKV}
+\end{equation}
 with:
@@
 \begin{split}
-    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)} \\
-    b^{MKV}(t)&=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right) \\
-    c^{MKV}(t)&=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.
-\end{split}
-\end{equation*}
-Note that $c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$. So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
-\begin{equation}
+    a^{MKV}(t)&=-\frac{b_2(t)}{r(t)+\bar{r}(t)}, \quad \text{and} \quad b^{MKV}(t)=-\frac{1}{r(t)+\bar{r}(t)}\left(\bar{b}_2(t)-\frac{\bar{r}(t)\bar{s}(t)(\bar{s}(t)-2)(b_2(t)+\bar{b}_2(t))}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2} \right).
+\end{split}
+\end{equation*}
+Then $\mathbb{E}(\hat{\alpha}_t)=c^{MKV}(t)\mathbb{E}(Y_t)$ with:
+   $$ c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)=-\frac{b_2(t)+\bar{b}_2(t)}{r(t)+\bar{r}(t)(1-\bar{s}(t))^2}.$$
+
+So the solution of the optimal control problem of McKean-Vlasov type is given by the solution to the FBSDE system:
+\begin{equation}
+\left\{
 \begin{split}
@@
 \end{split}
+\right.
 \label{eq:FBSDE_EMKV}
@@
 See Appendix \ref{appendix_solving_fbsdes}).
-Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ so that $Y_t=\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}$, $\mathbb{E}(Y_t)=\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}$, $\mathbb{E}(X_t)=\bar{x}_t^{MKV}$, and $Var(X_t)=v^{MKV}_t$ provide a solution to the LQEMKV problem.
-Then from the appendix, we have:
-\begin{equation}
-\begin{split}
-\dot{\bar{\eta}}^{MKV}_t+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) (\bar{\eta}^{MKV}_t)^2+2(b_1(t)+\bar{b}_1(t)) \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2&=0,\\
-\bar{\eta}^{MKV}_T-(q_T+\bar{q}_T(1-s_T)^2)&=0,
-\end{split}
+Let $\bar{\eta}_t^{MKV}$, $\eta_t^{MKV}$, $\bar{x}_t^{MKV}$, and $v^{MKV}_t$ denote the solutions for this problem as described in the appendix so that:
+\begin{align*}
+Y_t =\eta_t^{MKV}X_t+(\bar{\eta}_t^{MKV}-\eta_t^{MKV})\bar{x}_t^{MKV}, \quad &\mathbb{E}(Y_t) =\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},\\
+\mathbb{E}(X_t) =\bar{x}_t^{MKV}, \quad &Var(X_t)=v^{MKV},
+\end{align*}
+provide a solution to the LQEMKV problem. Then from the appendix, we have:
+\begin{itemize}
+	\item a scalar Riccati equation for $\bar{\eta}_t^{MKV}$:
+	\begin{equation}
+	\dot{\bar{\eta}}^{MKV}_t+ \left[ c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MKV}_t)^2+ 2\left(b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2 =0
 	\label{eq:eta_bar_MKV}
 	\end{equation}
-\begin{equation}
-\begin{split}
-\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)(\eta^{MKV}_t)^2+2b_1(t)\eta^{MKV}_t+q(t)+\bar{q}(t)&=0, \\
-\eta^{MKV}_T-(q_T+\bar{q}_T)&=0,
-\end{split}
-\end{equation}
-\begin{equation}
-\begin{split}
-\dot{\bar{x}}^{MKV}_t&=\left[b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t))\bar{\eta}^{MKV}_t\right]\bar{x}^{MKV}_t, \\
-\bar{x}^{MKV}_0&=\mathbb{E}(\xi).
-\end{split}
+	with terminal condition $\bar{\eta}^{MKV}_T = q_T+\bar{q}_T(1-s_T)^2$, 
+	\item a linear first order ODE for $\bar{x}_t^{MKV}$:
+	\begin{equation}
+	\dot{\bar{x}}^{MKV}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MKV}_t \right] \cdot \bar{x}^{MKV}_t
 	\label{eq:x_bar_MKV}
 	\end{equation}
-And thus,
-\begin{equation}
-\bar{x}^{MKV}_t=\mathbb{E}(\xi) e^{\int_0^t\left[b_1(u)+\bar{b}_1(u)+c^{MKV}(u)(b_2(u)+\bar{b}_2(u)\bar{\eta}^{MKV}_u)\right]du},
-\end{equation}
-\begin{equation}
-v^{MKV}_t=Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MKV}(s)b_2(s)\eta^{MKV}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u\right] du}ds.
+	with initial condition $\bar{x}^{MKV}_0=\mathbb{E}(\xi)$,
+	\item a scalar Riccati equation for $\eta_t^{MKV}$:
+	\begin{equation}
+	\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)\cdot (\eta^{MKV}_t)^2 + 2b_1(t) \cdot \eta^{MKV}_t+q(t)+\bar{q}(t)=0
+	\end{equation}
+	with terminal condition $\eta^{MKV}_T = q_T+\bar{q}_T$,
+\end{itemize}
+where the dot is the standard ODE notation for a derivative. 
+And thus, we obtain explicit solutions for $\bar{x}_t^{MKV}$ and $v_t^{MKV}$:
+\begin{IEEEeqnarray}{rCl}
+	\bar{x}^{MKV}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MKV}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MKV}_s\right) ds} \label{eq:x_bar_MKV_explicit} \\ 
+	v^{MKV}_t &=& Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MKV}(s)b_2(s) \cdot \eta^{MKV}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u\right] du}ds.
 	\label{eq:v_t_MKV}
-\end{equation}
-Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, i.e.
+\end{IEEEeqnarray}
+Note that while equations (\ref{eq:eta_bar_MKV})-(\ref{eq:v_t_MKV}) are quite similar to equations (\ref{eq:eta_bar_MFG})-(\ref{eq:v_t}) from the previous section, there are some subtle differences.
+Now we have $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, namely, from equation (\ref{eq:alpha_hat_MKV}), we have:
 \begin{equation*}
@@
 \begin{equation*}
-    \mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV},
-\end{equation*}
-and:
-\begin{equation*}
-    Var(\phi(t,X_t))=(a^{MKV}(t)\eta_t^{MKV})^2v^{MKV}_t.
+\mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\cdot \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}
+\qquad 
+\text{and}
+\qquad
+Var(\phi(t,X_t))=\left(a^{MKV}(t)\eta_t^{MKV} \right)^2 \cdot v^{MKV}_t.
 \end{equation*}

### 2018-08-02 PoA.tex
undoing: clarifying differences between 2.2 and 2.1

@@
 \end{IEEEeqnarray}
-Note that while equations (\ref{eq:eta_bar_MKV})-(\ref{eq:v_t_MKV}) are quite similar to equations (\ref{eq:eta_bar_MFG})-(\ref{eq:v_t}) from the previous section, there are some subtle differences.
-Now we have $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, namely, from equation (\ref{eq:alpha_hat_MKV}), we have:
+Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, namely, from equation (\ref{eq:alpha_hat_MKV}), we have:
 \begin{equation*}

### 2018-08-02 PoA.tex
changes to Theorem 2

@@
 	with:
-	\begin{IEEEeqnarray*}{rClcrClcrCl}
+	\begin{IEEEeqnarray}{rClcrClcrCl}
 		A^u &=& - \left(b_1 + \frac{\bar{b}_1}{2}\right), & \qquad & 
@@
 		D^\eta &=& q_T + \bar{q}_T .
-	\end{IEEEeqnarray*}
+		\label{eq:ABCD}
+	\end{IEEEeqnarray}
 If $B^u\neq 0$, $B^u D^u \geq 0$ and $B^uC^u >0$, we have (see equation (\ref{eq:riccati_ut_sol_app}) in Appendix A) the existence and uniqueness for $u_t$ which can be expressed by:
@@
 \begin{theorem}
-	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ satisfies that $\mathbb{E}(\xi)  \neq 0$, then 
+	Assume (\ref{eq:assumptions}) and the initial condition $\xi$ satisfies $\mathbb{E}(\xi)  \neq 0$. Let $A^u$, $A^w$, $B$, $C^u$, $C^w$, $D^u$, and $D^w$ as defined in equation (\ref{eq:ABCD}).
 	\begin{itemize}
-		\item when $\bar{b}_1 > 0$, we have $PoA = 1$ if and only if
-		\begin{equation}
-		D^u = D^w =:D \quad \text{and} \quad B D^2 + 2 A^{u} D - C^{u} = B D^2 + 2 A^{w} D - C^w  = 0,
+		\item When $\bar{b}_1 > 0$, we have $PoA = 1$ if and only if:
+		\begin{equation}
+		D^u = D^w =:D \quad \text{and} \quad B D^2 + 2 A^{u} D - C^{u} = B D^2 + 2 A^{w} D - C^w  = 0.
 		\label{eq:PoA=1_condition_b1_bar>0}
 		\end{equation}
-		\item when $\bar{b}_1 = 0$, then $A^u = A^w$ and we have $PoA = 1$ if and only if 
-		\begin{equation}
-			D^u = D^w \quad \text{and} \quad C^u = C^w, 
+		\item When $\bar{b}_1 = 0$, then $A^u = A^w$ and we have $PoA = 1$ if and only if:
+		\begin{equation}
+			D^u = D^w \quad \text{and} \quad C^u = C^w. 
 		\label{eq:PoA=1_condition_b1_bar=0}
@@
 	\end{itemize}
+	\begin{comment}
 	Namely, $PoA = 1$ if and only if the following two or three conditions hold true:
@@
 	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  - ( q + \bar{q}(1-s)^2 ) = 0. $$
-
+	\end{comment}
 	\label{thm:PoA_equivalent_1}
@@
 \begin{proof}
-	Under assumption (\ref{eq:assumptions}), we know from equation (\ref{eq:riccati_wt}) and from the explicit formula (\ref{eq:riccati_ut_sol}) for solution to scalar Riccati equation that $w_0$ is strictly positive.
-Thus, with the assumption $\mathbb{E}(\xi) \neq 0$, we have $SC^{MKV} > 0$.
+	From an analogous equation to (\ref{eq:riccati_ut_sol}) for $w_t$, we know that under assumption (\ref{eq:assumptions}), $w_0>0$.
+Thus, with the assumption $\mathbb{E}(\xi) \neq 0$, we have $0 < SC^{MKV} < \infty$.
 Hence, $PoA =1$ if and only if $\Delta SC = 0$.
-Since $\bar{x}_t^{MFG} \neq 0$ for all $t \in [0,T]$, from proposition \ref{prop:diff_SC} and the continuity of $u_t$ and $w_t$, we derive that
+Since $\bar{x}_t^{MFG} \neq 0$ for all $t \in [0,T]$, from Proposition \ref{prop:diff_SC} and the continuity of $u_t$ and $w_t$, we deduce that:
 	\begin{equation}
@@
 
-	From equation (\ref{eq:riccati_ut_sol_deriv}) and the uniqueness of solutions to Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$.
-Thus, $PoA = 1$.
-
-	Suppose now that $PoA =1$.
-Then by taking $t=T$ in equation (\ref{eq:PoA_equivalence_ut=w_t}), we obtain the first condition in both (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}):
+	From equation (\ref{eq:riccati_ut_sol_deriv}) and the uniqueness of solutions to Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, then $u_t=D^u=D^w = w_t$ for all $ t\in [0,T]$, and thus, $PoA = 1$.
+
+	Suppose now that $PoA =1$. Then $u_t = w_t$ for all $t \in [0,T]$ and clearly:
 	$$D^u = u_T = w_T = D^w.$$
-	Moreover, if we make the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by taking $u_t = w_t$ for all $t \in [0,T]$ into account, we obtain:
-	\begin{equation}
-		2 (A^u - A^w) w_t = C^u - C^w, \quad \forall \  t \in [0,T]
+	Now, if we take the difference between the two Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), and by using $u_t = w_t$ for all $t \in [0,T]$, we obtain:
+	\begin{equation}
+		2 (A^u - A^w) w_t = C^u - C^w, \quad \forall \  t \in [0,T].
 	\label{eq:wt=constant}
 	\end{equation}
-	Since $2(A^u - A^w) = \bar{b}_1$, so that in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$.
+	Since $2(A^u - A^w) = \bar{b}_1$, in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$.
 Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, which are constants for all $t \in [0,T]$.
-Thus, the derivatives with respect to time $t$ for $u_t$ and $w_t$ should be zero.
+Thus, the time derivatives of $u_t$ and $w_t$ should be zero.
 From equation (\ref{eq:riccati_ut_sol_deriv}), and the fact that $\delta_u^+ - \delta_u^- > 0$, we deduce:
@@
 
-	By replacing $(A^u,B, C^u, D^u)$ and $(A^w, B, C^w, D^w)$ with their explicit expressions, we obtain henceforth an equivalent condition for $PoA = 1$ in term of the coefficients of Linear Quadratic model.
+	%By replacing $(A^u,B, C^u, D^u)$ and $(A^w, B, C^w, D^w)$ with their explicit expressions, we obtain an equivalent condition for $PoA = 1$ in term of the coefficients of the linear quadratic model.
 

### 2018-08-02 PoA.tex
update to remark 6

@@
 	Consider Assumption \ref{assumption} and the case when $\bar{b}_2$ tends to zero.
-We have $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$, and therefore, $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$ implies $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
+We have $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$, and therefore, $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$ if and only if $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
+Therefore, we have an analogous result as Theorem \ref{thm:PoA_equivalent_1} but for the limiting coefficients $A^u$, $A^w$, $B^{\bar{b}_2 \to 0}$, $C^{u,\bar{b}_2 \to 0}$, $C^w$, $D^{u,\bar{b}_2 \to 0}$, and $D^w$.
+Therefore the assumption in Proposition 4 Case 2, $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, which is equivalent to $D^{u,\bar{b}_2 \to 0} \neq D^w$, is sufficient, but not necessary, in order to have $\lim_{b_2 \to 0}PoA^{b_2}>1$.
+
+	\begin{comment}
 	Hence, from equation (\ref{eq:x_bar_neq_0}) and Proposition \ref{prop:diff_SC}, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then for all $t \in [0,T]$:
@@
 	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality is equivalent to:
-	$$D^{u,\bar{b}_2 \to \infty} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D - C^w  = 0.$$
+	$$D^{u,\bar{b}_2 \to 0} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D - C^w  = 0.$$
 	In other words, the following three equations together imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
@@
 	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q + \bar{q}(1- s)^2 \right) = 0.$$\\
+	\end{comment}
 \label{remark_6}

### 2018-08-03 PoA.tex
minor edit Theorem 2
avoid saying unecessary assumption

@@
 	Since $2(A^u - A^w) = \bar{b}_1$, in the case when $\bar{b}_1 =0$ we must have $C^u = C^w$.
-Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, which are constants for all $t \in [0,T]$.
+Otherwise, equation (\ref{eq:wt=constant}) implies that $u_t = w_t = (C^u - C^w) / \bar{b}_1 $, are constant for all $t \in [0,T]$.
 Thus, the time derivatives of $u_t$ and $w_t$ should be zero.
@@
 For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$.
-Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is thus an unnecessary assumption.
+Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is therefore a sufficient, but not necessary, assumption.
 For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
-Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is thus an unnecessary assumption.
+Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is therefore a sufficient, but not necessary, assumption.
 This agrees with the conclusion of Remark \ref{remark_6}.

### 2018-08-03 PoA.tex
updated Prop 1 and Corollary 1, moved Corollary 2

@@
     \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
-    \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}\left[(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2\right]&=0,\ \forall t \in [0,T] \\
+    (b^{MFG}-b^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
     s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
@@
 \begin{proof}
-    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), the result is clear.
+    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $c^{MFG}-c^{MKV}=b^{MFG}-b^{MKV}$, the result is clear.
 \end{proof}
@@
 \begin{corollary}
-Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, and $s_T\bar{q}_T(s_T-1)=0$ and at least one of the following holds: $b_2=\bar{b}_2=0$ or $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$
+Assuming (\ref{eq:assumptions}), if furthermore, $s\bar{q}(s-1)=0$, $\bar{b}_1=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
 then $PoA=1$.
 \label{corollary_1}
+\end{corollary}
+
+\begin{corollary}
+	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then from equation (\ref{eq:x_bar_MKV_explicit}), $x^{MKV}_t =0$ for all $t\in[0,T]$, and thus, $PoA=1$.
 \end{corollary}
@@
 \end{equation}
-
-\begin{corollary}
-    Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then $PoA=1$.
-\end{corollary}
-\begin{proof}
-    By equation (\ref{eq:x_bar_MFG_explicit}), $\mathbb{E}(\xi)=0$ implies $\bar{x}^{MFG}_t=0,\ \forall t \in [0,T]$.
-Therefore by Proposition \ref{prop:diff_SC}, $\Delta SC=0$.
-From equation (\ref{eq:v_t}), which we recall is equivalent to equation (\ref{eq:v_t_MKV}), $v_t>0$ which implies $h_{var}>0$.
-Therefore by equation (\ref{eq:SC_MKV_2}), $SC^{MKV}>0$.
-We conclude from equation (\ref{eq:PoA_LQ}) that $PoA=1$.
-\end{proof}
 

### 2018-08-03 PoA.tex
modified Prop 2 and Corollary 1

@@
 \begin{split}
-    \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
-    (b^{MFG}-b^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
+    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
+    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
     s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
@@
 \begin{proof}
-    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $c^{MFG}-c^{MKV}=b^{MFG}-b^{MKV}$, the result is clear.
+    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
 \end{proof}
@@
 \begin{corollary}
-Assuming (\ref{eq:assumptions}), if furthermore, $s\bar{q}(s-1)=0$, $\bar{b}_1=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
+	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
 	then $PoA=1$.

### 2018-08-03 PoA.tex
added remark connection Theorem 2 and prop 1

@@
 Assuming (\ref{eq:assumptions}), if furthermore,
-\begin{equation*}
-\begin{split}
-    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
-    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
-    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
-\end{split}
-\end{equation*}
+\begin{equation}
+    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}=0,\ \forall t \in [0,T] \label{eq:prop_1_1}
+\end{equation}
+\begin{equation}
+    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}=0,\ \forall t \in [0,T]\label{eq:prop_1_2}
+\end{equation}
+\begin{equation}
+    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}=0, \label{eq:prop_1_3}
+\end{equation}
 then $PoA=1$.
@@
 	Assuming (\ref{eq:assumptions}), if the initial condition $\xi$ is such that $\mathbb{E}(\xi)=0$, then from equation (\ref{eq:x_bar_MKV_explicit}), $x^{MKV}_t =0$ for all $t\in[0,T]$, and thus, $PoA=1$.
+	\label{corollary_2}
 \end{corollary}
@@
 \end{proof}
+
+\begin{remark}
+	Assume (\ref{eq:assumptions}) and $\lambda=1$.
+Then Theorem \ref{thm:PoA_equivalent_1} tells us that the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$.
+To see this, assume $PoA=1$.
+Since $\lambda=1$, we have $c^{MFG}=c^{MKV}$ and thus, condition (\ref{eq:prop_1_2}) holds.
+If $\mathbb{E}(\xi)=0$, clearly conditions (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) hold, as noted in Corollary \ref{corollary_2}.
+If $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}.
+Now, if $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}).
+Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}).
+In particular, recall that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
+\end{remark}
 

### 2018-08-03 PoA.tex
added comment about Theorem 2 in flocking example

@@
 \end{equation*}
-They choose the control with two goals in mind: to minimize their kinetic energy put into their control, and to align their velocity with the average velocity of the group.
+Suppose the initial condition is $X_0=1$.
+They choose their control with two goals in mind: to minimize their effort put into their control, and to align their velocity with the average velocity of the group.
 Thus, they consider the cost functions given by:
@@
 \begin{split}
-    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(\bar{q}|x-s\bar{\mu}|^2 +\alpha^2 \right), \\
+    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(|x-\bar{\mu}|^2 +\alpha^2 \right), \\
     g(x,\mu)&=0.
@@
 
-In our general linear quadratic formulation, this is equivalent to taking $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $s=1$, $r=1$, $\bar{r}=0$, and $\bar{s}=0$.
+In our general linear quadratic formulation, this is equivalent to taking $\xi \equiv 1$, $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $\bar{q}=1$, $s=1$, $r=1$, $\bar{r}=0$, $\bar{s}=0$, $q_T=0$, $\bar{q}_T=0$, and $s_T=0$.
 Note that for these values of the parameters, the assumptions of Theorem \ref{th:exist_uniq} and Corollary \ref{corollary_1} are satisfied.
 Therefore, $PoA=1$.
+We also see that $D^u=0=D^w$ and $C^u=0=C^w$, and therefore, Theorem \ref{thm:PoA_equivalent_1} also implies $PoA=1$.
 In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.

### 2018-08-03 PoA.tex
emphasize Theorem 2 in Abstract, Intro, Conclusion

@@
 We illustrate properties of such a price of anarchy on linear quadratic extended mean field games, for which explicit computations are possible.
+A sufficient and necessary condition to have no price of anarchy is presented.
 Various asymptotic behaviors of the price of anarchy are proved for limiting behaviors of the coefficients in the model and numerics are presented.
@@
 In Section \ref{Price_Of_Anarchy}, we define the price of anarchy based on these two problem formulations.
-The class of linear quadratic models is explored in Section \ref{sec:PoA_LQ}, where we provide some theoretical results on the price of anarchy for this class of games, show numerical results, and detail a particular example of flocking.
+The class of linear quadratic models is explored in Section \ref{sec:PoA_LQ}, where we provide some theoretical results on the price of anarchy for this class of games.
+This includes our main result, Theorem \ref{thm:PoA_equivalent_1}, which provides a sufficient and necessary condition to have no price of anarchy.
+In Section \ref{sec:PoA_LQ}, we also show numerical results, and detail a particular example of flocking.
 We conclude in Section \ref{sec:conclusion}.
@@
 We computed the price of anarchy for linear quadratic extended mean field games, for which explicit computations are possible.
-We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollary \ref{corollary_1}), as well as some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity.
+We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1}).
+We also derive some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity.
 The numerics support our theoretical results.

### 2018-08-03 PoA.tex
minor edits

@@
 We shall compute this social cost in the limit $N\to\infty$ when all the players use the distributed control strategies given by the same feedback function $\phi$ identified by solving an optimization problem in the limit $N\to\infty$.
-We take the social cost to be the limit as $N\to\infty$ of $J^{(N)}_\phi$, namely
+We take the social cost to be the limit as $N\to\infty$ of $J^{(N)}_\phi$, namely:
 \begin{equation*}
@@
 \begin{equation*}
-SC(\phi)=\int_0^T<f(t,\,\cdot\,,\mu_t,\phi(t,\,\cdot\,),\nu_t),\mu_t>\,dt \;+\; <g(\,\cdot\,,\mu_T),\mu_T>
+SC(\phi)=\int_0^T<f(t,\,\cdot\,,\mu_t,\phi(t,\,\cdot\,),\nu_t),\mu_t>\,dt \;+\; <g(\,\cdot\,,\mu_T),\mu_T>,
 \end{equation*}
@@
 \end{equation*}
-According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha},\bar{\nu}_t,Y_t)=0$.
+According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,Y_t)=0$.
 Thus, we find the optimal control:
 \begin{equation}
-    \hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)Y_t}{r(t)+\bar{r}(t)},
+    \hat{\alpha}_t=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)Y_t}{r(t)+\bar{r}(t)}.
 \label{eq:MFG_opt_alpha_Pontryagin}
@@
 	\begin{equation}
-	\dot{\bar{\eta}}^{MFG}_t+ \left[ c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MFG}_t)^2+ \left(2b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t)) =0
+	\dot{\bar{\eta}}^{MFG}_t+ \left[ c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MFG}_t)^2+ \left(2b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MFG}_t +q(t)+\bar{q}(t)(1-s(t)) =0,
 	\label{eq:eta_bar_MFG}
@@
 	\begin{equation}
-	\dot{\bar{x}}^{MFG}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MFG}_t \right] \cdot \bar{x}^{MFG}_t
+	\dot{\bar{x}}^{MFG}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MFG}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MFG}_t \right] \cdot \bar{x}^{MFG}_t,
 	\label{eq:x_bar_MFG}
@@
 	\begin{equation}
-	\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)\cdot (\eta^{MFG}_t)^2 + 2b_1(t) \cdot \eta^{MFG}_t+q(t)+\bar{q}(t)=0
+	\dot{\eta}^{MFG}_t+a^{MFG}(t)b_2(t)\cdot (\eta^{MFG}_t)^2 + 2b_1(t) \cdot \eta^{MFG}_t+q(t)+\bar{q}(t)=0,
 	\end{equation}
@@
 \end{itemize}
-where the dot is the standard ODE notation for a derivative. 
+and where the dot is the standard ODE notation for a derivative. 
 And thus, we obtain explicit solutions for $\bar{x}_t^{MFG}$ and $v_t^{MFG}$:
 \begin{IEEEeqnarray}{rCl}
-	\bar{x}^{MFG}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MFG}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MFG}_s\right) ds} \label{eq:x_bar_MFG_explicit} \\ 
+	\bar{x}^{MFG}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MFG}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MFG}_s\right) ds} \label{eq:x_bar_MFG_explicit}, \\ 
 	v^{MFG}_t &=& Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MFG}(s)b_2(s) \cdot \eta^{MFG}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MFG}(u)b_2(u)\eta^{MFG}_u\right] du}ds.
@@
 Since we consider a Hamiltonian that depends on the means of $\bar{\mu}$ and $\bar{\nu}$ instead of the full distributions, the sufficient condition reduces to the following (see section 4 in \cite{carmona_acciaio}):
-$\hat{\alpha}_t=\hat{\alpha}(t,X_t,\bar{\mu},\bar{\nu},Y_t)$ should satisfy:
 \begin{equation*}
@@
 \end{equation*}
-where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
+and where $(\boldsymbol{\tilde{X}},\boldsymbol{\tilde{Y}},\boldsymbol{\tilde{\alpha}})$ denotes an independent copy of $(\boldsymbol{X},\boldsymbol{Y},\boldsymbol{\alpha})$.
 In the present LQ case, the sufficient condition can be used to solve for:
@@
 	\begin{equation}
-	\dot{\bar{\eta}}^{MKV}_t+ \left[ c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MKV}_t)^2+ 2\left(b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2 =0
+	\dot{\bar{\eta}}^{MKV}_t+ \left[ c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \right] \cdot (\bar{\eta}^{MKV}_t)^2+ 2\left(b_1(t)+\bar{b}_1(t) \right) \cdot \bar{\eta}^{MKV}_t +q(t)+\bar{q}(t)(1-s(t))^2 =0,
 	\label{eq:eta_bar_MKV}
@@
 	\begin{equation}
-	\dot{\bar{x}}^{MKV}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MKV}_t \right] \cdot \bar{x}^{MKV}_t
+	\dot{\bar{x}}^{MKV}_t=\left[ b_1(t)+\bar{b}_1(t)+c^{MKV}(t)(b_2(t)+\bar{b}_2(t)) \cdot \bar{\eta}^{MKV}_t \right] \cdot \bar{x}^{MKV}_t,
 	\label{eq:x_bar_MKV}
@@
 	\begin{equation}
-	\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)\cdot (\eta^{MKV}_t)^2 + 2b_1(t) \cdot \eta^{MKV}_t+q(t)+\bar{q}(t)=0
+	\dot{\eta}^{MKV}_t+a^{MKV}(t)b_2(t)\cdot (\eta^{MKV}_t)^2 + 2b_1(t) \cdot \eta^{MKV}_t+q(t)+\bar{q}(t)=0,
 	\end{equation}
@@
 \end{itemize}
-where the dot is the standard ODE notation for a derivative. 
+and where the dot is the standard ODE notation for a derivative. 
 And thus, we obtain explicit solutions for $\bar{x}_t^{MKV}$ and $v_t^{MKV}$:
 \begin{IEEEeqnarray}{rCl}
-	\bar{x}^{MKV}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MKV}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MKV}_s\right) ds} \label{eq:x_bar_MKV_explicit} \\ 
+	\bar{x}^{MKV}_t &=& \mathbb{E}(\xi) e^{ \int_0^t\left( b_1(s)+\bar{b}_1(s)+ \left[ c^{MKV}(s)(b_2(s)+\bar{b}_2(s))\right] \cdot \bar{\eta}^{MKV}_s\right) ds}, \label{eq:x_bar_MKV_explicit} \\ 
 	v^{MKV}_t &=& Var(\xi)e^{\int_0^t 2\left[b_1(s)+a^{MKV}(s)b_2(s) \cdot \eta^{MKV}_s\right]ds}+\sigma^2 \int_0^t e^{2 \int_s^t \left[b_1(u)+a^{MKV}(u)b_2(u)\eta^{MKV}_u\right] du}ds.
@@
 Mean field game models of flocking have been proposed in the literature by Nourian et al \cite{nourian2010synthesis}\cite{nourian2011mean}.
-Here we consider a slightly different formulation as described in Section 3.6.1 of the book \cite{Carmona_book}.
+Here we consider a slightly different formulation as described in Section 3.6.1 of the book of Carmona and Delarue \cite{Carmona_book}.
 A representative bird in the flock controls their velocity, $X_t$, through the drift:
@@
 \end{equation*}
-Suppose the initial condition is $X_0=1$.
+Suppose the initial condition is $X_0=1$ and the volatility is $\sigma=1$.
 They choose their control with two goals in mind: to minimize their effort put into their control, and to align their velocity with the average velocity of the group.
@@
 \begin{split}
-    f(t,x,\mu,\alpha,\nu)&=\frac{1}{2}\left(|x-\bar{\mu}|^2 +\alpha^2 \right), \\
-    g(x,\mu)&=0.
+    f(t,x,\mu,\alpha,\nu)=\frac{1}{2}\left(|x-\bar{\mu}|^2 +\alpha^2 \right), \quad \text{and} \quad g(x,\mu)=0.
 \end{split}
@@
 	\begin{array}{rl}
-		A=&-\frac{1}{2}(a^x+a^{\bar{x}}-b^y-b^{\bar{y}}) \\
-		B=&-(a^y+a^{\bar{y}}) \\
-		C=&-(b^x+b^{\bar{x}}) \\
-		D=&\ c^x+c^{\bar{x}}.
+		A=-\frac{1}{2}(a^x+a^{\bar{x}}-b^y-b^{\bar{y}}), \quad, B=-(a^y+a^{\bar{y}}), \quad C=-(b^x+b^{\bar{x}}),\quad D=\ c^x+c^{\bar{x}}.
 	\end{array}
@@
 	\begin{array}{rl}
-		A=&-\frac{1}{2}(a^x-b^y) \\
-		B=&-a^y \\
-		C=&-b^x \\
-		D=&\ c^x.
+		A=-\frac{1}{2}(a^x-b^y), \quad B=-a^y, \quad C=-b^x, \quad D=\ c^x.
 	\end{array}

### 2018-08-03 PoA.tex
refer to Remark 2 in Remark 6 about lambda for standard MFG
minor edit Theorem 1: refer to SC^MFG, SC^MKV equations directly

@@
 (See Theorem \ref{th:exist_uniq} for assumptions that provide existence and uniqueness.)
+\label{remark_2}
 \end{remark}
@@
 \end{IEEEeqnarray}
-Let $SC^{MFG}:=SC(\phi)$ in which $\phi=\phi(t,x)$ is the feedback function specified by this solution, namely, from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
-\begin{equation*}
-    \phi(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left[a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right]\bar{x}_t^{MFG}.
+Let $SC^{MFG}:=SC(\phi^{MFG})$ in which $\phi^{MFG}=\phi^{MFG}(t,x)$ is the feedback function specified by this solution, namely, from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
+\begin{equation*}
+    \phi^{MFG}(t,x)=a^{MFG}(t)\eta_t^{MFG}x+\left[a^{MFG}(t)(\bar{\eta}_t^{MFG}-\eta_t^{MFG})+b^{MFG}(t)\bar{\eta}_t^{MFG} \right]\bar{x}_t^{MFG}.
 \end{equation*}
 Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
-\begin{equation*}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
+\label{eq:SC_MFG_0}
+\end{equation}
 where we have used the fact that:
 \begin{equation*}
-    \mathbb{E}(\phi(t,X_t))=c^{MFG}(t)\cdot \bar{\eta}_t^{MFG}\bar{x}_t^{MFG}
+    \mathbb{E}(\phi^{MFG}(t,X_t))=c^{MFG}(t)\cdot \bar{\eta}_t^{MFG}\bar{x}_t^{MFG}
 	\qquad 
@@
 	\qquad
-    Var(\phi(t,X_t))=\left(a^{MFG}(t)\eta_t^{MFG} \right)^2 \cdot v^{MFG}_t.
+    Var(\phi^{MFG}(t,X_t))=\left(a^{MFG}(t)\eta_t^{MFG} \right)^2 \cdot v^{MFG}_t.
 \end{equation*}
@@
 \end{IEEEeqnarray}
-Then $SC^{MKV}=SC(\phi)$ where $\phi$ is the feedback function specified by this solution, namely, from equation (\ref{eq:alpha_hat_MKV}), we have:
-\begin{equation*}
-    \phi(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left[a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right]\bar{x}_t^{MKV}.
+Then $SC^{MKV}=SC(\phi^{MKV})$ where $\phi^{MKV}$ is the feedback function specified by this solution, namely, from equation (\ref{eq:alpha_hat_MKV}), we have:
+\begin{equation*}
+    \phi^{MKV}(t,x)=a^{MKV}(t)\eta_t^{MKV}x+\left[a^{MKV}(t)(\bar{\eta}_t^{MKV}-\eta_t^{MKV})+b^{MKV}(t)\bar{\eta}_t^{MKV} \right]\bar{x}_t^{MKV}.
 \end{equation*}
 Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
-\begin{equation*}
+\begin{equation}
 \begin{split}
@@
 \end{split}
-\end{equation*}
+\label{eq:SC_MKV_0}
+\end{equation}
 where we have used the fact that:
 \begin{equation*}
-\mathbb{E}(\phi(t,X_t))=c^{MKV}(t)\cdot \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}
+\mathbb{E}(\phi^{MKV}(t,X_t))=c^{MKV}(t)\cdot \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}
 \qquad 
@@
 \qquad
-Var(\phi(t,X_t))=\left(a^{MKV}(t)\eta_t^{MKV} \right)^2 \cdot v^{MKV}_t.
+Var(\phi^{MKV}(t,X_t))=\left(a^{MKV}(t)\eta_t^{MKV} \right)^2 \cdot v^{MKV}_t.
 \end{equation*}
@@
 Then there exists a unique solution to the LQEMFG problem, and there exists a unique solution to the LQEMKV problem.
-And therefore, $PoA=\frac{SC^{MFG}}{SC^{MKV}}$ where $SC^{MFG}:=SC(\phi)$ for $\phi$ given by the explicit solution constructed in Appendix \ref{appendix_solving_fbsdes}.
+And therefore, $PoA=\frac{SC^{MFG}}{SC^{MKV}}$ where $SC^{MFG}$ and $SC^{MKV}$ are given by equations (\ref{eq:SC_MFG_0}) and (\ref{eq:SC_MKV_0}), respectively.
 \end{theorem}
@@
 Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}).
-In particular, recall that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
+In particular, recall from Remark \ref{remark_2} that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
 \end{remark}

### 2018-08-03 PoA.tex
E(xi) \neq 0 not \neq 1

@@
 If $\mathbb{E}(\xi)=0$, clearly conditions (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) hold, as noted in Corollary \ref{corollary_2}.
-If $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}.
-Now, if $\mathbb{E}(\xi) \neq 1$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}).
+If $\mathbb{E}(\xi) \neq 0$ and $\bar{b}_1=0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ and $C^u=C^w$ which together with $\lambda=1$ imply conditions (\ref{eq:prop_1_1}) and (\ref{eq:prop_1_3}), similarly as Corollary \ref{corollary_1}.
+Now, if $\mathbb{E}(\xi) \neq 0$ and $\bar{b}_1>0$, from Theorem \ref{thm:PoA_equivalent_1}, we have $D^u=D^w$ which implies condition (\ref{eq:prop_1_3}).
 Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}).

### 2018-08-03 PoA.tex
changed remark into Corollary 3, added a remark after Prop 1

@@
 This includes our main result, Theorem \ref{thm:PoA_equivalent_1}, which provides a sufficient and necessary condition to have no price of anarchy.
-In Section \ref{sec:PoA_LQ}, we also show numerical results, and detail a particular example of flocking.
+In Section \ref{sec:PoA_LQ}, we also prove some limiting cases and show numerical results.
 We conclude in Section \ref{sec:conclusion}.
@@
 \end{proof}
+
+\begin{remark}
+	Recall from Remark \ref{remark_2} that in the standard mean field game, $\bar{b}_2=\bar{r}=0$, and thus, $\lambda=1$.
+Although Proposition \ref{eq:lq_prop} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
+\end{remark}
 
@@
 
-\begin{remark}
+\begin{corollary}
 	Assume (\ref{eq:assumptions}) and $\lambda=1$.
-Then Theorem \ref{thm:PoA_equivalent_1} tells us that the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$.
-To see this, assume $PoA=1$.
+Then the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$.
+\label{corollary_3}
+\end{corollary}
+\begin{proof}
+	Assume $PoA=1$.
 Since $\lambda=1$, we have $c^{MFG}=c^{MKV}$ and thus, condition (\ref{eq:prop_1_2}) holds.
@@
 Finally, the condition $B(D)^2+2A^uD-C^u=B(D)^2+2A^wD-C^w=0$ implies $\bar{\eta}^{MKV}_t=w_t=D=\frac{C^u-C^w}{2(A^u-A^2)}=\frac{s\bar{q}(1-s)}{\bar{b}_1}$ and thus, we have condition (\ref{eq:prop_1_1}).
-In particular, recall from Remark \ref{remark_2} that $\lambda=1$ for standard mean field games, where $\bar{b}_2=0$ and $\bar{r}=0$.
-\end{remark}
+\end{proof}
 
@@
 
+\begin{comment}
 \subsection{\textbf{A Particular Example: Flocking}}
@@
 In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.
+\end{comment}
 
@@
 
+\begin{comment}
 \bibitem{nourian2011mean}
@@
   Annual Allerton Conference on}, pages 814--819. IEEE, 2010.
+\end{comment}
 

### 2018-08-04 PoA.tex
moved lambda definition earlier

@@
 
+Also, it will be convenient to denote:
+\begin{equation}
+\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}.
+\label{eq:lambda}
+\end{equation}
+
 \begin{proposition}
@@
 \begin{corollary}
-	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
+	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $\lambda=1$, and $s_T\bar{q}_T(s_T-1)=0$,
 	then $PoA=1$.
@@
 If we denote:
-\begin{equation}
-\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
-\label{eq:lambda}
-\end{equation}
 \begin{equation*}

### 2018-08-04 PoA.tex
minor edit in conclusion

@@
 We computed the price of anarchy for linear quadratic extended mean field games, for which explicit computations are possible.
-We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1}).
+We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1} and Corollary \ref{corollary_3}).
 We also derive some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity.

### 2018-08-04 PoA.tex
minor edits

@@
 Since $\bar{x}_t^{MFG} \neq 0$ for all $t \in [0,T]$, from Proposition \ref{prop:diff_SC} and the continuity of $u_t$ and $w_t$, we deduce that:
-	\begin{equation}
-		PoA = 1 \qquad iff \qquad u_t = w_t, \quad \forall  t \in [0,T].
-	\label{eq:PoA_equivalence_ut=w_t} 
-	\end{equation}
+	\begin{equation*}
+		PoA = 1 \qquad \text{if and only if} \qquad u_t = w_t, \quad \forall  t \in [0,T]. 
+	\end{equation*}
 
@@
 	\end{equation*}
-	and thus,
+	and thus, from equation (\ref{eq:Delta_SC_LQ_new_notation}):
 	\begin{equation*}
@@
 	$$
-	The variance function $v_t^{r}$ is also uniformly bounded over $t \in [0,T]$. We also have $w^{r \to \infty }_0\geq0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence,
+	We also have $w^{r \to \infty }_0 >0$ and $v^{r \to \infty}_t >0$ for $t>0$. Hence, from equation (\ref{eq:SC_MKV_LQ_new_notation}):
 	\begin{equation*}
@@
 	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
-	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$ and thus:
+	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, from equations (\ref{eq:Delta_SC_LQ_new_notation}) and (\ref{eq:SC_MKV_LQ_new_notation}), we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$ and thus:
 	\begin{equation}
@@
 	\end{equation*}
-	and thus,
+	and thus, from equation (\ref{eq:PoA_LQ}):
 	$$ \lim_{b_2 \to \infty} PoA^{b_2} = 1.$$\\
@@
 	\end{equation*}
-	Therefore, we conclude: 
+	Therefore, from equation (\ref{eq:PoA_LQ}), we conclude: 
 	$$ \lim_{b_2 \to \infty} PoA^{b_2} > 1.$$ 

### 2018-08-04 PoA.tex
minor edits

@@
 	$$
-	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta\leq \frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}} e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}},
+	1=b_2\eta^{b_2}_{t^*_{b_2}}-c_\eta\leq \frac{ \frac{C^\eta}{b_2}+D^\eta\frac{\delta^{+,b_2}_\eta}{b_2}-\frac{D^\eta}{r+\bar{r}}c_\eta +\frac{\delta^{-,b_2}_\eta}{b_2^2}c_\eta+\left(-D^\eta\frac{\delta^{-,b_2}_\eta}{b_2} +\frac{D^\eta}{r+\bar{r}}c_\eta\right)e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})} }{ \frac{D^\eta}{r+\bar{r}} -\frac{\delta^{-,b_2}_\eta}{b_2^2} -\frac{D^\eta}{r+\bar{r}} e^{-(\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta)(T-t^*_{b_2})}}.
 	$$
@@
    	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
-	\begin{equation*}
+	\begin{equation}
 	\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = \frac{1}{2} B^{\bar{b}_2 \to 0} \int_0^T \left( (u_t^{\bar{b}_2 \to 0} - w_t^{\bar{b}_2 \to 0}\right)^2 \left (\bar{x}_t^{MFG,\bar{b}_2 \to 0} \right)^2 dt \  > 0.
-	\end{equation*}
-
-	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$.
+	\label{eq:prop_6_bounded_conv}
+	\end{equation}
+
+	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore, the variance $v_t$ also does not depend on $\bar{b}_2$.
 Clearly $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
@@
 We have $0< SC^{MKV, \bar{b}_2 \to 0} < \infty$, and therefore, $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$ if and only if $\lim_{\bar{b}_2 \to 0} \Delta SC^{\bar{b}_2} = 0$.
-Therefore, we have an analogous result as Theorem \ref{thm:PoA_equivalent_1} but for the limiting coefficients $A^u$, $A^w$, $B^{\bar{b}_2 \to 0}$, $C^{u,\bar{b}_2 \to 0}$, $C^w$, $D^{u,\bar{b}_2 \to 0}$, and $D^w$.
-Therefore the assumption in Proposition 4 Case 2, $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, which is equivalent to $D^{u,\bar{b}_2 \to 0} \neq D^w$, is sufficient, but not necessary, in order to have $\lim_{b_2 \to 0}PoA^{b_2}>1$.
+Since we can pass the limit as in equation (\ref{eq:prop_6_bounded_conv}), we have an analogous result as Theorem \ref{thm:PoA_equivalent_1} but for the limiting coefficients $A^u$, $A^w$, $B^{\bar{b}_2 \to 0}$, $C^{u,\bar{b}_2 \to 0}$, $C^w$, $D^{u,\bar{b}_2 \to 0}$, and $D^w$.
+Therefore, the assumption in Proposition 4 Case 2, $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, which is equivalent to $D^{u,\bar{b}_2 \to 0} \neq D^w$, is sufficient, but not necessary, in order to have $\lim_{b_2 \to 0}PoA^{b_2}>1$.
 
@@
 
-	Note that $\eta_t$, and therefore $v_t$, are independent of $\bar{b}_1$. Thus,
+	Note that $\eta_t$, and therefore, $v_t$, are independent of $\bar{b}_1$. Thus,
 	\begin{equation*}

### 2018-08-04 PoA.tex
minor edits

@@
 	Moreover, we have:
-	$$\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0, \quad \lim_{b_2 \to 0}\delta^{-,b_2}_u = 0, \quad \text{and} \quad \lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0.$$
+	$$\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0, \quad \text{and} \quad \lim_{b_2 \to 0}\delta^{-,b_2}_u = 0.$$
 	Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$, $\lim_{b_2 \to 0}u^{b_2}_t = 0.$
@@
 It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$.
-Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
+Hence, from equation (\ref{eq:Delta_SC_LQ_new_notation}) and the bounded convergence theorem, we deduce:
 	\begin{equation*}
@@
    	By the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, we have $D^{u,\bar{b}_2 \to 0} \neq D^{w}$, and thus by continuity, $u^{\bar{b}_2 \to 0}_t\neq w^{\bar{b}_2 \to 0}_t$ on a set of positive Lebesgue measure.
-   	 Thus, from Proposition \ref{prop:diff_SC} and by the bounded convergence theorem, we deduce:
+   	 Thus, by the bounded convergence theorem, we deduce:
 	\begin{equation}
@@
 	\begin{comment}
-	Hence, from equation (\ref{eq:x_bar_neq_0}) and Proposition \ref{prop:diff_SC}, if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then for all $t \in [0,T]$:
+	Hence, from equation (\ref{eq:x_bar_neq_0}) and equation (\ref{eq:Delta_SC_LQ_new_notation}), if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then for all $t \in [0,T]$:
 	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
@@
 
-	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$.
-By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
-	Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.
+	Therefore, by the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$ and $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$.
+Thus, $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty$ and we conclude $\lim_{b_1 \to 0} PoA^{b_1} > 1$.
+The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.
 \end{proof}

### 2018-08-04 PoA.tex
relabelled kappa_3-kappa_6 to kappa_1-kappa_4 in Proposition 4

@@
 		I_2^{b_2} &\leq&  \frac{(b_2+ \bar{b}_2)^3}{r + \bar{r}(1- \bar{s})^2} \cdot 4M^2 e^{2(b_1 + \bar{b}_1) T} \int_{\frac{T}{2}}^{T} \exp\left( - \frac{T(b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot m_u \right) dt \nonumber\\
-		&=& \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon,
+		&=& \kappa_1 (b_2 + \bar{b}_2)^3 e^{- \kappa_2 (b_2 + \bar{b}_2)} \leq \epsilon,
 	\label{eq:I2_b2_infty}
 	\end{IEEEeqnarray}
-	with $\kappa_3: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_4 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
+	with $\kappa_1: = \frac{2 TM^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} >0$ and $\kappa_2 :=  \frac{T  m_u}{r + \bar{r}(1-\bar{s})^2}>0$ are constants independent of $b_2$.
 
@@
 	We derive the following two results which are useful for deriving upper bounds for $J^{b_2}_1$ and $J^{b_2}_2$.
-First, let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
+First, let $\kappa_3 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
 Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, we have:
 	\begin{equation}
-		b_2 \cdot l(b_2,t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa_5 b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
+		b_2 \cdot l(b_2,t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_3} (1 - e^{- \kappa_3 b_2 t}) \leq \frac{1}{\kappa_3}, \quad \forall \  t \in [0,T].
 	\label{eq:l(t)_upper_bound_b2_infinity}
@@
 		&\leq& Var(\xi) e^{2b_1 T}\cdot b_2 e^{- \frac{2 b_2}{r + \bar{r}} m_\eta \cdot t} + \sigma^2 e^{2 b_1 T} b_2 \cdot l(t)  \nonumber \\
-		&\leq& e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right).
+		&\leq& e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_3 b_2 t} + \frac{\sigma^2}{\kappa_3} \right).
 	\end{IEEEeqnarray*}
@@
 	for all $b_2 \geq b_2^{*,J_1}$:
-	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad \text{and} \quad b_2 e^{- \kappa_5 b_2 T} \leq \frac{1}{\kappa_5}.$$
+	$$ (b_2 + \bar{b}_2) w_0^{b_2} \leq c_w + \frac{1}{2} c_w, \quad \text{and} \quad b_2 e^{- \kappa_3 b_2 T} \leq \frac{1}{\kappa_3}.$$
 	Then for all $b_2 \geq b_2^{*,J_1}$:
 	\begin{IEEEeqnarray}{rCl}
-		J^{b_2}_1 &\leq& \frac{q+\bar{q}}{2}  \cdot e^{2b_1 T} \int_0^T \left( Var(\xi) b_2 e^{-\kappa_5 b_2 t} + \frac{\sigma^2}{\kappa_5} \right) dt  \nonumber \\
-		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_5 T \cdot b_2 } + \frac{\sigma^2}{\kappa_5} \right) + \frac{b_2}{2(b_2 + \bar{b}_2)} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
-		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_5}  + \frac{\sigma^2 T}{\kappa_5} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_5} + \frac{\sigma^2}{\kappa_5} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{2} \nonumber \\
+		J^{b_2}_1 &\leq& \frac{q+\bar{q}}{2}  \cdot e^{2b_1 T} \int_0^T \left( Var(\xi) b_2 e^{-\kappa_3 b_2 t} + \frac{\sigma^2}{\kappa_3} \right) dt  \nonumber \\
+		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_3 T \cdot b_2 } + \frac{\sigma^2}{\kappa_3} \right) + \frac{b_2}{2(b_2 + \bar{b}_2)} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
+		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_3}  + \frac{\sigma^2 T}{\kappa_3} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_3} + \frac{\sigma^2}{\kappa_3} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{2} \nonumber \\
 		& =:& M_{J_1}.
@@
 	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
-	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_5 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_5}.$$
-	Thus, together with inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}), and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_6 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
+	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_3 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_3}.$$
+	Thus, together with inequalities (\ref{eq:eta_t_uniform_lower_bound_b2_infinity}), (\ref{eq:ut_wt_upper_bound_b2_infty}), (\ref{eq:l(t)_transformation_b2_infinity}), and (\ref{eq:intgeral_b2_eta_t_bound_b2_infinity}), and for $\kappa_4 := \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})}$, we deduce that:
 	\begin{IEEEeqnarray}{rCl}
-		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_5 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
-		&\leq& 	\kappa_6 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_5}(1- e^{-\kappa_5 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_5 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{l} \nonumber \\
-		&\leq& \frac{\kappa_6}{\kappa_5} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{l}}{2} =: M_{J_2}.
+		J^{b_2}_2 &\leq& \frac{Var(\xi) e^{2b_1 T} }{2 (r+\bar{r})} \left[ \int_0^{\frac{T}{2}} \left(b_2 \eta^{b_2}_t \right)^2 b_2 e^{- \kappa_3 b_2 t} dt  +  \int_{\frac{T}{2}}^{T} (\eta_t^{b_2})^2 b_2^3  e^{ - 2 B^{\eta, b_2} \int_0^{t} \eta_s^{b_2} ds } dt \right]  + \frac{\sigma^2  e^{2 b_1 T}}{2} \int_0^T b_2 \eta_t^{b_2} dt  \nonumber \\
+		&\leq& 	\kappa_4 \left[ \left(\frac{3 c_\eta}{2} \right)^2 \frac{1}{\kappa_3}(1- e^{-\kappa_3 b_2 \frac{T}{2}}) + M^2 \cdot b_2^3 e^{- \kappa_3 b_2 \frac{T}{2}} \cdot \frac{T}{2} \right] + \frac{\sigma^2  e^{2 b_1 T}}{2} M_{l} \nonumber \\
+		&\leq& \frac{\kappa_4}{\kappa_3} \left( \frac{9}{4} c_\eta^2 + \frac{M^2 T}{2} \right) + \frac{\sigma^2  e^{2 b_1 T}  M_{l}}{2} =: M_{J_2}.
 	\label{eq:J2_upper_bound_b2_infinity}

### 2018-08-04 PoA.tex
relabelled c_1 to \zeta and c_3 to \zeta_3, so we dont have any c_# constants

@@
 Let $\epsilon>0$.
-Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$ for $r \geq r^*$.
+Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$ for $r \geq r^*$.
 Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
@@
 	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
-	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }.
+	\leq  \frac{ \zeta + 2 \zeta \sqrt{(A^u)^2 + \zeta^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } }.
 	\end{equation*}
@@
 We have shown that for every $t \in[0,T/2]$,  $\lim_{b_2 \to \infty} h_u(b_2, t)= c_u$ and $\lim_{b_2 \to \infty} h_w(b_2, t)= c_w$.
-Let $c_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, c_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$, we have:
+Let $\zeta_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
+Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$, we have:
 	\begin{equation*}
@@
 Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, we have:
-	$$\max \left\{B^{b_2}, C^{u,b_2}, D^{u,b_2} \right\} \leq B^{b_2 \to \infty} + \epsilon =: c_1, \quad \text{and thus,} \quad
-	\vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\ \forall  \  t \in [0,T].$$
+	$$\max \left\{B^{b_2}, C^{u,b_2}, D^{u,b_2} \right\} \leq B^{b_2 \to \infty} + \epsilon =: \zeta, \quad \text{and thus,} \quad
+	\vert u_t^{b_2} \vert \leq \frac{\zeta + 2 \epsilon \sqrt{(A^u)^2 + \zeta^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + \zeta^2} } } ,\ \forall  \  t \in [0,T].$$
 
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$ for all $\bar{b}_2 \leq \bar{b}^*_2$.
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:\zeta_4$ for all $\bar{b}_2 \leq \bar{b}^*_2$.
 Thus, for all $\bar{b}_2\leq \bar{b}^*_2$ and for every $t \in [0,T]$:
 	\begin{equation*}
-		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
+		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{\zeta_4 + 2 \zeta_4 \sqrt{(A^u)^2 + \zeta_4^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + \zeta_4^2}}}.
 	\end{equation*}

### 2018-08-04 PoA.tex
reduced c_delta_ notations

@@
 	\begin{equation*}
-		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}},
+		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u},
 	\end{equation*}
@@
 		\\
-		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u^{b_2 \to \infty}}  =: c_u.
+		&\xrightarrow[b_2 \to \infty]{} \quad (r + \bar{r}(1-\bar{s})^2) c_{\delta_u}  =: c_u.
 	\end{split}
@@
 	Similarly, for all $t \in [0,T)$:
-	$$\lim_{b_2 \to \infty} h_w(b_2,t)=  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
+	$$\lim_{b_2 \to \infty} h_w(b_2,t)=  (r + \bar{r}(1-\bar{s})^2) c_{\delta_w} =: c_w,\qquad \text{with } \quad c_{\delta_w} := \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
 	and
-	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
+	$$ \lim_{b_2 \to \infty}b_2 \eta_t^{b_2} = (r + \bar{r}) c_{\delta_{\eta}} =: c_\eta, \qquad \text{with} \quad c_{\delta_\eta} := \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$
 
 	Next, we derive a strictly positive uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ over $[0,T]$ and large $b_2$.
-Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \right\}$.
+Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u}, D^{u,b_2 \to \infty} \right\}$.
 Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
 	$$ 
-	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u^{b_2 \to \infty}}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
+	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - \left(-c_{\delta_u}\right) \right\vert, \left\vert D^{u,b_2} - D^{u,b_2\to \infty} \right\vert,  \left\vert \frac{1}{b_2 + \bar{b}_2} \right\vert  \right\} \leq \zeta_1,
 	$$ 
@@
 		h_u(b_2,t) &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
-		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u^{b_2 \to \infty}} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u^{b_2 \to \infty}} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
+		&\geq& \frac{(D^{u,b_2 \to \infty} - \zeta_1 )(c_{\delta_u} - \zeta_1) }{ \zeta_1  (2 c_{\delta_u} + 2 \zeta_1) + (D^{u,b_2 \to \infty} + \zeta_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u>0.
 	\label{eq:ut_uniform_lower_bound_b2_infinity}
@@
 	\end{equation*}
-	Then $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
+	Then $c_{\delta_u}=c_{\delta_w}$ and therefore, $c_u = c_w =: c$. 
 	We want to show that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
@@
 	\begin{split}
-	\frac{D^\eta}{r+\bar{r}}-\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right]\\
+	\frac{D^\eta}{r+\bar{r}}-\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right)\right]\\
 	\leq  \left(-D^\eta\frac{\delta^{-,b_2}_\eta }{b_2}+\frac{D^\eta}{r+\bar{r}}(1+c_\eta) \right) e^{-\left(\delta^{+,b_2}_\eta -\delta^{-,b_2}_\eta\right)(T-t^*_{b_2})}.
@@
 	Since we have
-	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right) =0,$ there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$,
-	$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta^{b_2 \to \infty}_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$
+	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right) =0,$ there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$,
+	$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$
 	and thus returning to inequality (\ref{eq:lemma_1}), for $b_2 \geq \max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4} \}$:
@@
 	\end{equation}
-	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta^{b_2 \to \infty}}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
-	$$\frac{c_{\delta_\eta^{b_2 \to \infty}}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta^{b_2 \to \infty}}}{2}, \quad \text{and} \quad c_{\delta_\eta^{b_2 \to \infty}} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta^{b_2 \to \infty}}.$$
+	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
+	$$\frac{c_{\delta_\eta}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta}}{2}, \quad \text{and} \quad c_{\delta_\eta} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta}.$$
 	Returning to inequality (\ref{eq:lemma_2}), for $b_2 \geq b_2^{*,l}:=\max \{b_2^{*,1},b_2^{*,2},b_2^{*,3},b_2^{*,4},b_2^{*,5}\}$:
-	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(3 (r+\bar{r})c_{\delta_\eta^{b_2 \to \infty}}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left(5c_\eta+2 \right).$$
+	$$ b_2(T-t^*_{b_2})\leq \frac{1}{c_{\delta_\eta}} \ln \left(3 (r+\bar{r})c_{\delta_\eta}+2(1+c_\eta) \right)=\frac{1}{c_{\delta_\eta}} \ln \left(5c_\eta+2 \right).$$
 	Finally, for $b_2 \geq b_2^{*,l}$:
@@
 	\int_0^T b_2 \eta^{b_2}_t dt=\int_0^{t^*_{b_2}} b_2 \eta^{b_2}_t dt+\int_{t^*_{b_2}}^T b_2 \eta^{b_2}_t dt \leq t^*_{b_2}(c_\eta+1)+b_2 (T-t^*_{b_2})D^\eta \\
-	\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta^{b_2 \to \infty}}} \ln \left( 5c_\eta+2 \right)=:M^l.
+	\leq T(c_\eta+1)+\frac{D^\eta}{c_{\delta_\eta}} \ln \left( 5c_\eta+2 \right)=:M^l.
 	\end{split}
@@
 	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
-	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
+	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u},
 	\
-	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
+	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w},$$
 	and, for all $t \in [0,T)$:
@@
 	\begin{array}{l}
-	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
-	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2)^{\frac{3}{2}} u^{\bar{b}_2}_t = (r + \bar{r}(1-\bar{s})^2) c_{\delta_u} =: c_u, \\
+	\lim_{\bar{b}_2 \to \infty}(b_2 + \bar{b}_2) w_t^{\bar{b}_2} = (r + \bar{r}(1-\bar{s}^2) ) c_{\delta_w} =: c_w.
 	\end{array}
@@
 
-	\hspace{-7mm} Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$.
-Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
-	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1.
+	\hspace{-7mm} Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u}, \  c_{\delta_w} \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
+	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1.
 $$
@@
 	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
-	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1}.
+	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u} + 2 \zeta_1)}{ c_{\delta_u} - \zeta_1}.
 	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
@@
 	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} }
-	\geq  \frac{\zeta_2 \left(c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1\right)}{ \zeta_1 \left(2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1\right) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
+	\geq  \frac{\zeta_2 \left(c_{\delta_u} - \zeta_1\right)}{ \zeta_1 \left(2 c_{\delta_u} + 2 \zeta_1\right) + \zeta_2 / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
 	\label{eq:ut_lower_bound_b2_bar_infty}
@@
 Let $\zeta_3 := c_u / 2$.
-Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, from equation (\ref{eq:riccati_ut_sol_deriv}), there exists $\bar{b}_2^{*,0} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,0}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, from equation (\ref{eq:riccati_ut_sol_deriv}), there exists $\bar{b}_2^{*,inc} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,inc}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
@@
 	\end{IEEEeqnarray*}
-	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,0}$ we have:
+	Thus, for any $\bar{b}_2 \geq \bar{b}_2^{*,inc}$ we have:
 	\begin{IEEEeqnarray}{rCl}

### 2018-08-04 PoA.tex
minor edits

@@
 \end{IEEEeqnarray}
-Let $SC^{MFG}:=SC(\phi^{MFG})$ in which $\phi^{MFG}=\phi^{MFG}(t,x)$ is the feedback function specified by this solution, namely, from equation (\ref{eq:MFG_opt_alpha_Y_expY}) we have:
+Let $SC^{MFG}:=SC(\phi^{MFG})$ in which $\phi^{MFG}=\phi^{MFG}(t,x)$ is the feedback function specified by this solution, namely, from equation (\ref{eq:MFG_opt_alpha_Y_expY}), we have:
 \begin{equation*}
@@
 	For the sake of simplicity, denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$.
-From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
+From equation (\ref{eq:riccati_ut_sol}), for all $t \in[0,T)$, we deduce:
 	\begin{equation*}
@@
 	\end{equation*}
-	Thus, for any $t \in [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$, we have:
+	Thus, for any $t \in [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$:
 	$$
@@
 Let $\zeta_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$, we have:
+Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$:
 	\begin{equation*}
@@
 First, let $\kappa_3 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$.
-Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, we have:
+Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$:
 	\begin{equation}
@@
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
-Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$, we have:
+Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$:
 	$$\max \left\{B^{b_2}, C^{u,b_2}, D^{u,b_2} \right\} \leq B^{b_2 \to \infty} + \epsilon =: \zeta, \quad \text{and thus,} \quad
@@
 
-	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
+	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for all $t \in [0,T]$:
 	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
@@
 
-	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$, we have:
+	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$ and $\lim_{\bar{b}_1 \to \infty}B (D^{w})^2 + 2 A^{w,\bar{b}_1} D^{w} - C^{w}=-\infty$,   from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,lower}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,lower}$:
 	$$\max \left\{ \left|\frac{u^{\bar{b}_1}_0}{\bar{b}_1}-\frac{1}{B} \right|,\left|\frac{w^{\bar{b}_1}_{T/2}}{\bar{b}_1}-\frac{2}{B} \right| \right\} \leq \frac{1}{4B},$$
@@
 We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
-Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
+Clearly we have for all $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
 Next, we show that the three sequences are uniformly bounded.
 Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
-There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$.
-Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
+There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for all $b_1 \leq b_1^*$.
+Then for all $b_1 \leq b_1^*$ and $t\in[0,T]$:
 	\begin{equation*}

### 2018-08-04 PoA.tex
minor edits

@@
 Let $\epsilon>0$.
-Then there exists $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$ for $r \geq r^*$.
+Then there exists a $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$ for $r \geq r^*$.
 Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
@@
 Let $\zeta_1 :=\frac{1}{2} \min \left\{ c_{\delta_u}, D^{u,b_2 \to \infty} \right\}$.
-Then there exists $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
+Then there exists a $b_2^{*,u,lower}>0$ such that for all $b_2 \geq b_2^{*,u,lower}$:
 	$$ 
@@
 	\end{IEEEeqnarray}
-	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$ and all $t\in[0,T]$:
+	Then, by the same technique in inequality (\ref{eq:ut_uniform_lower_bound_b2_infinity}), there exists a $b_2^{*,\eta, lower} > 0$ and $m_\eta >0$ such that for all $b_2 \geq b_2^{*,\eta,lower}$ and all $t\in[0,T]$:
 	\begin{equation}
@@
 	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
-	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing.
+	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists a $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing.
 	Therefore,
@@
 	\end{equation*}
-	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
+	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists a $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
 	\begin{equation}
@@
 	$ \zeta_2: = \min \left\{ \frac{c}{2},  \frac{1}{2} e^{-T(b_1+\bar{b}_2)} \sqrt{\epsilon c} \right\}.$
-	Then there exists $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
+	Then there exists a $b_2^{*,I_1}  \geq b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
 	\begin{equation*}
@@
 	\end{equation*}
-	Hence, there exists $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
+	Hence, there exists a $b_2^{*,I_2} \geq \max \{ b_2^{*,upper}, b_2^{*,u,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$:
 	\begin{IEEEeqnarray}{rCl}
@@
 Let $\zeta_3 = \ln(2) \frac{r + \bar{r}(1-\bar{s})^2}{T (c_u + \vert c_u - c_w \vert / 4)} - \bar{b}_2$.
-Then, there exists $b_2^{*,num} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$:
+Then, there exists a $b_2^{*,num} \geq \max \{ b_2^{*,basic}, \zeta_3 \}$ such that for all $b_2 \geq b_2^{*,num}$ and all $s \in [0, T/2]$:
 	\begin{equation*}
@@
 	\end{IEEEeqnarray*}
-	We will make use of Lemma \ref{lemma:int_b2_eta_t}, which appears below, and states that there exists $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$:
+	We will make use of Lemma \ref{lemma:int_b2_eta_t}, which appears below, and states that there exists a $b_2^{*,l}>0$ and a constant $M_{l}$ independent of $b_2$ such that for all $b_2 \geq b_2^{*,l}$:
 	\begin{equation}
@@
 	\end{equation}
-	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
+	Since $\lim_{b_2 \to \infty} b_2 \eta_t^{b_2}= c_\eta$ for all $t \in [0, T/2]$, there exists a $b_2^{*,J_2} \geq \max\{ b_2^{*,l}, b_2^{*,basic} \}$ such that for all $b_2 \geq b_2^{*,J_2}$:
 	$$ b_2 \eta_t  \leq c_\eta + \frac{1}{2} c_\eta, \quad \forall \  t \in [0,T/2],  \quad \text{and} \quad b_2^{3} e^{-\kappa_3 b_2 \frac{T}{2} } \leq \frac{1}{\kappa_3}.$$
@@
 \begin{lemma}
-	Assume Assumption \ref{assumption}. There exists a $b_2^{*,l}>0$ and $M^l>0$, such that for all $b_2 \geq b_2^{*,l}$:
+	Assume Assumption \ref{assumption}. There exists a $b_2^{*,l}>0$ and a $M^l>0$, such that for all $b_2 \geq b_2^{*,l}$:
 	$$\int_0^T b_2 \eta^{b_2}_t dt \leq M^l.$$
@@
 \begin{proof}
-	Since $\lim_{b_2 \to \infty}b_2\eta^{b_2}_t= c_\eta,$ there exists $b_2^{*,1}$ such that for $b_2 \geq b_2^{*,1}$, we have
+	Since $\lim_{b_2 \to \infty}b_2\eta^{b_2}_t= c_\eta,$ there exists a $b_2^{*,1}>0$ such that for $b_2 \geq b_2^{*,1}$, we have
 	$b_2\eta^{b_2}_0 \leq c_\eta+\frac{1}{2}.$
-	Clearly there exists $b_2^{*,2}$ such that for $b_2 \geq b_2^{*,2}$:
+	Clearly there exists a $b_2^{*,2}>0$ such that for $b_2 \geq b_2^{*,2}$:
 	$$b_2\eta^{b_2}_T=b_2D^\eta=b_2(q_T+\bar{q}_T)\geq c_\eta+2.$$
@@
 	Since we have
-	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right) =0,$ there exists $b_2^{*,4}$ such that for $b_2 \geq b_2^{*,4}$,
+	$\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2^2}=\lim_{b_2 \to \infty}\frac{C^\eta}{b_2}=\lim_{b_2 \to \infty}\left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right) =0,$ there exists a $b_2^{*,4}>0$ such that for $b_2 \geq b_2^{*,4}$,
 	$\left[\frac{\delta^{-,b_2}_\eta}{b_2^2}(1+c_\eta)+\frac{C^\eta}{b_2}+D^\eta \left(\frac{\delta^{+,b_2}_\eta}{b_2}-c_{\delta_\eta} \right)\right] \leq \frac{D^\eta}{2(r+\bar{r})},$
@@
 	\end{equation}
-	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists $b_2^{*,5}$ such that for $b_2 \geq b_2^{*,5}$:
+	Since $\lim_{b_2 \to \infty}\frac{\delta^{+,b_2}_\eta}{b_2}=c_{\delta_\eta}=-\lim_{b_2 \to \infty}\frac{\delta^{-,b_2}_\eta}{b_2}$, there exists a $b_2^{*,5}>0$ such that for $b_2 \geq b_2^{*,5}$:
 	$$\frac{c_{\delta_\eta}}{2} \leq \frac{-\delta^{-,b_2}_\eta}{b_2} \leq \frac{3c_{\delta_\eta}}{2}, \quad \text{and} \quad c_{\delta_\eta} \leq \frac{\delta^{+,b_2}_\eta-\delta^{-,b_2}_\eta}{b_2} \leq 3c_{\delta_\eta}.$$
@@
 	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for small $b_2$.
-Indeed, for any fixed $\epsilon >0$ there exists $b_2^* >0$ such that for any $b_2 \leq b_2^*$:
+Indeed, for any fixed $\epsilon >0$ there exists a $b_2^* >0$ such that for any $b_2 \leq b_2^*$:
 	$$\max \left\{B^{b_2}, C^{u,b_2}, D^{u,b_2} \right\} \leq B^{b_2 \to \infty} + \epsilon =: \zeta, \quad \text{and thus,} \quad
@@
 
-	\hspace{-7mm} Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u}, \  c_{\delta_w} \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
+	\hspace{-7mm} Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u}, \  c_{\delta_w} \right\}$. Then there exists a $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
 	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1.
@@
 	\end{equation}
-	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
+	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists a $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
 	\begin{equation}
@@
 Let $\zeta_3 := c_u / 2$.
-Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, from equation (\ref{eq:riccati_ut_sol_deriv}), there exists $\bar{b}_2^{*,inc} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,inc}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
+Because $ \lim_{\bar{b}_2 \to \infty} B^{\bar{b}_2} (D^{u,\bar{b}_2})^2+ 2 A^{u} D^{u,\bar{b}_2} - C^{u,\bar{b}_2} >0$, from equation (\ref{eq:riccati_ut_sol_deriv}), there exists a $\bar{b}_2^{*,inc} \geq \bar{b}_2^{*,upper}$ so that for all $\bar{b}_2 \geq \bar{b}_2^{*,inc}$, the functions $s \mapsto u_s^{\bar{b}_2}$ and $s \mapsto w_s^{\bar{b}_2}$ are increasing, and so that for all $s \in [0, T/2]$:
 	\begin{IEEEeqnarray*}{c}
@@
 	with $\kappa_1: = \frac{\mathbb{E}(\xi)^2 [\zeta_3^2 + (c_w + \zeta_3)^2 ] e^{2(b_1 + \bar{b}_1) \frac{T}{2}} }{2 (c_u - \zeta_3)}$ and $ \kappa_2 := \frac{(c_u - \zeta_3)T}{r+ \bar{r}(1-\bar{s})^2}$ are independent of $\bar{b}_2$.
-Therefore, there exists $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
+Therefore, there exists a $\bar{b}_2^{*,I_1} \geq \bar{b}_2^{*,0}$ such that for $\bar{b}_2 \geq \bar{b}_2^{*,I_1}$, we have $I_1^{\bar{b}_1} \leq \epsilon$.
 
@@
 	\end{equation*}
-	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$:
+	Thus, similar to inequality (\ref{eq:I2_b2_infty}), there exists a $\bar{b}_2^{*,I_2} \geq \bar{b}_2^{*,upper}$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,I_2}$:
 	\begin{equation*}
@@
 	\end{equation}
-	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
+	From equation (\ref{eq:riccati_ut_sol_deriv}), and together with equation (\ref{eq:ut_wt_lim_b1_infty}), there exists a $b_1^{*,upper} >0$ such that for all $b_1 \geq b_1^{*,upper}$, the functions $t \mapsto u_t^{b_1}$ and $t \mapsto w_t^{b_1}$ are decreasing and such that:
 	$$ \sup_{0 \leq t \leq T} \left\{ g_u(b_1, t), g_w(b_1,t)\right\} \leq \max \left\{ g_u(b_1, 0), g_w(b_1,0) \right\} \leq 3.$$
 
-	Fix $\epsilon>0$. There exists $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3T/4]$,
+	Fix $\epsilon>0$. There exists a $b^{*,I_1}_1\geq b_1^{*,upper}$ such that for all $b_1 \geq b_1^{*,I_1} $, and for all $t \in [0, 3T/4]$,
 	\begin{equation*}
@@
 	\end{IEEEeqnarray*}
-	Therefore, there exists $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
+	Therefore, there exists a $b_1^{*} \geq b_1^{*,I_1}$, so that for $b_1 \geq b_1^*$, we have $I^{b_1}_2 \leq \epsilon$. Hence, for all $b_1 \geq b_1^{*}$,
 	$$ 	\frac{\Delta SC^{b_1}}{SC^{MKV,b_1}} \leq \frac{I^{b_1}_1 + I^{b_1}_2 }{g_w(b_1,0)} \leq \frac{3}{5} (\kappa_1 \epsilon^2 + \epsilon).$$
@@
 	\end{equation*}
-	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
+	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = -2b_1 < 0$, there exists a $\bar{b}_1^{*}\geq\bar{b}_1^{*,lower}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$.
 Returning to inequality (\ref{eq:prop_7_case_4_numerator}), and using inequality (\ref{eq:lower_bound_u_w}) we have for $\bar{b}_1 \geq \bar{b}^*_1$:
@@
 Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$.
-There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for all $b_1 \leq b_1^*$.
+There exists a $b_1^*>0$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for all $b_1 \leq b_1^*$.
 Then for all $b_1 \leq b_1^*$ and $t\in[0,T]$:

### 2018-08-05 PoA.tex
minor changes

@@
 \usepackage[retainorgcmds]{IEEEtrantools}
+%\usepackage[fleqn]{amsmath}
 
@@
 Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
-\begin{equation}
-\begin{split}
-    SC^{MFG}=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2\\
-    &+\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2\right]v_t^{MFG}dt\\
-    &+\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt\Big],
-\end{split}
-\label{eq:SC_MFG_0}
-\end{equation}
+\begin{IEEEeqnarray}{rCl}
+    SC^{MFG}&=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MFG}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2 \nonumber \\
+    && \quad +\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MFG}(t)\eta_t^{MFG})^2\right]v_t^{MFG}dt
+    \label{eq:SC_MFG_0} \\
+    && \quad +\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MFG}(t)\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt\Big], \nonumber
+\end{IEEEeqnarray}
 where we have used the fact that:
@@
 \begin{array}{lcl}
-    dY_t&=&-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\[8pt]
+    dY_t&=&-\left[\partial_x H(t,X_t,\bar{\mu}_t,\alpha_t,\bar{\nu}_t,Y_t)+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}H(t,\tilde{X}_t,\bar{\mu}_t,\tilde{\alpha}_t,\bar{\nu}_t,\tilde{Y}_t) \right] \right]dt+Z_tdW_t \\[5pt]
     Y_T&=&\partial_xg(X_T, \cL(X_T))+\tilde{\mathbb{E}} \left[\partial_{\bar{\mu}}g(\tilde{X}_T,\cL(X_T))(X_T) \right],
@@
 \begin{split}
-        dX_t=&\left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\
+        dX_t=&\left[b_1(t)X_t+\bar{b}_1(t) \mathbb{E}X_t+a^{MKV}(t)b_2(t)Y_t+(b^{MKV}(t)b_2(t)+c^{MKV}(t)\bar{b}_2(t))\mathbb{E}Y_t\right]dt+\sigma dW_t \\[5pt]
         dY_t=&-\left[(q(t)+\bar{q}(t))X_t+s(t)\bar{q}(t)(s(t)-2)\mathbb{E}X_t+b_1(t)Y_t+\bar{b}_1(t)\mathbb{E}Y_t\right]dt +Z_t dW_t,
@@
 Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
-\begin{equation}
-\begin{split}
-    SC^{MKV}=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2\\
-    &+\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2\right]v_t^{MKV}dt \\
-    &+\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2\right](\bar{x}_t^{MKV})^2dt\Big],
-\end{split}
-\label{eq:SC_MKV_0}
-\end{equation}
+\begin{IEEEeqnarray}{rCl}
+    SC^{MKV}&=&\frac{1}{2}\Big[(q_T+\bar{q}_T)v_T^{MKV}+(q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MKV})^2 \nonumber \\
+    && \quad +\int_0^T \left[q(t)+\bar{q}(t)+(r(t)+\bar{r}(t))(a^{MKV}(t)\eta_t^{MKV})^2\right]v_t^{MKV}dt \label{eq:SC_MKV_0} \\
+    && \quad +\int_0^T\left[q(t)+\bar{q}(t)(1-s(t))^2+(r(t)+\bar{r}(t)(1-\bar{s}(t))^2)(c^{MKV}(t)\bar{\eta}_t^{MKV})^2\right](\bar{x}_t^{MKV})^2dt\Big], \nonumber
+\end{IEEEeqnarray}
 where we have used the fact that:
@@
 \begin{split}
-    (a^{MFG}(t),b^{MFG}(t),c^{MFG}(t))&=(a^{MFG},b^{MFG},c^{MFG}) \\
-    (a^{MKV}(t) b^{MKV}(t),c^{MKV}(t))&=(a^{MKV},b^{MKV},c^{MKV}).
-\end{split}
-\end{equation*}
+    \left(a^{MFG}(t), b^{MFG}(t), c^{MFG}(t) \right)&=\left(a^{MFG}, b^{MFG}, c^{MFG} \right) \\
+    \left(a^{MKV}(t), b^{MKV}(t), c^{MKV}(t) \right)&=\left(a^{MKV}, b^{MKV}, c^{MKV}\right).
+\end{split}
+\end{equation*}
+Also, it will be convenient to denote:
+\begin{equation}
+\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},  \qquad u_t := \lambda \bar{\eta}_t^{MFG}, \qquad w_t := \bar{\eta}_t^{MKV}.
+\label{eq:lambda}
+\end{equation}
 
@@
 
-To compute the price of anarchy, it is useful to make the following observations:
-\begin{equation*}
-\begin{split}
-    a^{MFG}&=a^{MKV}=:a, \\
-    \eta_t^{MFG}&=\eta_t^{MKV}=:\eta_t, \\
-    v_t^{MFG}&=v_t^{MKV}=:v_t.
-\end{split}
-\end{equation*}
-
-Also, it will be convenient to denote:
-\begin{equation}
-\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}.
-\label{eq:lambda}
-\end{equation}
-
 \begin{proposition}
 Assuming (\ref{eq:assumptions}), if furthermore,
-\begin{equation}
-    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}=0,\ \forall t \in [0,T] \label{eq:prop_1_1}
-\end{equation}
-\begin{equation}
-    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}=0,\ \forall t \in [0,T]\label{eq:prop_1_2}
-\end{equation}
-\begin{equation}
-    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}=0, \label{eq:prop_1_3}
-\end{equation}
+\begin{IEEEeqnarray}{rCl}
+    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right] \cdot \bar{x}_t^{MKV} &=& 0,\quad \forall \  t \in [0,T] 
+    \label{eq:prop_1_1} \\ [3pt]
+    \left(c^{MFG}-c^{MKV} \right) \cdot \bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=& 0,\quad \forall \  t \in [0,T] 
+    \label{eq:prop_1_2} \\ [3pt]
+    s_T\bar{q}_T(s_T-1) \cdot \bar{x}_T^{MKV}&=& 0, 
+    \label{eq:prop_1_3}
+\end{IEEEeqnarray}
 then $PoA=1$.
-\label{eq:lq_prop}
+\label{prop: lq_subtract_FBSDEs}
 \end{proposition}
@@
 	Recall from Remark \ref{remark_2} that in the standard mean field game, $\bar{b}_2=\bar{r}=0$, and thus, $\lambda=1$.
-Although Proposition \ref{eq:lq_prop} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
+Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
+We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in case of separated Hamiltonian.
+See also Remark 6.1 in \cite{nourian2013nash} for a flocking model.
 \end{remark}
 
+%\begin{remark}
+%	The only result similar to Proposition \ref{prop: lq_subtract_FBSDEs} that we are aware of is Remark 6.1 in \cite{nourian2013nash}.
+%\end{remark}
+
 \begin{corollary}
-	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $\lambda=1$, and $s_T\bar{q}_T(s_T-1)=0$,
+	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $s_T\bar{q}_T(s_T-1)=0$, and $c^{MFG} = c^{MKV}$,
 	then $PoA=1$.
@@
 
-\begin{remark}
-The only result similar to Proposition \ref{eq:lq_prop} that we are aware of is Remark 6.1 in \cite{nourian2013nash}.
-\end{remark}
-
-Using the above observations, we can rewrite:
-\begin{equation}
-\begin{split}
-    SC^{MFG}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MFG})^2+\frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_tdt\\
-    &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MFG}\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt,
-\end{split}
-\label{eq:SC_MFG_1}
-\end{equation}
-and:
-\begin{equation}
-\begin{split}
-    SC^{MKV}=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MKV})^2+ \frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_tdt \\
-    &+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MKV}\bar{\eta}_t^{MKV})^2\right)](\bar{x}_t^{MKV})^2dt.
-\end{split}
+To compute the price of anarchy, it is useful to make the following observations:
+\begin{equation*}
+a^{MFG}=a^{MKV}=:a, \qquad
+\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
+v_t^{MFG}=v_t^{MKV}=:v_t,
+\end{equation*}
+we can rewrite:
+\begin{IEEEeqnarray}{rCl}
+    SC^{MFG} &=& \frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MFG})^2+\frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right] v_t dt \nonumber \\
+    && +\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MFG}\bar{\eta}_t^{MFG})^2\right](\bar{x}_t^{MFG})^2dt,
+    \label{eq:SC_MFG_1} \\ [8pt]
+    SC^{MKV}&=&\frac{1}{2}(q_T+\bar{q}_T)v_T+\frac{1}{2}\left(q_T+\bar{q}_T(1-s_T)^2\right)(\bar{x}_T^{MKV})^2+ \frac{1}{2}\int_0^T \left[q+\bar{q}+(r+\bar{r})(a\eta_t)^2\right]v_t dt \nonumber \\
+    &&+\frac{1}{2}\int_0^T\left[q+\bar{q}(1-s)^2+(r+\bar{r}(1-\bar{s})^2)(c^{MKV}\bar{\eta}_t^{MKV})^2\right)](\bar{x}_t^{MKV})^2dt.
 	\label{eq:SC_MKV_1}
-\end{equation}
-
+\end{IEEEeqnarray}
 In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems.
@@
 Using equation (\ref{eq:eta_bar_MFG}), we have:
-\begin{equation*}
-\begin{split}
+\begin{align*}
 &\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
-&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \right].\\
-\end{split}
-\end{equation*}
-Then we use integration by parts:
-\begin{equation*}
-\begin{split}
-= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
-& + \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg]. \\
-\end{split}
-\end{equation*}
-Then by using equation (\ref{eq:x_bar_MFG}), we have:
-\begin{equation*}
-\begin{split}
-= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
+&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \right],
+\end{align*}
+then we use the integration by parts for the first term in the bracket:
+\begin{align*}
+ =  -\frac{ 1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[  & \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2 -\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2 -2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t \cdot \dot{\bar{x}}^{MFG}_t dt \\
+& + \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg],
+\end{align*}
+and together with equation (\ref{eq:x_bar_MFG}) yields:
+\begin{align*}
+= 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ & \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
 &+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
-\end{split}
-\end{equation*}
+\end{align*}
 Finally, we solve:
-\begin{equation*}
-\begin{split}
-\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
-&+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
-\end{split}
-\end{equation*}
+\begin{align*}
+\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 + \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt}{c^{MFG}(b_2 + \bar{b}_2)}.
+\end{align*}
 If we denote:
@@
 \end{equation*}
-and use the terminal condition for $\bar{\eta}^{MFG}_T$ (see equation (\ref{eq:eta_bar_MFG})), then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
-\begin{equation}
-\begin{split}
-SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
-& + \frac{1}{2} \lambda \left[ \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right] + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
-\end{split}
-\label{eq:SC_MFG_2}
-\end{equation}
-Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
-\begin{equation*}
-\begin{split}
-\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
-&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg].
-\end{split}
-\end{equation*}
-Using the terminal condition for $\bar{\eta}^{MKV}_T$ (see equation (\ref{eq:eta_bar_MKV})), equation (\ref{eq:SC_MKV_1}) can be rewritten as:
+and use the terminal condition for $\bar{\eta}^{MFG}_T$, 
+%(see equation (\ref{eq:eta_bar_MFG})), 
+then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
+\begin{IEEEeqnarray}{rCl}
+SC^{MFG} & = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \label{eq:SC_MFG_2} \\
+& + & \frac{1}{2} \lambda \left[ \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right] + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2. \nonumber
+\end{IEEEeqnarray}
+%Repeating the same calculation for $\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt$, 
+%(using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), 
+%we arrive at:
+%\begin{equation*}
+%\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{\bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2
+%	+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt}{c^{MKV}(b_2 + \bar{b}_2)} 
+%\end{equation*}
+%Using the terminal condition for $\bar{\eta}^{MKV}_T$,
+% (see equation (\ref{eq:eta_bar_MKV})), 
+Similarly, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
 \begin{equation}
@@
 \begin{equation}
-	\Delta \bar{\eta}_t := \lambda \bar{\eta}_t^{MFG} - \bar{\eta}_t^{MKV} .
+	\Delta \bar{\eta}_t := \lambda \bar{\eta}_t^{MFG} - \bar{\eta}_t^{MKV} = u_t - w_t.
 \label{eq:delta_eta}
@@
 		\begin{array}{rcl}
-			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
+			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\ [8pt]
 			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
@@
 
-It will be useful for us to note here the scalar Riccati equations associated with $u_t := \lambda \bar{\eta}_t^{MFG}$, $w_t := \bar{\eta}_t^{MKV}$ and $\eta_t$:
+It will be useful for us to note here the scalar Riccati equations associated with $u_t = \lambda \bar{\eta}_t^{MFG}$, $w_t = \bar{\eta}_t^{MKV}$ and $\eta_t$:
     \begin{IEEEeqnarray}{lLLLClClCl}
@@
 	Assume (\ref{eq:assumptions}) and $\lambda=1$.
-Then the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{eq:lq_prop} is also a necessary condition to have $PoA=1$.
+Then the sufficient condition (equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3})) from Proposition \ref{prop: lq_subtract_FBSDEs} is also a necessary condition to have $PoA=1$.
 \label{corollary_3}
@@
 We computed the price of anarchy for linear quadratic extended mean field games, for which explicit computations are possible.
-We identify a large class of models for which $PoA=1$ (see Proposition \ref{eq:lq_prop} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1} and Corollary \ref{corollary_3}).
+We identify a large class of models for which $PoA=1$ (see Proposition \ref{prop: lq_subtract_FBSDEs} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1} and Corollary \ref{corollary_3}).
 We also derive some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity.

### 2018-08-05 PoA.tex
minor edits, moved observation earlier because it is used in Prop 1

@@
 \end{equation}
+and to make the following observations:
+\begin{equation}
+a^{MFG}=a^{MKV}=:a, \qquad
+\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
+v_t^{MFG}=v_t^{MKV}=:v_t.
+\label{eq:observations}
+\end{equation}
 
@@
 \begin{proof}
-    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
+    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $a^{MFG}=a^{MKV}$ and $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
 \end{proof}
@@
 Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
-We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in case of separated Hamiltonian.
-See also Remark 6.1 in \cite{nourian2013nash} for a flocking model.
+We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in the case of a separated Hamiltonian.
+See also Remark 6.1 in \cite{nourian2013nash}, where it is noted that the mean field game and control of McKean-Vlasov type problems are the same for a particular model of flocking.
 \end{remark}
@@
 
-To compute the price of anarchy, it is useful to make the following observations:
-\begin{equation*}
-a^{MFG}=a^{MKV}=:a, \qquad
-\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
-v_t^{MFG}=v_t^{MKV}=:v_t,
-\end{equation*}
-we can rewrite:
+Using the observations in equation (\ref{eq:observations}), we can rewrite:
 \begin{IEEEeqnarray}{rCl}
@@
 \end{align*}
-then we use the integration by parts for the first term in the bracket:
+then using integration by parts for the first term in the bracket:
 \begin{align*}
@@
 \end{align*}
-Finally, we solve:
+Finally, we arrive at:
 \begin{align*}

### 2018-08-05 PoA.tex
updating numerical results

@@
 For results involving only interaction through the controls, we set $\bar{b}_1=0$, $\bar{q}=0$, and $\bar{q}_T=0$.
-Figures \ref{fig:b1_b1bar}-\ref{fig:r_rbar} show the price of anarchy as we vary one parameter at a time for each of three interaction cases: full interaction (i.e.
+Figures \ref{fig:r_rbar}-\ref{fig:b1bar} show the price of anarchy as we vary one parameter at a time for each of three interaction cases: full interaction (i.e.
 through the states and the controls), interaction only through the states, and interaction only through the controls.
-
-\begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps}
-    \end{subfigure}
-    \caption{PoA as we vary $b_1$ (left) and $\bar{b}_1$ (right).}
-    \label{fig:b1_b1bar}
-\end{figure}
-\begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_b2.eps}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_even_more_steps_b2bar_2.eps}
-    \end{subfigure}
-    \caption{PoA as we vary $b_2$ (left) and $\bar{b}_2$ (right).}
-    \label{fig:b2_b2bar}
-\end{figure}
-\begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_q.eps}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar.eps}
-    \end{subfigure}
-    \caption{PoA as we vary $q$ (left) and $q_T$ (right).}
-    \label{fig:q_q_T}
-\end{figure}
-\begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_q_T.eps}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar_T.eps}
-    \end{subfigure}
-    \caption{PoA as we vary $\bar{q}$ (left) and $\bar{q}_T$ (right).}
-    \label{fig:qbar_qbar_T}
-\end{figure}
+The results show various limiting behaviors, such as some of the cases proved in the previous section.
+
 \begin{figure}[!htb]
@@
 	\end{subfigure}
-    \caption{PoA as we vary $r$ (left) and $\bar{r}$ (right).}
+	\caption{$PoA$ as we vary $r$ (left) and $\bar{r}$ (right).}
 	\label{fig:r_rbar}
 \end{figure}
-
-The results show various limiting behaviors, such as some of the cases proved in the previous section.
-In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
-Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}.
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_final_b2_0.eps}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_final_b2_large.eps}
+    \end{subfigure}
+    \caption{$PoA$ as we vary $b_2$.}
+    \label{fig:b2}
+\end{figure}
+\begin{figure}[!htb]
+	\centering
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_final_b2bar_0.eps}
+	\end{subfigure}
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_half_even_more_steps_b2bar_2.eps}
+	\end{subfigure}
+	\caption{$PoA$ as we vary $\bar{b}_2$.}
+	\label{fig:b2bar}
+\end{figure}
+\begin{figure}[!htb]
+	\centering
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_final_b1_0.eps}
+	\end{subfigure}
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
+	\end{subfigure}
+	\caption{$PoA$ as we vary $b_1$.}
+	\label{fig:b1}
+\end{figure}
+\begin{figure}[!htb]
+	\centering
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_final_b1bar_0.eps}
+	\end{subfigure}
+	\begin{subfigure}{.45\textwidth}
+		\includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps} %ToDo (code is running)
+	\end{subfigure}
+	\caption{$PoA$ as we vary $\bar{b}_1$.}
+	\label{fig:b1bar}
+\end{figure}
+
+Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
+Propositions \ref{prop:b2_to_infty} and \ref{prop:b2_to_0} are confirmed in Figure \ref{fig:b2}.
+In the case of full interaction, we have $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ and we see that $\lim_{b_2 \to \infty}PoA= 1$.
+In the cases of interaction only through the states or interaction only through the controls, this condition is not satisfied, and we see that $\lim_{b_2 \to \infty}PoA> 1$.
 For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
 When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$.
-For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$.
-Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is therefore a sufficient, but not necessary, assumption.
-For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
+For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
 Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is therefore a sufficient, but not necessary, assumption.
 This agrees with the conclusion of Remark \ref{remark_6}.
-Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
+In Figures \ref{fig:b1} and \ref{fig:b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
+The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
 

### 2018-08-05 PoA.tex
minor edit in conclusion (adding reference to Props 3-7

@@
 In the case of full interaction, we have $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ and we see that $\lim_{b_2 \to \infty}PoA= 1$.
-In the cases of interaction only through the states or interaction only through the controls, this condition is not satisfied, and we see that $\lim_{b_2 \to \infty}PoA> 1$.
+In the cases of interaction only through the states or interaction only through the controls, $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}\neq \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, and we see that $\lim_{b_2 \to \infty}PoA> 1$.
 For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
@@
 We identify a large class of models for which $PoA=1$ (see Proposition \ref{prop: lq_subtract_FBSDEs} and Corollaries \ref{corollary_1} and \ref{corollary_2}), as well as giving a sufficient and necessary condition to have $PoA=1$ (see Theorem \ref{thm:PoA_equivalent_1} and Corollary \ref{corollary_3}).
-We also derive some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity.
+We also derive some limiting cases where $PoA \rightarrow 1$ as certain parameters tend to zero or to infinity (see Propositions \ref{prop:r_bar_r}-\ref{prop:b1_b1bar}).
 The numerics support our theoretical results.

### 2018-08-06 PoA.tex
editing numerical results, removed comments

@@
 \usepackage[retainorgcmds]{IEEEtrantools}
-%\usepackage[fleqn]{amsmath}
 
@@
 \end{remark}
-
-%\begin{remark}
-%	The only result similar to Proposition \ref{prop: lq_subtract_FBSDEs} that we are aware of is Remark 6.1 in \cite{nourian2013nash}.
-%\end{remark}
 
@@
 and use the terminal condition for $\bar{\eta}^{MFG}_T$,  
-%(see equation (\ref{eq:eta_bar_MFG})), 
 then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
@@
 \end{IEEEeqnarray}
-%Repeating the same calculation for $\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt$, 
-%(using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), 
-%we arrive at:
-%\begin{equation*}
-%\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{\bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2
-%	+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt}{c^{MKV}(b_2 + \bar{b}_2)} 
-%\end{equation*}
-%Using the terminal condition for $\bar{\eta}^{MKV}_T$,
-% (see equation (\ref{eq:eta_bar_MKV})), 
 Similarly, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
@@
 	\end{itemize}
-	\begin{comment}
-	Namely, $PoA = 1$ if and only if the following two or three conditions hold true:
-	\begin{equation*}
-	\left\{
-	\begin{array}{rcl}
-	\displaystyle \lambda \cdot (q_T + \bar{q}_T(1-s_T) )  &=& q_T + \bar{q}_T (1- s_T)^2\\
-	\displaystyle \lambda \cdot (q+ \bar{q}(1-s)) &=& (q + \bar{q}(1-s)^2) + \bar{b}_1 \cdot (q_T + \bar{q}_T (1 - s_T)^2) 
-	\end{array}
-	\right.
-	\end{equation*}
-	where $\lambda = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})}$, and in the case when $\bar{b}_1 > 0$, there is an additional condition:
-	$$ \frac{(b_2+ \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} ( q_T + \bar{q}_T(1-s_T)^2 )^2 - 2 (b_1 + \bar{b}_1) ( q_T + \bar{q}_T(1-s_T)^2 )  - ( q + \bar{q}(1-s)^2 ) = 0. $$
-	\end{comment}
 	\label{thm:PoA_equivalent_1}
@@
 	Similarly we also have $B (D^{w})^2 + 2 A^w D^w - C^w = 0$.
-
-	%By replacing $(A^u,B, C^u, D^u)$ and $(A^w, B, C^w, D^w)$ with their explicit expressions, we obtain an equivalent condition for $PoA = 1$ in term of the coefficients of the linear quadratic model.
 
@@
 
-% proposition r to infty
 \begin{proposition}
@@
 
-% proposition b_2 to \infty
 \begin{proposition}
@@
 
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	% Case 1: c_u = c_w
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
 	\textbf{Case 1:} Assume:
@@
 
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	% case 2: c_u \neq c_w
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 	\textbf{Case 2:} Assume:
@@
 
-%proposition b_2 \to 0
 \begin{proposition}
@@
 
-% proposition b2 bar infinity
 \begin{proposition}
@@
 Therefore, the assumption in Proposition 4 Case 2, $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$, which is equivalent to $D^{u,\bar{b}_2 \to 0} \neq D^w$, is sufficient, but not necessary, in order to have $\lim_{b_2 \to 0}PoA^{b_2}>1$.
-
-	\begin{comment}
-	Hence, from equation (\ref{eq:x_bar_neq_0}) and equation (\ref{eq:Delta_SC_LQ_new_notation}), if $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$, then for all $t \in [0,T]$:
-	$$u_t^{\bar{b}_2 \to 0} = w_t^{\bar{b}_2 \to 0}.$$
-	From equation (\ref{eq:riccati_limiting_u}) and an analogous Riccati equation for $w_t^{\bar{b}_2 \to 0}$, the above equality is equivalent to:
-	$$D^{u,\bar{b}_2 \to 0} = D^w=:D \quad \text{and} \quad B^{\bar{b}_2 \to 0} D^2 + 2 A^{u}D - C^{u,\bar{b}_2 \to 0} = B^{\bar{b}_2 \to 0} D^2 + 2 A^{w} D - C^w  = 0.$$
-	In other words, the following three equations together imply $\lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2 } =1$:
-	$$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} = \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)},
-	\qquad
-	 \bar{b}_1 \frac{q_T + \bar{q}_T(1-s_T)^2}{q + \bar{q}(1-s)^2} =  \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot \frac{q + \bar{q}(1-s)}{q + \bar{q}(1-s)^2}-1,
-	$$
-	and
-	$$ \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \left(q_T + \bar{q}_T(1- s_T)^2 \right)^2 - 2 (b_1 + \bar{b}_1) \left(q_T + \bar{q}_T(1- s_T)^2 \right) - \left(q + \bar{q}(1- s)^2 \right) = 0.$$\\
-	\end{comment}
 \label{remark_6}
@@
 
-% proposition b1 and b1 bar
 \begin{proposition}\label{prop:b1_b1bar}
@@
 \subsection{\textbf{Numerical Results}}
-The solutions to the problems we have considered are given by the formulas derived in Appendix \ref{appendix_solving_fbsdes}, which are explicit up to evaluating integrals.
+The price of anarchy for the class of linear quadratic extended mean field games that we consider is given by the ratio of the two quantities given by equations (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}), which are explicit, up to evaluating integrals.
 Using the simple rectangle rule to estimate integrals, we numerically compute the price of anarchy when the coefficients are time-independent, non-negative, and satisfy Assumption \ref{assumption}.
@@
 	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
+		\includegraphics[scale=0.5]{PoA_final_b1_large.eps}
 	\end{subfigure}
@@
 	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps} %ToDo (code is running)
+		\includegraphics[scale=0.5]{PoA_final_b1bar_large.eps}
 	\end{subfigure}
@@
 In the case of full interaction, we have $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ and we see that $\lim_{b_2 \to \infty}PoA= 1$.
-In the cases of interaction only through the states or interaction only through the controls, $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}\neq \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, and we see that $\lim_{b_2 \to \infty}PoA> 1$.
+In the cases of interaction only through the states or interaction only through the controls, then $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}\neq \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, and we see that $\lim_{b_2 \to \infty}PoA> 1$, confirming Proposition \ref{prop:b2_to_infty}.
 For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
@@
 The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
-
-\begin{comment}
-\subsection{\textbf{A Particular Example: Flocking}}
-Mean field game models of flocking have been proposed in the literature by Nourian et al \cite{nourian2010synthesis}\cite{nourian2011mean}.
-Here we consider a slightly different formulation as described in Section 3.6.1 of the book of Carmona and Delarue \cite{Carmona_book}.
-A representative bird in the flock controls their velocity, $X_t$, through the drift:
-\begin{equation*}
-    b(t,x,\mu,\alpha,\nu)=\alpha.
-\end{equation*}
-Suppose the initial condition is $X_0=1$ and the volatility is $\sigma=1$.
-They choose their control with two goals in mind: to minimize their effort put into their control, and to align their velocity with the average velocity of the group.
-Thus, they consider the cost functions given by:
-\begin{equation*}
-\begin{split}
-    f(t,x,\mu,\alpha,\nu)=\frac{1}{2}\left(|x-\bar{\mu}|^2 +\alpha^2 \right), \quad \text{and} \quad g(x,\mu)=0.
-\end{split}
-\end{equation*}
-
-In our general linear quadratic formulation, this is equivalent to taking $\xi \equiv 1$, $b_1=0$, $\bar{b}_1=0$, $b_2=1$, $\bar{b}_2=0$, $q=0$, $\bar{q}=1$, $s=1$, $r=1$, $\bar{r}=0$, $\bar{s}=0$, $q_T=0$, $\bar{q}_T=0$, and $s_T=0$.
-Note that for these values of the parameters, the assumptions of Theorem \ref{th:exist_uniq} and Corollary \ref{corollary_1} are satisfied.
-Therefore, $PoA=1$.
-We also see that $D^u=0=D^w$ and $C^u=0=C^w$, and therefore, Theorem \ref{thm:PoA_equivalent_1} also implies $PoA=1$.
-In fact, if we took the state space to be $\mathbb{R}^d$ instead of $\mathbb{R}$, the result would still hold.
-\end{comment}
+Thus, the numerical computations confirm the results presented in Propositions \ref{prop:r_bar_r}-\ref{prop:b1_b1bar}.
 
@@
 
-\begin{comment}
-\bibitem{nourian2011mean}
-M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
-\newblock Mean field analysis of controlled {C}ucker-{S}male type flocking:
-Linear analysis and perturbation equations.
-\newblock {\em IFAC Proceedings Volumes}, 44(1):4471--4476, 2011.
-
-\bibitem{nourian2010synthesis}
-M.~Nourian, P.~E. Caines, and R.~P. Malham{\'e}.
-\newblock Synthesis of {C}ucker-{S}male type flocking via mean field stochastic
-  control theory: {N}ash equilibria.
-\newblock In {\em Communication, Control, and Computing (Allerton), 2010 48th
-  Annual Allerton Conference on}, pages 814--819. IEEE, 2010.
-\end{comment}
-
 \bibitem{nourian2013nash}

### 2018-08-06 PoA.tex
referee report major pt 5

--- 2018-08-05 PoA.tex
@@
 \end{equation}
-and to make the following observations:
-\begin{equation}
-a^{MFG}=a^{MKV}=:a, \qquad
-\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
-v_t^{MFG}=v_t^{MKV}=:v_t.
-\label{eq:observations}
-\end{equation}
 
@@
 \begin{proof}
-    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $a^{MFG}=a^{MKV}$ and $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
+    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
 \end{proof}
@@
 Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
-We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in the case of a separated Hamiltonian.
-See also Remark 6.1 in \cite{nourian2013nash}, where it is noted that the mean field game and control of McKean-Vlasov type problems are the same for a particular model of flocking.
+We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in case of separated Hamiltonian.
+See also Remark 6.1 in \cite{nourian2013nash} for a flocking model.
 \end{remark}
@@
 
-Using the observations in equation (\ref{eq:observations}), we can rewrite:
+To compute the price of anarchy, it is useful to make the following observations:
+\begin{equation*}
+a^{MFG}=a^{MKV}=:a, \qquad
+\eta_t^{MFG} = \eta_t^{MKV}=:\eta_t, \qquad
+v_t^{MFG}=v_t^{MKV}=:v_t,
+\end{equation*}
+we can rewrite:
 \begin{IEEEeqnarray}{rCl}
@@
 \end{align*}
-then using integration by parts for the first term in the bracket:
+then we use the integration by parts for the first term in the bracket:
 \begin{align*}
@@
 \end{align*}
-Finally, we arrive at:
+Finally, we solve:
 \begin{align*}
@@
 		&& \quad + \frac{q_T+\bar{q}_T}{2} \cdot e^{2b_1 T} \left( Var(\xi) b_2 e^{-\kappa_3 T \cdot b_2 } + \frac{\sigma^2}{\kappa_3} \right) + \frac{b_2}{2(b_2 + \bar{b}_2)} (\mathbb{E}(\xi))^2 \cdot (b_2 + \bar{b}_2) w_0^{b_2}\nonumber \\
-		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_3}  + \frac{\sigma^2 T}{\kappa_3} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_3} + \frac{\sigma^2}{\kappa_3} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{2} \nonumber \\
+		&\leq & \frac{(q+\bar{q}) e^{2b_1 T} }{2}\left[ \frac{Var(\xi)}{\kappa_3}  + \frac{\sigma^2 T}{\kappa_3} \right] + \frac{(q_T+\bar{q}_T) e^{2b_1 T}}{2} \left(  \frac{Var(\xi)}{\kappa_3} + \frac{\sigma^2}{\kappa_3} \right)  + \frac{3 c_w (\mathbb{E}(\xi))^2 }{4} \nonumber \\
 		& =:& M_{J_1}.
@@
 For results involving only interaction through the controls, we set $\bar{b}_1=0$, $\bar{q}=0$, and $\bar{q}_T=0$.
-Figures \ref{fig:r_rbar}-\ref{fig:b1bar} show the price of anarchy as we vary one parameter at a time for each of three interaction cases: full interaction (i.e.
+Figures \ref{fig:b1_b1bar}-\ref{fig:r_rbar} show the price of anarchy as we vary one parameter at a time for each of three interaction cases: full interaction (i.e.
 through the states and the controls), interaction only through the states, and interaction only through the controls.
-The results show various limiting behaviors, such as some of the cases proved in the previous section.
-
+
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps}
+    \end{subfigure}
+    \caption{PoA as we vary $b_1$ (left) and $\bar{b}_1$ (right).}
+    \label{fig:b1_b1bar}
+\end{figure}
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_b2.eps}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_even_more_steps_b2bar_2.eps}
+    \end{subfigure}
+    \caption{PoA as we vary $b_2$ (left) and $\bar{b}_2$ (right).}
+    \label{fig:b2_b2bar}
+\end{figure}
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_q.eps}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar.eps}
+    \end{subfigure}
+    \caption{PoA as we vary $q$ (left) and $q_T$ (right).}
+    \label{fig:q_q_T}
+\end{figure}
+\begin{figure}[!htb]
+    \centering
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_q_T.eps}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+        \includegraphics[scale=0.5]{PoA_half_more_steps_qbar_T.eps}
+    \end{subfigure}
+    \caption{PoA as we vary $\bar{q}$ (left) and $\bar{q}_T$ (right).}
+    \label{fig:qbar_qbar_T}
+\end{figure}
 \begin{figure}[!htb]
@@
     \end{subfigure}
-	\caption{$PoA$ as we vary $r$ (left) and $\bar{r}$ (right).}
+    \caption{PoA as we vary $r$ (left) and $\bar{r}$ (right).}
     \label{fig:r_rbar}
 \end{figure}
-\begin{figure}[!htb]
-    \centering
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_final_b2_0.eps}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_final_b2_large.eps}
-    \end{subfigure}
-    \caption{$PoA$ as we vary $b_2$.}
-    \label{fig:b2}
-\end{figure}
-\begin{figure}[!htb]
-	\centering
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_final_b2bar_0.eps}
-	\end{subfigure}
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_half_even_more_steps_b2bar_2.eps}
-	\end{subfigure}
-	\caption{$PoA$ as we vary $\bar{b}_2$.}
-	\label{fig:b2bar}
-\end{figure}
-\begin{figure}[!htb]
-	\centering
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_final_b1_0.eps}
-	\end{subfigure}
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_half_more_steps_b1_2.eps}
-	\end{subfigure}
-	\caption{$PoA$ as we vary $b_1$.}
-	\label{fig:b1}
-\end{figure}
-\begin{figure}[!htb]
-	\centering
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_final_b1bar_0.eps}
-	\end{subfigure}
-	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_half_more_steps_b1bar.eps} %ToDo (code is running)
-	\end{subfigure}
-	\caption{$PoA$ as we vary $\bar{b}_1$.}
-	\label{fig:b1bar}
-\end{figure}
-
-Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
-Propositions \ref{prop:b2_to_infty} and \ref{prop:b2_to_0} are confirmed in Figure \ref{fig:b2}.
-In the case of full interaction, we have $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ and we see that $\lim_{b_2 \to \infty}PoA= 1$.
-In the cases of interaction only through the states or interaction only through the controls, this condition is not satisfied, and we see that $\lim_{b_2 \to \infty}PoA> 1$.
+
+The results show various limiting behaviors, such as some of the cases proved in the previous section.
+In Figure \ref{fig:b1_b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
+The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
+Propositions \ref{prop:b2_to_infty}-\ref{prop:b2bar} are confirmed in Figure \ref{fig:b2_b2bar}.
 For Proposition \ref{prop:b2_to_0}, when there is only interaction through the states, then $\bar{b}_2=0$ and we see that $\lim_{b_2 \to 0}PoA= 1$.
 When there is full interaction or only interaction through the controls, then $\bar{b}_2>0$ and we see that $\lim_{b_2 \to 0}PoA>1$.
-For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
+For Proposition \ref{prop:b2_to_infty}, we see that $\lim_{b_2 \to \infty}PoA= 1$.
+Note that the condition $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})}= \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$ is  not satisfied for the cases of interaction only through the states or interaction only through the controls, and is therefore a sufficient, but not necessary, assumption.
+For Proposition \ref{prop:b2bar}, Figure \ref{fig:b2_b2bar} confirms that $\lim_{\bar{b}_2 \to 0}PoA>1$ and $\lim_{\bar{b}_2 \to \infty}PoA= 1$.
 Note that the condition $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ is not satisfied for the full interaction case, and is therefore a sufficient, but not necessary, assumption.
 This agrees with the conclusion of Remark \ref{remark_6}.
-In Figures \ref{fig:b1} and \ref{fig:b1bar}, we note that Proposition \ref{prop:b1_b1bar} is confirmed.
-The condition $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2$ is satisfied for all three interaction cases and we see that $\lim_{b_1 \to 0}PoA >1$, $\lim_{\bar{b}_1 \to 0}PoA>1$, $\lim_{b_1 \to \infty}PoA = 1$, and $\lim_{\bar{b}_1 \to \infty}PoA = \infty$.
+Figure \ref{fig:r_rbar} confirms as in Proposition \ref{prop:r_bar_r} that $\lim_{r \to \infty}PoA= 1$ and $\lim_{\bar{r} \to \infty}PoA= 1$.
 

### 2018-08-06 PoA_response_to_referee.tex
referee report major pt 5

@@
 If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
-	\item
+	\item We specify that the convergence in Proposition 3 is of pointwise convergence for every $t \in [0,T]$ when $r \to \infty$.
+In order to apply the bounded convergence theorem correctly, we provide an explicit uniform upper bound for $u_t^{r}$, which is independent of $t$ and $r$ for all $t \in [0,T]$ and for all $r$ large enough.
+	This uniform upper bound is obtained by maximizing the numerator and minimizing the denominator of explicit formula (35).
+Indeed, from equation (36), we notice that the solution to Riccati equation is monotone over $[0,T]$, so that all we have to do remains to bound $u_0^r$ and $u_T^r$ from above independently with $r$.
 	\item

### 2018-08-06 PoA_response_to_referee.tex
referee report major pt 6

--- 2018-07-31 PoA_response_to_referee.tex
@@
 \documentclass[]{article}
+\usepackage{amssymb}
 
@@
 There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
-	\item We have made many modifications in the computation of $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt$ on pages 10-11 to make it much more readable.
+
+	\item We have made many modifications in the computation of
+	 $$\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt$$
+	  on pages 10-11 to make it much more readable.
 Whereas we previously dropped the superscripts $MFG$ and $MKV$ to address both simultaneously, we now show the computation fully for the $MFG$ case.
@@
 We believe pages 10-11 should be much easier to follow in their present form.
+
 	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$.
@@
 If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
-	\item
-	\item
+
+	\item We specify that the convergence in Proposition 3 is of pointwise convergence for every $t \in [0,T]$ when $r \to \infty$.
+In order to apply the bounded convergence theorem, we provide an explicit uniform upper-bound for $\vert u_t^{r} \vert $.
+This uniform upper-bound is independent of $t$ and $r$ when $r$ is large enough, and it is obtained by maximizing the numerator and minimizing the denominator of equation (35).
+Indeed, from equation (36), we notice that the solution to Riccati equation is monotone over $[0,T]$.
+By consequence, the idea is to bound $\vert u_0^r \vert$ and $\vert u_T^r \vert$ from above independent of $r$.
+The uniform upper-bound in Proposition 3 is written in a more concise manner.
+
+	\item Yes, in this specific example, there should be an additional constant term, depending on $t$, in the power of exponential when we tried to determine the equivalence of $\bar{x}_t^{MFG}$ when $b_2 \to \infty$.
+
+	In this asymptotic regime, we observe that both $\Delta SC^{b2}$ and $SC^{MKV,b2}$ tend towards $0$.
+By consequence, in order to compute the limit of $PoA$, we need to compare the rate of convergence in terms of $b_2$ for these two quantities.
+We notice that the use of big $\mathcal{O}$ creates a lot of ambiguities and imprecisions in Proposition 4, especially when we need to keep trace of the quantity $c_u -c_w$ inside some big $\mathcal{O}$s along the proof.
+Hence, we decide to rewrite the whole proof in the scope of $\delta-\epsilon$ approach.
+The idea used in the new proof of Proposition 4 remains exactly the same as in its previous version, however, the techniques involved are more subtle.
+In short, we provide some explicit upper-bounds and lower-bounds for $(b_2 + \bar{b}_2) \Delta SC^{b_2}$ and $b_2 \cdot SC^{MKV,b_2}$ in order to justify the limit of $PoA$ when $b_2 \to \infty$.
+
+	More precisely, in the case when $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s}) } = \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, or equivalently $c_u = c_w$, we show that for any given $\epsilon > 0$, there exists $b_2^*>0$ such that for all $b_2 \geq b_2^{*}$, we have the inequalities $(b_2 + \bar{b}_2) \Delta SC^{b_2} \leq 2\epsilon$ and
+	$(b_2 + \bar{b}_2) SC^{MKV,b_2} \geq constant > 0$ (see equations (47)-(49).) Thus we conclude that $PoA \to 1$ when $b_2 \to \infty$.
+
+	In the case when $c_u \neq c_w$, we show that there exists $b_2^{*,case2}>0$ such that we can bound from below $(b_2 + \bar{b_2}) \Delta SC^{b_2}$ by a constant $c_{num}>0$ independent of $b_2$ (see equation (50)).
+Meanwhile, we can also bound from above the term $b_2 \cdot SC^{MKV,b_2}$ (see equation (51)-(57) and Lemma 1) by:
+	$$ b_2 \cdot SC^{MKV,b_2} = J_1 + J_2 \leq M_{J_1} + M_{J_2}.$$
+	Hence, the Price of Anarchy can be bounded from below by a constant strictly greater than $1$ and independent of $b_2$ in the asymptotic regime $b_2 \to \infty$.
+
 	\item We added a sentence at the beginning of section 2.4 on page 27 stating that we use a simple rectangular integration rule to numerically compute integrals.

### 2018-08-06 PoA_response_to_referee.tex
referee report major pt 6 & pt 4

@@
 This was overlooked by the authors.
-If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
+%If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
+
+	We replace Corollary 3 by another result Theorem 2 in which we provide an equivalent condition for $PoA = 1$.
+We also propose a corollary afterwards (see Corollary 3 in the new version) and point out its connection to Proposition 1.
+This new Corollary 3 actually indicates that for the standard mean field games, there is no price of anarchy if and only if the FBSDE systems (4) and (12) are identical to one another.
 

### 2018-08-06 PoA_response_to_referee.tex
editing respone to referee

--- 2018-08-06 PoA_response_to_referee.tex
@@
-\documentclass[]{article}
+\documentclass[11pt]{article}
+\usepackage{fullpage}
+\usepackage{amssymb}
 
-%opening
 \title{Response to Referee}
@@
 	\item This was a good suggestion.
-We have added equations (3)-(7) on page 7, and equations (9)-(13) on page 8, and we refer to these equations often.
-In the same vein we have added equations (26)-(29) on pages 13-14, which are used frequently in Propositions 3-7.
-	\item Since the Hamiltonian depends on the scalars $\bar{\mu}$ and $\bar{\nu}$, instead of the full measures, the derivative in the measure argument greatly simplifies.
-On page 8 line 6, we refer to section 4 in [5], where they write what this condition should be in the linear quadratic case.
-On page 8 lines 7 and 8, the derivative is a standard derivative and does not need explaining further.
-There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
-	\item We have made many modifications in the computation of $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt$ on pages 10-11 to make it much more readable.
-Whereas we previously dropped the superscripts $MFG$ and $MKV$ to address both simultaneously, we now show the computation fully for the $MFG$ case.
-Then after the computation, we state on page 11 line -5: `Repeating the calculation for $\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2dt$...
-we arrive at...' and we provide the result for the $MKV$ case.
+We have added equations (5)-(9) on page 7, and equations (13)-(17) on page 9, and we refer to these equations often.
+In the same vein we have added equations (41)-(44) on page 15, which are used frequently in Propositions 3-7.
+	\item There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
+Since the Hamiltonian depends on the scalars $\bar{\mu}$ and $\bar{\nu}$, instead of the full measures, the derivative in the measure argument greatly simplifies.
+On page 8 lines 10-12, we refer to section 4 in [5], where they write what this condition should be in the linear quadratic case.
+On page 8 lines 13 and 15, the derivative is a standard derivative and does not need explaining further.
+	\item We have made many modifications in the computation of
+	 $$\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt$$
+	  on pages 11-12 to make it much more readable.
+Whereas we previously dropped the superscripts $MFG$ and $MKV$ to address both problems simultaneously, we now show the computation fully for the $MFG$ case.
+Since the computation can be done in the exact same way for the $MKV$ case, we omit it.
+
 	  We now only use the notation introduced thus far, instead of mixing in the notation from the appendix, which could cause confusion.
-We also take the suggestion from the reviewer of explicitly writing the end result of our computation.
+We also take the suggestion from the reviewer of explicitly writing the end result of the computation, which is given by page 12 line 2.
 Also, we now give an explanation for each step of the calculation.
-Finally, we separated the equations in the former equation (7) and give more explanation for how they are derived.
-They are now equations (18) and (19) in the final version.
+Finally, we separated the equations in the former equation (7).
+They are now equations (27) and (28) in the final version, and they should be easy to follow now that the above computation is more clear.
 And yes, there should not have been a $t$ in $h_{var}$.
-We believe pages 10-11 should be much easier to follow in their present form.
-	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$.
-This was overlooked by the authors.
-If we were to rewrite Corollary 3 with the correct condition to have $(A^u,B^u,C^u,D^u)=(A^w,B^w,C^w,D^w)$, it would not be substantially different from Corollary 1 and thus, we dropped Corollary 3.
-	\item We specify that the convergence in Proposition 3 is of pointwise convergence for every $t \in [0,T]$ when $r \to \infty$.
-In order to apply the bounded convergence theorem correctly, we provide an explicit uniform upper bound for $u_t^{r}$, which is independent of $t$ and $r$ for all $t \in [0,T]$ and for all $r$ large enough.
-	This uniform upper bound is obtained by maximizing the numerator and minimizing the denominator of explicit formula (35).
-Indeed, from equation (36), we notice that the solution to Riccati equation is monotone over $[0,T]$, so that all we have to do remains to bound $u_0^r$ and $u_T^r$ from above independently with $r$.
-	\item
-	\item We added a sentence at the beginning of section 2.4 on page 27 stating that we use a simple rectangular integration rule to numerically compute integrals.
+Pages 11-12 should be much easier to follow in their present form.
+
+	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$. This was overlooked by the authors.
+
+	We replace Corollary 3 by another result, Theorem 2, which provides a necessary and sufficient condition to have $PoA = 1$.
+We also propose a corollary afterwards (see Corollary 3 in the new version) and point out its connection to Proposition 1.
+This new Corollary 3 indicates that for the standard mean field game setting, the sufficient conditions in Proposition 1 are also necessary to have $PoA=1$.
+
+	\item In Proposition 3, we specify that the limits as $r \to \infty$ are pointwise for every $t \in [0,T]$.
+In order to apply the bounded convergence theorem, we provide an explicit uniform upper-bound for $\vert u_t^{r} \vert $ for all $t\in[0,T]$ and $r\geq r^*$.
+This uniform upper-bound is obtained by upper-bounding the numerator and lower-bounding the denominator of equation (36).
+Similar techniques are used throughout Propositions 3-7 to provide uniform bounds for any time that we use the bounded convergence theorem.
+
+	\item Yes, the use of big $\mathcal{O}$ created a lot of ambiguities and imprecisions in Proposition 4.
+Hence, we decide to rewrite the whole proof using a $\delta-\epsilon$ approach.
+The main ideas used in the new proof of Proposition 4 remain exactly the same as in its previous version.
+However, the techniques involved are more subtle.
+In short, we provide some explicit upper-bounds and lower-bounds for $(b_2 + \bar{b}_2) \Delta SC^{b_2}$ and $b_2 \cdot SC^{MKV,b_2}$ in order to justify the limit of $PoA$ when $b_2 \to \infty$.
+
+	More precisely, in the case when $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s}) } = \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, or equivalently $c_u = c_w$, we show that for any given $\epsilon > 0$, there exists $b_2^*>0$ such that for all $b_2 \geq b_2^{*}$, we have the inequalities $(b_2 + \bar{b}_2) \Delta SC^{b_2} \leq 2\epsilon$ and
+	$(b_2 + \bar{b}_2) SC^{MKV,b_2} \geq constant > 0$ (see equations (48)-(50).) Thus we conclude that $PoA \to 1$ when $b_2 \to \infty$.
+
+	In the case when $c_u \neq c_w$, we show that there exists $b_2^{*,case2}>0$ such that we can bound from below $(b_2 + \bar{b_2}) \Delta SC^{b_2}$ by a constant $c_{num}>0$ independent of $b_2$ (see equation (51)).
+Meanwhile, we can also bound from above the term $b_2 \cdot SC^{MKV,b_2}$ (see equation (52)-(58) and Lemma 1) by:
+	$$ b_2 \cdot SC^{MKV,b_2} = J_1 + J_2 \leq M_{J_1} + M_{J_2}.$$
+	Hence, the price of anarchy can be bounded from below by a constant strictly greater than $1$ and independent of $b_2$ in the asymptotic regime $b_2 \to \infty$.
+
+	\item We added two sentences at the beginning of section 2.4 on page 32 stating that we compute equations (25) and (26) using a simple rectangular integration rule to numerically compute integrals.
 \end{enumerate}
@@
 	\item We have used the pronoun `their' throughout the text, so we will continue to use it here.
-	\item The missing parenthesis have been added.
-	\item We agree. Now page 6 line 10 reads `According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is...'
+	\item The missing parenthesis has been added.
+	\item We agree. Now page 6 line 15 reads `According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is...'
 	\item Yes, this was a typo.
-On page 6 line 13, we have replaced $x$ by $X_t$.
-At this point, the fixed point is not addressed, and the control is the best response when the mean field is fixed.
-So we should not yet replace $\bar{\mu}$ and $\bar{\nu}$.
-	\item On page 6 line -6, we have added: `Note $c^{MFG}(t)=a^{MFG}(t)+b^{MFG}(t)$.' We also added `Note $c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$.' on page 8 line -12.
+Since equation (2) is before addressing the fixed point and not yet in the feedback form $\hat{\alpha}_t=\phi(t,X_t)$, we only write $\hat{\alpha}_t=\frac{\bar{r}(t)\bar{s}(t)\bar{\nu}-b_2(t)Y_t}{r(t)+\bar{r}(t)}$ to avoid confusion.
+	\item On page 6 line -4, we have added: `Note that $c^{MFG}(t)=a^{MFG}(t)+b^{MFG}(t)$.' We also added `$c^{MKV}(t)=a^{MKV}(t)+b^{MKV}(t)$' on page 8 line -8.
 	\item The extra parenthesis has been removed.
-	\item We have added equation (6) and refer to it in the proof of Corollary 2, page 13 line 2. And yes, it should have been $\bar{x}_t^{MFG}$.
+	\item We moved Corollary 2 (which was previously a consequence of Proposition 2) to after Corollary 1 (since it is also a consequence of Proposition 1, if we refer to $\bar{x}_t^{MKV}$ instead of $\bar{x}_t^{MFG}$).
+We have added equation (16) and refer to it in the proof of Corollary 2 on page 11, and we include the superscript of $\bar{x}_t^{MKV}$ which was previously missing.
 	\item We changed `tends' to `tend'.
-	\item In the proof of Proposition 3, page 15 line -6, we replaced the limit of $v^r_t$ with our new notation $v^{r \to \infty}_t$.
-	\item Yes, this was a typo. These values were indeed after taking the limit. The limits in a slightly different presentation now appear in the proof of Proposition 5 Case 2, page 19 line 12.
+	\item In the proof of Proposition 3, page 16 line -6, we replaced the limit of $v^r_t$ with our new notation $v^{r \to \infty}_t$.
+	\item Yes, this was a typo. These values were indeed after taking the limit. The limits in a slightly different presentation now appear in the proof of Proposition 5 Case 2, page 24 line -8.
 \end{enumerate}
@@
 
-Finally, we would like to acknowledge that the length of our paper has increased from 26 pages at submission to 33 pages for the final version.
+Finally, we would like to acknowledge that the length of our paper has increased from 26 pages at submission to 38 pages for the final version.
 The issues in our proofs raised by the reviewer required us to write many more details, and in some cases, new approaches altogether.
 We feel that the increase in length was necessary to address all of the issues pointed out by the reviewer.
-(ToDo: Is this comment necessary?)
 

### 2018-08-06 PoA.tex
editing respone to referee

@@
 \item $\phi$ is a feedback function providing a mean field game equilibrium.
-We detail more precisely what is meant by $\phi$ providing a mean field game equilibrium in Section \ref{sub:MFG_formulation}.
+We detail more precisely what is meant by $\phi$ providing a mean field game equilibrium in section \ref{sub:MFG_formulation}.
 \item $\phi$ is the feedback function minimizing the social cost $SC(\phi)$, without having to be a mean field game equilibrium, in which case we use the notation $SC^{MKV}$ for $SC(\phi)$.
-This is a control problem of McKean-Vlasov type, which is detailed more precisely in Section \ref{sub:MKV_formulation}.
+This is a control problem of McKean-Vlasov type, which is detailed more precisely in section \ref{sub:MKV_formulation}.
 \end{itemize}
-The two problems are detailed more precisely in Sections \ref{sub:MFG_formulation} and \ref{sub:MKV_formulation}.
-In Section \ref{Price_Of_Anarchy}, we define the price of anarchy based on these two problem formulations.
-The class of linear quadratic models is explored in Section \ref{sec:PoA_LQ}, where we provide some theoretical results on the price of anarchy for this class of games.
+The two problems are detailed more precisely in sections \ref{sub:MFG_formulation} and \ref{sub:MKV_formulation}.
+In section \ref{Price_Of_Anarchy}, we define the price of anarchy based on these two problem formulations.
+The class of linear quadratic models is explored in section \ref{sec:PoA_LQ}, where we provide some theoretical results on the price of anarchy for this class of games.
 This includes our main result, Theorem \ref{thm:PoA_equivalent_1}, which provides a sufficient and necessary condition to have no price of anarchy.
-In Section \ref{sec:PoA_LQ}, we also prove some limiting cases and show numerical results.
-We conclude in Section \ref{sec:conclusion}.
+In section \ref{sec:PoA_LQ}, we also prove some limiting cases and show numerical results.
+We conclude in section \ref{sec:conclusion}.
 
@@
 To begin, we need to describe in more detail the two problems that will be used to compute the price of anarchy: the linear quadratic extended mean field game, and the linear quadratic control problem of McKean-Vlasov type with dependence on the law of the control.
-To specify the problems, we only need to specify the drift and cost functions, $b$, $f$, and $g$ introduced in Section \ref{se:introduction}.
+To specify the problems, we only need to specify the drift and cost functions, $b$, $f$, and $g$ introduced in section \ref{se:introduction}.
 For the linear quadratic models, we take the drift to be linear:
@@
 \end{equation*}
-Then we can compute the social cost as described in Section \ref{sub:MFG_formulation}:
+Then we can compute the social cost as described in section \ref{sub:MFG_formulation}:
 \begin{IEEEeqnarray}{rCl}
@@
 \end{equation*}
-Then we can compute the social cost, denoted $SC^{MKV}$, as described in Section \ref{sub:MKV_formulation}:
+Then we can compute the social cost, denoted $SC^{MKV}$, as described in section \ref{sub:MKV_formulation}:
 \begin{IEEEeqnarray}{rCl}
@@
 Uniqueness comes from the connection between LQEMFG or LQEMKV and deterministic LQ optimal control.
-(See Section 3.5.1 in \cite{Carmona_book}).
+(See section 3.5.1 in \cite{Carmona_book}).
 \end{remark}
@@
 Although Proposition \ref{prop: lq_subtract_FBSDEs} is a simple result, we will see shortly in Corollary \ref{corollary_3} that in the case when $\lambda=1$, the sufficient condition given by equations (\ref{eq:prop_1_1})-(\ref{eq:prop_1_3}) is also a necessary condition to have $PoA=1$.
-We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of MFG equilibria in the case of a separated Hamiltonian.
+We can see that in the standard mean field game setting, Proposition \ref{prop: lq_subtract_FBSDEs} is similar to Theorem 3.4 in \cite{pierre_poa} which characterizes the global efficiency of mean field game equilibria in the case of a separated Hamiltonian.
 See also Remark 6.1 in \cite{nourian2013nash}, where it is noted that the mean field game and control of McKean-Vlasov type problems are the same for a particular model of flocking.
@@
 	We can see directly from Proposition \ref{prop:diff_SC} that the social cost in the LQEMFG problem is larger than (or possibly equal to) the social cost in the LQEMKV problem.
-This result is consistent with the definition of the price of anarchy in Section \ref{Price_Of_Anarchy}.
+This result is consistent with the definition of the price of anarchy in section \ref{Price_Of_Anarchy}.
 \end{remark}
@@
 \end{equation}
-For the LQEMFG model considered in Section \ref{sec:EMFG}, the FBSDE system in equation (\ref{eq:FBSDE_EMFG}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
+For the LQEMFG model considered in section \ref{sec:EMFG}, the FBSDE system in equation (\ref{eq:FBSDE_EMFG}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
 \begin{equation*}
@@
 \end{equation*}
-For the LQEMKV model considered in Section \ref{sec:EMKV}, the FBSDE system in equation (\ref{eq:FBSDE_EMKV}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
+For the LQEMKV model considered in section \ref{sec:EMKV}, the FBSDE system in equation (\ref{eq:FBSDE_EMKV}) is of the form of equation (\ref{eq:FBSDE_general}) if we set:
 \begin{equation*}

### 2018-08-06 PoA_response_to_referee.tex
finished!!!! :D :D :D

@@
 We have added equations (5)-(9) on page 7, and equations (13)-(17) on page 9, and we refer to these equations often.
-In the same vein we have added equations (41)-(44) on page 15, which are used frequently in Propositions 3-7.
+In the same vein, we have added equations (41)-(44) and repeated equation (19) on page 15.
+These equations restate previous equations in the new notation introduced on page 13, and are a handy reference for Propositions 3-7.
 	\item There was a typo in the previous version that may have caused confusion, where we mistakenly wrote $\partial_{\mu}$ instead of $\partial_{\bar{\mu}}$.
@@
 
-	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $C^w$. This was overlooked by the authors.
+	\item Yes, it is correct that there is a square in the definitions of $C^w$ and $D^w$ that doesn't appear in the definitions of $C^u$ and $D^u$. This was overlooked by the authors.
 
@@
 
-	More precisely, in the case when $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s}) } = \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, or equivalently $c_u = c_w$, we show that for any given $\epsilon > 0$, there exists $b_2^*>0$ such that for all $b_2 \geq b_2^{*}$, we have the inequalities $(b_2 + \bar{b}_2) \Delta SC^{b_2} \leq 2\epsilon$ and
-	$(b_2 + \bar{b}_2) SC^{MKV,b_2} \geq constant > 0$ (see equations (48)-(50).) Thus we conclude that $PoA \to 1$ when $b_2 \to \infty$.
+	More precisely, in the case when $\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s}) } = \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2}$, or equivalently, $c_u = c_w=:c$, we show that for any given $\epsilon > 0$, there exists $b_2^*>0$ such that for all $b_2 \geq b_2^{*}$, we have the inequalities $(b_2 + \bar{b}_2) \Delta SC^{b_2} \leq 2\epsilon$ and
+	$(b_2 + \bar{b}_2) SC^{MKV,b_2} \geq \frac{c}{2} > 0$ (see equations (48)-(50).) Thus we conclude that $PoA \to 1$ when $b_2 \to \infty$.
 
@@
 
-\hspace{-7mm} In addition to the suggested revisions, we have also made the following minor modifications:
+\hspace{-7mm} In addition to the suggested revisions, and the changes noted above, we have also made the following modifications:
 \begin{enumerate}
-	\item 
+	\item Added the following sentence to the abstract to highlight our main result in the new Theorem 2: `A sufficient and necessary condition to have no price of anarchy is presented.'
+	\item Add page 10 line 4, to make it clear that the coefficients for the terminal cost, $q_T$, $\bar{q}_T$, and $s_T$ are also assumed to be non-negative.
+	\item Added equation (19) and moved up the observations in equation (20), which were previously below Remark 3.
+	\item We made minor edits to the statement of Proposition 1: since $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, we can rewrite $(b^{MFG}-b^{MKV})b_2+(c^{MFG}-c^{MKV})\bar{b}_2=(c^{MFG}-c^{MKV})(b_2+\bar{b}_2)$.
+Since we assume $b_2+\bar{b}_2>0$, we remove this factor from equation (23).
+We also added more to the proof of Proposition 1 to make it more clear.
+	\item We moved Remark 4 above Corollary 1.
+We also elaborated in Remark 4 about the connection to the recent paper of Cardaliaguet and Rainer [5], and we remark that we will see later (in Corollary 3 on pages 14-15) that the sufficient condition in Proposition 1 is also a necessary condition in the standard mean field game setting.
+	\item We added an extra equality in the last line of page 12 to make the computations easier to follow.
+	\item At the bottom of page 13, we added comments on the signs of $\delta^{\pm}_u$ and the non-negativity of $u_t$.
+	\item At the top of page 14, we added the time derivative of $u_t$ and comment that $u_t$ is increasing if $B(D^u)^2+2A^uD^u-C^u>0$ and likewise, decreasing if $B(D^u)^2+2A^uD^u-C^u<0$.
+	\item We added Assumption 1, as to simplify the statements of Propositions 3-7.
+	\item Propositions 3-7 have had several changes to make the arguments rigorous.
+Note that the previous Proposition 4 has now been split into the current Proposition 4, Lemma 1, and Proposition 5.
+We made some remarks above on the modifications of Propositions 3 and 4.
+Propositions 5-7 follow similar modifications to make the arguments more rigorous.
+	\item We modified the assumption in the statement of Proposition 6 in the case $\bar{b}_2 \to 0$.
+Previously, we assumed $\bar{b}_1>0$ so that $A^u \neq A^w$ and we claimed that $u_t^{\bar{b}_2 \to 0}\neq w_t^{\bar{b}_2 \to 0}$ on a set of positive Lebesgue measure.
+We realized that because of continuity, this claim would be obvious if instead, we assumed $D^{u,\bar{b}_2 \to 0}=u_T^{\bar{b}_2 \to 0}\neq w_T^{\bar{b}_2 \to 0}=D^w$, hence the assumption $\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$.
+	\item We have added Remark 6, where we point out that our new assumption in Proposition 6 was sufficient, but not necessary, to have $\lim_{\bar{b}_2 \to 0}PoA>1$.
+This follows from making a similar argument as Theorem 2 but in the limiting regime $\bar{b}_2 \to \infty$.
+	\item In Proposition 7, which was previously labeled Proposition 6, we changed the assumption from $\lambda \neq 1$ to $\lambda (q_T+\bar{q}_T(1-s_T))\neq(q_T+\bar{q}_T(1-s_T)^2)$, since what we wanted to assume is $D^u \neq D^w$.
+	\item In the numerical results, section 2.4, we removed the four plots that we did not discuss ($PoA$ as a function of $q$, $\bar{q}$, $q_T$ and $\bar{q}_T$).
+To make the limits more clear, we put two plots for each parameter: one focused on the limit towards 0 and the other focused on the limit towards infinity.
+We also reordered the figures to be in the same order as Propositions 3-7.
+We also added some discussion about which of our assumptions were satisfied.
+Note that all of the cases presented in Propositions 3-7 are confirmed by the numerical results.
+	\item We removed section 2.5 on the particular example of flocking.
+We realized that the assumption (17) is not satisfied for this example because $q+\bar{q}(1-s)=0$.
+Also, we felt that the example did not add much to the paper, as it is just one trivial example where the FBSDEs for the LQEMFG and LQEMKV problems are identical.
+	\item We updated the last half of the conclusion to reflect the new results.
+
 \end{enumerate}
@@
 Finally, we would like to acknowledge that the length of our paper has increased from 26 pages at submission to 38 pages for the final version.
-The issues in our proofs raised by the reviewer required us to write many more details, and in some cases, new approaches altogether.
-We feel that the increase in length was necessary to address all of the issues pointed out by the reviewer.
+The issues in our proofs raised by the reviewer required us to write many more details.
+We feel that the increase in length was necessary to make the results rigorous.
 

### 2018-08-06 PoA.tex
finished!!!! :D :D :D

@@
 \end{equation*}
-Thus, the cost of the solution to the optimal control problem of McKean-Vlasov is given by
+Thus, the cost of the solution to the optimal control problem of McKean-Vlasov is given by:
 \begin{equation*}
@@
 		B^r \longrightarrow 0,\quad \ B^{\eta,r} \longrightarrow 0,\\
-		C^{u,r} \longrightarrow C_u^{r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D_u^{r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
+		C^{u,r} \longrightarrow C^{u,r\to \infty} := \lambda^{r \to \infty}(q + \bar{q}(1-s)),\quad \ D^{u,r} \to D^{u,r \to \infty} := \lambda^{r \to \infty}(q_T+ \bar{q}_T(1-s_T)).
 	\end{array}
@@
 	\begin{equation*}
-		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{r \to \infty}_u = 0, \qquad u_T^{r \to \infty} = D^{r \to \infty}_u.
+		\left({u}^{r \to \infty}_t\right)' - 2A^u u_t^{r \to \infty} + C^{u,r \to \infty} = 0, \qquad u_T^{r \to \infty} = D^{u,r \to \infty}.
 	\end{equation*}
@@
 	\begin{equation*}
-	u_t^{r \to \infty} = \left(D^{r \to \infty}_u - \frac{C^{r \to \infty}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{r \to \infty}_u}{2A^u}.
+	u_t^{r \to \infty} = \left(D^{u,r \to \infty} - \frac{C^{u,r \to \infty}}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{u,r \to \infty}}{2A^u}.
 	\end{equation*}
@@
 	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large $r$.
-	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u$, $D^{u,r}$, $D^{r \to \infty}_u> 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
+	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{u,r \to \infty}$, $D^{u,r}$, $D^{u,r \to \infty}> 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$.
 Let $\epsilon>0$.
-Then there exists a $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: \zeta$ for $r \geq r^*$.
+Then there exists a $r^*>0$ such that $\max\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{u,r \to \infty},D^{u,r \to \infty} \}+\epsilon=: \zeta$ for $r \geq r^*$.
 Thus, we can deduce that for $r \geq r^*$, and for every $t \in [0,T]$:
@@
 		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
-		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
-		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u > 0,
+		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{u,\bar{b}_2 \to 0} >0,\qquad 
+		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{u,\bar{b}_2 \to 0} > 0,
 	\end{array}
@@
 	\begin{equation}
-	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{\bar{b}_2 \to 0} = D^{\bar{b}_2 \to 0}_u,
+	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} -B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{u,\bar{b}_2 \to 0} = 0, \qquad u_T^{\bar{b}_2 \to 0} = D^{u,\bar{b}_2 \to 0},
 	\label{eq:riccati_limiting_u}
@@
 Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}.
-For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:\zeta_4$ for all $\bar{b}_2 \leq \bar{b}^*_2$.
+For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max\{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{u,\bar{b}_2 \to 0},D^{u,\bar{b}_2 \to 0} \}+\epsilon=:\zeta_4$ for all $\bar{b}_2 \leq \bar{b}^*_2$.
 Thus, for all $\bar{b}_2\leq \bar{b}^*_2$ and for every $t \in [0,T]$:
@@
 	\textbf{Cases 3 and 4:} First, we consider $b_1 \to 0$.
-We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
+We have $A^{u,b_1} \to A^{u,b_1\to 0}$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$.
 Clearly we have for all $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$.
@@
 
+\bibitem{basar}
+T. Başar and Q. Zhu.
+\newblock Prices of anarchy, information, and cooperation in differential games.
+\newblock In {\em Dynamic Games and Applications, 1(1):50-73, 2011}.
+
 \bibitem{bensoussan2013mean}

### 2018-09-28 PoA.tex
new plots fixing y-axis labeling
added sentence to acknowledgments
last few changes

@@
 We work over the interval $[0,T]$ limited by a finite time horizon $T \in \mathbb{R}^+$.
-We assume the drift function $b:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha,\nu)  \rightarrow \mathbb{R}$ is Lipschitz in each of it's inputs.
+We assume the drift function $b:[0,T] \times \mathbb{R} \times \cP(\mathbb{R}) \times \mathbb{A} \times \cP(\mathbb{A}) \ni (t,x,\mu,\alpha,\nu)  \rightarrow \mathbb{R}$ is Lipschitz in each of its inputs.
 For the sake of simplicity, we assume that the volatility, $\sigma$, is a positive constant.
@@
 if we use the notation $<\varphi,\rho>$ for the integral $\int \varphi(z)\rho(dz)$ of the function $\varphi$ with respect to the measure $\rho$.
-Now if we assume that in the limit $N\to\infty$ the empirical distributions $\mu^N_{t}$ converge toward a measure $\mu_t$, and thus $\nu^N_{t}=\frac1N\sum_{i=1}^N\delta_{\phi(t,X^i_t)}$ also converges toward a measure $\nu_t$, then the social cost of the feedback function $\phi$ becomes:
+Now if we assume that in the limit $N\to\infty$ the empirical distributions $\mu^N_{t}$ converge toward a measure $\mu_t$, and thus $\nu^N_{t}=\frac1N\sum_{i=1}^N\delta_{\phi(t,X^i_t)}$ also converges toward a measure $\nu_t$, where
+$\nu_t=\mu_t \circ \phi(t,\cdot)^{-1}$, then the social cost of the feedback function $\phi$ becomes:
 \begin{equation*}
@@
 In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems.
-First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$.
+First, consider the quantity $\Lambda :=\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$.
 Using equation (\ref{eq:eta_bar_MFG}), we have:
 \begin{align*}
-&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
-&= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \right],
+&\Lambda= - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \right],
 \end{align*}
@@
 \begin{align*}
- =  -\frac{ 1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[  & \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2 -\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2 -2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t \cdot \dot{\bar{x}}^{MFG}_t dt \\
+ \Lambda=  -\frac{ 1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[  & \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2 -\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2 -2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t \cdot \dot{\bar{x}}^{MFG}_t dt \\
 & + \int_0^T \left[(2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg],
@@
 \begin{align*}
-= 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ & \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
+\Lambda= 2 \Lambda  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ & \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
 &+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
@@
 \begin{align*}
-\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 + \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt}{c^{MFG}(b_2 + \bar{b}_2)}.
+\Lambda= \frac{ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 + \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt}{c^{MFG}(b_2 + \bar{b}_2)}.
 \end{align*}
@@
     \begin{IEEEeqnarray}{lLLLClClCl}
-		\dot{u}_t &- 2A^u u_t &- B u_t^2 &+ C^u &= & 0, &\qquad& u_T &=& D^u,
+		\dot{u}_t &- 2A^u u_t &- B^u u_t^2 &+ C^u &= & 0, &\qquad& u_T &=& D^u,
 		\label{eq:riccati_ut} \\
-	    \dot{w}_t &- 2A^w w_t &- B w_t^2 &+ C^w &=&0, &\qquad &w_T &= & D^w,
+	    \dot{w}_t &- 2A^w w_t &- B^w w_t^2 &+ C^w &=&0, &\qquad &w_T &= & D^w,
 		\label{eq:riccati_wt}\\
@@
     \begin{subfigure}{.45\textwidth}
-        \includegraphics[scale=0.5]{PoA_final_b2_large.eps}
+        \includegraphics[scale=0.5]{new_PoA_final_b2_large.eps}
     \end{subfigure}
@@
 	\begin{subfigure}{.45\textwidth}
-		\includegraphics[scale=0.5]{PoA_final_b1_large.eps}
+		\includegraphics[scale=0.5]{new_PoA_final_b1_large.eps}
 	\end{subfigure}
@@
 The authors would like to thank the organizers of CEMRACS 2017 for putting together such a successful summer school.
+We would also like to thank the referees of the CEMRACS 2017 proceedings for their feedback.
 

### 2018-09-28 PoA.tex
new templete

@@
-\documentclass[11pt]{article}
+\documentclass[proc]{edpsmath}
 \usepackage{fullpage}
@@
 
+\begin{document}
+
 \title{Price of Anarchy for Mean Field Games}
-\author{
-Ren\'{e} Carmona\thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1716673 and ARO \#W911NF-17-1-0578} 
-\and 
-Christy V. Graves\thanks{Program in Applied and Computational Mathematics, Princeton University, Partially supported by NSF \#DMS-1515753 and NSF GRFP}
-\and
-Zongjun Tan \thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1515753} 
-}
-
-\begin{document}
-
-\maketitle
+
+\author{Ren\'{e} Carmona} \address{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1716673 and ARO \#W911NF-17-1-0578}
+
+\author{Christy V. Graves} \address{Program in Applied and Computational Mathematics, Princeton University, Partially supported by NSF \#DMS-1515753 and NSF GRFP}
+
+\author{ Zongjun Tan} \address{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1515753}
 
@@
 \end{abstract}
+
+\maketitle
 

### 2018-09-28 PoA.tex
fix one overflow, unsplit one equation

@@
 \end{equation*}
-According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is $\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,Y_t)=0$.
+According to the Pontryagin stochastic maximum principle, a sufficient condition for optimality is:
+$$\partial_{\alpha}H(t,X_t,\bar{\mu}_t,\hat{\alpha}_t,\bar{\nu}_t,Y_t)=0.$$
 Thus, we find the optimal control:
@@
 \begin{align*}
-\Lambda= 2 \Lambda  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ & \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
-&+ \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
+\Lambda= 2 \Lambda  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 + \int_0^T  \left[-\bar{b}_1 \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))\right] (\bar{x}^{MFG}_t)^2 dt \Bigg].
 \end{align*}
